### 2018-12-12 texs/abstract_base.tex
add sample abstract

\documentclass[senior,final,11pt]{iscs-thesis}
%論文の種類とフォントサイズをオプションに
%\usepackage{graphicx}% 必要に応じて
%\usepackage{mysettings}% 自分用設定
%-------------------
\etitle{Decompiler for Machine Code using Neural Networks}
\jtitle{ニューラルネットを用いた機械語のための逆コンパイラ}
__NAMES__
\date{December 11, 2018}
%-------------------

\begin{document}
\begin{eabstract}
A decompiler is a tool which aims to recover source code from compiled binary data.
There are various decompilers, but they often output source code that is not quite intelligible to humans. 
Therefore, we tried to apply machine translantion techniques to generate human intelligible decompiled source code. 
In this paper, we used Recurrent Neural Networks with Attention, which is useful for machine translation. 
We made training and test data by collecting source code from open source projects and compiled them to generate source code and binary pairs. 
Then we trained neural networks by using the pairs, and evaluated the effectiveness of the method.
\end{eabstract}
\begin{jabstract}
逆コンパイラはコンパイル後のバイナリデータからソースコードを復元するためのツールである。
既存の逆コンパイラはしばしば分かりにくいソースコードを出力する。
そこで、我々は統計的機械翻訳の技術を逆コンパイラに用いて、解析者にとってわかりやすいソースコードを出力するような逆コンパイラを提案する。
この論文では、機械翻訳において有用とされる Attention 付き Reccurent Neural Netowk を用いる。
我々はまず、オープンソースプロジェクトからソースコードを収集し、コンパイラを用いて学習用のソースコードとバイナリデータの組を生成した。
そして、そのデータを用いてネットワークのトレーニングを行い、手法の性能を検証した。
\end{jabstract}

\maketitle

\end{document}

### 2018-12-12 texs/make_abst.sh

@@ -1,0 +1,3 @@
+cp ../../tex-srcs/iscs-thesis.cls ./
+sed '/__NAMES__/r ../../names.txt' abstract_base.tex | sed 's/__NAMES__//g' > abstract.tex
+platex abstract.tex && dvipdfm abstract.dvi

### 2018-12-18 texs/abstract_base.tex
not to delete with build miss

@@
 %-------------------
-\etitle{Decompiler for Machine Code using Neural Networks}
+\etitle{Neural Network based Decompiler for Machine Coding}
 \jtitle{ニューラルネットを用いた機械語のための逆コンパイラ}
@@
 \begin{eabstract}
-A decompiler is a tool which aims to recover source code from compiled binary data.
-There are various decompilers, but they often output source code that is not quite intelligible to humans. 
-Therefore, we tried to apply machine translantion techniques to generate human intelligible decompiled source code. 
-In this paper, we used Recurrent Neural Networks with Attention, which is useful for machine translation. 
-We made training and test data by collecting source code from open source projects and compiled them to generate source code and binary pairs. 
-Then we trained neural networks by using the pairs, and evaluated the effectiveness of the method.
+A decompiler is a tool for recovering a source code from compiled binary data.
+There are various decompilers, but they often output a source code that is not intelligible to humans. 
+In this thesis, we tried to apply machine translation techniques to generate human intelligible decompiled source codes. 
+More specifically, we propose to use recurrent neural networks with attention, which are useful for machine translation. 
+In experiments, we use source codes collected from open source projects and their binary data for training and evaluating the neural networks.
 \end{eabstract}
@@
 逆コンパイラはコンパイル後のバイナリデータからソースコードを復元するためのツールである。
-既存の逆コンパイラはしばしば分かりにくいソースコードを出力する。
-そこで、我々は統計的機械翻訳の技術を逆コンパイラに用いて、解析者にとってわかりやすいソースコードを出力するような逆コンパイラを提案する。
-この論文では、機械翻訳において有用とされる Attention 付き Reccurent Neural Netowk を用いる。
-我々はまず、オープンソースプロジェクトからソースコードを収集し、コンパイラを用いて学習用のソースコードとバイナリデータの組を生成した。
-そして、そのデータを用いてネットワークのトレーニングを行い、手法の性能を検証した。
+様々な逆コンパイラが存在するが、既存の逆コンパイラはしばしば人間にとって分かりにくいソースコードを出力する。
+そこで本論文では、統計的機械翻訳の技術を逆コンパイラに用いた、解析者にとってわかりやすいソースコードを出力する逆コンパイラを提案する。
+具体的には、機械翻訳において有用とされる注意機構付き再帰型ニューラルネットワークを用いる。
+実験では、オープンソースプロジェクトから収集したソースコードとそのバイナリデータを用いてニューラルネットワークを学習し、その性能を検証した。
 \end{jabstract}

### 2018-12-18 build.py

@@ -2,33 +2,45 @@
 
 import os
 
-os.chdir('build')
 #os.system('pwd')
-os.system('rm *')
-os.system('cp ../../xv6-public/* ./')
+#os.system('rm *')
 
 import subprocess
-fns = str(subprocess.check_output(['ls'])).split('\\n')
-fns = filter(lambda x: x[-2:]=='.c',fns)
-tfns = []
-for fn in fns:
-	fn = fn[:-2]
-	d = subprocess.call('gcc -E %s.c | grep -v "#" | grep -v "^[[:space:]]*$" > %s.pp.c 2> /dev/null' % (fn,fn),shell=True)
+
+import code
+import binascii
+
+
+def convert(path):
+	bfn = subprocess.check_output(['sha1sum',path]).decode().split(' ')[0]
+	bfn = bfn + '_' + binascii.hexlify(path.encode()).decode()
+	if bfn in os.listdir('./build'):
+		return bfn
+	fn = './build/' + bfn
+	subprocess.call('touch %s' % bfn,shell=True)
+
+	d = subprocess.call('gcc -E %s > /dev/null 2> /dev/null' % path,shell=True) 
+	
+	if d == 0:
+		d = subprocess.call('gcc -E %s | grep -v "#" | grep -v "^[[:space:]]*$" > %s.pp.c 2> /dev/null' % (path,fn),shell=True)
 	
 	if d == 0:
 		d = subprocess.call('clang -Xclang -dump-tokens -fsyntax-only %s.pp.c > /dev/null 2> %s.tokenized' % (fn,fn),shell=True)
 	
-	with open('%s.tokenized' % fn,"r") as fp:
-		s = fp.read()
+		with open('%s.tokenized' % fn,"r") as fp:
+			s = fp.read()
+		
+		if '__asm__' in s: #避けたい...
+			d = -1
+		
+		ts = ""
+		for cs in s.split('\n'):
+			#print(cs)
+			cs = "'".join(cs.split("'")[1:-1])
+			ts += cs + '\n'
 	
-	ts = ""
-	for cs in s.split('\n'):
-		#print(cs)
-		cs = "'".join(cs.split("'")[1:-1])
-		ts += cs + '\n'
-	
-	with open('%s.tokenized.c' % fn,"w") as fp:
-		fp.write(ts)
+		with open('%s.tokenized.c' % fn,"w") as fp:
+			fp.write(ts)
 	
 	if d == 0:
[…]

### 2018-12-18 gen_data.py

@@ -1,10 +1,8 @@
-#!/usr/bin/python3
+#! /usr/bin/env /home/satos/sotsuron/neural_decompiler/python_fix_seed.sh
 
-	
 from pycparser import c_parser, c_ast, parse_file
 	
-srcs = ['bio', 'bootmain', 'cat', 'console', 'echo', 'exec', 'file', 'forktest', 'fs', 'grep', 'ide', 'init', 'ioapic', 'kalloc', 'kbd', 'kill', 'lapic', 'ln', 'ls', 'main', 'memide', 'mkdir', 'mkfs', 'mp', 'picirq', 'pipe', 'printf', 'rm', 'sh', 'sleeplock', 'stressfs', 'string', 'syscall', 'sysfile', 'sysproc', 'uart', 'ulib', 'umalloc', 'wc', 'zombie']
-
+srcs = ['abspath', 'advice', 'alias', 'alloc', 'archive-tar', 'archive-zip', 'archive', 'argv-array', 'base85', 'bisect', 'blame', 'blob', 'branch', 'bulk-checkin', 'cache-tree', 'chdir-notify', 'check-racy', 'checkout', 'column', 'combine-diff', 'commit-graph', 'commit-reach', 'commit', 'common-main', 'connect', 'connected', 'convert', 'copy', 'credential-cache--daemon', 'credential-cache', 'credential-store', 'credential', 'csum-file', 'ctype', 'daemon', 'date', 'decorate', 'delta-islands', 'diff-delta', 'diff-lib', 'diff-no-index', 'diff', 'diffcore-break', 'diffcore-delta', 'diffcore-pickaxe', 'diffcore-rename', 'dir-iterator', 'editor', 'entry', 'environment', 'fast-import', 'fetch-negotiator', 'fetch-object', 'fetch-pack', 'fsck', 'fsmonitor', 'fuzz-pack-headers', 'fuzz-pack-idx', 'gpg-interface', 'graph', 'grep', 'hashmap', 'help', 'hex', 'http-backend', 'http-fetch', 'http-push', 'http-walker', 'http', 'ident', 'imap-send', 'interdiff', 'json-writer', 'kwset', 'levenshtein', 'line-log', 'line-range', 'linear-assignment', 'list-objects-filter-options', 'list-objects-filter', 'list-objects', 'll-merge', 'lockfile', 'ls-refs', 'mailinfo', 'match-trees', 'mem-pool', 'merge-blobs', 'merge
[…]

### 2018-12-18 python_fix_seed.sh

@@ -1,0 +1,1 @@
+env PYTHONHASHSEED=3 python3 $1

### 2018-12-18 train.py

@@ -1,127 +1,206 @@
+#! /usr/bin/python3
+#coding: utf-8
 
+import numpy as np
 import chainer
 import chainer.links as L
+import chainer.functions as F
 from chainer import training
 from chainer.training import extensions
 
 def sequence_embed(embed, xs):
-    x_len = [len(x) for x in xs]
-    x_section = numpy.cumsum(x_len[:-1])
-    ex = embed(F.concat(xs, axis=0))
-    exs = F.split_axis(ex, x_section, 0)
-    return exs
+	x_len = [len(x) for x in xs]
+	x_section = np.cumsum(x_len[:-1])
+	ex = embed(F.concat(xs, axis=0))
+	exs = F.split_axis(ex, x_section, 0)
+	return exs
 
 class Seq2seq(chainer.Chain):
-    def __init__(self, n_layers, n_source_vocab, n_target_vocab, n_units):
-        super(Seq2seq, self).__init__()
-        with self.init_scope():
-            self.embed_x = L.EmbedID(n_source_vocab, n_units)
-            self.embed_y = L.EmbedID(n_target_vocab, n_units)
-            self.encoder = L.NStepLSTM(n_layers, n_units, n_units, 0.1)
-            self.decoder = L.NStepLSTM(n_layers, n_units, n_units, 0.1)
-            self.W = L.Linear(n_units, n_target_vocab)
+	def __init__(self, n_layers, n_source_vocab, n_target_vocab, n_units,v_eos):
+		super(Seq2seq, self).__init__()
+		with self.init_scope():
+			self.embed_x = L.EmbedID(n_source_vocab, n_units)
+			self.embed_y = L.EmbedID(n_target_vocab, n_units)
+			self.encoder = L.NStepLSTM(n_layers, n_units, n_units, 0.1)
+			self.decoder = L.NStepLSTM(n_layers, n_units, n_units, 0.1)
+			self.W = L.Linear(n_units, n_target_vocab)
 
-        self.n_layers = n_layers
-        self.n_units = n_units
+		self.n_layers = n_layers
+		self.n_units = n_units
+		self.v_eos = v_eos
 
-    def forward(self, xs, ys):
-        print(xs,ys)
-        xs = [x[::-1] for x in xs]
+	def forward(self, xs, ys):
+		#print(xs,ys)
+		#exit()
+		xs = [x[::-1] for x in xs]
+		
+		eos = self.xp.array([self.v_eos], np.int32)
+		ys_in = [F.concat([eos, y], axis=0) for y in ys]
[…]

### 2019-01-11 texs/decompiler.tex
start writing tex, implemented global attention, use disassemble result.

A compiler is a program which translates source code written in language X into other language Y. 
Usually, X is high-level language and Y is relatively low-level language. 
For example, clang compiler translates C language into x64 assembly language, javac compiler translates Java to Java virtual machine code.

A decompiler is a program which aims to reverse the process of a compiler, retrive a source code of the high-level language X from the source code of the low-level language Y. 
This reversing process is usually insufficient or impossible.
This is because many informaitions, such as variaible name or function name, are lost when compiling.
Additionaly, the program structure descripted in the high level language are lost too. 
For example, a simple {\sl for} loop can be represented by the combination of a {\sl while} loop and an {\sl if} statement, or the combination of {\sl if} and {\sl goto} statement, which is more primitive. 
So a decompiler can't distinguish their representation difference, despite in the real situation {\sl for} loop are often used and {\sl goto} statement are rarely.

Existing deterministic decompilers are made up with many steps similer to compilers. 
They find patterns in binary data, convert them to more high-level structure, and chain them so that they finally generate high-level psudecode.
Their output psudecodes are sometimes wrong or hard to understand.

% https://github.com/torvalds/linux/blob/70c25259537c073584eb906865307687275b527f/lib/rbtree.c#L528
Figure 1 shows the example decompilation result of the Hopper disassembler and the snowman decompiler and a hand decompilation for a C language code.
The output of Hopper decompiler seems not so bad, but some essential statements are missing and there are some verbose variables.
The output of snowman decompiler also seems broken. 
The snowman decompiler finds some variablels are pointer of a structure, but fails to detect the range of the function, and generates many unneccesary casts.
Idealy, the decompiler can find correct function ranges and structure of statements as a hand decompilation result, but the decompilers failed.

In this paper, we try to apply statistical approach, specifically SMT (statical machine translation) technique, for decompilation.
The decompilation problem is folmulated as follows. 
Given sx as a source code of domain language X, compiler generates sy as a source code of target language with probability p(sy|sx). 
We assume the prior distribution p(sx) as the human-generated souce code. 
With that assumption, the provability of decompilation p(sx|sy) is in proportion to p(sy|sx)p(sx) according to the bayesian low. 
The sy_decomp = argmax(sx) p(sx|sy) is considered as the best human-intelligible decompilation result for the low-level code sy,  
so we try to generate argmax(sx) p(sy|sx)p(sx) for decompilation result.
And if the compiler is deterministic, there wolud be a function f which represents the compiler and p(f(sx)|sx) = 1,
then sy_decomp = argmax sx, f(sx) = sy, p(sx).

The distribution p(sx) is approximated by collecting source code from open source projects.
So if we had enough high-level source code data, we could choose most popular high-level source code which generats given low-level code for the decompile result.
But high-level source code data can't be comprehensive, so we have to model the structure of compilation process somehow.
We modeled the structure by the LSTM, which is commonly used in resent SMT techniques.

### 2019-01-11 texs/paper_base.tex
start writing tex, implemented global attention, use disassemble result.

\documentclass[senior,final,11pt]{iscs-thesis}
%論文の種類とフォントサイズをオプションに
%\usepackage{graphicx}% 必要に応じて
%\usepackage{mysettings}% 自分用設定
%-------------------
\etitle{Neural Network based Decompiler for Machine Coding}
\jtitle{ニューラルネットを用いた機械語のための逆コンパイラ}

\eauthor{Sota Sato}
\jauthor{佐藤聡太}
\esupervisor{Masashi Sugiyama}
\jsupervisor{杉山将}
\supervisortitle{Professor} % Professor, etc.

\date{December 11, 2018}
%-------------------

\newcommand{\argmax}{\mathop{\rm arg\,max}\limits}
\newcommand{\argmin}{\mathop{\rm arg\,smin}\limits}

\usepackage{listings}

\lstdefinestyle{myCustomMatlabStyle}{
  language=C,
  numbers=none,
  stepnumber=1,
  numbersep=10pt,
  tabsize=2,
  showspaces=false,
  showstringspaces=false
}

\lstset{%
  basicstyle={\tiny},%
  commentstyle={\tiny\itshape},%
  keywordstyle={\tiny\bfseries},%
  % style={myCustomMatlabStyle},
  stringstyle={\tiny\ttfamily},
  frame={tb},
  breaklines=true,
  columns=[l]{fullflexible},%
  numbers=left,%
  xrightmargin=0zw,%
  xleftmargin=3zw,%
  numberstyle={\scriptsize},%
  stepnumber=1,
  numbersep=1zw,%
  lineskip=-0.5ex%
}

\begin{document}
\begin{eabstract}
A decompiler is a tool for recovering a source code from compiled binary data.
There are various decompilers, but they often output a source code that is not intelligible to humans. 
In this thesis, we tried to apply machine translation techniques to generate human intelligible decompiled source codes. 
More specifically, we propose to use recurrent neural networks with attention, which are useful for machine translation. 
In experiments, we use source codes collected from open source projects and their binary data for training and evaluating the neural networks.
\end{eabstract}
\begin{jabstract}
逆コンパイラはコンパイル後のバイナリデータからソースコードを復元するためのツールである。
様々な逆コンパイラが存在するが、既存の逆コンパイラはしばしば人間にとって分かりにくいソースコードを出力する。
そこで本論文では、統計的機械翻訳の技術を逆コンパイラに用いた、解析者にとってわかりやすいソースコードを出力する逆コンパイラを提案する。
具体的には、機械翻訳において有用とされる注意機構付き再帰型ニューラルネットワークを用いる。
実験では、オープンソースプロジェクトから収集したソースコードとそのバイナリデータを用いてニューラルネットワークを学習し、その性能を検証した。
\end{jabstract}

\maketitle

\chapter{Introduction}
% For dinamic analysis, malware is executed in the sandbox and the behaviour is examined with the changes ocuuring in the sandbox. 
% Usually, there are two malware analysis approach, the dinamic analysis and the static analysis.
% In the static analysys, the behaviour of the malware is analysed by

These days, the amount of malware has been increasing rapidly.
So the development of malware analysis tools, such as decompilers, has been becoming important.
A decompiler is a tool for analysing the behavior of malwares. 
This tool generates C-like pseudocode which represents the behaviour of the malware, and analyst can infer the behavior of the malware with the pseudocode.
This is much easier compare to analysing raw binary.

But sometimes the decompiler generate  unstructured code, which calls for some effort to understand the behavior of the program. 
This is due to the flexibility of the high level language. If the decompiler chooses a human-friendly representation of the language as the result of decompiling, we can analyze malware with less effort.

In this paper, we apply a statistical machine translation tequnique for a decompiler to generate human-friendly pseudocode. 
This idea was already mentioned by Katz et al. [1], in which they use end-to-end machine translation with Recurrent Neural Networks.

\section{Decompiler}

% 573 words.

A compiler is a program which translates source code written in language X into other language Y. 
Usually, X is high-level language and Y is relatively low-level language. 
For example, clang compiler translates C language into x64 assembly language, javac compiler translates Java to Java virtual machine code.

A decompiler is a program which aims to reverse the process of a compiler, retrive a source code of the high-level language X from the source code of the low-level language Y. 
This reversing process is usually insufficient or impossible.
This is because many informaitions, such as variaible name or function name, are lost when compiling.
Additionaly, the program structure descripted in the high level language are lost too. 
For example, a simple {\sl for statement} can be represented by the combination of a {\sl while statement} and an {\sl if statement}, or the combination of {\sl if statement} and {\sl goto statement}. 
So a decompiler can't distinguish their representation difference, despite in the real situation {\sl for statement} are often used and {\sl goto statement} are rarely.

Existing deterministic decompilers are made up with many steps similer to compilers. 
They find patterns in binary data, convert them to more high-level structure, and chain them so that they finally generate high-level psudecode.
Their output psudecodes are sometimes wrong or hard to understand.

% https://github.com/torvalds/linux/blob/70c25259537c073584eb906865307687275b527f/lib/rbtree.c#L528

\begin{figure}
	\begin{tabular}{cc}
		\begin{minipage}[t]{0.5\hsize}
			\lstinputlisting[]{rb_tree.c}
		\end{minipage}
		\begin{minipage}[t]{0.5\hsize}
			\lstinputlisting[]{hopper.c}
		\end{minipage}
		\\
		\begin{minipage}[c]{0.5\hsize}
			\lstinputlisting[]{snowman.c}
		\end{minipage}
		\begin{minipage}[c]{0.5\hsize}
			\lstinputlisting[]{handdecomp.c}
		\end{minipage}
	\end{tabular}
	\caption{ hogehugapiyo.}
	\label{fig:cw}
\end{figure}

Figure~\ref{fig:cw} shows the example decompilation result of the Hopper disassembler and the snowman decompiler and a hand decompilation for a C language code.
The output of Hopper decompiler seems not so bad, but some essential statements are missing and there are some verbose variables.
The output of snowman decompiler also seems broken. 
The snowman decompiler finds some variablels are pointer of a structure, but fails to detect the range of the function, and generates many unneccesary casts.
Idealy, the decompiler can find correct function ranges and structure of statements as a hand decompilation result, but the decompilers failed.

In this paper, we try to apply statistical approach, specifically SMT (statical machine translation) technique, for decompilation.
The decompilation problem is folmulated as follows. 
Given $sx$ as a source code of domain language X, compiler generates $sy$ as a code of target language Y with probability $p(sy|sx)$. 
We assume the prior distribution $p(sx)$ as the human-generated souce code. 
With that assumption, the provability of decompilation $p(sx|sy)$ is in proportion to $p(sy|sx)p(sx)$ according to the bayesian low. 
The $\argmax_{sx} p(sx|sy)$ is considered as the best human-intelligible decompilation result for the low-level code $sy$,  
so we try to estimate $ \argmax_{sx} p(sy|sx)p(sx)$ for decompilation result.
And if the compiler is deterministic, there wolud be a function $f$ which represents the compiler and $p(f(sx)|sx) = 1$,
then the objective becomes to $ \argmax_{sx,f(sx)=sy} p(sx)$.

The distribution $p(sx)$ is approximated by collecting source code from open source projects.
So if we had enough high-level source code data, we could choose the most popular high-level source code which generats given low-level code for the decompile result.
But high-level source code data can't be comprehensive.
So we have to model the structure of compilation process somehow.
We modeled the structure by the LSTM, which is commonly used in resent SMT techniques.

\section{Deep learning and LSTM}

\chapter{Related works}

\chapter{Related works}

\chapter{Preliminaries}

\chapter{Imprementation and Experiment}
First, we collect data sets from online

\end{document}

### 2019-01-11 analysys.py

@@ -2,6 +2,15 @@
 
 from matplotlib import pyplot as plt
 
+
+with open('ml.txt') as fp:
+	s = fp.readlines()
+	s = list(map(lambda x: eval(x.split('_')[5]),s))
+
+plt.plot(s)
+plt.show()
+exit()
+
 import pickle
 
 ds = pickle.load(open('dist_dist.pickle','rb'))

### 2019-01-11 build.py

@@ -11,20 +11,35 @@ import code
 import binascii
 
 
+def chain_functions(fs):
+	for f,ouf,errf in fs:
+		d = subprocess.call(f,stdout=ouf,stderr=errf)
+		#print(d,f)
+		if d != 0:
+			#exit()
+			return False
+	return True
+
+devnull = open('/dev/null','w')
+with open('correspond_table.txt','r') as fp:
+	corresp_table = fp.read()
+	
 def convert(path):
+	global devnull
+	global corresp_table
+	if path in corresp_table:
+		return
 	bfn = subprocess.check_output(['sha1sum',path]).decode().split(' ')[0]
 	#bfn = binascii.hexlify(path.encode()).decode()
-	if bfn in os.listdir('./build'):
-		return
-	subprocess.call('echo "%s | %s" >> correspond_table.txt' % (path,bfn),shell=True)
-	fn = './build/' + bfn
-	subprocess.call('touch %s' % fn,shell=True)
+	fn = bfn
+	with open('../correspond_table.txt','a') as fp:
+		fp.write('%s | %s\n' % (path,bfn))
 	
 	print(path)
-	d = subprocess.call('gcc -E %s > /dev/null 2> /dev/null' % path,shell=True) 
+	d = subprocess.call('clang -E %s > /dev/null 2> /dev/null' % path,shell=True) 
 	
 	if d == 0:
-		d = subprocess.call('gcc -E %s | grep -v "#" | grep -v "^[[:space:]]*$" > %s.pp.c 2> /dev/null' % (path,fn),shell=True)
+		d = subprocess.call('clang -E %s | grep -v "#" | grep -v "^[[:space:]]*$" > %s.pp.c 2> /dev/null' % (path,fn),shell=True)
 
 	if d == 0 and int(list(filter(lambda x: x!= '',subprocess.check_output(['wc','%s.pp.c' % fn]).decode().split(' ')))[0]) > 5000:
 		# too big.
@@ -48,33 +63,48 @@ def convert(path):
 		with open('%s.tokenized.c' % fn,"w") as fp:
 			fp.write(ts)
 	
-	if d == 0:
-		d = subprocess.call('gcc -O0 -S -g -c %s.tokenized.c -o %s.s > /dev/null 2> /dev/null' % (fn,fn),shell=True)
+	#print('tokenized',path)
+	tcfn = '%s.tokenized.c' % fn
+	sfn = '%s.s' % fn
[…]

### 2019-01-11 c_cfg.py

@@ -62,66 +62,136 @@ nont_reduce = [
 	]),
 ]
 
+
+reduce_data = nont_reduce
+#def get_node_type
+
 # None is for pass.
-cfg = [
-	(CursorKind.ADDR_LABEL_EXPR,None),
-	(CursorKind.ARRAY_SUBSCRIPT_EXPR,['expr','expr']),
-	(CursorKind.ASM_LABEL_ATTR,None),	
-	(CursorKind.ASM_STMT,None),
-	(CursorKind.BINARY_OPERATOR,['expr','binary_op','expr']), 
-	(CursorKind.BREAK_STMT,[]),
-	(CursorKind.CALL_EXPR,['expr','expr_list']),
-	(CursorKind.CASE_STMT,['expr','stmt']),
-	(CursorKind.CHARACTER_LITERAL,['literal']),
-	(CursorKind.COMPOUND_ASSIGNMENT_OPERATOR,['expr','compound_assign_op','expr']),
-	(CursorKind.COMPOUND_LITERAL_EXPR,None), # TODO(satos)   (struct S){.x=1}  or (int[]){1,2,3,some_int} like.
-	(CursorKind.COMPOUND_STMT,['stmt_list']),
-	(CursorKind.CONDITIONAL_OPERATOR,['expr','expr','expr']),
-	(CursorKind.CONST_ATTR,None), #TODO(satos) pending. __const__
-	(CursorKind.CONTINUE_STMT,[]),
-	(CursorKind.CSTYLE_CAST_EXPR,['type_list','expr']), #TODO(satos) ayasii  -> # retrive type from .type.get_canonical().spelling 
-	(CursorKind.CXX_UNARY_EXPR,['unary_op','expr_option']),  # only sizeof like things.
-	(CursorKind.DECL_REF_EXPR,['var']),
-	(CursorKind.DECL_STMT,['decl_list']),
-	(CursorKind.DEFAULT_STMT,['stmt']),
-	(CursorKind.DO_STMT,['stmt','expr']),
-	(CursorKind.ENUM_CONSTANT_DECL,['expr_option']),
-	(CursorKind.ENUM_DECL,['decl_list']),
-	(CursorKind.FIELD_DECL,['var','type_list']), # [int hogehuga] in [struct{int hogehuga};]
-	(CursorKind.FLOATING_LITERAL,['literal']),
-	(CursorKind.FOR_STMT,['expr_option','expr_option','expr_option','stmt']),
[…]

### 2019-01-11 clang_ast_dump.py

@@ -1,0 +1,55 @@
+class HelpAST:
+	def __init__(sl,tag,data=None):
+		sl.tag = tag
+		sl.data = data
+		sl.cs = []
+
+def s2tree(s):
+	s = s.split('\n')
+	ls = len(s)
+	i = 0
+	def parse(d):
+		nonlocal i,s,ls
+		ds = s[i][d:].split(' ')
+		tag = ds[0]
+		data = ds[1:]
+		i += 1
+		if tag == '<<<NULL>>>':
+			return None
+		node = HelpAST(tag,data)
+		if i >= ls or len(s[i])<=d or (s[i][d]!='|' and s[i][d]!='`'):
+			return node
+		
+		cs = []
+		while True:
+			if s[i][d:d+2]=='|-':
+				cs.append(parse(d+2))
+			elif s[i][d:d+2]=='`-':
+				cs.append(parse(d+2))
+				break
+			else:
+				#return res
+				#print(s[i][d:])
+				raise ParseErr('miss at %d:%d' % (i,d))
+		
+		
+		node.cs = cs
+		return node
+	
+	return parse(0)
+
+import os
+def fn_to_clang_ast(fn):
+	os.system('clang -Xclang -ast-dump -fsyntax-only %s > %s.astdump 2>/dev/null' % (fn,fn))
+	with open(fn + '.astdump') as fp:
+		parsed = fp.read()
+	return s2tree(parsed)
+
+
+
+
+
+
+
+
+

### 2019-01-11 clang_tes.py

@@ -1,7 +1,7 @@
 #! /usr/bin/env /home/satos/sotsuron/neural_decompiler/python_fix_seed.sh
 
 from clang.cindex import Config,Index,CursorKind
-Config.set_library_path("/usr/lib/llvm-6.0/lib/")
+Config.set_library_path("/usr/lib/llvm-8/lib/")
 
 import code,os
 
@@ -25,7 +25,7 @@ def traverse(x,d,fnsrc):
 	rule = (str(x.kind),len(cs))
 	rules |= set([rule])
 	
-	if x.kind == CursorKind.UNEXPOSED_EXPR and len(cs)>=2:
+	if x.kind == CursorKind.CONST_ATTR:# and len(cs)>=2:
 		tfn,src = fnsrc
 		st,ed = x.extent.start.line,x.extent.end.line
 		nsrcs = src[st-1:ed]

### 2019-01-11 csrc2ast.py

@@ -1,0 +1,218 @@
+#! /usr/bin/env /home/satos/sotsuron/neural_decompiler/python_fix_seed.sh
+#coding: utf-8
+
+import c_cfg
+import clang_ast_dump
+import types
+
+import code
+
+from clang.cindex import Config,Index,CursorKind
+Config.set_library_path("/usr/lib/llvm-7/lib")
+
+
+
+# clang python bindings is inefficient,
+# so I need to use information from clang -ast-dump 
+
+class AST:
+	def debug(sl,x):
+		"""
+		vs = dir(x)
+		def f(a):
+			try:
+				res = x.__getattribute__(a)
+			except AssertionError:
+				res = AssertionError
+			res = (a,res)
+			return res
+		
+		ats = list(map(f,vs))
+		for kv in ats:
+			print(kv)
+		"""
+		code.interact(local={'sl':sl,'x': x,'cs':list(x.get_children())})
+		exit()
+	
+	def checkalign(sl,vs):
+		h = sl.top
+		res = []
+		for d in vs:
+			if d == 1:
+				res.append(sl.src[h-1])
+				h += d
+			elif type(d) is str:
+				#print(sl.src[h-1],d)
+				assert sl.src[h-1]==d
+				h += 1
+			else:
+				assert h == d.top
+				h = d.bottom + 1
+		assert h == sl.bottom + 1
+		
+		if len(res)==1:
+			res = res[0]
+		return res
+	
+	def __init__(sl,x,ast_hint=None,src=None):
+		sl.src = src
+		if type(x) is tuple:
+			sl.kind = x[0]
+			sl.children = []
+			sl.show = lambda: x[1]
+			sl.isleaf = True
+			return
+		#sl.debug(x)r
+		sl.isleaf = False
+		sl.kind = x.kind
+		sl.top = x.extent.start.line
+		sl.bottom = x.extent.end.line
+		#print(x.kind,sl.top,sl.bottom)
+		d = c_cfg.cfg[sl.kind]
+		sl.invalid = d is None
+		if sl.invalid:
+			return
+		
+		print(ast_hint)
+		cvs = list(x.get_children())
+		if sl.kind == CursorKind.TRANSLATION_UNIT:
+			#print(ast_hint.tag)
[…]

### 2019-01-11 gen_data.py

@@ -90,52 +90,113 @@ def parse_c(prsc):
 	return res
 	
 def get_line_from_list(asm,objd):
-	asm = asm.split('\n')
-	asm2 = filter(lambda x: x!='' and x[0]!='.' and x[:2] != '\t.',asm)
-	asm2 = list(asm2)
-	asm = filter(lambda x: x!='' and x[0]!='.' and (x[:2] != '\t.' or x[:5]=='\t.loc'),asm)
-	asm = list(asm)
-	
+	asm = list(map(lambda x: x.split('#')[0].strip(),asm.split('\n')))
+	asm_with_loc = list(filter(lambda x: x!='' and x[0]!='#' and x[-1]!=':' and (x[0] != '.' or x[:5]=='.loc '),asm))
+	asm_noloc = list(filter(lambda x: x!='' and x[0]!='#' and x[-1]!=':' and x[0]!='.',asm))
+
+	"""
+	while asm_with_loc[-1][-1]==':':
+		asm_with_loc = asm_with_loc[:-1]
+	while asm_noloc[-1][-1]==':':
+		asm_noloc = asm_noloc[:-1]
+	"""
+	#exit()
 	objd = objd.split('\n')[5:]
-	objd = filter(lambda x: x!='',objd)
-	objd = list(objd)
-	
+	objd = list(filter(lambda x: x!='',objd))
+	objd = list(map(lambda x: x.split('#')[0].strip(),objd))
+	objd_asm_len = len(list(filter(lambda x: x[-1]!=':',objd)))
+	"""
+	# only for clang
+	tobjd = []
+	for i,v in enumerate(objd[:-1]):
+		if objd[i+1][-1]==':':
+			continue
+		tobjd.append(v)
+	objd = tobjd + [objd[-1]]
+	"""
+	#print(objd)
 	#print(len(asm2),len(objd))
-	#print('\n'.join(asm2))
-	#print('-' * 100)
-	#print('\n'.join(objd))
 	#assert len(objd) == len(asm2)
-	if len(objd) != len(asm2):
+	#print(len(objd),len(asm_noloc))
+	"""
+	print('\n'.join(asm_with_loc))
+	print('-' * 100)
+	print('\n'.join(objd))
+	"""
+	if objd_asm_len != len(asm_noloc):
+		"""
+		print('\n'.join(asm_noloc))
+		print('-' * 100)
+		print('\n'.join(objd))
[…]

### 2019-01-11 model_rnn.py

@@ -48,8 +48,9 @@ class Seq2seq(chainer.Chain):
 		batch = len(xs)
 		# None represents a zero vector in an encoder.
 		hx, cx, _ = self.encoder(None, None, exs)
+		#print(hx.shape,cx.shape)
 		_, _, os = self.decoder(hx, cx, eys)
-
+		
 		#print(list(map(lambda x: len(x),os)))
 		
 		# It is faster to concatenate data before calculating loss

### 2019-01-11 model_rnn_with_att.py

@@ -1,0 +1,202 @@
+import numpy as np
+import chainer
+import chainer.links as L
+import chainer.functions as F
+from chainer import training
+from chainer.training import extensions
+from chainer import serializers
+
+
+	
+def sequence_embed(embed, xs):
+	x_len = [len(x) for x in xs]
+	x_section = np.cumsum(x_len[:-1])
+	ex = embed(F.concat(xs, axis=0))
+	exs = F.split_axis(ex, x_section, 0)
+	return exs
+
+
+# from https://arxiv.org/pdf/1409.0473.pdf. Global attention.
+class Attention(chainer.Chain):
+	def __init__(self, n_units):
+		super(Attention, self).__init__()
+		with self.init_scope():
+			self.att_W = L.Linear(n_units, n_units)
+			self.att_U = L.Linear(n_units*2, n_units)
+			self.att_v = L.Linear(n_units, 1)
+		
+		self.n_units = n_units
+		self.Uhxs = None
+	
+	def init_hxs(self,hxs):
+		self.hxs = hxs
+		self.Uhxs = self.att_U(hxs)
+		self.Uhxs_len = hxs.shape[0]
+	
+	def forward(self,nhx):
+		nhx_for_att = nhx[-1]
+		Wnhx = self.att_W(nhx_for_att)
+		#print(Wnhx.shape,Uhxs.shape)
+		#print((Wnhx + Uhxs).shape)
+		
+		att_rates = F.softmax(F.reshape(self.att_v(
+				F.tanh(
+					Wnhx + self.Uhxs
+				)
+		),(1,self.Uhxs_len)))
+		#print(hxs.shape,att_rates.shape)
+		#print(att_rates)
+		#print(F.matmul(att_rates,hxs).shape)
+		ctx = F.matmul(att_rates,self.hxs)[0]
+		#print(ctx.shape)
+		return ctx
+		
+	def reset(self):
+		self.hxs = None
+		self.Uhxs = None
+	
+class Seq2seq_with_Att(chainer.Chain):
+	def __init__(self, n_layers, n_source_vocab, n_target_vocab, n_units,v_eos_src,v_eos_dst,n_maxlen):
+		super(Seq2seq_with_Att, self).__init__()
+		with self.init_scope():
+			self.embed_x = L.EmbedID(n_source_vocab, n_units)
+			self.embed_y = L.EmbedID(n_target_vocab, n_units)
[…]

### 2019-01-11 texs/compile.sh

@@ -1,0 +1,3 @@
+cp ../../tex-srcs/iscs-thesis.cls ./
+sed '/__NAMES__/r ../../names.txt' paper_base.tex | sed 's/__NAMES__//g' > paper.tex
+platex paper.tex && dvipdfm paper.dvi

### 2019-01-11 tokenizer.py

@@ -1,0 +1,20 @@
+
+
+def conv(fn):
+	if d == 0:
+		d = subprocess.call('clang -Xclang -dump-tokens -fsyntax-only %s.pp.c > /dev/null 2> %s.tokenized' % (fn,fn),shell=True)
+	
+		with open('%s.tokenized' % fn,"r") as fp:
+			s = fp.read()
+		
+		if '__asm__' in s: #避けたい...
+			d = -1
+		
+		ts = ""
+		for cs in s.split('\n'):
+			#print(cs)
+			cs = "'".join(cs.split("'")[1:-1])
+			ts += cs + '\n'
+	
+		with open('%s.tokenized.c' % fn,"w") as fp:
+			fp.write(ts)

### 2019-01-11 train.py

@@ -10,6 +10,7 @@ from chainer.training import extensions
 from chainer import serializers
 
 from model_rnn import Seq2seq
+from model_rnn_with_att import Seq2seq_with_Att
 
 def convert(batch, device):
 	def to_device_batch(batch):
@@ -36,7 +37,8 @@ def main():
 	n_maxlen = 100
 	
 	with open('data.pickle','rb') as fp:
-			(data,c_vocab) = pickle.load(fp)
+	#with open('data_simple.pickle','rb') as fp:
+			(data,c_vocab,asm_vocab) = pickle.load(fp)
 	
 	#data.data = list(filter(lambda xy: len(xy[0])<20 and len(xy[1])<10,data.data))
 	data = list(filter(lambda xy: len(xy[1])<n_maxlen,data))
@@ -52,18 +54,32 @@ def main():
 	maxlen_c   = max(map(lambda xy: len(xy[1]),data)) + 1
 	print(maxlen_asm,maxlen_c)
 	
-	v_eos_src = 256 #現状asmなので
-	src_vocab_len = v_eos_src + 1
+	v_eos_src = len(asm_vocab)
+	asm_vocab += ['__EOS__']
+	src_vocab_len = len(asm_vocab)
 	
 	v_eos_dst = len(c_vocab)
 	c_vocab += ['__EOS__']
 	dst_vocab_len = len(c_vocab)
  
-	model = Seq2seq(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_src, v_eos_dst, n_maxlen)
-	serializers.load_npz('save_models/models_prestudy_edit_dist_0.65/iter_47600__edit_dist_0.691504__time_2018_12_28_01_36_30.npz',model)
+	model = Seq2seq_with_Att(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_src, v_eos_dst, n_maxlen)
+	#serializers.load_npz('models/iter_100__time_2019_01_10_02_01_29.npz',model)
+	#serializers.load_npz('save_models/models_prestudy_edit_dist_0.65/iter_47600__edit_dist_0.691504__time_2018_12_28_01_36_30.npz',model)
 
 
-
+	def normalize_sentense(s):
+		ts = []
+		names = []
+		for d in s:
+			sd = c_vocab[d]
+			if sd[:5]=='__ID_':
+				if not sd in names:
+					names.append(sd)
[…]

### 2019-01-13 texs/paper.tex
continue writing paper

--- 2019-01-11 texs/paper_base.tex
@@
 \usepackage{listings}
+\usepackage{cite}
+\usepackage{url}
 
@@
 
+\section{Previous Studies}
+\subsection{Decompilation techniques}
+
+% Compiler and Optimization Level Estimation for Improving Anti-malware Technologies
+
+%
+
+\subsection{Improvement of decompilation results}
+In this paper, we don't try to recover the function name and variable name. 
+But for hand-decompilation, sometimes the name can be estimated by the functionality of the variable.
+For example, assume there is a variable X which seems to have a C struct type and has two fields P and Q.
+And there are two functions F and G which operate with X. 
+The function F recieves X and other value V, assigns V to the memory indicated by P, adds 8 to P and increments Q. 
+The function G recieves X, subs 8 from P and decrements Q, then returns the value indicated by P.
+In the situation, analyst can estimate X represents a stuck structure, and the function F is for push function, G is for pop function.
+
+\cite{name_recover_from_decompile_result} is the paper for tuckling this task.
+
+This kind of name estimation also appears in the context of deobfsucation.
+Deobfsucation is a reverse process of obfsucation.
+Obfsucation is a technique to modify the program source code so that the code becomes hard to understand for humans. 
+Obfsucation is used for hiding the behaviour of a program whose source code have to be distributed.
+For example,
+
+\subsection{Deep learning for programming task}
+
+\chapter{Problem Settings and Methots}
+
 \section{Decompiler}
@@
 
-\section{Deep learning and LSTM}
+\section{LSTM}
+To generate $ \argmax_{sx} p(sx|sy)$, we decomposit $ p(sx|sy) = p([sx_1, \dots, sx_n] |sy) $ to $ p(sx_1|sy,[]) \dots p(sx_n|sy,[sx_1,\dots,sx_{n-1}]) $,
+where $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ represents the probability that the token $ sx_k $ follows to the sequence $ [sx_1,\dots,sx_{k-1}] $ 
+when the input sequence is $ sy $. We try to estimate the probability $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ by LSTM.
+LSTM is
 
-\chapter{Related works}
+\chapter{Experiments}
 
-\chapter{Related works}
+\section{Data Collection}
+% 219 words
+First, we collected source codes by crawling \cite[GitHub]{github}, cloning about 900 repositories with C language topic, 
+and recursevily searched each folders to enumerate C language source code.
+From each source code, we generated pairs of C source code fragment and x64 assembly code corresponds to the C fragment.
+Some sample flagments are shown in figure~\ref{fig:pairsofflagments}.
 
-\chapter{Preliminaries}
+% Here the reason for fragments?
 
-\chapter{Imprementation and Experiment}
-First, we collect data sets from online
+\begin{figure}
+	\begin{tabular}{cc}
+	\end{tabular}
+	\caption{Sample data flagments}
+	\label{fig:pairsofflagments}
+\end{figure}
+
+The pairs were generated as follows. Let {\sl S0} be a original C source code.
+\begin{enumerate}
+\item Remove all preprocessor, such as {\sl \#include}, in {\sl S0} to generate preprosessed C code {\sl S1}. 
+\item Tokenize {\sl S1} and rearrange them in {\sl S2} so that there is exactly one token for each lines. 
+\item 
+Compile {\sl S2} by gcc (GNU C compiler) with no optimization (-O0) and debug option to get assembly code {\sl S3}. 
+With debug option, {\sl S3} contains informations about the source code position which each assembly operations are originated from.
+\item Assemble {\sl S3} to object file {\sl S4} and disassemble {\sl S4} to get information eliminated assembly code {\sl S5}.
+\item 
+Parse {\sl S2} with clang to get AST (abstract syntax tree) of the source code. 
+And for each subtree of AST, we can get C flagment source code which corresponds to the subtree, 
+and we can get assembly code corresponds to the C flagment by employing {\sl S5} combine with {\sl S3}.
+\end{enumerate}
+
+The C flagment and assembly code pairs are preprocessed for the training and testing data.
+
+\section{Data Preprocessing}
+In order to apply LSTM, input and output for the LSTM must be the sequence of tokens. 
+So we have to preprocess the assembly data and C flagments to the token sequences by somehow.
+
+The assemblies were preprocessed in two ways.
+First way is the raw binary integers. The assemblies are finally assembled to the sequence of the one byte integers, ranged from 0 to 255.
+So the one byte integer sequences can be directly used for input sequences.
+Second way is the tokenized sequence of assemby codes. 
+The disassemble opecodes and operands in {\sl S5} are splited to symbols, and concatnated the sequences to one sequence, then we modified followings.
+\begin{itemize}
+\item For each end of the operations, the {\sl ENDLINE} symbol is added to indicate the end of operation.
+\item 
+The relative access of code address, such as {\sl call} or {\sl jump} operations, 
+are relabeled like alpha-conversion for position independentness of the code and for reducing the vocabulary size.
+\item The big integer values are substituted. 
+In detail, the intager in the range from -255 to 256 are preverved as it is, and the other intengeres are substituted with the {\sl \_\_HEX\_\_} symbol.
+This also reduces the vocabulary size.
+\end{itemize}
+
+The C source codes were preprocessed like the second way of the assembly preprosess.
+C source code was tokenized to the sequence and preprocessed with following modifications.
+\begin{itemize}
+\item Function names and variable names were renamed like alpha-conversion.
+\item Big integer values were substituted too. 
+\item All string literals were replaced to the {\sl \_\_STRING\_\_} symbol.
+\end{itemize}
+
+\section{Model Configuration}
+The training model was implemented with Chainer 6.0.0b1.
+The
+
+\chapter{Results}
+\chapter{Discussion}
+\chapter{Conclusion}
+
+\bibliographystyle{plainnat}
+\bibliography{reference}
 

### 2019-01-13 texs/paper_base.tex
continue writing paper

@@
 
-\section{Deep learning and LSTM}
+\section{LSTM}
+To generate $ \argmax_{sx} p(sx|sy)$, we decomposit $ p(sx|sy) = p([sx_1, \dots, sx_n] |sy) $ to $ p(sx_1|sy,[]) \dots p(sx_n|sy,[sx_1,\dots,sx_{n-1}]) $,
+where $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ represents the probability that the token $ sx_k $ follows to the sequence $ [sx_1,\dots,sx_{k-1}] $ 
+when the input sequence is $ sy $. We try to estimate the probability $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ by LSTM.
+LSTM is
 
-\chapter{Related works}
+\chapter{Experiments}
 
-\chapter{Related works}
+\section{Data Collection}
+% 219 words
+First, we collected source codes by crawling \cite[GitHub]{github}, cloning about 900 repositories with C language topic, 
+and recursevily searched each folders to enumerate C language source code.
+From each source code, we generated pairs of C source code fragment and x64 assembly code corresponds to the C fragment.
+Some sample flagments are shown in figure~\ref{fig:pairsofflagments}.
 
-\chapter{Preliminaries}
+% Here the reason for fragments?
 
-\chapter{Imprementation and Experiment}
-First, we collect data sets from online
+\begin{figure}
+	\begin{tabular}{cc}
+	\end{tabular}
+	\caption{Sample data flagments}
+	\label{fig:pairsofflagments}
+\end{figure}
+
+The pairs were generated as follows. Let {\sl S0} be a original C source code.
+\begin{enumerate}
+\item Remove all preprocessor, such as {\sl \#include}, in {\sl S0} to generate preprosessed C code {\sl S1}. 
+\item Tokenize {\sl S1} and rearrange them in {\sl S2} so that there is exactly one token for each lines. 
+\item 
+Compile {\sl S2} by gcc (GNU C compiler) with no optimization (-O0) and debug option to get assembly code {\sl S3}. 
+With debug option, {\sl S3} contains informations about the source code position which each assembly operations are originated from.
+\item Assemble {\sl S3} to object file {\sl S4} and disassemble {\sl S4} to get information eliminated assembly code {\sl S5}.
+\item 
+Parse {\sl S2} with clang to get AST (abstract syntax tree) of the source code. 
+And for each subtree of AST, we can get C flagment source code which corresponds to the subtree, 
+and we can get assembly code corresponds to the C flagment by employing {\sl S5} combine with {\sl S3}.
+\end{enumerate}
+
+The C flagment and assembly code pairs are preprocessed for the training and testing data.
+
+\section{Data Preprocessing}
+
+% 244 words
+In order to apply LSTM, input and output for the LSTM must be the sequence of tokens. 
+So we have to preprocess the assembly data and C flagments to the token sequences by somehow.
+
+The assemblies were preprocessed in two ways.
+First way is the raw binary integers. The assemblies are finally assembled to the sequence of the one byte integers, ranged from 0 to 255.
+So the one byte integer sequences can be directly used for input sequences.
+Second way is the tokenized sequence of assemby codes. 
+The disassemble opecodes and operands in {\sl S5} are splited to symbols, and concatnated the sequences to one sequence, then we modified followings.
+\begin{itemize}
+\item For each end of the operations, the {\sl ENDLINE} symbol is added to indicate the end of operation.
+\item 
+The relative access of code address, such as {\sl call} or {\sl jump} operations, 
+are relabeled like alpha-conversion for position independentness of the code and for reducing the vocabulary size.
+\item The big integer values are substituted. 
+In detail, the intager in the range from -255 to 256 are preverved as it is, and the other intengeres are substituted with the {\sl \_\_HEX\_\_} symbol.
+This also reduces the vocabulary size.
+\end{itemize}
+
+The C source codes were preprocessed like the second way of the assembly preprosess.
+C source code was tokenized to the sequence and preprocessed with following modifications.
+\begin{itemize}
+\item Function names and variable names were renamed like alpha-conversion.
+\item Big integer values were substituted too. 
+\item All string literals were replaced to the {\sl \_\_STRING\_\_} symbol.
+\end{itemize}
+
+\section{Model Configuration}
+The training model was implemented with Chainer 6.0.0b1.
+The
+
+\chapter{Results}
+\chapter{Discussion}
+\chapter{Conclusion}
+
+\bibliographystyle{plainnat}
+\bibliography{reference}
 

### 2019-01-13 c_cfg.py

@@ -3,17 +3,11 @@ from clang.cindex import CursorKind
 
 # liteeal can be expr
 # expr can be stmt
-nont_reduce = [
-	('toplevel',[
-		CursorKind.TRANSLATION_UNIT
-	]),
-	('type',[
-		CursorKind.TYPE_REF,
-	]),
-	('label',[
-		CursorKind.LABEL_REF,
-	]),
-	('expr',[
+nont_reduce = {
+	'toplevel': [CursorKind.TRANSLATION_UNIT],
+	#'type': CursorKind.TYPE_REF,
+	'labelref': [CursorKind.LABEL_REF],
+	'expr': [
 		CursorKind.ARRAY_SUBSCRIPT_EXPR,
 		CursorKind.BINARY_OPERATOR,
 		CursorKind.CALL_EXPR,
@@ -31,8 +25,8 @@ nont_reduce = [
 		CursorKind.STRING_LITERAL,
 		CursorKind.UNARY_OPERATOR,
 		CursorKind.UNEXPOSED_EXPR,
-	]),
-	('stmt',[
+	],
+	'stmt': [
 		CursorKind.BREAK_STMT,
 		CursorKind.CASE_STMT,
 		CursorKind.COMPOUND_STMT,
@@ -49,8 +43,8 @@ nont_reduce = [
 		CursorKind.SWITCH_STMT,
 		CursorKind.WHILE_STMT,
 		CursorKind.WHILE_STMT,
-	]),
-	('decl',[
+	],
+	'decl': [
 		CursorKind.ENUM_CONSTANT_DECL,
 		CursorKind.ENUM_DECL,
 		CursorKind.FIELD_DECL,
@@ -59,11 +53,12 @@ nont_reduce = [
 		CursorKind.TYPEDEF_DECL,
 		CursorKind.UNION_DECL,
 		CursorKind.VAR_DECL,
-	]),
-]
+		CursorKind.FUNCTION_DECL,
+	],
+}
 
 
-reduce_data = nont_reduce
+reduced_type = dict(sum(map(lambda ds: list(map(lambda v: (v,ds[0]),ds[1])), nont_reduce.items()),[]))
 #def get_node_type
 
 # None is for pass.
@@ -72,57 +67,57 @@ cfg = {
 	CursorKind.ARRAY_SUBSCRIPT_EXPR: ['expr','expr'],
 	CursorKind.ASM_LABEL_ATTR: None,	
[…]

### 2019-01-13 csrc2ast.py

@@ -15,9 +15,12 @@ Config.set_library_path("/usr/lib/llvm-7/lib")
 # clang python bindings is inefficient,
 # so I need to use information from clang -ast-dump 
 
+
+struct_decl_list = []
+import copy
 class AST:
 	def debug(sl,x):
-		"""
+		
 		vs = dir(x)
 		def f(a):
 			try:
@@ -30,7 +33,7 @@ class AST:
 		ats = list(map(f,vs))
 		for kv in ats:
 			print(kv)
-		"""
+		
 		code.interact(local={'sl':sl,'x': x,'cs':list(x.get_children())})
 		exit()
 	
@@ -55,6 +58,7 @@ class AST:
 		return res
 	
 	def __init__(sl,x,ast_hint=None,src=None):
+		global struct_decl_list;
 		sl.src = src
 		if type(x) is tuple:
 			sl.kind = x[0]
@@ -73,7 +77,7 @@ class AST:
 		if sl.invalid:
 			return
 		
-		print(ast_hint)
+		#print(ast_hint)
 		cvs = list(x.get_children())
 		if sl.kind == CursorKind.TRANSLATION_UNIT:
 			#print(ast_hint.tag)
@@ -84,32 +88,44 @@ class AST:
 			#code.interact(local={'hi': ast_hint})
 			cvs = list(filter(lambda x: x.kind != CursorKind.TYPE_REF,cvs))
 			cvs = cvs[len(cvs)-len(ast_hint.cs):]
+		elif sl.kind == CursorKind.FIELD_DECL:
+			assert ast_hint.tag == 'FieldDecl'
+			#code.interact(local={'hi': ast_hint})
+			cvs = list(filter(lambda x: x.kind != CursorKind.TYPE_REF,cvs))
+			cvs = cvs[len(cvs)-len(ast_hint.cs):]
 		elif sl.kind == CursorKind.FUNCTION_DECL:
 			assert ast_hint.tag == 'FunctionDecl'
 			#code.interact(local={'hi': ast_hint})
-			cvs = list(filter(lambda x: x.kind != CursorKind.TYPE_REF,cvs))
+			cvs = list(filter(lambda x: not (x.kind == CursorKind.TYPE_REF or (x.kind == CursorKind.PARM_DECL and len(x.spelling) == 0)),cvs))
+			#print(len(cvs))
 		elif sl.kind == CursorKind.GOTO_STMT:
[…]

### 2019-01-13 model_rnn.py

@@ -28,6 +28,7 @@ class Seq2seq(chainer.Chain):
 		self.v_eos_src = v_eos_src
 		self.v_eos_dst = v_eos_dst
 		self.n_maxlen = n_maxlen
+		self.n_target_vocab = n_target_vocab
 
 	def forward(self, xs, ys):
 		#print(xs,ys)
@@ -85,6 +86,47 @@ class Seq2seq(chainer.Chain):
 				ys = self.xp.argmax(wy.array, axis=1).astype(np.int32)
 				result.append(ys)
 
+
+		beam_with = 3
+		with chainer.no_backprop_mode(), chainer.using_config('train', False):
+			xs = [x[::-1] for x in xs]
+			exs = sequence_embed(self.embed_x, xs)
+			hx, cx, _ = self.encoder(None, None, exs)
+			#print(hx.shape,cx.shape,(1,xs_states[0].shape))
+			#sprint(xs_states)
+			hx = F.transpose(hx,axes=(1,0,2))
+			cx = F.transpose(cx,axes=(1,0,2))
+			
+			ivs = [self.embed_y(self.xp.full(1,i,np.int32))[0] for i in range(self.n_target_vocab)]
+			v = ivs[EOS_DST]
+			
+			result = []
+			
+			for i in range(len(xs)):
+				nhx,ncx = hx[i],cx[i]
+				ncx = F.reshape(ncx,(ncx.shape[0],1,ncx.shape[1]))
+				nhx = F.reshape(nhx,(nhx.shape[0],1,nhx.shape[1]))
+				beam_data = [(0.0,([],v,nhx,ncx))]
+				
+				for j in range(self.n_maxlen):
+					to_beam = []
+					for r,(kd,v,nhx,ncx) in beam_data:
+						tv = F.reshape(v,(1,self.n_units))
+						thx,tcx,ys = self.decoder(nhx,ncx,[tv])
+						
+						wy = self.W(ys[0]).data[0]
+						#print(wy.shape,wy)
+						wy = F.reshape(F.log_softmax(F.reshape(wy,(1,self.n_target_vocab)),axis=1),(self.n_target_vocab,)).data
+						#print(wy.shape)
+						to_beam += [(r+nr,(kd + [i],ivs[i],thx,tcx)) for i,nr in enumerate(wy)]
+					
+					#print(to_beam[0][0])
+					#print(list(map(lambda a: a[0],to_beam[:10])))
+					beam_data = sorted(to_beam)[::-1][:beam_with]
[…]

### 2019-01-13 model_rnn_with_att.py

@@ -167,7 +167,7 @@ class Seq2seq_with_Att(chainer.Chain):
 				ncx = F.reshape(ncx,(ncx.shape[0],1,ncx.shape[1]))
 				nhx = F.reshape(nhx,(nhx.shape[0],1,nhx.shape[1]))
 				self.att.init_hxs(hxs)
-				beam_data = [(1.0,([],v,nhx,ncx))]
+				beam_data = [(0.0,([],v,nhx,ncx))]
 				
 				for j in range(self.n_maxlen):
 					to_beam = []
@@ -180,6 +180,7 @@ class Seq2seq_with_Att(chainer.Chain):
 						thx,tcx,ys = self.decoder(nhx,ncx,[tv])
 						
 						wy = self.W(ys[0]).data[0]
+						wy = F.reshape(F.log_softmax(F.reshape(wy,(1,self.n_target_vocab)),axis=1),(self.n_target_vocab,)).data
 						#print(wy.shape)
 						to_beam += [(r+nr,(kd + [i],ivs[i],thx,tcx)) for i,nr in enumerate(wy)]
 					
@@ -187,7 +188,8 @@ class Seq2seq_with_Att(chainer.Chain):
 					#print(list(map(lambda a: a[0],to_beam)))
 					beam_data = sorted(to_beam)[::-1][:beam_with]
 					#print(list(map(lambda a: a[0],beam_data)))
-					
+				
+				self.att.reset()
 				result.append(beam_data[0][1][0])			
 		
 		# Remove EOS taggs

### 2019-01-13 train.py

@@ -42,6 +42,7 @@ def main():
 	
 	#data.data = list(filter(lambda xy: len(xy[0])<20 and len(xy[1])<10,data.data))
 	data = list(filter(lambda xy: len(xy[1])<n_maxlen,data))
+	data = data[:1000000]
 	print(len(data))
 	
 	lds = len(data)
@@ -62,7 +63,7 @@ def main():
 	c_vocab += ['__EOS__']
 	dst_vocab_len = len(c_vocab)
  
-	model = Seq2seq_with_Att(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_src, v_eos_dst, n_maxlen)
+	model = Seq2seq(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_src, v_eos_dst, n_maxlen)
 	#serializers.load_npz('models/iter_100__time_2019_01_10_02_01_29.npz',model)
 	#serializers.load_npz('save_models/models_prestudy_edit_dist_0.65/iter_47600__edit_dist_0.691504__time_2018_12_28_01_36_30.npz',model)
 
@@ -142,8 +143,8 @@ def main():
 		 'elapsed_time']),
 		trigger=(1, 'iteration'))
 
-	logt = 100
-	train_iter_step = 1
+	logt = 0
+	train_iter_step = 100
 	
 	
 

### 2019-01-14 texs/paper.tex
sleep

@@
 
-In this paper, we apply a statistical machine translation tequnique for a decompiler to generate human-friendly pseudocode. 
-This idea was already mentioned by Katz et al. [1], in which they use end-to-end machine translation with Recurrent Neural Networks.
+In this paper, we apply neural networks for a decompiler to generate human-friendly pseudocode. 
+This idea is oridinated from \cite{Motoneta}, in which they use Recurrent Neural Networks.
 
-\section{Previous Studies}
-\subsection{Decompilation techniques}
+(TODO)このあとに今回やる更に具体的な内容とその成果についてが入る。
+
+\section{Related Works}
+\subsection{Decompilation with Machine learning}
+Perfect decompilation is naturally impossible. So there are many machine learning applications for decompilation.
+
+The idea of applying LSTM to decompilation is originated from \cite{Motoneta}.
+
+In \cite{genetic_decompiler}, they applied genetic programming to decompilation.
+
+(TODO)もっとちゃんと説明する(手法をどこまで書くか)
 
@@
 The function G recieves X, subs 8 from P and decrements Q, then returns the value indicated by P.
-In the situation, analyst can estimate X represents a stuck structure, and the function F is for push function, G is for pop function.
+In the situation, analyst can estimate X has a name related to {\sl stuck}, and the function F has a name related to {\sl push}, G has a name related to {\sl pop}.
 
 \cite{name_recover_from_decompile_result} is the paper for tuckling this task. 
+In this paper, they try to estimate the name of a variable whcih appears in the decompilation result of a compiled C program.
 
@@
 Obfsucation is used for hiding the behaviour of a program whose source code have to be distributed.
-For example,
+For example, in the web application, the javascript code of the program should be distributed in order to be executed on client web browsers.
+To protect the program from cracking, the javascript code are sometimes minfified. All coments, newlines, indents are removed and the 
+variable names are substituted to automaticaly generated meaningless name.
 
-\subsection{Deep learning for programming task}
+\cite{JSNaughty} applys statistical machine translation for this task.
+
+\subsection{Neural networks for program synthesis}
+
+There are so many applications of neural networks for program synthesis. They are summurized in \cite{deep_programming_matome}.
 
@@
 
-A compiler is a program which translates source code written in language X into other language Y. 
+A compiler is a program which compiles source code written in language X to other language Y. 
 Usually, X is high-level language and Y is relatively low-level language. 
-For example, clang compiler translates C language into x64 assembly language, javac compiler translates Java to Java virtual machine code.
+For example, clang compiler translates C language to x64 assembly language, javac compiler translates Java to Java virtual machine code.
 
@@
 % https://github.com/torvalds/linux/blob/70c25259537c073584eb906865307687275b527f/lib/rbtree.c#L528
+
+(TODO)表がはみ出しているのでどうにかする。
 
@@
 \section{LSTM}
-To generate $ \argmax_{sx} p(sx|sy)$, we decomposit $ p(sx|sy) = p([sx_1, \dots, sx_n] |sy) $ to $ p(sx_1|sy,[]) \dots p(sx_n|sy,[sx_1,\dots,sx_{n-1}]) $,
+To generate $ \argmax_{sx} p(sx|sy)$, we decomposit $ p(sx|sy) = p([sx_1, \dots, sx_n] |sy) $ to $ \prod_{k=1}^{n} p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $,
 where $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ represents the probability that the token $ sx_k $ follows to the sequence $ [sx_1,\dots,sx_{k-1}] $ 
-when the input sequence is $ sy $. We try to estimate the probability $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ by LSTM.
-LSTM is
+when the input sequence is $ sy $. We try to estimate the probability 
+$ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ by LSTM.
+
+(TODO)LSTMの説明、その後Attentionについて説明、さらにその後seq2treeについて説明する。
 
@@
 Some sample flagments are shown in figure~\ref{fig:pairsofflagments}.
-
-% Here the reason for fragments?
 
@@
 \section{Data Preprocessing}
+
+% 244 words
 In order to apply LSTM, input and output for the LSTM must be the sequence of tokens. 
@@
 
+(TODO)木状にする方法について述べる。
+
 \section{Model Configuration}
-The training model was implemented with Chainer 6.0.0b1.
-The
+The training model was implemented with Chainer.
+(TODO)レイヤ数、ロスについてのべる。
 
 \chapter{Results}
+(TODO)seq2seq、アテンション付きseq2seq、seq2treeとバイナリそのまま/逆アセンブル後 の6パターンのデータを出す。
 \chapter{Discussion}

### 2019-01-14 build_ast_data.py

@@ -55,9 +55,13 @@ def convert(path):
 	
 	if d == 0:
 		d = subprocess.call('clang -Xclang -dump-tokens -fsyntax-only %s.pp.c > /dev/null 2> %s.tokenized' % (fn,fn),shell=True)
-	
-		with open('%s.tokenized' % fn,"r") as fp:
-			s = fp.read()
+		
+		try:
+			with open('%s.tokenized' % fn,"r") as fp:
+				s = fp.read()
+		except UnicodeDecodeError:
+			print('mousiran',fn)
+			return
 		
 		ts = ""
 		bc = ""
@@ -100,7 +104,24 @@ def convert(path):
 			return
 	
 	return
-		
+	
+	
+	"""
+	satos@ispc2016:~/sotsuron/neural_decompiler/build_ast$ ls *.pp.c | wc
+  	18109   18109  833014
+	satos@ispc2016:~/sotsuron/neural_decompiler/build_ast$ ls *.tokenized | wc
+		16829   16829  858279
+	satos@ispc2016:~/sotsuron/neural_decompiler/build_ast$ ls *.tokenized.bef.c | wc
+		16845   16845  960165
+	satos@ispc2016:~/sotsuron/neural_decompiler/build_ast$ ls *.tokenized.bef.c.astdump | wc
+		12728   12728  827320
+	satos@ispc2016:~/sotsuron/neural_decompiler/build_ast$ ls *.tokenized.bef.o | wc
+		12656   12656  721392
+	satos@ispc2016:~/sotsuron/neural_decompiler/build_ast$ ls *.tokenized.c | wc
+		10327   10327  547331
+	satos@ispc2016:~/sotsuron/neural_decompiler/build_ast$ ls *.tokenized.o | wc
+		 9615    9615  509595
+	"""
 	
 
 	

### 2019-01-17 texs/paper_base.tex
build_ast

--- 2019-01-11 texs/paper_base.tex
@@
 
-\eauthor{Sota Sato}
-\jauthor{佐藤聡太}
-\esupervisor{Masashi Sugiyama}
-\jsupervisor{杉山将}
-\supervisortitle{Professor} % Professor, etc.
+__NAMES__
 
@@
 \lstset{%
-  basicstyle={\tiny},%
-  commentstyle={\tiny\itshape},%
-  keywordstyle={\tiny\bfseries},%
+  basicstyle={\small},%
+  commentstyle={\small\itshape},%
+  keywordstyle={\small\bfseries},%
   % style={myCustomMatlabStyle},
-  stringstyle={\tiny\ttfamily},
+  stringstyle={\small\ttfamily},
   frame={tb},
@@
   numbersep=1zw,%
-  lineskip=-0.5ex%
+  lineskip=-0.5ex,%
+  captionpos=b
 }
@@
 \chapter{Introduction}
-% For dinamic analysis, malware is executed in the sandbox and the behaviour is examined with the changes ocuuring in the sandbox. 
+% For dinamic analysis, malware is executed in the sandbox and the behavior is examined with the changes ocuuring in the sandbox. 
 % Usually, there are two malware analysis approach, the dinamic analysis and the static analysis.
-% In the static analysys, the behaviour of the malware is analysed by
+% In the static analysys, the behavior of the malware is analyzed by
 
 These days, the amount of malware has been increasing rapidly.
-So the development of malware analysis tools, such as decompilers, has been becoming important.
-A decompiler is a tool for analysing the behavior of malwares. 
-This tool generates C-like pseudocode which represents the behaviour of the malware, and analyst can infer the behavior of the malware with the pseudocode.
-This is much easier compare to analysing raw binary.
+So the importance to develop malware analysis tools has been rising.
 
-But sometimes the decompiler generate  unstructured code, which calls for some effort to understand the behavior of the program. 
-This is due to the flexibility of the high level language.
-If the decompiler chooses a human-friendly representation of the language as the result of decompiling, we can analyze malware with less effort.
+One of these tools is a decompiler, which is a tool for analyzing the behavior of malwares. 
+This tool generates C-like pseudocode which represents the behavior of the malware, and analyst can infer the behavior of the malware from the pseudocode.
+This is much easier compare to analyzing raw binary.
 
-In this paper, we apply a statistical machine translation tequnique for a decompiler to generate human-friendly pseudocode. 
-This idea was already mentioned by Katz et al. [1], in which they use end-to-end machine translation with Recurrent Neural Networks.
+However, sometimes a decompiler generate unstructured code, which requires users to make an effort to understand the behavior of the program. 
+This is due to flexibility of the high level language. If the decompiler chooses a human-friendly representation of the language as the result of decompiling, we can analyze malware with less effort.
+
+In this paper, we apply neural networks to a decompiler to generate human-friendly pseudocode. 
+This idea is originated from \cite{Motoneta}, in which they use Recurrent Neural Networks.
+
+(TODO)このあとに今回やる更に具体的な内容とその成果についてが入る。
+
+\section{Related Works}
+\subsection{Decompilation with Machine Learning}
+Because perfect decompilation is naturally impossible, there are many machine learning applications for decompilation.
+
+% The idea of applying LSTM to decompilation is originated from \cite{Motoneta}.
+
+In \cite{genetic_decompiler}, they applied genetic programming to decompilation.
+
+(TODO)更にいろいろ説明する(手法をどこまで書くか)
+
+% Compiler and Optimization Level Estimation for Improving Anti-malware Technologies
+
+%
+
+\subsection{Improvement of decompilation results}
+In this paper, we don't try to recover the function name and variable name. 
+However, for hand-decompilation, sometimes the name can be estimated by the functionality of the variable.
+For example, assume there is a variable X which seems to have a C struct type and has two fields P and Q.
+And there are two functions F and G which operate with X. 
+The function F receives X and other value V, assigns V to the memory indicated by P, adds 8 to P and increments Q. 
+The function G receives X, subs 8 from P and decrements Q, then returns the value indicated by P.
+In the situation, analyst can estimate X has a name related to {\sl stuck}, and the function F has a name related to {\sl push}, G has a name related to {\sl pop}.
+
+\cite{name_recover_from_decompile_result} is the paper for tackling this task. 
+In this paper, they try to estimate the name of a variable which appears in the decompilation result of a compiled C program.
+
+This kind of name estimation also appears in the context of deobfuscation.
+Deobfuscation is a reverse process of obfuscation.
+Obfuscation is a technique to modify the program source code so that the code becomes hard to understand for humans. 
+Obfuscation is used for hiding the behavior of a program whose source code have to be distributed.
+For example, on the web application, the JavaScript code of the program should be distributed in order to be executed on client web browsers.
+To protect the program from cracking, the JavaScript code are sometimes minified. All comments, newlines, indents are removed and the 
+variable names are substituted to automatically generated meaningless name.
+
+\cite{JSNaughty} apply statistical machine translation for this task.
+
+\subsection{Neural Networks for Program Synthesis}
+
+There are so many applications of neural networks for program synthesis. They are summurized in \cite{deep_programming_matome}.
+
+(TODO)最低限Seq2Treeについては触れる。更にいろいろ。
+
+\chapter{Problem Settings and Methots}
 
@@
 
-% 573 words.
+% 320 words.
 
-A compiler is a program which translates source code written in language X into other language Y. 
+A compiler is a program which compiles source code written in language X to other language Y. 
 Usually, X is high-level language and Y is relatively low-level language. 
-For example, clang compiler translates C language into x64 assembly language, javac compiler translates Java to Java virtual machine code.
+For example, clang compiler translates C language to x64 assembly language, javac compiler translates Java to Java virtual machine code.
 
-A decompiler is a program which aims to reverse the process of a compiler, retrive a source code of the high-level language X from the source code of the low-level language Y. 
+A decompiler is a program which aims to reverse the process of a compiler, retrieve a source code of the high-level language X from the source code of the low-level language Y. 
 This reversing process is usually insufficient or impossible.
-This is because many informaitions, such as variaible name or function name, are lost when compiling.
-Additionaly, the program structure descripted in the high level language are lost too. 
+This is because many informaition, such as variable name or function name, are lost when compiling.
+Additionally, the program structure described in the high level language are lost too. 
 For example, a simple {\sl for statement} can be represented by the combination of a {\sl while statement} and an {\sl if statement}, or the combination of {\sl if statement} and {\sl goto statement}.
@@
 
-Existing deterministic decompilers are made up with many steps similer to compilers. 
+Existing decompilers are made up with many steps similar to compilers. 
 They find patterns in binary data, convert them to more high-level structure, and chain them so that they finally generate high-level psudecode.
@@
 
+% (DONE)表がはみ出しているのでどうにかした。
+
 \begin{figure}
 	\begin{tabular}{cc}
-		\begin{minipage}[t]{0.5\hsize}
-			\lstinputlisting[]{rb_tree.c}
-		\end{minipage}
-		\begin{minipage}[t]{0.5\hsize}
-			\lstinputlisting[]{hopper.c}
+		\begin{minipage}[c]{0.5\hsize}
+			\lstinputlisting[title={sample C source code},breaklines=false]{bintree.c}
 		\end{minipage}
@@
 		\begin{minipage}[c]{0.5\hsize}
-			\lstinputlisting[]{snowman.c}
+			\lstinputlisting[title={result of the Hopper Decompiler}]{hopper.c}
 		\end{minipage}
 		\begin{minipage}[c]{0.5\hsize}
-			\lstinputlisting[]{handdecomp.c}
+			\lstinputlisting[title={result of the Snowman Decompiler}]{snowman.c}
 		\end{minipage}
 	\end{tabular}
-	\caption{ hogehugapiyo.}
+	\vspace*{-0.6cm}
+	\caption{ decompilation results of existing decompilers for C source code}
 	\label{fig:cw}
@@
 
-Figure~\ref{fig:cw} shows the example decompilation result of the Hopper disassembler and the snowman decompiler and a hand decompilation for a C language code.
-The output of Hopper decompiler seems not so bad, but some essential statements are missing and there are some verbose variables.
-The output of snowman decompiler also seems broken. 
-The snowman decompiler finds some variablels are pointer of a structure, but fails to detect the range of the function, and generates many unneccesary casts.
-Idealy, the decompiler can find correct function ranges and structure of statements as a hand decompilation result, but the decompilers failed.
+Figure~\ref{fig:cw} shows the example decompilation results of the Hopper disassembler and the snowman decompiler 
+for a sample C language code.
+The Hopper decompiler fails to detect while statements, and the variable {\sl now} is incorrectly analyzed.
+The output of snowman seems rather correct, as type {\sl struct tree} is reconstructed to {\sl struct s0}, 
+and the {\sl if} statement and {\sl while} statement are correctly restored. 
+However, it fails to detect the function epilogue, and the {\sl free} function call is incorrectly analyzed.
+Ideally, the decompilers can find correct function ranges and structure of statements, but they failed.
 
-In this paper, we try to apply statistical approach, specifically SMT (statical machine translation) technique, for decompilation.
-The decompilation problem is folmulated as follows. 
-Given $sx$ as a source code of domain language X, compiler generates $sy$ as a code of target language Y with probability $p(sy|sx)$. 
-We assume the prior distribution $p(sx)$ as the human-generated souce code. 
-With that assumption, the provability of decompilation $p(sx|sy)$ is in proportion to $p(sy|sx)p(sx)$ according to the bayesian low. 
-The $\argmax_{sx} p(sx|sy)$ is considered as the best human-intelligible decompilation result for the low-level code $sy$,  
-so we try to estimate $ \argmax_{sx} p(sy|sx)p(sx)$ for decompilation result.
-And if the compiler is deterministic, there wolud be a function $f$ which represents the compiler and $p(f(sx)|sx) = 1$,
-then the objective becomes to $ \argmax_{sx,f(sx)=sy} p(sx)$.
+\section{Problem Settings}
 
-The distribution $p(sx)$ is approximated by collecting source code from open source projects.
-So if we had enough high-level source code data, we could choose the most popular high-level source code which generats given low-level code for the decompile result.
-But high-level source code data can't be comprehensive.
-So we have to model the structure of compilation process somehow.
-We modeled the structure by the LSTM, which is commonly used in resent SMT techniques.
+% 189
+In this paper, we try to apply statistical approach, specifically SMT (statistical machine translation) technique, for decompilation.
+The decompilation problem is formulated as follows.
 
-\section{Deep learning and LSTM}
+Given $sx = [sx_1, \dots, sx_n] $ as a tokenized sequence of the source code of domain language X, compiler generates $sy$ as a code of target language Y with probability $p(sy|sx)$.
+Then, the best decompilation result for target source code $sy$ is $ \argmax_{sx} p(sx|sy)$. 
+To generate $ \argmax_{sx} p(sx|sy)$, we decomposit $ p(sx|sy) = p([sx_1, \dots, sx_n] |sy) = \prod_{k=1}^{n} p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $,
+where $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ represents the probability that the token $ sx_k $ follows to the sequence $ [sx_1,\dots,sx_{k-1}] $ 
+when the input sequence is $ sy $. 
+We try to estimate the probability $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ by LSTM, which is described in the next section.
+With estimated $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $, we can generate approximated $ \argmax_{sx} p(sx|sy)$ sequentially from $sx_1$ to $sx_n$ by selecting token $ \argmax_{sx_{k}} p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ at each timing.
 
-\chapter{Related works}
+% The LSTM is 
+% We assume the prior distribution $p(sx)$ as the human-generated source code. 
+% With that assumption, is in proportion to $p(sy|sx)p(sx)$ according to the Bayesian low, and 
+% the $\argmax_{sx} p(sx|sy)$ is considered as the best human-intelligible decompilation result for the low-level code $sy$.  
+% So we try to estimate $ \argmax_{sx} p(sy|sx)p(sx)$ for decompilation result.
+% And if the compiler is deterministic, there would be a function $f$ which represents the compiler and $p(f(sx)|sx) = 1$,
+% then the objective becomes to $ \argmax_{sx,f(sx)=sy} p(sx)$.
 
-\chapter{Related works}
+% The distribution $p(sx)$ is approximated by collecting source code from open source projects.
+% So if we had enough high-level source code data, we could choose the most popular high-level source code which generates given low-level code for the decompile result.
+% However, high-level source code data can't be comprehensive.
+% So we have to model the structure of compilation process somehow.
+% We modeled the structure by the LSTM, which is commonly used in resent SMT techniques.
 
-\chapter{Preliminaries}
+\section{Modelings}
 
-\chapter{Imprementation and Experiment}
-First, we collect data sets from online
+% (TODO)LSTM,Seq2seqの説明、その後Attentionについて説明、さらにその後seq2treeについて説明する。
+\subsection{LSTM}
+LSTM (Long Short-Term Memory) is a unit of Recurrent Neural Network. 
+It is first introduced in \cite{first_LSTM}, for overcoming the vanishing gradient problem and exploding gradient problem.
+Roughly speaking, LSTM unit recieves two input vectors, 
+the one represents the internal state of the LSTM, and the other is the input for the LSTM unit, 
+and LSTM emits one output vectors, which represents the next internal state of the LSTM.
+
+\subsection{Seq2Seq}
+% This model is called seq2seq (sequence to seqence) model.
+
+LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the seq2seq (sequence to sequence) model.
+SMT is the task which tries to translate one sentense $sx$ written in a language L into the sentense $sy$ written in another a language M.
+
+Seq2seq model is composed of two modules, the encoder netwrok and the decoder network.
+
+The purpose of the encoder network is to summerize the input sequence $sx$, whose length varies depending on the sequence, into one fixed length vector.
+This process is carried out as follows. 
+First, $sx$ is tokenized to sequence $sx_{1} \dots sx_{n}$, and each token $sx_{k}$ is embedded to vector representation $vx_{k}$. 
+Then, the initial LSTM internal state $enc_0$ is intialized randomely, 
+and for each vector $vx_{k}$ and internal state $s{k-1}$, next internal state $enc_{k}$ is calculated as $ LSTM_{enc}(enc_{k-1},vx_{k}) $.
+Finally, the last internal state $ enc_{n}$ is returned as the reduced representation of the input sequence $sx$.
+
+The purpose of the decoder network is to estimate the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
+
+The training process is carried out as follows. 
+First, $sy$ is tokenized and embedded to vector representation $vy_{1} \dots vy_{m}$ in the same way as $sx$.
+And from the start vector $y_begin$ and encoded input $ enc_{n} $, first internal state $ dec_{1}$ is calcuated as $ LSTM_{dec}(enc_{n},y_begin) $.
+Then, with for all vector $vy_{k}$, $dec_{k+1}$ is calculated as $ LSTM_{dec}(dec_{k},vy_{k}) $.
+Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_dec $ then softmaxed to a probability vector $ py_{k} $.
+The probability vector $ py_{k} $ is intended to represent the probability distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
+% (TODO)このへんで V_eosについて述べないといけない
+So the network is trained to reduce the difference between predicted distribution $ py_{k} $ and actual distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
+In the experiment, we choiced cross-entropy of $ py_{k} $ and $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for loss function.
+
+The inference is obteining $ \argmax_{sy} p(sy|sx) = \argmax_{sy} \prod_{k=1}^n p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
+Calculating argmax directly is time consuming, so we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_n]$ sequentially.
+First, $sy_1$ is calculated as $ \argmax_{sy_1} p(sy_1|sx,[]) $, where distribution $ p(sy_1|sx,[]) $ is approximated by 
+$ softmax(W_dec(dec_{1})) = softmax(W_dec(LSTM_{dec}(enc_{n},y_begin))) $. Then, the next
+
+\chapter{Experiments}
+
+\section{Data Collection}
+% 219 words
+First, we collected source codes by crawling \cite[GitHub]{github}, cloning about 900 repositories with C language topic, 
+and recursively searched each folder to enumerate C language source code.
+From each source code, we generated pairs of C source code fragment and x64 assembly code corresponds to the C fragment.
+Some sample fragments are shown in figure~\ref{fig:pairsoffragments}.
+
+\begin{figure}
+	\begin{tabular}{cc}
+		(TODO)データ対の例を載せる
+	\end{tabular}
+	\caption{Sample data fragments}
+	\label{fig:pairsoffragments}
+\end{figure}
+
+The pairs were generated as follows. Let {\sl S0} be an original C source code.
+\begin{enumerate}
+\item Remove all preprocessor, such as {\sl \#include}, in {\sl S0} to generate preprosessed C code {\sl S1}. 
+\item Tokenize {\sl S1} and rearrange them in {\sl S2} so that there is exactly one token for each line. 
+\item 
+Compile {\sl S2} by gcc (GNU C compiler) with no optimization (-O0) and debug option to get assembly code {\sl S3}. 
+With debug option, {\sl S3} contains information about the source code position which each assembly operations are originated from.
+\item Assemble {\sl S3} to object file {\sl S4} and disassemble {\sl S4} to get information eliminated assembly code {\sl S5}.
+\item 
+Parse {\sl S2} with clang to get AST (abstract syntax tree) of the source code. 
+And for each subtree of AST, we can get C fragment source code which corresponds to the subtree, 
+and we can get assembly code corresponds to the C fragment by employing {\sl S5} combine with {\sl S3}.
+\end{enumerate}
+
+The C fragment and assembly code pairs are preprocessed for the training and testing data.
+
+\section{Data Preprocessing}
+
+% 244 words
+In order to apply LSTM, input and output for the LSTM must be the sequence of tokens. 
+So we have to preprocess the assembly data and C fragments to the token sequences by somehow.
+
+The assemblies were preprocessed in two ways.
+First way is the raw binary integers. The assemblies are finally assembled to the sequence of the one byte integers, ranged from 0 to 255.
+So the one byte integer sequences can be directly used for input sequences.
+Second way is the tokenized sequence of assembly codes. 
+The disassembled opcodes and operands in {\sl S5} are split to symbols, and concatenated the sequences to one sequence, then we modified followings.
+\begin{itemize}
+\item For each end of the operations, the {\sl ENDLINE} symbol is added to indicate the end of operation.
+\item 
+The relative access of code address, such as {\sl call} or {\sl jump} operations, 
+are relabeled like $\alpha$-conversion for making code position independent and for reducing the vocabulary size.
+\item The big integer values are substituted. 
+In detail, the integer in the range from -255 to 256 are preserved as it is, and the other integeres are substituted with the {\sl \_\_HEX\_\_} symbol.
+This also reduces the vocabulary size.
+\end{itemize}
+
+The C source codes were preprocessed like the second way of the assembly preprosess.
+C source code was tokenized to the sequence and preprocessed with following modifications.
+\begin{itemize}
+\item Function names and variable names were renamed like $\alpha$-conversion.
+\item Big integer values were substituted too. 
+\item All string literals were replaced to the {\sl \_\_STRING\_\_} symbol.
+\end{itemize}
+
+% (TODO)木状にする方法について述べる。
+
+\section{Model Configuration}
+The training model was implemented with Chainer.
+(TODO)レイヤ数、ロスについてのべる。
+
+\chapter{Results}
+(TODO)seq2seq、アテンション付きseq2seq、seq2treeとバイナリそのまま/逆アセンブル後 の6パターンのデータを出す。
+\chapter{Discussion}
+\chapter{Conclusion}
+
+\bibliographystyle{plainnat}
+\bibliography{reference}
 

### 2019-01-17 asm_objd_conv.py

@@ -1,0 +1,113 @@
+import code
+import re
+
+def get_line_from_list(asm,objd):
+	asm = list(map(lambda x: x.split('#')[0].strip(),asm.split('\n')))
+	asm_with_loc = list(filter(lambda x: x!='' and x[0]!='#' and x[-1]!=':' and (x[0] != '.' or x[:5]=='.loc '),asm))
+	asm_noloc = list(filter(lambda x: x!='' and x[0]!='#' and x[-1]!=':' and x[0]!='.',asm))
+
+	"""
+	while asm_with_loc[-1][-1]==':':
+		asm_with_loc = asm_with_loc[:-1]
+	while asm_noloc[-1][-1]==':':
+		asm_noloc = asm_noloc[:-1]
+	"""
+	#exit()
+	objd = objd.split('\n')[5:]
+	objd = list(filter(lambda x: x!='',objd))
+	objd = list(map(lambda x: x.split('#')[0].strip(),objd))
+	objd_asm_len = len(list(filter(lambda x: x[-1]!=':',objd)))
+	"""
+	# only for clang
+	tobjd = []
+	for i,v in enumerate(objd[:-1]):
+		if objd[i+1][-1]==':':
+			continue
+		tobjd.append(v)
+	objd = tobjd + [objd[-1]]
+	"""
+	#print(objd)
+	#print(len(asm2),len(objd))
+	#assert len(objd) == len(asm2)
+	#print(len(objd),len(asm_noloc))
+	"""
+	print('\n'.join(asm_with_loc))
+	print('-' * 100)
+	print('\n'.join(objd))
+	"""
+	if objd_asm_len != len(asm_noloc):
+		"""
+		print('\n'.join(asm_noloc))
+		print('-' * 100)
+		print('\n'.join(objd))
+		print('nanka hen',objd_asm_len,len(asm_noloc))
+		exit()
+		
+		asm volatile があるので諦める
+		"""
+		raise ParseErr("nanka hen")
+	
+	"""
+	print(len(asm),len(objd))
+	print('\n'.join(asm_with_loc))
+	print('-' * 100)
+	print('\n'.join(objd))
+	"""
+	
+	addrs = set([])
+	for d in objd:
+		if d[-1]==':':
+			continue
+		op = d.split('\t')[2]
+		if op[0]=='j' or op[:4] == 'call':
+			nad = list(filter(lambda a: a!='',op.split(' ')))[1]
+			addrs |= set([nad])
[…]

### 2019-01-17 build_ast_data.py

@@ -12,7 +12,6 @@ import binascii
 import csrc2ast
 import c_cfg
 
-
 tmp_cnt = 0
 def gen_tmp_name():
 	global tmp_cnt
@@ -30,7 +29,9 @@ def chain_functions(fs):
 
 devnull = open('/dev/null','w')
 with open('correspond_table_ast.txt','r') as fp:
-	corresp_table = fp.read()
+	corresp_table = fp.read()	
+
+
 
 def convert(path):
 	global devnull
@@ -46,6 +47,7 @@ def convert(path):
 	print(path)
 	d = subprocess.call('clang -E %s > /dev/null 2> /dev/null' % path,shell=True) 
 	
+	
 	if d == 0:
 		d = subprocess.call('clang -E %s | grep -v "#" | grep -v "^[[:space:]]*$" > %s.pp.c 2> /dev/null' % (path,fn),shell=True)
 	
@@ -53,6 +55,7 @@ def convert(path):
 		# too big.
 		d = 1
 	
+	# OSError: [Errno 28] No space left on device !!
 	if d == 0:
 		d = subprocess.call('clang -Xclang -dump-tokens -fsyntax-only %s.pp.c > /dev/null 2> %s.tokenized' % (fn,fn),shell=True)
 		
@@ -96,6 +99,10 @@ def convert(path):
 		except ValueError:
 			print('mousiran',fn)
 			return
+		except KeyError:
+			print('mousiran',fn)
+			return
+		
 		with open(tkcfn,'w') as fp:
 			fp.write(psrc)
 		
@@ -124,9 +131,19 @@ def convert(path):
 	"""
 	
 
+import tokenizer
+
+def convert_from_purified(fn):
+	global devnull
+	tsrc = '\n'.join(tokenizer.tokenize('%s.c' % fn))
+	tcfn = '%s.tokenized.c' % fn
+	with open(tcfn,'w') as fp:
+		fp.write(tsrc)
+		
+	#ast = csrc2ast.src2ast(tcfn)
 	
 	#print('tokenized',path)
-	tcfn = '%s.tokenized.c' % fn
+	atcfn = '%s.tokenized.aligned.c' % fn
 	sfn = '%s.s' % fn
 	ofn = '%s.o' % fn
 	
@@ -139,14 +156,11 @@ def convert(path):
 				(['objdump','-d','-M','intel','-w',ofn]              ,objdfp,devnull),
 			])
 	
[…]

### 2019-01-17 c_ast.py

@@ -1,0 +1,471 @@
+import c_cfg
+import clang_ast_dump
+import types
+from clang.cindex import Config,Index,CursorKind
+
+import code
+
+# clang python bindings is inefficient,
+# so I need to use information from clang -ast-dump 
+
+struct_decl_list = []
+import copy
+class AST:
+	def debug(sl,x=None,ast_help=None):
+		"""
+		vs = dir(x)
+		def f(a):
+			try:
+				res = x.__getattribute__(a)
+			except AssertionError:
+				res = AssertionError
+			res = (a,res)
+			return res
+		ats = list(map(f,vs))
+		for kv in ats:
+			print(kv)
+		"""
+		print(sl.kind)
+		t,b = sl.top,sl.bottom
+		print('source range:',t,b)
+		with open(sl.filename) as fp:
+			src = fp.readlines()[t-1:b]
+		print(' '.join(src))
+		code.interact(local={'sl':sl,'x': x,'cs':(list(x.get_children()) if x is not None else None),'ah':ast_help})
+		exit()
+	
+	def checkalign(sl,vs):
+		h = sl.top
+		res = []
+		for d in vs:
+			if d == 1:
+				res.append(sl.src[h-1])
+				h += d
+			elif type(d) is str:
+				#print(sl.src[h-1],d)
+				assert sl.src[h-1]==d
+				h += 1
+			else:
+				assert h == d.top
+				h = d.bottom + 1
+		assert h == sl.bottom + 1
+		
+		if len(res)==1:
+			res = res[0]
+		return res
+	
+	def __init__(sl,x,ast_hint=None,src=None,*,isnull=False):
+		if isnull:
+			sl.kind = None
+			return
+		global struct_decl_list
+		sl.src = src
+		if type(x) is tuple:
+			sl.kind = x[0]
+			sl.leafdata = x[1]
+			sl.children = []
+			sl.show = lambda: sl.leafdata
+			sl.isleaf = True
+			sl.invalid = False
+			return
+		#sl.debug(x)r
+		sl.isleaf = False
+		sl.kind = x.kind
+		sl.top = x.extent.start.line
+		sl.bottom = x.extent.end.line
+		sl.filename = x.extent.start.file.name
+		#print(x.kind,sl.top,sl.bottom)
[…]

### 2019-01-17 c_cfg.py

@@ -1,9 +1,6 @@
 from clang.cindex import CursorKind
-
-
-node_id_data = {
-
-}
+import pycparser
+import c_ast
 
 # liteeal can be expr
 # expr can be stmt
@@ -60,11 +57,33 @@ nont_reduce = {
 		CursorKind.VAR_DECL,
 		CursorKind.FUNCTION_DECL,
 	],
+	
+	#from c_type_cfg
+	'type': [
+		pycparser.c_ast.ArrayDecl,
+		pycparser.c_ast.FuncDecl,
+		pycparser.c_ast.TypeDecl,
+		pycparser.c_ast.PtrDecl,
+	],
+	'paramlist': [
+		pycparser.c_ast.ParamList
+	],
+	'typename': [
+		pycparser.c_ast.Typename
+	],
+	'typedecltype': [
+		pycparser.c_ast.Struct,
+		pycparser.c_ast.Union,
+		pycparser.c_ast.IdentifierType,
+	],
 }
 
 
 reduced_type = dict(sum(map(lambda ds: list(map(lambda v: (v,ds[0]),ds[1])), nont_reduce.items()),[]))
 #def get_node_type
+
+for v in nont_reduce['expr']:
+	nont_reduce['stmt'].append(v)
 
 # None is for pass.
 cfg = {
@@ -112,7 +131,7 @@ cfg = {
 	CursorKind.PURE_ATTR: None, # __attribute__((__pure__))    skip. (or remove?)
 	CursorKind.RETURN_STMT: [['expr','option']],
 	CursorKind.STRING_LITERAL: ['stringliteral'],
-	CursorKind.STRUCT_DECL: ['name',['decl','list']],
+	CursorKind.STRUCT_DECL: ['type_name',['decl','list']],
 	CursorKind.SWITCH_STMT: ['expr','stmt'],
 	CursorKind.StmtExpr: None, # return ({int x = 3;4;});   GNU extension?, skip.
 	CursorKind.TRANSLATION_UNIT: [['decl','list']],
@@ -121,11 +140,24 @@ cfg = {
 	CursorKind.UNARY_OPERATOR: ['unop','expr'], #what is difference with CursorKind.CXX_UNARY_EXPR
 	CursorKind.UNEXPOSED_ATTR: None, # __attribute__((__nothrow__))   skip. (or remove?)
[…]

### 2019-01-17 c_type_cfg.py

@@ -1,0 +1,125 @@
+
+"""
+type_exps = {<class 'pycparser.c_ast.Typename'>: {('name', 'quals', 'type')}, <class 'pycparser.c_ast.FuncDecl'>: {('args', 'type')}, <class 'pycparser.c_ast.ParamList'>: {('params',)}, <class 'pycparser.c_ast.TypeDecl'>: {('declname', 'quals', 'type')}, <class 'pycparser.c_ast.Struct'>: {('name', 'decls')}, <class 'pycparser.c_ast.IdentifierType'>: {('names',)}, <class 'pycparser.c_ast.PtrDecl'>: {('quals', 'type')}, <class 'pycparser.c_ast.Union'>: {('name', 'decls')}, <class 'pycparser.c_ast.Enum'>: {('name', 'values')}, <class 'pycparser.c_ast.ArrayDecl'>: {('type', 'dim', 'dim_quals')}, <class 'pycparser.c_ast.Constant'>: {('type', 'value')}, <class 'pycparser.c_ast.ID'>: {('name',)}, <class 'pycparser.c_ast.BinaryOp'>: {('op', 'left', 'right')}, <class 'pycparser.c_ast.TernaryOp'>: {('cond', 'iftrue', 'iffalse')}, <class 'pycparser.c_ast.StructRef'>: {('name', 'type', 'field')}, <class 'pycparser.c_ast.UnaryOp'>: {('op', 'expr')}}
+"""
+
+"""
+type_exps = {
+	pycparser.c_ast.Typename: ('name', 'quals', 'type'),
+	pycparser.c_ast.FuncDecl: ('args', 'type'), 
[…]

### 2019-01-17 clang_ast_dump.py

@@ -50,9 +50,9 @@ def s2tree(s):
 	return parse(0)
 
 import os
-def fn_to_clang_ast(fn):
-	os.system('clang -Xclang -ast-dump -fsyntax-only %s > %s.astdump 2>/dev/null' % (fn,fn))
-	with open(fn + '.astdump') as fp:
+def fn_to_clang_ast(pfn):
+	#os.system('clang -Xclang -ast-dump -fsyntax-only %s > %s.astdump 2>/dev/null' % (fn,fn))
+	with open(pfn) as fp:
 		parsed = fp.read()
 	return s2tree(parsed)
 

### 2019-01-17 csrc2ast.py

@@ -16,375 +16,20 @@ Config.set_library_path("/usr/lib/llvm-7/lib")
 # so I need to use information from clang -ast-dump 
 
 
-struct_decl_list = []
-import copy
-class AST:
-	def debug(sl,x=None,ast_help=None):
-		"""
-		vs = dir(x)
-		def f(a):
-			try:
-				res = x.__getattribute__(a)
-			except AssertionError:
-				res = AssertionError
-			res = (a,res)
-			return res
-		ats = list(map(f,vs))
-		for kv in ats:
-			print(kv)
-		"""
-		print(sl.kind)
-		t,b = sl.top,sl.bottom
-		print('source range:',t,b)
-		with open(sl.filename) as fp:
-			src = fp.readlines()[t-1:b]
-		print(' '.join(src))
-		code.interact(local={'sl':sl,'x': x,'cs':(list(x.get_children()) if x is not None else None),'ah':ast_help})
-		exit()
-	
-	def checkalign(sl,vs):
-		h = sl.top
-		res = []
-		for d in vs:
-			if d == 1:
-				res.append(sl.src[h-1])
-				h += d
-			elif type(d) is str:
-				#print(sl.src[h-1],d)
-				assert sl.src[h-1]==d
-				h += 1
-			else:
-				assert h == d.top
-				h = d.bottom + 1
-		assert h == sl.bottom + 1
-		
-		if len(res)==1:
-			res = res[0]
-		return res
-	
-	def __init__(sl,x,ast_hint=None,src=None):
-		global struct_decl_list;
-		sl.src = src
-		if type(x) is tuple:
-			sl.kind = x[0]
-			sl.leafdata = x[1]
-			sl.children = []
-			sl.show = lambda: x[1]
-			sl.isleaf = True
-			sl.invalid = False
-			return
-		#sl.debug(x)r
-		sl.isleaf = False
-		sl.kind = x.kind
-		sl.top = x.extent.start.line
-		sl.bottom = x.extent.end.line
-		sl.filename = x.extent.start.file.name
-		#print(x.kind,sl.top,sl.bottom)
-		d = c_cfg.cfg[sl.kind]
-		sl.invalid = d is None
-		if sl.invalid:
-			return
-		
-		#print(ast_hint)
-		cvs = list(x.get_children())
[…]

### 2019-01-17 gen_ast_data.py

@@ -1,0 +1,176 @@
+#! /usr/bin/env /home/satos/sotsuron/neural_decompiler/python_fix_seed.sh
+
+class InvalidToken(Exception):
+	pass
+
+data = []
+vocab_src = set([])
+vocab_dst = set([])
+types = set([])
+
+import collections 
+import os
+import sys
+import random
+import asm_objd_conv
+import csrc2ast
+
+def getsub(fn,s):
+	if fn[-len(s):]==s:
+		return fn[:-len(s)]
+	else:
+		return None
+
+os.chdir('./build_ast_save_csrc')
+srcs = list(filter(lambda x: x is not None,map(lambda x: getsub(x,'.objd'),os.listdir('.'))))
+#srcs = ['cat']
+
+len_srcs = len(srcs)
+idx_srcs = 0
+for fn in srcs[:10]:
+	print(fn)
+	idx_srcs += 1
+	if idx_srcs % 100 == 0:
+		sys.stderr.write('finish %d/%d\n' % (idx_srcs,len_srcs))
+	
+	with open(fn + '.s') as fp:
+		asm = fp.read()
+	with open(fn + '.objd') as fp:
+		objd = fp.read()
+		if objd.count('\n')<=5:
+			continue
+	try:
+		#print(asm,objd)
+		#exit()
+		ds = asm_objd_conv.get_line_from_list(asm,objd)
+	except ParseErr as s:
+		#print(s)
+		continue
+	#print(ds)
+	
+	astdata = csrc2ast.src2ast(fn + '.tokenized.c',fn + '.parsed').subexpr_line_list()
+
+	nibeki = [1<<(i*8) for i in range(8)]
+	def asm_trim(v):
+		if v in x64_opcodes_registers:
+			return v
+		elif v[:6]=='LABEL_':
+			return v
+		elif v[:2]=='0x':
+			d = int(v[2:],0x10)
+			if d <= 256 or ((d + 256) & 0x1ffffffffffffff00) in nibeki:
+				return v
+			else:
+				return '__HEX__'
+		else:
+			print('unknown asm token:',v,'in file',fn)
+		raise InvalidToken
+			
+				
+	
+	LABEL_MAX = 60
+	ds = list(map(lambda i_d: (i_d[0],list(map(asm_trim,i_d[1]))),ds))
+	for _,d in ds:
+		vocab_dst |= set(filter(lambda x: x[:6] != 'LABEL_',d))
+	vocab_dst |= set(['LA_%d' % i for i in range(LABEL_MAX+1)])
[…]

### 2019-01-17 model_rnn.py

@@ -19,7 +19,7 @@ class Seq2seq(chainer.Chain):
 		with self.init_scope():
 			self.embed_x = L.EmbedID(n_source_vocab, n_units)
 			self.embed_y = L.EmbedID(n_target_vocab, n_units)
-			self.encoder = L.NStepLSTM(n_layers, n_units, n_units, 0.1)
+			self.encoder = L.NStepBiLSTM(n_layers, n_units, n_units, 0.1)
 			self.decoder = L.NStepLSTM(n_layers, n_units, n_units, 0.1)
 			self.W = L.Linear(n_units, n_target_vocab)
 
@@ -33,7 +33,7 @@ class Seq2seq(chainer.Chain):
 	def forward(self, xs, ys):
 		#print(xs,ys)
 		#exit()
-		xs = [x[::-1] for x in xs]
+		#xs = [x[::-1] for x in xs]
 		
 		eos_dst = self.xp.array([self.v_eos_dst], np.int32)
 		ys_in = [F.concat([eos_dst, y], axis=0) for y in ys]

### 2019-01-17 model_seq2tree.py

@@ -1,5 +1,3 @@
-#coding: utf-8
-
 import numpy as np
 import chainer
 import chainer.links as L
@@ -9,111 +7,201 @@ from chainer.training import extensions
 from chainer import serializers
 
 
-
-
-
-def preprocess_train_data(seq,tree):
 	
-
-
-
-
 def sequence_embed(embed, xs):
-	if len(xs[0].shape) == 1: #通常の1次元配列のやつ
-		x_len = [len(x) for x in xs]
-		x_section = np.cumsum(x_len[:-1])
-		ex = embed(F.concat(xs, axis=0))
-		exs = F.split_axis(ex, x_section, 0)
-		return exs
-	else:
-		ls = len(embed)
-		ds = [sequence_embed(embed[i],[x[i] for x in xs]) for i in range(ls)]
-		res = F.concat([y, eos_dst], axis=1)
-		return res
+	x_len = [len(x) for x in xs]
+	x_section = np.cumsum(x_len[:-1])
+	ex = embed(F.concat(xs, axis=0))
+	exs = F.split_axis(ex, x_section, 0)
+	return exs
 
+
+# from https://arxiv.org/pdf/1409.0473.pdf. Global attention.
+class Attention(chainer.Chain):
+	def __init__(self, n_units):
+		super(Attention, self).__init__()
+		with self.init_scope():
+			self.att_W = L.Linear(n_units, n_units)
+			self.att_U = L.Linear(n_units*2, n_units)
+			self.att_v = L.Linear(n_units, 1)
+		
+		self.n_units = n_units
+		self.Uhxs = None
+	
+	def init_hxs(self,hxs):
+		self.hxs = hxs
+		self.Uhxs = self.att_U(hxs)
+		self.Uhxs_len = hxs.shape[0]
+	
+	def forward(self,nhx):
+		nhx_for_att = nhx[-1]
+		Wnhx = self.att_W(nhx_for_att)
+		#print(Wnhx.shape,Uhxs.shape)
+		#print((Wnhx + Uhxs).shape)
+		
+		att_rates = F.softmax(F.reshape(self.att_v(
+				F.tanh(
+					Wnhx + self.Uhxs
+				)
+		),(1,self.Uhxs_len)))
+		#print(hxs.shape,att_rates.shape)
+		#print(att_rates)
+		#print(F.matmul(att_rates,hxs).shape)
+		ctx = F.matmul(att_rates,self.hxs)[0]
+		#print(ctx.shape)
+		return ctx
+		
[…]

### 2019-01-17 tokenizer.py

@@ -1,20 +1,21 @@
+import subprocess
 
-
-def conv(fn):
-	if d == 0:
-		d = subprocess.call('clang -Xclang -dump-tokens -fsyntax-only %s.pp.c > /dev/null 2> %s.tokenized' % (fn,fn),shell=True)
-	
-		with open('%s.tokenized' % fn,"r") as fp:
-			s = fp.read()
-		
-		if '__asm__' in s: #避けたい...
-			d = -1
-		
-		ts = ""
+devnull = open('/dev/null','w')
+def tokenize(fn):
+	global devnull
+	p = subprocess.Popen(['clang','-Xclang','-dump-tokens','-fsyntax-only',fn],stdout=devnull,stderr=subprocess.PIPE)
+	_,s = p.communicate()
+	s = s.decode()
+	#print(s)
+	res = 0
+	if len(s)>0:
+		ts = []
+		bc = ""
 		for cs in s.split('\n'):
 			#print(cs)
 			cs = "'".join(cs.split("'")[1:-1])
-			ts += cs + '\n'
-	
-		with open('%s.tokenized.c' % fn,"w") as fp:
-			fp.write(ts)
+			ts.append(cs)
+		return ts
+	else:
+		return None	
+

### 2019-01-17 train.py

@@ -11,6 +11,8 @@ from chainer import serializers
 
 from model_rnn import Seq2seq
 from model_rnn_with_att import Seq2seq_with_Att
+from model_seq2tree import Seq2Tree,ast2str,ast2token_seq
+
 
 def convert(batch, device):
 	def to_device_batch(batch):
@@ -27,18 +29,22 @@ import code
 import edit_distance
 import random
 import pickle
+import csrc2ast
 
 
 
-def main():
+def init_seq2seq():
 	n_layer = 4
 	n_unit = 128
 	
 	n_maxlen = 100
 	
-	with open('data.pickle','rb') as fp:
-	#with open('data_simple.pickle','rb') as fp:
-			(data,c_vocab,asm_vocab) = pickle.load(fp)
+	with open('data_with_gcc_binary.pickle','rb') as fp:
+			(data,c_vocab) = pickle.load(fp)
+			asm_vocab = [i for i in range(256)]
+	
+	#with open('data_with_asmstring.pickle','rb') as fp:
+	#		(data,c_vocab,asm_vocab) = pickle.load(fp)
 	
 	#data.data = list(filter(lambda xy: len(xy[0])<20 and len(xy[1])<10,data.data))
 	data = list(filter(lambda xy: len(xy[1])<n_maxlen,data))
@@ -64,10 +70,125 @@ def main():
 	dst_vocab_len = len(c_vocab)
  
 	model = Seq2seq(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_src, v_eos_dst, n_maxlen)
-	#serializers.load_npz('models/iter_100__time_2019_01_10_02_01_29.npz',model)
+	#serializers.load_npz('models/iter_5600_editdist_0.866712_time_2019_01_15_04_50_45.npz',model)
 	#serializers.load_npz('save_models/models_prestudy_edit_dist_0.65/iter_47600__edit_dist_0.691504__time_2018_12_28_01_36_30.npz',model)
+	
+	
+	#ddata  = list(map(lambda xy: np.array(xy[0] + (maxlen_asm - len(xy[0])) * [v_eos],np.int32),data.data))
+	#dlabel = list(map(lambda xy: np.array(xy[1] + (maxlen_src - len(xy[1])) * [v_eos],np.int32),data.data))
+	ddata  = list(map(lambda xy: np.array(xy[0] + [v_eos_src],np.int32),train_data))
+	dlabel = list(map(lambda xy: np.array(xy[1] + [v_eos_dst],np.int32),train_data))
[…]

### 2019-01-17 type2tree.py

@@ -1,0 +1,59 @@
+from pycparser import c_parser,c_ast,plyparser
+
+parser = c_parser.CParser()
+
+import code
+
+
+kvs = {}
+def ty2tree(ty):
+	try:
+		ki = parser.parse('int _ = (' + ty + ')0;', filename='<stdin>')
+	except plyparser.ParseError:
+		return
+	ki = ki.ext[0].init.to_type
+	#print(type(ki))
+	#return
+	#code.interact(local={'ki':ki})
+	
+	def f(t):
+		if type(t) is c_ast.TypeDecl:
+			print(t)
+			code.interact(local={'t':t})
+		attrs = list(filter(lambda x: x not in ['coord', '__weakref__'], list(t.__slots__)))
+		#print(type(t),attrs)
+		for d in attrs:
+			nv = t.__getattribute__(d)
+			if type(nv).__module__ == 'pycparser.c_ast':
+				f(nv)
+			elif type(nv) is list:
+				for knv in nv:
+					if type(knv).__module__ == 'pycparser.c_ast':
+						f(knv)
+		
+		
+		def g(v):
+			rt = type(v)
+			if type(v) is list and len(v)>0:
+				rt = (rt,type(v[0]))
+			return rt
+		
+		tt = type(t)
+		attrs_types = list(map(lambda x: (g(t.__getattribute__(x)),x),attrs))
+		if tt in kvs.keys():
+			kvs[tt] |= set([tuple(attrs_types)])
+		else:
+			kvs[tt] = set([tuple(attrs_types)])
+
+	f(ki)
+#def tree2tys(ty):
+#	
+
+
+if __name__=='__main__':
+	import pickle
+	with open('node_expand_data.pickle','rb') as fp:
+		d = pickle.load(fp)
+	for t in list(d['type']):
+		ty2tree(t)
+	print(kvs)

### 2019-01-18 texs/paper_base.tex
maybe ast data generation worked

@@
 
-\section{Modelings}
+\section{Modeling}
 
@@
 \subsection{LSTM}
+%72 words.
 LSTM (Long Short-Term Memory) is a unit of Recurrent Neural Network. 
@@
 
+% 477 words.
 LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the seq2seq (sequence to sequence) model.
-SMT is the task which tries to translate one sentense $sx$ written in a language L into the sentense $sy$ written in another a language M.
+SMT is the task which tries to translate one sentense $sx$ written in one language into the sentense $sy$ written in another language.
 
@@
 The purpose of the decoder network is to estimate the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $. 
-
 The training process is carried out as follows. 
@@
 The inference is obteining $ \argmax_{sy} p(sy|sx) = \argmax_{sy} \prod_{k=1}^n p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
-Calculating argmax directly is time consuming, so we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_n]$ sequentially.
+Calculating argmax directly is time consuming, so we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_m]$ sequentially.
 First, $sy_1$ is calculated as $ \argmax_{sy_1} p(sy_1|sx,[]) $, where distribution $ p(sy_1|sx,[]) $ is approximated by 
-$ softmax(W_dec(dec_{1})) = softmax(W_dec(LSTM_{dec}(enc_{n},y_begin))) $. Then, the next
+$ softmax(W_dec(dec_{1})) = softmax(W_dec(LSTM_{dec}(enc_{n},y_begin))) $. 
+Then, the next token $sy_2 = \argmax_{sy_1} p(sy_2|sx,[sy_2]) $ is calculated from $ dec_{1} $ and the vector embedding of $sy_1$, and so on.
+When the token $sy_{m+1}$ is the EOF token, generating process is stopped and the sequence $ [sy_1, \dots sy_m]$ is returned as the inference result.
+
+% (TODO) このへんで 図を入れる
+% (TODO) 理由/気持ち について述べたいですね。
+
+% (TODO) BiLSTMとmulti-layerについてさらっと
+
+\subsection{Attention}
+Attention is a extension module of Seq2Seq model to improve the quality of translation.
+
+\subsection{Seq2Tree}
 

### 2019-01-18 c_cfg.py

@@ -1,6 +1,6 @@
 from clang.cindex import CursorKind
 import pycparser
-import c_ast
+import my_c_ast
 
 # liteeal can be expr
 # expr can be stmt
@@ -59,7 +59,7 @@ nont_reduce = {
 	],
 	
 	#from c_type_cfg
-	'type': [
+	'type_type': [
 		pycparser.c_ast.ArrayDecl,
 		pycparser.c_ast.FuncDecl,
 		pycparser.c_ast.TypeDecl,
@@ -68,22 +68,27 @@ nont_reduce = {
 	'paramlist': [
 		pycparser.c_ast.ParamList
 	],
+	'type': [
+		pycparser.c_ast.Typename
+	],
 	'typename': [
 		pycparser.c_ast.Typename
 	],
 	'typedecltype': [
 		pycparser.c_ast.Struct,
 		pycparser.c_ast.Union,
+		pycparser.c_ast.Enum,
 		pycparser.c_ast.IdentifierType,
 	],
 }
-
 
 reduced_type = dict(sum(map(lambda ds: list(map(lambda v: (v,ds[0]),ds[1])), nont_reduce.items()),[]))
 #def get_node_type
 
 for v in nont_reduce['expr']:
 	nont_reduce['stmt'].append(v)
+
+#print(nont_reduce)
 
 # None is for pass.
 cfg = {
@@ -109,7 +114,7 @@ cfg = {
 	CursorKind.DEFAULT_STMT: ['stmt'],
 	CursorKind.DO_STMT: ['stmt','expr'],
 	CursorKind.ENUM_CONSTANT_DECL: ['name',['expr','option']],
-	CursorKind.ENUM_DECL: ['name',['decl','list']],
+	CursorKind.ENUM_DECL: ['enumname',['decl','list']],
 	CursorKind.FIELD_DECL: ['type','name',['expr','option']], # [int hogehuga] in [struct{int hogehuga};]
 	CursorKind.FLOATING_LITERAL: ['floatliteral'],
 	CursorKind.FOR_STMT: [['stmt','option'],['expr','option'],['expr','option'],'stmt'],
@@ -131,7 +136,7 @@ cfg = {
 	CursorKind.PURE_ATTR: None, # __attribute__((__pure__))    skip. (or remove?)
 	CursorKind.RETURN_STMT: [['expr','option']],
 	CursorKind.STRING_LITERAL: ['stringliteral'],
[…]

### 2019-01-18 c_type_cfg_save.py

@@ -107,19 +107,7 @@ nont_reduce = {
 	],
 }
 
-cfg = {
-	pycparser.c_ast.Typename: [(('string','list'),'quals'),('type','type')],
-	
-	pycparser.c_ast.ArrayDecl: [(('expr','option'),'dim'),('type','type')],
-	pycparser.c_ast.TypeDecl: [(('string','list'),'quals'),('typedecltype','type')],
-	pycparser.c_ast.PtrDecl: [(('string','list'),'quals'),('type','type')],
-	pycparser.c_ast.FuncDecl: [(('paramlist','option'),'args'),('type','type')],
-	pycparser.c_ast.ParamList: [(('typename','list'),'params')],
-	
-	pycparser.c_ast.Struct: [('string','type_name')],
-	pycparser.c_ast.Union: [('string','type_name')],
-	pycparser.c_ast.IdentifierType: [(('string','list'),'names')],
-}
+
 
 
 

### 2019-01-18 csrc2ast.py

@@ -18,7 +18,7 @@ Config.set_library_path("/usr/lib/llvm-7/lib")
 
 
 import tokenizer
-import c_ast
+import my_c_ast
 
 def ast2token_seq(data,terminal_ids):
 	ast = c_ast.AST([],isnull=True).load_astdata(data,terminal_ids)
@@ -64,17 +64,17 @@ def src2ast(fn,pfn):
 	index = Index.create()
 	ast = index.parse(fn).cursor
 	#sys.stdin.read()
-	res = c_ast.AST(ast,ast_hint,src)
-	res.treenize()
-	resrc = res.show()
-	resrc = 'struct __va_list_tag{    unsigned int gp_offset;    unsigned int fp_offset;    void *overflow_arg_area;    void *reg_save_area;};' + resrc
-	return resrc
+	res = my_c_ast.AST(ast,ast_hint,src)
+	res.get_astdata()
+	#resrc = res.show()
+	#resrc = 'struct __va_list_tag{    unsigned int gp_offset;    unsigned int fp_offset;    void *overflow_arg_area;    void *reg_save_area;};' + resrc
+	return res
 
 
 
 
 
-fn = 'tesx'
+fn = 'y'
 if __name__ == '__main__':
 	import os
 	os.system('clang -Xclang -dump-tokens -fsyntax-only ' + fn + '.c 2>&1 |  sed -e "s/[^\']*\'\(.*\)\'[^\']*/\\1/" > ' + fn + '.tokenized.c')
@@ -83,6 +83,33 @@ if __name__ == '__main__':
 		exit()
 	
 	os.system('clang -Xclang -ast-dump -fsyntax-only %s.tokenized.c > %s.astdump 2>/dev/null' % (fn,fn))
-	ass = src2ast('%s.tokenized.c' % fn,'%s.astdump' % fn)
+	csrc = open('%s.tokenized.c' % fn,'r').read().split('\n')
+	ast = src2ast('%s.tokenized.c' % fn,'%s.astdump' % fn)
+	aststr = ast.show()
 	with open('t.c','w') as fp:
-		fp.write(ass)
+		fp.write(aststr)
+	#print(ast.get_astdata())
+	#c_cfg.data_miyasui(ast.get_astdata())
+	c_cfg.validate_astdata(ast.get_astdata(),CursorKind.TRANSLATION_UNIT)
+	print('validate passed')
+	ds = ast.subexpr_line_list()
[…]

### 2019-01-18 my_c_ast.py

@@ -55,8 +55,11 @@ class AST:
 		return res
 	
 	def __init__(sl,x,ast_hint=None,src=None,*,isnull=False):
+		sl.astdata = None
+		sl.size = 0
 		if isnull:
 			sl.kind = None
+			sl.isnullast = True
 			return
 		global struct_decl_list
 		sl.src = src
@@ -234,7 +237,11 @@ class AST:
 			#if na == 'satos_temporary_struct_union_decl_16':
 			#	sl.debug(x)
 			assert len(na)>0
-			tcs = [AST(('name',na)),] + tcs
+			if sl.kind == CursorKind.STRUCT_DECL:
+				nana = 'structname'
+			else:
+				nana = 'unionname'
+			tcs = [AST((nana,na)),] + tcs
 		elif sl.kind == CursorKind.FUNCTION_DECL:
 			#sl.debug(x)
 			na = x.spelling
@@ -258,7 +265,7 @@ class AST:
 			tcs = [re,AST(('memberrefop',op)),AST(('name',na))]
 		elif sl.kind ==	CursorKind.ENUM_DECL:
 			na = x.spelling
-			tcs = [AST(('name',na))] + tcs
+			tcs = [AST(('enumname',na))] + tcs
 		elif sl.kind ==	CursorKind.ENUM_CONSTANT_DECL:
 			na = x.spelling
 			tcs = [AST(('name',na))] + tcs
@@ -297,159 +304,225 @@ class AST:
 			return 'INVALID'
 	
 	
-	def treenize(sl):
-		if type(sl.kind) is str:
-			d = sl.leafdata
-			if sl.kind in c_cfg.node_id_data.keys():
-				c_cfg.node_id_data[sl.kind] |= set([d])
-			else:
-				c_cfg.node_id_data[sl.kind] = set([d])
-		else:
-			expt = c_cfg.cfg[sl.kind]
-			for c in sl.children:
-				c.treenize()
+	
+	def get_alignmented_children(sl):
+		expt = c_cfg.cfg[sl.kind]
+		def f(v):
+			nk = v.kind
+			if type(nk) is not str:
+				nk = c_cfg.reduced_type[nk]
+			return nk
 			
-			#print(sl.kind)
-			def f(v):
-				nk = v.kind
-				if type(nk) is not str:
-					nk = c_cfg.reduced_type[nk]
-				return nk
-								
-			cks = list(map(f,sl.children))
-			#print(expt,cks)
+		cks = list(map(f,sl.children))
+		#print(expt,cks)
 			
[…]

### 2019-01-18 train.py

@@ -152,12 +152,8 @@ def init_seq2tree():
 	
 	n_maxlen = 100
 	
-	with open(
-			(data,c_vocab) = pickle.load(fp)
-			asm_vocab = [i for i in range(256)]
-	
-	with open('data_ast.pickle','rb') as fp:
-			(data,c_vocab,asm_vocab) = pickle.load(fp)
+	with open('data_asm_ast.pickle','rb') as fp:
+			(data,asm_vocab) = pickle.load(fp)
 	
 	#data.data = list(filter(lambda xy: len(xy[0])<20 and len(xy[1])<10,data.data))
 	data = list(filter(lambda xy: len(xy[1])<n_maxlen,data))
@@ -177,10 +173,6 @@ def init_seq2tree():
 	v_eos_src = len(asm_vocab)
 	asm_vocab += ['__EOS__']
 	src_vocab_len = len(asm_vocab)
-	
-	v_eos_dst = len(c_vocab)
-	c_vocab += ['__EOS__']
-	dst_vocab_len = len(c_vocab)
  
 	model = Seq2Tree(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_src, v_eos_dst, n_maxlen)
 	#serializers.load_npz('models/iter_5600_editdist_0.866712_time_2019_01_15_04_50_45.npz',model)
@@ -253,7 +245,7 @@ def init_seq2tree():
 
 
 def main():
-	model,dataset,translate = init_seq2seq()
+	model,dataset,translate = init_seq2tree()
 	
 	optimizer = chainer.optimizers.Adam()
 	optimizer.setup(model)

### 2019-01-19 texs/paper_base.tex
save

@@
 The training process is carried out as follows. 
-First, $sy$ is tokenized and embedded to vector representation $vy_{1} \dots vy_{m}$ in the same way as $sx$.
+First, $sy$ is tokenized and appended token $ EOS $ for indicating the end of the sequence, then embedded to vector representation $vy_{1} \dots vy_{m}$ in the same way as $sx$.
 And from the start vector $y_begin$ and encoded input $ enc_{n} $, first internal state $ dec_{1}$ is calcuated as $ LSTM_{dec}(enc_{n},y_begin) $.
 Then, with for all vector $vy_{k}$, $dec_{k+1}$ is calculated as $ LSTM_{dec}(dec_{k},vy_{k}) $.
-Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_dec $ then softmaxed to a probability vector $ py_{k} $.
+Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_dec $ then softmaxed to generate a probability vector $ py_{k} $.
 The probability vector $ py_{k} $ is intended to represent the probability distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
-% (TODO)このへんで V_eosについて述べないといけない
 So the network is trained to reduce the difference between predicted distribution $ py_{k} $ and actual distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
@@
 Then, the next token $sy_2 = \argmax_{sy_1} p(sy_2|sx,[sy_2]) $ is calculated from $ dec_{1} $ and the vector embedding of $sy_1$, and so on.
-When the token $sy_{m+1}$ is the EOF token, generating process is stopped and the sequence $ [sy_1, \dots sy_m]$ is returned as the inference result.
+When the token $sy_{m+1}$ is the $ EOS $ token, generating process is stopped and the sequence $ [sy_1, \dots sy_m]$ is returned as the inference result.
 
@@
 \subsection{Seq2Tree}
+% 184 words
+Compare to natural languages, programming languages obeys rigid grammer, wich is usually context free grammer,  
+and it is reasonable to consider the grammer of the programming language in generating programs.
+Seq2Tree is a model for generating tree-structured output from sequence input.
+This model is introduced in \cite{Seq2Tree} for generating programs from the program specification written in natural languages.
+This task is similer to our task, which aims to generate programs from the sequence of the assembly code, so we implemented this model in the experiment.
+
+Now, we will describe about the Seq2Tree model.
+Seq2Tree model is composed of two modules, the encoder netwrok and the decoder network.
+The encoder network of Seq2Tree model is the same as the encoder network of Seq2Seq model. It summerize the input sequence into one fixed length vector.
+
+The decoder network is a network for generating tree structured output. 
+In this paper, our implemented model is different from the model in \cite{Seq2Tree}. 
+So first, we briefly describe the model implemented in the paper, and then, we describe our model.
+
+\subsubsection{Previous Model}
+% 312 words
+In algorithmic parspective, the inference of the Seq2Seq model tries to generate sequence one by one, from the first token to the last.
+% The Seq2Tree model also tries to generate tree structure one by one, with depth-first order.
+The inference of the SeqTree model starts from the start symbol, and recursively expand the nonterminal symbols in depth-first order.
+
+The tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
+Suppose the tree $ty$ is generated by the action sequence $ [a_1, \dots a_m] $, 
+where $ a_k $ is the action which expands left-most symbol of the nonterminal symbol in the tree generated by the action sequence $ [a_1, \dots a_{k-1}] $. 
+Then, the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(a_k|sx,[a_1, \dots a_{k-1}]) $, 
+so the Seq2Seq model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
+calculating $ LSTM_{dec}(dec_{k},av_{k}) $ for estimating $p(a_{k+1}|sx,[a_1, \dots a_{k}]) $.
+
+In the paper, they additionaly tries to use the information which is peculiar to the tree structure. 
+For expanding the node $d$, they also use the information of node type $ nf_{d} $ and the parent action $p_{d}$ from which $d$ is generated.
+And they calculalte $ LSTM_{dec}(dec_{k},[av_{k}; nfv_{d}; pv_{d}; ctx_{k}]) $ instead of $ LSTM_{dec}(dec_{k},av_{k}) $, 
+where $nfv_{d},pv_{d}$ are the vector embedding of $nf_{d},p_{d}$, and $ctx_{k}$ is the attention at k.
+
+They also used devised method for generating terminal symbols, because they need to copy the name of some variables from the program specification.
+But in our case, we don't need copy the information from the input, because the name information is lost when compiling, so we omit the discriptionp of this copy method.
+
+\subsubsection{Our Model}
+Our model tries to exploit the intuitive that the each node of the tree is basically independent from its sibling.
 

### 2019-01-19 gen_ast_data.py

@@ -9,7 +9,7 @@ vocab_dst = set([])
 types = set([])
 
 x64_opcodes_registers = [
-	'setbe', 'bl', 'addsd', 'cmovge', 'divss', 'es', 'movs', 'fchs', 'rsi', 'cvtsi2sd', 'ror', 'cmovns', 'fmulp', 'andpd', 'r10d', 'setb', 'setne', '[', 'rcx', 'movaps', 'shr', 'cvttsd2si', 'xmm6', 'esi', 'cx', 'cmovg', 'cmovae', 'r15', 'movdqa', ':', 'and', 'setnp', 'fldcw', 'DWORD', 'fnstcw', ')', 'fldpi', 'fprem', 'al', 'WORD', '2', 'scas', 'sub', 'cvtpd2ps', 'or', 'ret', 'ja', 'mulsd', 'dil', 'r14b', 'r9d', 'mfence', 'QWORD', 'xmm0', 'ucomisd', 'fs', 'xmm2', 'fld', 'unpcklpd', '*', 'fstsw', 'si', 'sete', 'tzcnt', 'fdivp', 'dl', 'test', 'sahf', 'rax', '(', 'fsubp', 'sil', 'movd', 'cmp', 'r13', 'shrd', 'call', 'jp', 'bx', 'jg', 'add', '1', '8', 'subsd', 'divsd', 'setg', 'sqrtss', 'r12b', 'jae', 'leave', 'xmm5', 'imul', 'cmpxchg', 'cvttss2si', 'rsp', 'fsubrp', 'r11b', 'cdqe', 'jnp', 'movzx', 'cmova', 'ds', 'lea', 'andps', 'r9b', 'r15d', 'st', 'unpcklps', ',', 'idiv', 'xmm4', 'setp', 'movsx', 'TBYTE', 'mulss', 'js', 'repnz', 'setge', 'r8b', 'edi', 'stos', 'eax', 'xmm7', 'syscall', 'cdq', 'jle', 'fistp', 'sar', 'ah', 'rol', 'pop', 'ucomiss', 'push', 'jge', 'xmm1', 'movsd', 'xmm3', 'cmovbe', 'movapd', '0', 'addss', 'seta', 'cbw', 'subss', 'ecx', 'movabs', 'fldz', 'jl', 'int', 'cmovs', 'cvtps2pd', 'XMMWORD', ']', 'jne', 'xorpd', 'orpd', 'cmovl', 'lock', 
[…]

### 2019-01-19 train.py

@@ -30,6 +30,7 @@ import edit_distance
 import random
 import pickle
 import csrc2ast
+import c_cfg
 
 
 
@@ -144,8 +145,9 @@ def init_seq2seq():
 	return (model,dataset,translate)
 
 
-
+train_iter_step = None
 def init_seq2tree():
+	global train_iter_step
 	n_layer = 4
 	n_unit = 128
 	
@@ -178,7 +180,7 @@ def init_seq2tree():
 	src_vocab_len = len(asm_vocab)
  
 	model = Seq2Tree(n_layer, src_vocab_len, c_syntax_arr, n_unit, v_eos_src, n_maxdepth)
-	#serializers.load_npz('models/iter_5600_editdist_0.866712_time_2019_01_15_04_50_45.npz',model)
+	serializers.load_npz('models/iter_200_time_2019_01_19_09_41_08.npz',model)
 	#serializers.load_npz('save_models/models_prestudy_edit_dist_0.65/iter_47600__edit_dist_0.691504__time_2018_12_28_01_36_30.npz',model)
 	
 	#print(train_data[0])
@@ -200,7 +202,7 @@ def init_seq2tree():
 			ts.append(sd)
 		return ts
 	
-	logt = 0
+	logt = 200
 	
 	def calcurate_edit_distance():
 		ratio = 0.0
@@ -219,29 +221,33 @@ def init_seq2tree():
 	
 	@chainer.training.make_extension()
 	def translate(trainer):
-		eds = calcurate_edit_distance()
-		print('edit distance:',eds)
 		nonlocal logt
 		logt += train_iter_step
-		with open('log/iter_%s_editdist_%f_time_%s.txt' % (logt,eds,getstamp()),'w') as fp:
-			res = ""
-			for _ in range(10):
-				source,_, target = test_data[np.random.choice(len(test_data))]
-				result = model.translate([model.xp.array(source)])[0]
+		serializers.save_npz('models/iter_%s_time_%s.npz' % (logt,getstamp()),model)
+		try:
+			eds = calcurate_edit_distance()
+			print('edit distance:',eds)
+			with open('log/iter_%s_editdist_%f_time_%s.txt' % (logt,eds,getstamp()),'w') as fp:
+				res = ""
+				for _ in range(10):
+					source,_, target = test_data[np.random.choice(len(test_data))]
+					result = model.translate([model.xp.array(source)])[0]
 				
-				target = tree2normalizedsentense(target,normalize=False)
-				result = tree2normalizedsentense(result,normalize=False)
[…]

### 2019-01-20 texs/paper_base.tex
add .c for tex

@@
 
+For
+
 % (TODO) BiLSTMとmulti-layerについてさらっと
@@
 \subsubsection{Our Model}
-Our model tries to exploit the intuitive that the each node of the tree is basically independent from its sibling.
+Our model tries to exploit the intuitive that each node of the tree is basically independent from its sibling.
+This intuition is not true when the compiler optimizes the assembler. 
+However
 
@@
 
+\subsection{Assembly Code Preprocess}
 The assemblies were preprocessed in two ways.
@@
 
-The C source codes were preprocessed like the second way of the assembly preprosess.
-C source code was tokenized to the sequence and preprocessed with following modifications.
+\subsection{C Code Preprocess}
+The C source codes were parsed to AST by the \cite{clang} and its Python bindings together with \cite{pycparser}, 
+because all of the tools are individualy not sufficient for generating dataset.
+Then, the AST is converted to input data by following modifications.
+
 \begin{itemize}
-\item Function names and variable names were renamed like $\alpha$-conversion.
-\item Big integer values were substituted too. 
-\item All string literals were replaced to the {\sl \_\_STRING\_\_} symbol.
+\item The variable-ary nodes and optional nodes are converted. 
+For example, the {\sl CompoundStatement} node has variable number of statements. 
+We converted such list of nodes to the chains of concatnation and terminal, like a list representation in functional language.
+Another example is the  {\sl If} statement, whose {\sl else} clausure are sometimes missing. 
+We converted such optional node to the alternative of some node and Null node, like a optional data structure in functional language.
+\item The variable names, function names, label names, or type names were renamed like $\alpha$-conversion.
+\item There are four type of literals in C language. 
+The integer literal less than 256 is preserved, and the literal greater than 256 is clipped to 256.
+The string, float and character literals are converted to {\sl \_\_LITERAL\_(string|float|char)\_\_} simbol.
+
+Modifying the node to indicate the value in the assembly code corresponding to the literal is also conceibable way,
+but we couldn't implement this because of its technical difficalty, so this is left to future work.
 \end{itemize}
 
-% (TODO)木状にする方法について述べる。
+The AST is used for Seq2Tree model dataset as it is.
+Also, the AST is converted to C token sequence for Seq2Seq model dataset.
 
 \section{Model Configuration}
-The training model was implemented with Chainer.
+The training model was implemented with Chainer. Source codes are avaiable at \url{}.
+
 (TODO)レイヤ数、ロスについてのべる。
 
+\section{Training and Testing}
+
+We trained the model to reduce the cross-entropy loss between predicted and actual conditional probability.
+The conditional probability is the probability of next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for Seq2Seq model, 
+and the probability of next action $p(a_{k+1}|sx,[a_1, \dots a_{k}]) $ for Seq2Tree model.
+
+We calculated the accuracy with the edit distance ratio between ground truth and output source code from the model.
+Here, the edit distance ratio between two strings means the Levenshtein distance divided by the longer length of the strings.
+For the Seq2Seq model, the distance is
+
 \chapter{Results}
+
+We tested our methods for
+
 (TODO)seq2seq、アテンション付きseq2seq、seq2treeとバイナリそのまま/逆アセンブル後 の6パターンのデータを出す。

### 2019-01-20 gen_ast_data.py

@@ -6,6 +6,15 @@ class InvalidToken(Exception):
 data = []
 vocab_src = set([])
 vocab_dst = set([])
+
+import pickle
+with open('dataset_asm_ast/vocab_asm.pickle','rb') as fp:
+	vocab_dst = pickle.load(fp)
+
+import c_cfg
+with open('dataset_asm_ast/c_trans_array.pickle','wb') as fp:
+	pickle.dump(c_cfg.trans_array,fp)
+
 types = set([])
 
 x64_opcodes_registers = [
@@ -19,7 +28,7 @@ import random
 import asm_objd_conv
 import csrc2ast
 import my_c_ast
-import c_cfg
+
 
 def getsub(fn,s):
 	if fn[-len(s):]==s:
@@ -31,10 +40,37 @@ os.chdir('./build_ast_save_csrc')
 srcs = list(filter(lambda x: x is not None,map(lambda x: getsub(x,'.objd'),os.listdir('.'))))
 #srcs = ['cat']
 
+
+	
 len_srcs = len(srcs)
 idx_srcs = 0
 
+file_start_num = 0
 file_num_sum = 0
+data_set_num = 0
+
+
+def dump_save_data():
+	global data,vocab_dst,file_start_num,file_num_sum,data_set_num
+	data = list(map(lambda xy: (
+						list(map(lambda t: vocab_dst.index(t),xy[0])),
+						xy[1],
+						xy[2]
+				),data))
+	dfn = file_num_sum - file_start_num 
+	dls = len(data)
+	print('save idx:',data_set_num)
+	print('file num diff:',dfn)
+	print('data length:',dls)
+	
+	import pickle
+	with open('../dataset_asm_ast/data_%d.pickle' % data_set_num,'wb') as fp:
+		pickle.dump((dfn,data),fp)
+	
+	file_start_num = file_num_sum
+	data_set_num += 1
+	data = []
+
 for fn in srcs:
 	print(fn)
 	idx_srcs += 1
@@ -63,10 +99,7 @@ for fn in srcs:
 		print('too long',fn)
 		continue
 	
-	try:
-		astdata = csrc2ast.src2ast(fn + '.tokenized.c',fn + '.parsed').subexpr_line_list()
-	except c_cfg.Oteage:
-		continue
+
 
 	nibeki = [1<<(i*8) for i in range(8)]
 	def asm_trim(v):
[…]

### 2019-01-20 sample_dataset.py

@@ -1,0 +1,30 @@
+import pickle
+
+import random
+
+def sample_dataset():
+	with open('dataset_asm_ast/c_trans_array.pickle','rb') as fp:
+		c_syntax_arr = pickle.load(fp)
+	with open('dataset_asm_ast/vocab_asm.pickle','rb') as fp:
+		asm_vocab = pickle.load(fp)
+	print('start')
+	data = []
+	for i in range(12):
+		with open('dataset_asm_ast/data_%d.pickle' % i,'rb') as fp:
+			nd = pickle.load(fp)[1]
+		
+		print(len(nd))
+		for d in nd:
+			if random.randint(1,12)==1:
+				data.append(d)
+		print('done',i)
+		print('nl',len(data))
+		del nd
+	print(len(data))
+	print('start saving')
+	with open('sampled_asm_ast_dataset.picikle','wb') as fp:
+		print('opened')
+		pickle.dump((data,asm_vocab,c_syntax_arr),fp)
+		print('dumped')
+		
+sample_dataset()

### 2019-01-20 texs/bintree.c

@@ -1,0 +1,24 @@
+struct tree{
+	int key,value;
+	struct tree *l,*r;
+};
+void free(struct tree* p);
+void insert(struct tree** root,struct tree* node){
+	int nk = node->key;
+	struct tree** pos = root;
+	struct tree* now = *root;
+	while(now != 0){
+		if(now->key == nk){
+			now->value = node->value;
+			free(node);
+			return;
+		}
+		if(now->value > nk){
+			pos = &(now->l);
+		} else { 
+			pos = &(now->r);
+		}
+		now = *pos;
+	}
+	*pos = node;
+}

### 2019-01-20 texs/hopper.c

@@ -1,0 +1,27 @@
+function insert {
+    var_30 = arg1;
+    var_14 = *(int32_t *)var_30;
+    var_10 = arg0;
+    goto loc_86;
+loc_86:
+    if (insert != 0x0) goto loc_2e;
+loc_8d:
+    rax = var_10;
+    insert = var_30;
+    return rax;
+loc_2e:
+    if (*(int32_t *)insert != var_14) goto loc_55;
+loc_39:
+    *(int32_t *)(insert + 0x4) = *(int32_t *)(var_30 + 0x4);
+    rax = free(var_30);
+    return rax;
+loc_55:
+    if (*(int32_t *)(insert + 0x4) > var_14) {
+            var_10 = insert + 0x8;
+    }
+    else {
+            var_10 = insert + 0x10;
+    }
+    goto loc_86;
+}
+

### 2019-01-20 texs/snowman.c

@@ -1,0 +1,39 @@
+struct s0 {
+    int32_t f0;
+    int32_t f4;
+    struct s0* f8;
+    struct s0* f16;
+};
+struct s1 {
+    signed char[8] pad8;
+    int64_t f8;
+};
+void fun_53(struct s0* rdi) {
+    struct s1* rbp2;
+    goto rbp2->f8;
+}
+void free(struct s0** rdi, struct s0* rsi) {
+    struct s0* v3;
+    int32_t v4;
+    struct s0** v5;
+    struct s0* v6;
+    v3 = rsi;
+    v4 = v3->f0;
+    v5 = rdi;
+    v6 = *rdi;
+    while (!reinterpret_cast<int1_t>(v6 == free)) {
+        if (v6->f0 == v4) 
+            goto addr_39_4;
+        if (v6->f4 <= v4) {
+            v5 = &v6->f16;
+        } else {
+            v5 = &v6->f8;
+        }
+        v6 = *v5;
+    }
+    *v5 = v3;
+    addr_39_4:
+    v6->f4 = v3->f4;
+    fun_53(v3);
+}
+

### 2019-01-22 texs/paper_base.tex
sarani

@@
 \usepackage{url}
+\usepackage{natbib}
 
@@
 There are various decompilers, but they often output a source code that is not intelligible to humans. 
-In this thesis, we tried to apply machine translation techniques to generate human intelligible decompiled source codes. 
-More specifically, we propose to use recurrent neural networks with attention, which are useful for machine translation. 
+In this thesis, we apply machine translation techniques to generate human intelligible decompiled source codes. 
+More specifically, we propose to use recurrent neural networks with attention, 
+which have been demonstrated to be useful for machine translation. 
 In experiments, we use source codes collected from open source projects and their binary data for training and evaluating the neural networks.
+(TODO)実験結果について述べること(まだ未確定)
 \end{eabstract}
@@
 These days, the amount of malware has been increasing rapidly.
-So the importance to develop malware analysis tools has been rising.
 
-One of these tools is a decompiler, which is a tool for analyzing the behavior of malwares. 
-This tool generates C-like pseudocode which represents the behavior of the malware, and analyst can infer the behavior of the malware from the pseudocode.
-This is much easier compare to analyzing raw binary.
+要参考文献
+So the importance of developing malware analysis tools has been rising.
+要参考文献
+One of these tools is a decompiler, which is a tool for analyzing the behavior of malware. 
+This tool generates a C-like pseudocode which represents the behavior of the malware, and analysts can infer the behavior of the malware from the pseudocode.
+This is much easier compared to analyzing raw binary codes.
 
-However, sometimes a decompiler generate unstructured code, which requires users to make an effort to understand the behavior of the program. 
-This is due to flexibility of the high level language. If the decompiler chooses a human-friendly representation of the language as the result of decompiling, we can analyze malware with less effort.
+However, sometimes a decompiler generates an unstructured code, which requires users to make an effort to understand the behavior of the program. 
+This is due to flexibility of the high level language. If the decompiler chooses a human-friendly representation of the language as a result of decompiling, we can analyze malware with less effort.
 
-In this paper, we apply neural networks to a decompiler to generate human-friendly pseudocode. 
-This idea is originated from \cite{Motoneta}, in which they use Recurrent Neural Networks.
+In this thesis, we apply neural networks to the problem of decompilation to generate human-friendly pseudocodes. 
+This idea is originated from \cite{Motoneta}, in which they used recurrent neural networks.
+They used sequence-to-sequence model, which ignores the structure of the C language code. 
+Therefore, we implemented sequence-to-tree model, which is suggested in \cite{Seq2Tree}, for generating structured C language source code 
+結果が向上していれば(and improving the decompilation accuracy.)といいたい。
 
+従来法の何が悪いのかを説明する．たぶんした。
 (TODO)このあとに今回やる更に具体的な内容とその成果についてが入る。
@@
 \section{Related Works}
+In this section, we review related works.
+
 \subsection{Decompilation with Machine Learning}
+
 Because perfect decompilation is naturally impossible, there are many machine learning applications for decompilation.
 
-% The idea of applying LSTM to decompilation is originated from \cite{Motoneta}.
+In \cite{Motoneta}, they used the seqence-to-sequence approach, which is a popular technique in the machine translation.
 
 In \cite{genetic_decompiler}, they applied genetic programming to decompilation.
-
-(TODO)更にいろいろ説明する(手法をどこまで書くか)
+They prepared big corpus of C source codes, and they repeatedly mutated C code to reduce the difference of the target binary and the compilation result of the source code.
 
@@
 \subsection{Improvement of decompilation results}
-In this paper, we don't try to recover the function name and variable name. 
+In this section, we do not try to recover the function name and variable name. 
 However, for hand-decompilation, sometimes the name can be estimated by the functionality of the variable.
+要参考文献
 For example, assume there is a variable X which seems to have a C struct type and has two fields P and Q.
-And there are two functions F and G which operate with X. 
-The function F receives X and other value V, assigns V to the memory indicated by P, adds 8 to P and increments Q. 
-The function G receives X, subs 8 from P and decrements Q, then returns the value indicated by P.
-In the situation, analyst can estimate X has a name related to {\sl stuck}, and the function F has a name related to {\sl push}, G has a name related to {\sl pop}.
+Also, there are two functions F and G which operate with X. 
+The function F receives X and another value V, assigns V to the memory indicated by P, adds 8 to P and increases Q. 
+The function G receives X, subtracts 8 from P, decreases Q, and returns the value indicated by P.
+In the situation, is is estimated that X has a name related to {\sl stuck}, the function F has a name related to {\sl push},
+ands G has a name related to {\sl pop}.
 
-\cite{name_recover_from_decompile_result} is the paper for tackling this task. 
-In this paper, they try to estimate the name of a variable which appears in the decompilation result of a compiled C program.
+\cite{name_recover_from_decompile_result} tackled this work. 
+In that paper, they tried to estimate the name of a variable which appears in the decompilation result of a compiled C program.
 
 This kind of name estimation also appears in the context of deobfuscation.
+要参考文献
 Deobfuscation is a reverse process of obfuscation.
 Obfuscation is a technique to modify the program source code so that the code becomes hard to understand for humans. 
-Obfuscation is used for hiding the behavior of a program whose source code have to be distributed.
-For example, on the web application, the JavaScript code of the program should be distributed in order to be executed on client web browsers.
-To protect the program from cracking, the JavaScript code are sometimes minified. All comments, newlines, indents are removed and the 
-variable names are substituted to automatically generated meaningless name.
+Obfuscation is used for hiding the behavior of a program whose source code has to be distributed.
+For example, in the web application, a JavaScript code of a program should be distributed in order to be executed on client web browsers.
+To protect the program from cracking, the JavaScript code is sometimes minified.
+All comments, newlines, indents are removed and variable names are substituted to automatically generated meaningless names.
 
-\cite{JSNaughty} apply statistical machine translation for this task.
+\cite{JSNaughty} applied statistical machine translation for this task. 
+They calculated estimated the name of the variable by the functionality of it
 
-\subsection{Neural Networks for Program Synthesis}
+\subsection{Neural Network for Program Generation}
 
-There are so many applications of neural networks for program synthesis. They are summurized in \cite{deep_programming_matome}.
+There are many applications of neural networks for program synthesis. They are summurized in \cite{deep_programming_matome}.
 
-(TODO)最低限Seq2Treeについては触れる。更にいろいろ。
+In this thesis, we applied seq-to-tree model suggested in \cite{Seq2Tree}, because the input of the decompiler is the sequence of machine codes.
+
+For another example, in \cite{coffeescript_to_javascript}, they tried to mutually translate from JavaScript to CoffeeScript, and its inverse.
+In that case, both JavaScript codes and CoffeeScript codes are tree structured, so they suggested tree-to-tree model.
 
@@
 
+In this chapter, we explain about the statistical formalization of the decompilation problem,
+and the neural network models used in the experiment.
 \section{Decompiler}
@@
 
-\subsection{Seq2Seq}
+\subsection{Seq-to-Seq}
 % This model is called seq2seq (sequence to seqence) model.
@@
 % 477 words.
-LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the seq2seq (sequence to sequence) model.
+LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the seq-to-seq (sequence to sequence) model.
 SMT is the task which tries to translate one sentense $sx$ written in one language into the sentense $sy$ written in another language.
 
-Seq2seq model is composed of two modules, the encoder netwrok and the decoder network.
+Seq-to-seq model is composed of two modules, the encoder netwrok and the decoder network.
 
@@
 This process is carried out as follows. 
-First, $sx$ is tokenized to sequence $sx_{1} \dots sx_{n}$, and each token $sx_{k}$ is embedded to vector representation $vx_{k}$. 
+First, $sx$ is tokenized to sequence $sx_{1} \dots sx_{n}$, and each token $sx_{k}$ is embedded to its vector representation $vx_{k}$. 
 Then, the initial LSTM internal state $enc_0$ is intialized randomely, 
-and for each vector $vx_{k}$ and internal state $s{k-1}$, next internal state $enc_{k}$ is calculated as $ LSTM_{enc}(enc_{k-1},vx_{k}) $.
+and $ enc_{1} \dots enc_{n} $ are calculated in accordance with the recursive formula $ enc_{k} = lstm_{enc}(enc_{k-1},vx_{k}) $.
 Finally, the last internal state $ enc_{n}$ is returned as the reduced representation of the input sequence $sx$.
@@
 The training process is carried out as follows. 
-First, $sy$ is tokenized and appended token $ EOS $ for indicating the end of the sequence, then embedded to vector representation $vy_{1} \dots vy_{m}$ in the same way as $sx$.
-And from the start vector $y_begin$ and encoded input $ enc_{n} $, first internal state $ dec_{1}$ is calcuated as $ LSTM_{dec}(enc_{n},y_begin) $.
-Then, with for all vector $vy_{k}$, $dec_{k+1}$ is calculated as $ LSTM_{dec}(dec_{k},vy_{k}) $.
-Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_dec $ then softmaxed to generate a probability vector $ py_{k} $.
+First, $sy$ is tokenized, appended the token $ EOS $ for indicating the end of the sequence, then embedded to a vector representation $vy_{1} \dots vy_{m}$ in the same way as embedding $sx$.
+From the start vector $y_{begin}$ and encoded input $ enc_{n} $, first internal state $ dec_{1}$ is calcuated as $ LSTM_{dec}(enc_{n},y_{begin}) $.
+Then, $ dec_{1} \dots dec_{m} $ are calculated in accordance with the recursive formula $ dec_{k} = lstm_{dec}(dec_{k-1},vy_{k}) $.
+Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_{dec} $ and then softmaxed to generate a probability vector $ py_{k} $.
 The probability vector $ py_{k} $ is intended to represent the probability distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
@@
 
-The inference is obteining $ \argmax_{sy} p(sy|sx) = \argmax_{sy} \prod_{k=1}^n p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
+The inference for sequence $sx$ is carried out by calculating 
+$ \argmax_{sy} p(sy|sx) = \argmax_{sy} \prod_{k=1}^n p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
 Calculating argmax directly is time consuming, so we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_m]$ sequentially.
 First, $sy_1$ is calculated as $ \argmax_{sy_1} p(sy_1|sx,[]) $, where distribution $ p(sy_1|sx,[]) $ is approximated by 
-$ softmax(W_dec(dec_{1})) = softmax(W_dec(LSTM_{dec}(enc_{n},y_begin))) $. 
+$ softmax(W_{dec}(dec_{1}))$. 
 Then, the next token $sy_2 = \argmax_{sy_1} p(sy_2|sx,[sy_2]) $ is calculated from $ dec_{1} $ and the vector embedding of $sy_1$, and so on.
@@
 
-For
-
 % (TODO) BiLSTMとmulti-layerについてさらっと
@@
 \subsection{Attention}
-Attention is a extension module of Seq2Seq model to improve the quality of translation.
+Attention is a extension module of seq-to-seq model to improve the quality of translation. 
+Simple seq-to-seq model has a problem that the length of the encoded vector $enc_{n}$ is fixed 
+regardless of the length of the input sequence $sx$. 
+Therefore, the longer the length of the input becomes, the more likely the information of the input will be lost.
+This problem is eased by using the information in the encoding network when decoding the output sequence.
 
-\subsection{Seq2Tree}
+The attention module is first developed in \cite{attention_paper}.
+However, the attention 
+We inplemented the global general attention, which is intoduced in \cite{dot_attention}, for improving the quality of decompilation.
+In this subsection, we will describe about the global general attention.
+
+After generating $ dec_{k} $, the context vector $ c_{k} $ is calculated from the hidden states $ enc_{1} \dots enc_{n} $.
+
+$ c_{k} = \sum_{k=1}^{n} $
+
+The attentional hidden state $ dec'_{k} $ is calculated from the $ dec_{k} $ and $ c_{k} $.
+Then, the probability $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ is estimated as $ softmax(W_{dec}(dec'_{k}))$, instead of $ softmax(W_{dec}(dec_{k}))$.
+
+\subsection{Seq-to-Tree}
 % 184 words
@@
 and it is reasonable to consider the grammer of the programming language in generating programs.
-Seq2Tree is a model for generating tree-structured output from sequence input.
+Seq-to-Tree is a model for generating tree-structured output from sequence input.
 This model is introduced in \cite{Seq2Tree} for generating programs from the program specification written in natural languages.
@@
 
-Now, we will describe about the Seq2Tree model.
-Seq2Tree model is composed of two modules, the encoder netwrok and the decoder network.
-The encoder network of Seq2Tree model is the same as the encoder network of Seq2Seq model. It summerize the input sequence into one fixed length vector.
+Now, we will describe about the seq-2-tree model.
+seq-2-tree model is composed of two modules, the encoder netwrok and the decoder network.
+The encoder network of seq-2-tree model is the same as the encoder network of seq-2-tree model. It summerize the input sequence into one fixed length vector.
 
 The decoder network is a network for generating tree structured output. 
-In this paper, our implemented model is different from the model in \cite{Seq2Tree}. 
+In this paper, our implemented model is based on model in \cite{Seq2Tree}. 
 So first, we briefly describe the model implemented in the paper, and then, we describe our model.
@@
 % 312 words
-In algorithmic parspective, the inference of the Seq2Seq model tries to generate sequence one by one, from the first token to the last.
+In algorithmic parspective, the inference of the seq2seq model tries to generate sequence one by one, from the first token to the last.
 % The Seq2Tree model also tries to generate tree structure one by one, with depth-first order.
@@
 Then, the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(a_k|sx,[a_1, \dots a_{k-1}]) $, 
-so the Seq2Seq model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
+so the seq-2-seq model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
 calculating $ LSTM_{dec}(dec_{k},av_{k}) $ for estimating $p(a_{k+1}|sx,[a_1, \dots a_{k}]) $.
@@
 \subsubsection{Our Model}
+
+Calculating context With 
+We changed previous model
+
 Our model tries to exploit the intuitive that each node of the tree is basically independent from its sibling.
 This intuition is not true when the compiler optimizes the assembler. 
-However
+However, in this paper, we tested the
 
 \chapter{Experiments}
+In this chapter, we explain the detail of the data preparetion and implementation.
+The implementation source codes are avaiable at \url{https://github.com/satos---jp/neural_decompiler}.
 
@@
 
-% 244 words
+% 34 words
 In order to apply LSTM, input and output for the LSTM must be the sequence of tokens. 
@@
 \subsection{Assembly Code Preprocess}
+% 155 words
 The assemblies were preprocessed in two ways.
@@
 \subsection{C Code Preprocess}
+% 232 words
 The C source codes were parsed to AST by the \cite{clang} and its Python bindings together with \cite{pycparser}, 
@@
 
-The AST is used for Seq2Tree model dataset as it is.
-Also, the AST is converted to C token sequence for Seq2Seq model dataset.
+The AST is used for sequence-to-Tree model dataset as it is.
+Also, the AST is converted to C token sequence for sequence-to-sequence model dataset.
 
@@
 \section{Training and Testing}
+% 91 words
+We trained the model to reduce the cross-entropy loss between predicted and actual conditional probability.
+The conditional probability is the probability of next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for sequence-to-sequence model, 
+and the probability of next action $p(a_{k+1}|sx,[a_1, \dots a_{k}]) $ for sequence-to-tree model.
 
-We trained the model to reduce the cross-entropy loss between predicted and actual conditional probability.
-The conditional probability is the probability of next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for Seq2Seq model, 
-and the probability of next action $p(a_{k+1}|sx,[a_1, \dots a_{k}]) $ for Seq2Tree model.
+We calculated the quality of the decompilation by two metrics, edit distance ratio and BLEU.
 
-We calculated the accuracy with the edit distance ratio between ground truth and output source code from the model.
+Edit distance ratio is the metrics for the correctness of the decompilation result.
 Here, the edit distance ratio between two strings means the Levenshtein distance divided by the longer length of the strings.
-For the Seq2Seq model, the distance is
+Idealy, the correctness of the decompilation result should be measured by the distance of the meaning of the program.
+However the decompilation result is usually uncompilable, so we used the edit distance of the source codes as the approximation of the correctness.
+
+BLEU is
 

### 2019-01-22 c_cfg.py

@@ -261,9 +261,15 @@ def type_embedding(ty,na):
 		elif len(nt)==3:
 			return nt[0] + '(' + f(nt[1]) + ')' + strize(nt[2])
 		else:
+			#print('assert_at_type_embedding')
+			#print(nt,len(nt),ty)
 			assert False
 	
-	return f(td)
+	try:
+		return f(td)
+	except (IndexError,AssertionError,TypeError):
+		return 'INDALID_TYPE ' + na
+	#except AssertError:
 	#return "%s %s" % (ty,na)
 
 
@@ -277,10 +283,14 @@ def function_decl_func(cs):
 	try:
 		assert len(s)==0 and len(td)==2 and type(td[1]) is list
 	except AssertionError:
-		raise Oteage
-		print('function_decl_func_fisrt_miss')
-		print(cs)
-		exit()
+		#raise Oteage
+		#print('function_decl_func_fisrt_miss')
+		#print(cs)
+		#exit()
+		#print('invalid function decl')
+		#print(cs)
+		#exit()
+		return 'INVALID_FUNCTION_DECL{' + ''.join(cs) + '}'
 	arg_types_len = 0
 	if len(td[1])!=0 and td[1][0] != 'void':
 		arg_types_len = 1
@@ -294,15 +304,16 @@ def function_decl_func(cs):
 	#print(arg_types_len)
 	arg_names = cs[:arg_types_len]
 	cs = cs[arg_types_len:]
-	assert len(cs)<=1
+	#assert len(cs)<=1
 	if len(cs)==0:
 		body = ';'
 	else:
 		body = cs[0]
 	
 	try:
-		return td[0] + na + '(' + ','.join(map(lambda ab: type_embedding(*ab),arg_names)) + ')' + body
+		return td[0] + na + '(' + ','.join(arg_names) + ')' + body
 	except TypeError:
+		return 'INVALID_FUNCTION_DECL{' + ''.join(cs) + '}'
 		print('nazono type embedding no yatu')
 		raise AssertionError
 		print(cs)
@@ -331,8 +342,8 @@ class Oteage(Exception):
 
 def for_check(cs):
 	s = cs[0].strip()
-	if ';' in s[:-1]:
-		raise Oteage
+	#if ';' in s[:-1]:
+	#	raise Oteage
[…]

### 2019-01-22 csrc2ast.py

@@ -27,6 +27,7 @@ def ast2token_seq(data):
 	src = ast.show()
 	with open('tmp.c','w') as fp:
 		fp.write(src)
+	#print(src)
 	res = tokenizer.tokenize('tmp.c')
 	#print(src,res)
 	return res
@@ -75,10 +76,61 @@ def src2ast(fn,pfn):
 	return res
 
 
+import random
+
+
+def randtree(ty):
+	cs = c_cfg.trans_array[ty]
+	nc = random.randint(0,len(cs)-(1 if random.randint(0,10) else 0))
+	
+	if nc == len(cs):
+		return (ty,-1,[])
+	else:
+		res = [randtree(d) for d in cs[nc]]
+		return (ty,nc,res)
+
+def fuzzing():
+	for _ in range(10000):
+		tree = randtree(c_cfg.rootidx)
+		if len(tree[2])==0:
+			continue
+		#print(tree)
+		ts = ast2token_seq(tree)
+		#assert not ts is None
+		#print(ts)
+
+"""
+print(list(enumerate(c_cfg.alltypes)))
+[(0, ['expr', 'option']), (1, ['stmt', 'option']), (2, ['decl', 'list']), (3, ['expr', 'list']), (4, ['stmt', 'list']), (5, ['tyspec', 'list']), (6, ['paramlist', 'option']), (7, ['integerliteral', 'option']), (8, ['typename', 'list']), (9, 'integerliteral'), (10, 'stringliteral'), (11, 'floatliteral'), (12, 'charliteral'), (13, 'binop'), (14, 'unop'), (15, 'casop'), (16, 'memberrefop'), (17, 'NULL'), (18, 'tyspec'), (19, 'name'), (20, 'structname'), (21, 'unionname'), (22, 'enumname'), (23, 'label'), (24, 'toplevel'), (25, 'labelref'), (26, 'expr'), (27, 'stmt'), (28, 'decl'), (29, 'type_type'), (30, 'paramlist'), (31, 'type'), (32, 'typename'), (33, 'typedecltype'), (34, CursorKind.ARRAY_SUBSCRIPT_EXPR), (35, CursorKind.BINARY_OPERATOR), (36, CursorKind.BREAK_STMT), (37, CursorKind.CALL_EXPR), (38, CursorKind.CASE_STMT), (39, CursorKind.CHARACTER_LITERAL), (40, CursorKind.COMPOUND_ASSIGNMENT_OPERATOR), (41, CursorKind.COMPOUND_STMT
[…]

### 2019-01-22 model_seq2tree.py

@@ -15,47 +15,12 @@ def sequence_embed(embed, xs):
 	return exs
 
 
-# from https://arxiv.org/pdf/1409.0473.pdf. Global attention.
-class Attention(chainer.Chain):
-	def __init__(self, n_units):
-		super(Attention, self).__init__()
-		with self.init_scope():
-			self.att_W = L.Linear(n_units, n_units)
-			self.att_U = L.Linear(n_units*2, n_units)
-			self.att_v = L.Linear(n_units, 1)
-		
-		self.n_units = n_units
-		self.Uhxs = None
-	
-	def init_hxs(self,hxs):
-		self.hxs = hxs
-		self.Uhxs = self.att_U(hxs)
-		self.Uhxs_len = hxs.shape[0]
-	
-	def forward(self,nhx):
-		nhx_for_att = nhx[-1]
-		Wnhx = self.att_W(nhx_for_att)
-		#print(Wnhx.shape,Uhxs.shape)
-		#print((Wnhx + Uhxs).shape)
-		
-		att_rates = F.softmax(F.reshape(self.att_v(
-				F.tanh(
-					Wnhx + self.Uhxs
-				)
-		),(1,self.Uhxs_len)))
-		#print(hxs.shape,att_rates.shape)
-		#print(att_rates)
-		#print(F.matmul(att_rates,hxs).shape)
-		ctx = F.matmul(att_rates,self.hxs)[0]
-		#print(ctx.shape)
-		return ctx
-		
-	def reset(self):
-		self.hxs = None
-		self.Uhxs = None
-	
+from model_attention import Attention,DotAttention,LocalDotAttention
+
+
+
 class Seq2Tree(chainer.Chain):
-	def __init__(self, n_layers, n_source_vocab, trans_data, n_units,v_eos_src,n_maxdepth):
+	def __init__(self, n_layers, n_source_vocab, trans_data, n_units,v_eos_src,n_maxsize):
 		super(Seq2Tree, self).__init__()
 
 		# for each nodetype, for each move, the result array.
@@ -70,27 +35,40 @@ class Seq2Tree(chainer.Chain):
 		self.embed_root_idx = ns
 		self.embed_y_size = ns+1
 		
+		#self.choice_num_sum = sum(list(map(lambda d: len(d),self.trans_data)))
+		
+		self.type_size = len(self.embed_idx)
+		
[…]

### 2019-01-22 model_seq2tree_flatten.py

@@ -1,0 +1,217 @@
+import numpy as np
+import chainer
+import chainer.links as L
+import chainer.functions as F
+from chainer import training
+from chainer.training import extensions
+from chainer import serializers
+import c_cfg
+	
+def sequence_embed(embed, xs):
+	x_len = [len(x) for x in xs]
+	x_section = np.cumsum(x_len[:-1])
+	ex = embed(F.concat(xs, axis=0))
+	exs = F.split_axis(ex, x_section, 0)
+	return exs
+
+
+from model_attention import Attention,DotAttention,GlobalGeneralAttention
+
+class Seq2Tree_Flatten(chainer.Chain):
+	def __init__(self, n_layers, n_source_vocab, trans_data, n_units,v_eos_src,n_maxsize):
+		super(Seq2Tree_Flatten, self).__init__()
+
+		# for each nodetype, for each move, the result array.
+		self.trans_data = trans_data
+		self.embed_idx = []
+		ns = 0
+		def inc():
+			nonlocal ns
+			ns += 1
+			return ns-1
+		self.embed_idx = [[[inc() for v in vs] for vs in moves] for moves in self.trans_data]
+		self.embed_root_idx = ns
+		self.embed_y_size = ns+1
+		
+		self.choicerange = []
+		self.choice_idx = []
+		s = 0
+		for d in self.trans_data:
+			b = s
+			s += len(d)
+			self.choicerange.append((b,s))
+			self.choice_idx.append(list(range(b,s)))
+		#self.choice_num_sum = sum(list(map(lambda d: len(d),self.trans_data)))
+		
+		self.type_size = len(self.embed_idx)
+		self.n_all_choice = sum(map(lambda x: len(x),self.trans_data))
+		
+		with self.init_scope():
+			self.embed_x = L.EmbedID(n_source_vocab, n_units)
+			#self.embed_y = L.EmbedID(self.embed_y_size, n_units) # maybe mergable
+			self.embed_y_0 = L.EmbedID(self.embed_y_size, n_units) # maybe mergable
+			self.embed_y_1 = L.EmbedID(self.type_size, n_units) # maybe mergable
+			
+			self.encoder = L.NStepBiLSTM(n_layers, n_units, n_units, 0.1)
[…]

### 2019-01-22 my_c_ast.py

@@ -299,6 +299,7 @@ class AST:
 				elif type(s) is types.FunctionType:
 					res = s(cs)
 			except IndexError:
+				return 'INVALID_SUBTREE'
 				print('indexerror')
 				sl.debug()
 			return res

### 2019-01-22 sample_dataset.py

@@ -9,22 +9,36 @@ def sample_dataset():
 		asm_vocab = pickle.load(fp)
 	print('start')
 	data = []
+	dss = 0
 	for i in range(12):
 		with open('dataset_asm_ast/data_%d.pickle' % i,'rb') as fp:
 			nd = pickle.load(fp)[1]
 		
-		print(len(nd))
+		#print(len(nd))
+		data = []
 		for d in nd:
 			if random.randint(1,12)==1:
 				data.append(d)
 		print('done',i)
 		print('nl',len(data))
+		dls = int(len(data)/10)
+		for j in range(10):
+			with open('dataset_asm_ast/data_sampled_%d.pickle' % (i*10+j),'wb') as fp:
+				pickle.dump(data[dls*j:dls*(j+1)],fp)
+				dss += dls
 		del nd
+		del data
+	print('sum length:',dss)
+	
+	"""
 	print(len(data))
 	print('start saving')
 	with open('sampled_asm_ast_dataset.picikle','wb') as fp:
 		print('opened')
 		pickle.dump((data,asm_vocab,c_syntax_arr),fp)
 		print('dumped')
-		
+	"""
+
 sample_dataset()
+
+

### 2019-01-22 texs/compile.sh

@@ -1,3 +1,3 @@
 cp ../../tex-srcs/iscs-thesis.cls ./
 sed '/__NAMES__/r ../../names.txt' paper_base.tex | sed 's/__NAMES__//g' > paper.tex
-platex paper.tex && pbibtex paper && platex paper.tex && dvipdfm paper.dvi
+platex paper.tex && pbibtex paper && platex paper.tex && platex paper.tex && platex paper.tex && dvipdfm paper.dvi

### 2019-01-22 tokenizer.py

@@ -16,6 +16,8 @@ def tokenize(fn):
 			#print(cs)
 			cs = "'".join(cs.split("'")[1:-1])
 			ts.append(cs)
+		
+		ts = list(filter(lambda x: x!='',ts))
 		return ts
 	else:
 		return None	

### 2019-01-22 train.py

@@ -12,14 +12,15 @@ from chainer import serializers
 from model_rnn import Seq2seq
 from model_rnn_with_att import Seq2seq_with_Att
 from model_seq2tree import Seq2Tree
+from model_seq2tree_flatten import Seq2Tree_Flatten
 
 
 def convert(batch, device):
 	def to_device_batch(batch):
 		return batch
 
-	return {'xs': to_device_batch([x for x, _ in batch]),
-			'ys': to_device_batch([y for _, y in batch])}
+	return {'xs': to_device_batch([x for x,_ in batch]),
+			'ys': to_device_batch([y for _,y in batch])}
 
 import datetime
 def getstamp():
@@ -36,9 +37,9 @@ import c_cfg
 
 def init_seq2seq():
 	n_layer = 4
-	n_unit = 128
+	n_unit = 64
 	
-	n_maxlen = 100
+	n_maxlen = 128
 	
 	with open('data_with_gcc_binary.pickle','rb') as fp:
 			(data,c_vocab) = pickle.load(fp)
@@ -145,61 +146,117 @@ def init_seq2seq():
 	return (model,dataset,translate)
 
 
+
+
+
+class Asm_ast_dataset(chainer.dataset.DatasetMixin):
+	def __init__(self):
+		super(Asm_ast_dataset,self).__init__()
+		
+		self.len = 1000190
+		#self.len = 3200
+		self.cache = []
+		self.data_idx = []
+		
+		self.get_example = self.data_range(0,100)
+		self.get_test = self.data_range(100,120)
+		
+	def __len__(self):
+		return self.len
+	
+	def data_range(self,a,b):
+		def gex(_):
+			if self.cache == []:
+				if self.data_idx == []:
+					self.data_idx =list(range(a,b))
+					random.shuffle(self.data_idx)
+			
+				fn = self.data_idx.pop()
+				with open('dataset_asm_ast/data_sampled_%d.pickle' % fn,'rb') as fp:
+					self.cache = pickle.load(fp)
+					#self.cache = list(map(lambda xy: (np.array(xy[0],np.int32),xy[2]),self.cache))
+					random.shuffle(self.cache)
+					
+			res = self.cache.pop()
+			p,size,q = res
+			#print(size)
+			return (np.array(p,np.int32),q)
+			#return (np.array([0],np.int32),(c_cfg.rootidx,0,[(0,0,[])]))
+		
+		return gex
+
 def load_dataset():
-	"""
+	
[…]

### 2019-01-24 texs/paper_base.tex
implement for cuda

@@
 
-In this thesis, we applied seq-to-tree model suggested in \cite{Seq2Tree}, because the input of the decompiler is the sequence of machine codes.
+In this thesis, we applied sequence-to-tree model suggested in \cite{Seq2Tree}, because the input of the decompiler is the sequence of machine codes.
 
@@
 % 477 words.
-LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the seq-to-seq (sequence to sequence) model.
+LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the sequence-to-sequence (sequence to sequence) model.
 SMT is the task which tries to translate one sentense $sx$ written in one language into the sentense $sy$ written in another language.
 
-Seq-to-seq model is composed of two modules, the encoder netwrok and the decoder network.
+Sequence-to-sequence model is composed of two modules, the encoder netwrok and the decoder network.
 
@@
 
-% (TODO) BiLSTMとmulti-layerについてさらっと
+In addition to
+
+First is the Bidirectional Reccurent Neural Networks (BRNN) is the architecture introduced in \cite{BiRNN}.
+In the experiment, this architecture is used for the encoder network as follows.
+In addition to the internal state $ enc_{k} $, the reverse internal state $ enc_{k}^{\gets} $ is also calculated 
+in accordance with the recursive formula $ enc_{k}^{\gets} = lstm_{enc}^{\gets}(enc_{k+1}^{\gets},vx_{k}) $.
+Then both of the internal states $ enc_{n} $ and $ enc_{1}^{\gets} $ are used for decoder network.
+
+Second is the multi-layer reccurent neural networks, introduced in ここ決める.
+It is reported that, instead of the output of the LSTM units to another LSTM units will improve the accuracy of the prediction.
+This architecture is called as stucked reccurent neural networks or multi-layer reccurent neural networks.
 
 \subsection{Attention}
-Attention is a extension module of seq-to-seq model to improve the quality of translation. 
-Simple seq-to-seq model has a problem that the length of the encoded vector $enc_{n}$ is fixed 
+Attention is a extension module of sequence-to-sequence model to improve the quality of translation. 
+Simple sequence-to-sequence model has a problem that the length of the encoded vector $enc_{n}$ is fixed 
 regardless of the length of the input sequence $sx$. 
@@
 The attention module is first developed in \cite{attention_paper}.
-However, the attention 
 We inplemented the global general attention, which is intoduced in \cite{dot_attention}, for improving the quality of decompilation.
 In this subsection, we will describe about the global general attention.
+
+In the pure sequence-to-sequence model, the conditional probability  $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ is calculated from $ dec_{k} $ ,which is the internal state of the decoder network.
+In the sequence-to-sequence with attention model, the probability is calcutated from $ dec_{k} $ and the context vevctor $ c_{k} $.
+$ c_{k} $
 
@@
 
-\subsection{Seq-to-Tree}
+\subsection{Sequence-to-Tree}
 % 184 words
@@
 and it is reasonable to consider the grammer of the programming language in generating programs.
-Seq-to-Tree is a model for generating tree-structured output from sequence input.
+Sequence-to-Tree is a model for generating tree-structured output from sequence input.
 This model is introduced in \cite{Seq2Tree} for generating programs from the program specification written in natural languages.
@@
 
-Now, we will describe about the seq-2-tree model.
-seq-2-tree model is composed of two modules, the encoder netwrok and the decoder network.
-The encoder network of seq-2-tree model is the same as the encoder network of seq-2-tree model. It summerize the input sequence into one fixed length vector.
+Now, we will describe about the sequence-2-tree model.
+sequence-to-tree model is composed of two modules, the encoder netwrok and the decoder network.
+The encoder network of sequence-2-tree model is the same as the encoder network of sequence-to-tree model. It summerize the input sequence into one fixed length vector.
 
 The decoder network is a network for generating tree structured output. 
-In this paper, our implemented model is based on model in \cite{Seq2Tree}. 
-So first, we briefly describe the model implemented in the paper, and then, we describe our model.
-
-\subsubsection{Previous Model}
-% 312 words
-In algorithmic parspective, the inference of the seq2seq model tries to generate sequence one by one, from the first token to the last.
-% The Seq2Tree model also tries to generate tree structure one by one, with depth-first order.
-The inference of the SeqTree model starts from the start symbol, and recursively expand the nonterminal symbols in depth-first order.
-
-The tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
+A tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
 Suppose the tree $ty$ is generated by the action sequence $ [a_1, \dots a_m] $, 
@@
 Then, the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(a_k|sx,[a_1, \dots a_{k-1}]) $, 
-so the seq-2-seq model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
+so the sequence-to-sequence model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
 calculating $ LSTM_{dec}(dec_{k},av_{k}) $ for estimating $p(a_{k+1}|sx,[a_1, \dots a_{k}]) $.
+
+% In algorithmic parspective, the inference of the seq2seq model tries to generate sequence one by one, from the first token to the last.
+% The Seq2Tree model also tries to generate tree structure one by one, with depth-first order.
+% The inference of the SeqTree model starts from the start symbol, and recursively expand the nonterminal symbols in depth-first order.
 
@@
 But in our case, we don't need copy the information from the input, because the name information is lost when compiling, so we omit the discriptionp of this copy method.
-
-\subsubsection{Our Model}
-
-Calculating context With 
-We changed previous model
-
-Our model tries to exploit the intuitive that each node of the tree is basically independent from its sibling.
-This intuition is not true when the compiler optimizes the assembler. 
-However, in this paper, we tested the
 
@@
 \section{Model Configuration}
-The training model was implemented with Chainer. Source codes are avaiable at \url{}.
+The training model was implemented with Chainer. 
+We implemented three models, Seq2seq, Seq2seqWithAattention, and Seq2tree.
+
+The encoding module was bidirectional LSTM in all of three models.
+The decoding module of Seq2seq and Seq2seqWithAattention predict the conditional probability of a next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
+The decoding module of Seq2tree predicts the conditional probability of a next action $ p(a_{k}|sx,[a_1, \dots a_{k-1}]) $.
+
+Seq2seqWithAattention and Seq2tree have attention module, while Seq2seq have not.
+
+\begin{figure}
+	\begin{tabular}{c|c}
+		Number of Layers & 4
+		%Dimensionality of Embedded Vectors & 128
+	\end{tabular}
+	\caption{The configuration parameter of the models}
+	\label{fig:parameterofmodels}
+\end{figure}
+
+Figure~\ref{fig:parameterofmodels} shows the parameter of the models.
 
@@
 
-BLEU is
+BLEU is the metrics for the naturallity of the generated program. 
+It is first introduced in \cite{BLEU}, for evaluating the performance of the machine translation.
 
@@
 
-We tested our methods for
+We tested three models. 
+Seq2seq is a model with
 

### 2019-01-24 cuda_setting.py

@@ -1,0 +1,6 @@
+import sys
+
+isgpu = False
+if len(sys.argv)>=2 and sys.argv[1]=='gpu':
+	isgpu = True
+

### 2019-01-24 gen_ast_all_data.py

@@ -1,0 +1,396 @@
+#! /usr/bin/env /home/satos/sotsuron/neural_decompiler/python_fix_seed.sh
+
+from pycparser import c_parser, c_ast, parse_file
+	
+class ParseErr(Exception):
+	def __init__(sl,s):
+		pass
+
+def s2tree(s):
+	s = s.split('\n')
+	ls = len(s)
+	i = 0
+	def parse(d):
+		nonlocal i,s,ls
+		
+		node = s[i][d:]
+		nt = node.split(' ')[0]
+		#print(node)
+		#try:
+		ps = re.findall('<line:\d*:\d, line:\d*:\d*>',node)
+		if len(ps)>0:
+			pos = ps[0]
+		else:
+			pos = None
+		
+		node = (nt,pos)
+		
+		i += 1
+		#print(i,d)
+		#print(s[i])
+		if i >= ls or len(s[i])<=d or (s[i][d]!='|' and s[i][d]!='`'):
+			#print(node)
+			return (node,[])
+		
+		res = []
+		while True:
+			if s[i][d:d+2]=='|-':
+				res.append(parse(d+2))
+			elif s[i][d:d+2]=='`-':
+				res.append(parse(d+2))
+				break
+			else:
+				#return res
+				#print(s[i][d:])
+				raise ParseErr('miss at %d:%d' % (i,d))
+		return (node,res)
+	
+	return parse(0)
+
+import code
+import re
+
+def parse_c(prsc):
+	#print(s2tree(prsc))
+	
+	res = []
+	tree = s2tree(prsc)
+	#print(tree)
+	def trav(d):
+		nonlocal res
+		ntp,ds = d
+		nt,pos = ntp
+		
+		# CompoundStmt は多分飛ばさないといけない(if文のあととかがへんになる)
+		if nt != 'CompoundStmt' and pos is not None:
+			v = pos.split(':')
+			a,b = int(v[1])-1,int(v[3])-1 #0-indexed !!
+			#print(nt,pos,a,b)
+			res.append((a,b))
+		
+		for x in ds:
+			trav(x)
+		
+	trav(tree)
+	return res
+
+class InvalidToken(Exception):
+	pass
+
+data = []
+vocab_src = set([])
+vocab_dst = set([])
+
+import pickle
+with open('dataset_asm_ast/vocab_asm.pickle','rb') as fp:
+	vocab_dst = pickle.load(fp)
+with open('dataset_asm_csrc/vocab_csrc.pickle','rb') as fp:
[…]

### 2019-01-24 gen_ast_data.py

@@ -99,8 +99,6 @@ for fn in srcs:
 		print('too long',fn)
 		continue
 	
-
-
 	nibeki = [1<<(i*8) for i in range(8)]
 	def asm_trim(v):
 		if v in x64_opcodes_registers:

### 2019-01-24 gen_data_from_ast.py

@@ -1,0 +1,508 @@
+#! /usr/bin/env /home/satos/sotsuron/neural_decompiler/python_fix_seed.sh
+
+from pycparser import c_parser, c_ast, parse_file
+	
+class ParseErr(Exception):
+	def __init__(sl,s):
+		pass
+
+def s2tree(s):
+	s = s.split('\n')
+	ls = len(s)
+	i = 0
+	def parse(d):
+		nonlocal i,s,ls
+		
+		node = s[i][d:]
+		nt = node.split(' ')[0]
+		#print(node)
+		#try:
+		ps = re.findall('<line:\d*:\d, line:\d*:\d*>',node)
+		if len(ps)>0:
+			pos = ps[0]
+		else:
+			pos = None
+		
+		node = (nt,pos)
+		
+		i += 1
+		#print(i,d)
+		#print(s[i])
+		if i >= ls or len(s[i])<=d or (s[i][d]!='|' and s[i][d]!='`'):
+			#print(node)
+			return (node,[])
+		
+		res = []
+		while True:
+			if s[i][d:d+2]=='|-':
+				res.append(parse(d+2))
+			elif s[i][d:d+2]=='`-':
+				res.append(parse(d+2))
+				break
+			else:
+				#return res
+				#print(s[i][d:])
+				raise ParseErr('miss at %d:%d' % (i,d))
+		return (node,res)
+	
+	return parse(0)
+
+import code
+import re
+
+def parse_c(prsc):
+	#print(s2tree(prsc))
+	
+	res = []
+	tree = s2tree(prsc)
+	#print(tree)
+	def trav(d):
+		nonlocal res
+		ntp,ds = d
+		nt,pos = ntp
+		
+		# CompoundStmt は多分飛ばさないといけない(if文のあととかがへんになる)
+		if nt != 'CompoundStmt' and pos is not None:
+			v = pos.split(':')
+			a,b = int(v[1])-1,int(v[3])-1 #0-indexed !!
+			#print(nt,pos,a,b)
+			res.append((a,b))
+		
+		for x in ds:
+			trav(x)
+		
+	trav(tree)
+	
+	"""
+	lines = re.findall('<line:\d*:\d*, line:\d*:\d*>',prsc)
+	#print(lines)
+	#code.interact(local={'tree':tree})
+	
+	res = []
+	for d in lines:
+		v = d.split(':')
+		#print(v)
+		a,b = int(v[1])-1,int(v[3])-1 #0-indexed !!
[…]

### 2019-01-24 model_attention.py

@@ -71,7 +71,7 @@ class GlobalGeneralAttention(chainer.Chain):
 		self.n_units = n_units
 		self.hxs = None
 		with self.init_scope():
-			self.Wa = L.Linear(n_units, n_units*2)
+			self.Wa = L.Linear(n_units*2, n_units*2)
 		
 	#@profile
 	def forward(self,xh,yh):

### 2019-01-24 model_rnn_with_globalatt.py

@@ -14,7 +14,7 @@ if isgpu:
 else:
 	xp = np
 
-from model_attention import Attention,DotAttention,GlobalGeneralAttention
+from model_attention import GlobalGeneralAttention
 
 def sequence_embed(embed, xs):
 	x_len = [len(x) for x in xs]
@@ -24,22 +24,22 @@ def sequence_embed(embed, xs):
 	return exs
 
 	
-class Seq2seq_with_Att(chainer.Chain):
-	def __init__(self, n_layers, n_source_vocab, n_target_vocab, n_units,v_eos_src,v_eos_dst,n_maxlen):
-		super(Seq2seq_with_Att, self).__init__()
+class Seq2seq_with_GlobalAtt(chainer.Chain):
+	def __init__(self, n_layers, n_source_vocab, n_target_vocab, n_units,v_eos_dst,n_maxlen):
+		super(Seq2seq_with_GlobalAtt, self).__init__()
+		self.n_target_vocab = n_target_vocab
 		with self.init_scope():
 			self.embed_x = L.EmbedID(n_source_vocab, n_units)
 			self.embed_y = L.EmbedID(n_target_vocab, n_units)
 			self.encoder = L.NStepBiLSTM(n_layers, n_units, n_units, 0.1)
-			self.decoder = L.NStepLSTM(n_layers, n_units*3, n_units, 0.1)
-			self.W = L.Linear(n_units, n_target_vocab)
+			self.decoder = L.NStepLSTM(n_layers, n_units, n_units*2, 0.1)
+			self.Wc = L.Linear(n_units*4, n_units)
+			self.Ws = L.Linear(n_units, self.n_target_vocab)
 			
-			self.att = Attention(n_units)
+			self.att = GlobalGeneralAttention(n_units)
 		
-		self.n_target_vocab = n_target_vocab
 		self.n_layers = n_layers
 		self.n_units = n_units
-		self.v_eos_src = v_eos_src
 		self.v_eos_dst = v_eos_dst
 		self.n_maxlen = n_maxlen
 
@@ -62,54 +62,20 @@ class Seq2seq_with_Att(chainer.Chain):
 		batch = len(xs)
 		# None represents a zero vector in an encoder.
 		hx, cx, xs_states = self.encoder(None, None, exs)
-		#_, _, os = self.decoder(hx, cx, eys)
-		
[…]

### 2019-01-24 model_seq2seq_pure.py

@@ -14,8 +14,6 @@ if isgpu:
 else:
 	xp = np
 
-from model_attention import Attention,DotAttention,GlobalGeneralAttention
-
 def sequence_embed(embed, xs):
 	x_len = [len(x) for x in xs]
 	x_section = np.cumsum(x_len[:-1])
@@ -24,22 +22,19 @@ def sequence_embed(embed, xs):
 	return exs
 
 	
-class Seq2seq_with_Att(chainer.Chain):
-	def __init__(self, n_layers, n_source_vocab, n_target_vocab, n_units,v_eos_src,v_eos_dst,n_maxlen):
-		super(Seq2seq_with_Att, self).__init__()
+class Seq2seq(chainer.Chain):
+	def __init__(self, n_layers, n_source_vocab, n_target_vocab, n_units,v_eos_dst,n_maxlen):
+		super(Seq2seq, self).__init__()
+		self.n_target_vocab = n_target_vocab
 		with self.init_scope():
 			self.embed_x = L.EmbedID(n_source_vocab, n_units)
 			self.embed_y = L.EmbedID(n_target_vocab, n_units)
 			self.encoder = L.NStepBiLSTM(n_layers, n_units, n_units, 0.1)
-			self.decoder = L.NStepLSTM(n_layers, n_units*3, n_units, 0.1)
-			self.W = L.Linear(n_units, n_target_vocab)
-			
-			self.att = Attention(n_units)
+			self.decoder = L.NStepLSTM(n_layers, n_units, n_units*2, 0.1)
+			self.W = L.Linear(n_units*2, self.n_target_vocab)
 		
-		self.n_target_vocab = n_target_vocab
 		self.n_layers = n_layers
 		self.n_units = n_units
-		self.v_eos_src = v_eos_src
 		self.v_eos_dst = v_eos_dst
 		self.n_maxlen = n_maxlen
 
@@ -62,54 +57,17 @@ class Seq2seq_with_Att(chainer.Chain):
 		batch = len(xs)
 		# None represents a zero vector in an encoder.
 		hx, cx, xs_states = self.encoder(None, None, exs)
-		#_, _, os = self.decoder(hx, cx, eys)
+		hx = F.transpose(F.reshape(F.transpose(hx,(1,0,2)),(batch,self.n_layers,self.n_units*2)),(1,0,2))
[…]

### 2019-01-24 model_seq2tree.py

@@ -5,8 +5,15 @@ import chainer.functions as F
 from chainer import training
 from chainer.training import extensions
 from chainer import serializers
-import c_cfg
+
+from chainer import cuda
+from cuda_setting import isgpu
 	
+if isgpu:
+	xp = cuda.cupy
+else:
+	xp = np
+
 def sequence_embed(embed, xs):
 	x_len = [len(x) for x in xs]
 	x_section = np.cumsum(x_len[:-1])
@@ -15,7 +22,7 @@ def sequence_embed(embed, xs):
 	return exs
 
 
-from model_attention import Attention,DotAttention,LocalDotAttention
+from model_attention import GlobalGeneralAttention
 
 
 
@@ -37,183 +44,101 @@ class Seq2Tree(chainer.Chain):
 		
 		#self.choice_num_sum = sum(list(map(lambda d: len(d),self.trans_data)))
 		
-		self.type_size = len(self.embed_idx)
+		self.choicerange = []
+		self.choice_idx = []
+		s = 0
+		for d in self.trans_data:
+			b = s
+			s += len(d)
+			self.choicerange.append((b,s))
+			self.choice_idx.append(list(range(b,s)))
 		
-		self.n_max_choice = max(map(lambda x: len(x),self.trans_data))
+		self.type_size = len(self.embed_idx)
+		self.n_all_choice = sum(map(lambda x: len(x),self.trans_data))
 		
 		with self.init_scope():
 			self.embed_x = L.EmbedID(n_source_vocab, n_units)
-			#self.embed_y = L.EmbedID(self.embed_y_size, n_units) # maybe mergable
-			self.embed_y_0 = L.EmbedID(self.embed_y_size, n_units) # maybe mergable
-			self.embed_y_1 = L.EmbedID(self.type_size, n_units) # maybe mergable
-			self.W = [None for _ in self.trans_data]
-			for i,moves in enumerate(self.trans_data):
-				if len(moves)>1:
-					self.W[i] = L.Linear(n_units*2, len(moves))
-			
-			self.encoder = L.NStepLSTM(n_layers, n_units, n_units, 0.1)
-			self.decoder = L.NStepLSTM(n_layers, n_units*2, n_units, 0.1)
[…]

### 2019-01-24 model_seq2tree_flatten.py

@@ -5,8 +5,17 @@ import chainer.functions as F
 from chainer import training
 from chainer.training import extensions
 from chainer import serializers
-import c_cfg
-	
+#import c_cfg
+
+from chainer import cuda
+
+from cuda_setting import isgpu
+
+if isgpu:
+	xp = cuda.cupy
+else:
+	xp = np
+
 def sequence_embed(embed, xs):
 	x_len = [len(x) for x in xs]
 	x_section = np.cumsum(x_len[:-1])
@@ -53,8 +62,8 @@ class Seq2Tree_Flatten(chainer.Chain):
 			self.embed_y_1 = L.EmbedID(self.type_size, n_units) # maybe mergable
 			
 			self.encoder = L.NStepBiLSTM(n_layers, n_units, n_units, 0.1)
-			self.decoder = L.NStepLSTM(n_layers, n_units*2, n_units, 0.1)
-			self.Wc = L.Linear(n_units*3, n_units)
+			self.decoder = L.NStepLSTM(n_layers, n_units*2, n_units*2, 0.1)
+			self.Wc = L.Linear(n_units*4, n_units)
 			self.Ws = L.Linear(n_units, self.n_all_choice)
 			
 			#self.att = Attention(n_units)
@@ -64,14 +73,13 @@ class Seq2Tree_Flatten(chainer.Chain):
 		self.n_units = n_units
 		self.v_eos_src = v_eos_src
 		self.n_maxsize = n_maxsize
-		self.v_eos_dst = c_cfg.rootidx
+		self.rootidx = len(trans_data)-1
 		
 
 
 	#@profile
 	def forward(self, xs, ys):
-		xs = [x[::-1] for x in xs]
-		
+		xs = [xp.array(x[::-1]) for x in xs]
 		
 		def flatten(y,pa=self.embed_root_idx):
 			ty,ch,cs = y
@@ -84,10 +92,10 @@ class Seq2Tree_Flatten(chainer.Chain):
 		#assert all(map(lambda x: unflatten(flatten(x),c_cfg.rootidx)[0]==x,ys))
 		
 		ys = list(map(flatten,ys))
-		ys_in_0  = [np.array(list(map(lambda ab: ab[0][0],y))) for y in ys]
-		ys_in_1  = [np.array(list(map(lambda ab: ab[0][1],y))) for y in ys]
[…]

### 2019-01-24 precision.py

@@ -1,0 +1,130 @@
+import pickle
+
+def prec_seq2seq(model):
+	def normalize_sentense(s):
+		ts = []
+		names = {}
+		for d in s:
+			if d[:5]=='__ID_':
+				if not sd in names.keys():
+					names[d] = '__NORMALIZE_TMP_ID_%d__' % len(names.keys())
+				d = names[d]
+			ts.append(d)
+		return ts
+	
+	logt = 0
+	
+	def calcurate_edit_distance():
+		ratio = 0.0
+		ds = random.sample(test_data, 100)
+		for fr,to in ds:
+			result = model.translate([model.xp.array(fr)])[0]
+			result = list(result)
+			result = normalize_sentense(result)
+			to = normalize_sentense(to)
+			ratio += 1.0 - edit_distance.SequenceMatcher(to,result).ratio()
+		#print(ratio)
+		ratio /= len(ds)
+		return ratio
+	
+	@chainer.training.make_extension()
+	def translate(trainer):
+		eds = calcurate_edit_distance()
+		print('edit distance:',eds)
+		nonlocal logt
+		logt += train_iter_step
+		with open('log/iter_%s_editdist_%f_time_%s.txt' % (logt,eds,getstamp()),'w') as fp:
+			res = ""
+			for _ in range(10):
+				source, target = test_data[np.random.choice(len(test_data))]
+				result = model.translate([model.xp.array(source)])[0]
+				
+				#target = normalize_sentense(target)
+				#result = normalize_sentense(result)
+				
+				#source_sentence = ' '.join([asm_vocab[x] for x in source])
+				source_sentence = ' '.join([str(x) for x in source])
+				target_sentence = ' '.join(csrc2ast.ast2token_seq(target))
+				result_sentence = ' '.join(csrc2ast.ast2token_seq(result))
+				res += ('# source : ' + source_sentence) + "\n"
+				res += ('# expect : ' + target_sentence) + "\n"
+				#print('# result_array : ' + ' '.join(["%d" % y for y in result]))
+				res += ('# result : ' + result_sentence) + "\n"
+			fp.write(res)
+		
+		serializers.save_npz('models/iter_%s_editdist_%f_time_%s.npz' % (logt,eds,getstamp()),model)
+		
+		#import code
+		#code.interact(local={'d':model.embed_x})
+		#print('embed data : ', model.embed_x.W)
+	
+	return translate
+
+
+import csrc2ast
[…]

### 2019-01-27 texs/paper_base.tex
save

@@
 
+\lstdefinestyle{Csample}{
+  language=C,
+  tabsize=2,
+}
+
+\lstdefinestyle{Asmsample}{
+  tabsize=2,
+}
+
 \lstset{%
@@
   stringstyle={\small\ttfamily},
-  frame={tb},
+  %frame={tb},
   breaklines=true,
   columns=[l]{fullflexible},%
-  numbers=left,%
+  % numbers=left,%
   xrightmargin=0zw,%
@@
 
+TODO(satos)
+
 \section{Related Works}
@@
 They prepared big corpus of C source codes, and they repeatedly mutated C code to reduce the difference of the target binary and the compilation result of the source code.
+
+TODO(satos)
 
@@
 This kind of name estimation also appears in the context of deobfuscation.
-要参考文献
+\cite{deobfsucation_matome}
+% これ雑にreferenceしたけどあんま意味ないよなぁ...?
 Deobfuscation is a reverse process of obfuscation.
@@
 \cite{JSNaughty} applied statistical machine translation for this task.
+
+TODO(satos)
+
+変数の性質から統計情報を取り出し、それを元に
+
 They calculated estimated the name of the variable by the functionality of it
@@
 
-In addition to
+The foregoing is the basic structure of the sequence-to-sequence model.
+To improve the performance of the model, there are some devices for the model.
+In the following, we introduce two devices, which are used in our experiment.
 
@@
 Second is the multi-layer reccurent neural networks, introduced in ここ決める.
-It is reported that, instead of the output of the LSTM units to another LSTM units will improve the accuracy of the prediction.
-This architecture is called as stucked reccurent neural networks or multi-layer reccurent neural networks.
+
+LSTMの出力を別のLSTMに入力して
+
+TODO(satos)
+
+% It is reported that, instead of the output of the LSTM units to another LSTM units will improve the accuracy of the prediction.
+% This architecture is called as stucked reccurent neural networks or multi-layer reccurent neural networks.
 
 \subsection{Attention}
-Attention is a extension module of sequence-to-sequence model to improve the quality of translation. 
+Attention is a extension module for sequence-to-sequence model to improve the quality of translation. 
 Simple sequence-to-sequence model has a problem that the length of the encoded vector $enc_{n}$ is fixed 
@@
 We inplemented the global general attention, which is intoduced in \cite{dot_attention}, for improving the quality of decompilation.
-In this subsection, we will describe about the global general attention.
+In the following, we will describe about the global general attention.
 
-In the pure sequence-to-sequence model, the conditional probability  $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ is calculated from $ dec_{k} $ ,which is the internal state of the decoder network.
-In the sequence-to-sequence with attention model, the probability is calcutated from $ dec_{k} $ and the context vevctor $ c_{k} $.
-$ c_{k} $
+The model with attention
 
-After generating $ dec_{k} $, the context vector $ c_{k} $ is calculated from the hidden states $ enc_{1} \dots enc_{n} $.
+TODO(satos)
 
-$ c_{k} = \sum_{k=1}^{n} $
+アテンション機構を用いる場合、前述したようにdecoder networkの出力 $ dec_{k} $ をそのまま用いて分布をesitmateするのではなく、
+$ dec_{k} $ と encoder network の出力 $ enc_{1} \dots enc_{n} $ (encoder が BiLSTMの場合 $ enc^{\gets}_{1} \dots enc^{\gets}_{n} $ も)
+を用いて context vector $ ctx_{k} $ を生成し、 $ dec_{k} $ と $ ctx_{k} $ によって条件付き分布をesitmateする。
 
-The attentional hidden state $ dec'_{k} $ is calculated from the $ dec_{k} $ and $ c_{k} $.
-Then, the probability $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ is estimated as $ softmax(W_{dec}(dec'_{k}))$, instead of $ softmax(W_{dec}(dec_{k}))$.
+$ ctx_{k} $ は、 $ enc_{1} \dots enc_{n} $ の加重平均によって計算される。 具体的には、
+各状態 $ enc_{l} $ について その状態のスコア $ a_{l} = score(dec_{k},enc_{l}) $ を計算し、
+$ ctx_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc{l} $ として計算される。
+
+この $ ctx_{k} $ を併せて用いることにより、 分布予測時に入力データの情報にアクセスすることができ、精度の向上が見込める。
+
+% In the pure sequence-to-sequence model, the conditional probability  $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ is calculated from $ dec_{k} $ ,which is the internal state of the decoder network.
+% In the sequence-to-sequence with attention model, the probability is calcutated from $ dec_{k} $ and the context vevctor $ c_{k} $.
+% $ c_{k} $
+
+% After generating $ dec_{k} $, the context vector $ c_{k} $ is calculated from the hidden states $ enc_{1} \dots enc_{n} $.
+
+% $ c_{k} = \sum_{k=1}^{n} $
+
+% The attentional hidden state $ dec'_{k} $ is calculated from the $ dec_{k} $ and $ c_{k} $.
+% Then, the probability $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ is estimated as $ softmax(W_{dec}(dec'_{k}))$, instead of $ softmax(W_{dec}(dec_{k}))$.
 
@@
 A tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
-Suppose the tree $ty$ is generated by the action sequence $ [a_1, \dots a_m] $, 
-where $ a_k $ is the action which expands left-most symbol of the nonterminal symbol in the tree generated by the action sequence $ [a_1, \dots a_{k-1}] $. 
-Then, the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(a_k|sx,[a_1, \dots a_{k-1}]) $, 
+Suppose the tree $ty$ is generated by the action sequence $ [act_1, \dots act_m] $, 
+where $ act_k $ is the action which expands left-most symbol of the nonterminal symbol in the tree generated by the action sequence $ [act_1, \dots act_{k-1}] $. 
+Then, the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(act_k|sx,[act_1, \dots act_{k-1}]) $, 
 so the sequence-to-sequence model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
-calculating $ LSTM_{dec}(dec_{k},av_{k}) $ for estimating $p(a_{k+1}|sx,[a_1, \dots a_{k}]) $.
+calculating $ LSTM_{dec}(dec_{k},av_{k}) $ for estimating $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $.
 
@@
 
-In the paper, they additionaly tries to use the information which is peculiar to the tree structure. 
+In that paper, they additionaly tries to use the information which is peculiar to the tree structure. 
 For expanding the node $d$, they also use the information of node type $ nf_{d} $ and the parent action $p_{d}$ from which $d$ is generated.
-And they calculalte $ LSTM_{dec}(dec_{k},[av_{k}; nfv_{d}; pv_{d}; ctx_{k}]) $ instead of $ LSTM_{dec}(dec_{k},av_{k}) $, 
-where $nfv_{d},pv_{d}$ are the vector embedding of $nf_{d},p_{d}$, and $ctx_{k}$ is the attention at k.
+And they calculalte $ LSTM_{dec}(dec_{k},[av_{k}; nfv_{d}; pv_{d}]) $ instead of $ LSTM_{dec}(dec_{k},av_{k}) $, 
+where $nfv_{d},pv_{d}$ are the vector embedding of $nf_{d},p_{d}$.
 
 They also used devised method for generating terminal symbols, because they need to copy the name of some variables from the program specification.
-But in our case, we don't need copy the information from the input, because the name information is lost when compiling, so we omit the discriptionp of this copy method.
+However, in our case, we don't need copy the information from the input, because the name information is lost when compiling.
+Nevertheless, it is found from the experiments that our decompilers often fail to recover the constant values in the programs.
+Therefore, implementing the copying method is left for future work.
+
+% しかしながら、実験の結果、ソースコード中の定数に関しては復元が困難であることが観察された。このため、プログラム中の定数に関してこのcopy method を実装することが考えられるが、
+% これは future work とする。
+
+% \subsection{Path Decomposite Sequence-to-Tree}
+% 前述の Sequence-to-Tree は プログラムの構造を考慮しているものの、アクションをそのまま列にするのは結局プログラムの木としての構造がある程度失われてしまっているのではないかと考えられる。
+% すなわち、アクションを列に展開しているため、ある部分木からその兄弟の部分木の生成に移る際に大幅なジャンプが生じている。
 
@@
 From each source code, we generated pairs of C source code fragment and x64 assembly code corresponds to the C fragment.
-Some sample fragments are shown in figure~\ref{fig:pairsoffragments}.
+Some example data pairs are shown in figure~\ref{fig:pairsoffragments}. 
+\\*
 
 \begin{figure}
-	\begin{tabular}{cc}
-		(TODO)データ対の例を載せる
+	\begin{tabular}{|l|l|} \hline
+	 C source code & x64 assembly \\ \hline 
+		\begin{lstlisting}[style=Csample]
+		r *= a;
+		\end{lstlisting}
+		&
+		\begin{lstlisting}[style=Asmsample]
+	mov eax,DWORD [rbp-0x4]
+	imul eax,DWORD [rbp-0x14]
+	mov DWORD [rbp-0x4],eax
+		\end{lstlisting} \\ \hline	
+		\begin{lstlisting}[style=Csample]
+	while(p >= 0){
+		p--;
+		r *= a;
+	}
+		\end{lstlisting}
+		&
+		\begin{lstlisting}[style=Asmsample]
+	jmp LABEL_0
+LABEL_1 :
+	sub DWORD [rbp-0x18],0x1
+	mov eax,DWORD [rbp-0x4]
+	imul eax,DWORD [rbp-0x14]
+	mov DWORD [rbp-0x4],eax
+LABEL_0 :
+	cmp DWORD [rbp-0x18],0x0
+	jns LABEL_1
+		\end{lstlisting} \\ \hline		
+		\begin{lstlisting}[style=Csample]
+int pow(int a,int p){
+	int r = 1;
+	while(p >= 0){
+		p--;
+		r *= a;
+	}
+	return r;
+}
+		\end{lstlisting}
+		&
+		\begin{lstlisting}[style=Asmsample]
+	push rbp
+	mov rbp,rsp
+	mov DWORD [rbp-0x14],edi
+	mov DWORD [rbp-0x18],esi
+	mov DWORD [rbp-0x4],0x1
+	jmp LABEL_0
+LABEL_1 :
+	sub DWORD [rbp-0x18],0x1
+	mov eax,DWORD [rbp-0x4]
+	imul eax,DWORD [rbp-0x14]
+	mov DWORD [rbp-0x4],eax
+LABEL_0 :
+	cmp DWORD [rbp-0x18],0x0
+	jns LABEL_1
+	mov eax,DWORD [rbp-0x4]
+	pop rbp
+	ret
+		\end{lstlisting} \\ \hline
 	\end{tabular}
-	\caption{Sample data fragments}
+	\caption{Example of training data pairs}
 	\label{fig:pairsoffragments}
@@
 \section{Model Configuration}
-The training model was implemented with Chainer. 
-We implemented three models, Seq2seq, Seq2seqWithAattention, and Seq2tree.
+The training model was implemented with Chainer version 4.5.0. (\url{https://chainer.org/})
+We implemented three models, Seq2seq, Seq2seqAtt, and Seq2tree.
 
-The encoding module was bidirectional LSTM in all of three models.
-The decoding module of Seq2seq and Seq2seqWithAattention predict the conditional probability of a next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
-The decoding module of Seq2tree predicts the conditional probability of a next action $ p(a_{k}|sx,[a_1, \dots a_{k-1}]) $.
+The encoder module was bidirectional LSTM in all of three models.
+The decoder module of Seq2seq and Seq2seqAtt predict the conditional probability of a next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $,
+while the decoder module of Seq2tree predicts the conditional probability of a next action $ p(a_{k}|sx,[a_1, \dots a_{k-1}]) $.
 
-Seq2seqWithAattention and Seq2tree have attention module, while Seq2seq have not.
+Seq2seqAtt and Seq2tree are the models with attention, while Seq2seq is not.
 
 \begin{figure}
-	\begin{tabular}{c|c}
-		Number of Layers & 4
-		%Dimensionality of Embedded Vectors & 128
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		 model & Seq2seq & Seq2seqAtt & Seq2tree \\ \hline
+		 Predict & \multicolumn{2}{|c|}{next token} & next action \\ \hline
+		 With Attention & no & \multicolumn{2}{|c|}{yes} \\ \hline
+		 Encoder & \multicolumn{3}{|c|}{Bidirectional LSTM} \\ \hline
+		Number of LSTM Layers & \multicolumn{3}{|c|}{4} \\ \hline
+		% Vector Dim & \multicolumn{3}{|c|}{128} \\ \hline
 	\end{tabular}
-	\caption{The configuration parameter of the models}
+	\caption{The configuration parameters of the models}
 	\label{fig:parameterofmodels}
@@
 
-Figure~\ref{fig:parameterofmodels} shows the parameter of the models.
+Figure~\ref{fig:parameterofmodels} shows the parameters of the models.
 
-(TODO)レイヤ数、ロスについてのべる。
+% (TODO)レイヤ数、ロスについてのべる。
 
-\section{Training and Testing}
+\section{Model Training}
 % 91 words
@@
 
-We calculated the quality of the decompilation by two metrics, edit distance ratio and BLEU.
+For the optimizer of the training, we used Adam, which is introduced in \cite{Adam}.
+The paremeters of Adam are $ (\alpha,\beta_1,\beta_2) = (0.001,0.9,0.999) $, which are the default parameters of Chainer version 4.5.0.
+% 学習の際のoptimizerにはAdam(文献)を用いた。
+
+\section{Model Evaluation}
+We evaluated the quality of the decompilation by two metrics, edit distance ratio and BLEU.
 
@@
 
-BLEU is the metrics for the naturallity of the generated program. 
+BLEU is the metrics for the similality of the ground truth and the decompilation result. 
 It is first introduced in \cite{BLEU}, for evaluating the performance of the machine translation.
+BLEU is calculated from the sets of the n-gram for each sentense. 
+If the two sentens has similar n-gram sets, the BLEU score becomes higher.
+In our case, it means that the decompilation result is more similer to the program written by human, that is, more human intelligible.
+
+% 2つの文のn-gram集合が似ているほど、BLEUスコアは高くなります。今回の場合はデコンパイル結果がより人間らしい自然な出力となっていることを意味します。
+
+In the experiment, we normalized variable names in the source codes by renaming. 
+% 補足として、今回は edit distance と BLEU を計算する際に、変数名を先頭から順に順番に付け直すことにより、ソースコード中の変数名の付けなおしを行っている。
+% これはプログラムの意味は変数名に依らないためである。
 
@@
 
-We tested three models. 
-Seq2seq is a model with
+TODO(satos)
 
-(TODO)seq2seq、アテンション付きseq2seq、seq2treeとバイナリそのまま/逆アセンブル後 の6パターンのデータを出す。
+まず先に、学習に用いたデータ長の分布を Figure~\ref{fig:editdist} に示す。
+ソースコードの部分木を全て列挙するデータ生成法の性質上、長さの短いコード辺が極端に多いことが確認できる。
+
+% We tested three models.
+
+今回、それぞれのモデルの学習には、東京大学のreedbushを用い、各モデルについて4時間学習させた。
+
+精度計測では、各モデルに対して テストケースから100個のデータをランダムに取り出して翻訳させ、それらの編集距離とBLEU値の平均を計測した。
+
+% 図1は各モデルについて、学習に用いたデータ数と編集距離をプロットしたグラフである。
+% 図2は各モデルについて、学習に用いたデータ数と編集距離をプロットしたグラフである。
+Figure~\ref{fig:editdist} shows the relation of trainig data size and the edit disatnce for each models.
+Figure~\ref{fig:bleu} shows the relation of trainig data size and the BLEU score for each models.
+
+図1からわかるように、attention付きのネットワークとそうでないネットワークの間には有意に差が存在しているが、
+Seq2seqWithAattention,Seq2Tree の間にはあまり差がみられない。
+
+% 図3はSeq2Treeについて、木の大きさと正確さをプロットしたグラフである。
+
+% (TODO)seq2seq、アテンション付きseq2seq、seq2treeとバイナリそのまま/逆アセンブル後 の6パターンのデータを出す。
+
 \chapter{Discussion}
+結果より、まずattention機構によって有意に精度が向上することが確認できた。
+しかしながら、 seq2seq と seq2tree の間に
+
 \chapter{Conclusion}

### 2019-01-27 calc_precision.py

@@ -1,6 +1,8 @@
 import edit_distance
 import pickle
 
+from nltk.translate import bleu_score
+
 import csrc2ast
 	
 import sys
@@ -24,23 +26,28 @@ def calc_csrc(fn):
 				d = names[d]
 			ts.append(d)
 		return ts
-	
-	ratio = 0
-	for (a,b),c in ds:	
-		b = normalize_sentense(b)
-		c = normalize_sentense(c)
+
+	ds = [(a,normalize_sentense(b),normalize_sentense(c)) for (a,b),c in ds]
+
+	edit_ratio = 0
+	bleu_ratio = 0
+	for a,b,c in ds:	
 		assert type(b) is list
 		assert type(c) is list
-		print(b)
-		print(c)
-		ratio += 1.0 - edit_distance.SequenceMatcher(b,c).ratio()
-	ratio /= len(ds)
-	return ratio
+		#print(b)
+		#print(c)
+		edit_ratio += 1.0 - edit_distance.SequenceMatcher(b,c).ratio()
+		bleu_ratio += bleu_score.sentence_bleu([b],c,smoothing_function=bleu_score.SmoothingFunction().method1)
+	edit_ratio /= len(ds)
+	bleu_ratio /= len(ds)
+	return (edit_ratio,bleu_ratio)
 	
 
 def calc_ast(fn):
 	with open(fn,'rb') as fp:
 		ds = pickle.load(fp)
+	#print(len(ds))
+	ds = ds[:1000]
 	def tree2normalizedsentense(tree,normalize=True):
 		s = csrc2ast.ast2token_seq(tree)
 		if not normalize:
@@ -55,24 +62,55 @@ def calc_ast(fn):
 			ts.append(sd)
 		return ts
 	
-	ratio = 0
-	for (a,b),c in ds:	
-		b = tree2normalizedsentense(b)
-		c = tree2normalizedsentense(c)
+	ds = [(a,tree2normalizedsentense(b),tree2normalizedsentense(c)) for (a,b),c in ds]
+	ds = list(filter(lambda abc: (abc[1],abc[2]) != ([],[]),ds))
+	edit_ratio = 0
+	bleu_ratio = 0
+	for a,b,c in ds:	
 		assert type(b) is list
 		assert type(c) is list
-		print(' '.join(b))
-		print(' '.join(c))
-		print('-' * 100)
-		ratio += 1.0 - edit_distance.SequenceMatcher(b,c).ratio()
[…]

### 2019-01-27 gen_handsample.py

@@ -1,0 +1,38 @@
+import os
+import csrc2ast
+import asm_objd_conv
+import my_c_ast
+
+def getds(fn):
+	os.system('clang -Xclang -ast-dump -fsyntax-only %s.c > %s.parsed 2>/dev/null' % (fn,fn))
+	ast = csrc2ast.src2ast('%s.c' % fn,'%s.parsed' % fn)
+	
+	os.system('gcc -O0 -S -g -c %s.c -o %s.s' % (fn,fn))
+	os.system('as %s.s -o %s.o' % (fn,fn))
+	os.system('objdump -d -M intel -w %s.o > %s.objd' % (fn,fn))
+	with open('%s.s' % fn,'r') as fp:
+		asm = fp.read()
+	with open('%s.objd' % fn,'r') as fp:
+		objd = fp.read()
+	ds = asm_objd_conv.get_line_from_list(asm,objd)
+	astdata = ast.subexpr_line_list()
+	
+	for (a,b),nsize,tree in astdata:
+		nas = ''
+		for i,d in ds:
+			if a <= i and i < b:
+				nas += ' '.join(d) + '\n'
+				#nas.append(d)
+		if len(nas)==0:
+			continue
+		
+		print(nas)
+		print('.' * 100)
+		nast = my_c_ast.load_astdata(tree)
+		nast.before_show()
+		print(nast.show())
+		print('-' * 100)
+
+
+
+getds('y')

### 2019-01-27 model_seq2seq_pure.py

@@ -92,6 +92,7 @@ class Seq2seq(chainer.Chain):
 			result = []
 			
 			for i,hxs in enumerate(xs_outputs):
+				print('translate',i)
 				nhx,ncx = hx[i],cx[i]
 				ncx = F.reshape(ncx,(ncx.shape[0],1,ncx.shape[1]))
 				nhx = F.reshape(nhx,(nhx.shape[0],1,nhx.shape[1]))
@@ -99,11 +100,16 @@ class Seq2seq(chainer.Chain):
 				
 				for j in range(self.n_maxlen):
 					to_beam = []
-					for r,(kd,v,nhx,ncx) in beam_data:
+					for ci,(r,(kd,v,nhx,ncx)) in enumerate(beam_data):
+						if len(kd)>0 and kd[-1]==EOS_DST:
+							to_beam.append((r,(kd,v,nhx,ncx)))
+							if ci == 0:
+								break
+							continue
 						#print(v.shape)
 						thx,tcx,ys = self.decoder(nhx,ncx,[v])
 						yh = ys[0]
-						wy = self.Ws(yh).data[0]
+						wy = self.W(yh).data[0]
 						wy = F.reshape(F.log_softmax(F.reshape(wy,(1,self.n_target_vocab))),(self.n_target_vocab,)).data
 						#print(wy.shape)
 						to_beam += [(r+nr,(kd + [i],ivs[i],thx,tcx)) for i,nr in enumerate(wy)]

### 2019-01-27 model_seq2tree.py

@@ -23,7 +23,7 @@ def sequence_embed(embed, xs):
 
 
 from model_attention import GlobalGeneralAttention
-
+import random
 
 
 class Seq2Tree(chainer.Chain):
@@ -42,29 +42,34 @@ class Seq2Tree(chainer.Chain):
 		self.embed_root_idx = ns
 		self.embed_y_size = ns+1
 		
-		#self.choice_num_sum = sum(list(map(lambda d: len(d),self.trans_data)))
-		
 		self.choicerange = []
+		self.is_trivial = []
 		self.choice_idx = []
 		s = 0
 		for d in self.trans_data:
+			ist = len(d)<=1
+			self.is_trivial.append(ist)
+			if ist:
+				self.choicerange.append(None)
+				self.choice_idx.append([0])
+				continue
 			b = s
 			s += len(d)
 			self.choicerange.append((b,s))
 			self.choice_idx.append(list(range(b,s)))
-		
+		#self.choice_num_sum = sum(list(map(lambda d: len(d),self.trans_data)))
+		self.n_choicables = s
 		self.type_size = len(self.embed_idx)
-		self.n_all_choice = sum(map(lambda x: len(x),self.trans_data))
 		
 		with self.init_scope():
 			self.embed_x = L.EmbedID(n_source_vocab, n_units)
 			self.embed_y = L.EmbedID(self.embed_y_size, n_units) # maybe mergable
-						
+			
 			self.encoder = L.NStepBiLSTM(n_layers, n_units, n_units, 0.1)
 			self.decoder = L.NStepLSTM(n_layers, n_units, n_units*2, 0.1)
 			self.Wc = L.Linear(n_units*4, n_units)
-			self.Ws = L.Linear(n_units, self.n_all_choice)
-						
+			self.Ws = L.Linear(n_units, self.n_choicables)
+			
 			#self.att = Attention(n_units)
 			self.att = GlobalGeneralAttention(n_units)
 		
@@ -73,133 +78,129 @@ class Seq2Tree(chainer.Chain):
 		self.v_eos_src = v_eos_src
 		self.n_maxsize = n_maxsize
 		self.rootidx = len(trans_data)-1
+	
 		
 	def forward(self, xs, ys):
 		batch = len(xs)
 		xs = [xp.array(x[::-1]) for x in xs]
[…]

### 2019-01-27 model_seq2tree_flatten.py

@@ -44,8 +44,15 @@ class Seq2Tree_Flatten(chainer.Chain):
 		
 		self.choicerange = []
 		self.choice_idx = []
+		self.is_trivial = []
 		s = 0
 		for d in self.trans_data:
+			ist = len(d)<=1
+			self.is_trivial.append(ist)
+			if ist:
+				self.choicerange.append(None)
+				self.choice_idx.append([0])
+				continue
 			b = s
 			s += len(d)
 			self.choicerange.append((b,s))
@@ -95,6 +102,8 @@ class Seq2Tree_Flatten(chainer.Chain):
 		ys_in_0  = [xp.array(list(map(lambda ab: ab[0][0],y))) for y in ys]
 		ys_in_1  = [xp.array(list(map(lambda ab: ab[0][1],y))) for y in ys]
 		ys_out = [xp.array(list(map(lambda ab: self.choice_idx[ab[0][1]][ab[1]],y))) for y in ys]
+		ys_conds = [xp.array(list(map(lambda ab: self.is_trivial[ab[0][1]],d)),dtype=xp.bool) for d in ys]
+		#print(ys_conds)
 		#ys_out = [xp.array(list(map(lambda ab: ab[1],y))) for y in ys]
 		
 		# Both xs and ys_in are lists of arrays.
@@ -128,8 +137,11 @@ class Seq2Tree_Flatten(chainer.Chain):
 		
 		concat_os = F.concat(att_os, axis=0)
 		concat_ys_out = F.concat(ys_out, axis=0)
-		loss = F.sum(F.softmax_cross_entropy(
-			self.Ws(concat_os), concat_ys_out, reduce='no')) / batch
+		concat_cond = F.concat(ys_conds, axis=0)
+		sxe = F.softmax_cross_entropy(self.Ws(concat_os), concat_ys_out, reduce='no')
+		sxec = F.where(concat_cond,xp.zeros(sxe.shape,dtype=xp.float32),sxe)
+
+		loss = F.sum(sxec) / batch
 		#print('lossed')
 		chainer.report({'loss': loss}, self)
 		#n_words = concat_ys_out.shape[0]

### 2019-01-27 model_seq2tree_heavy.py

@@ -1,0 +1,206 @@
+import numpy as np
+import chainer
+import chainer.links as L
+import chainer.functions as F
+from chainer import training
+from chainer.training import extensions
+from chainer import serializers
+
+from chainer import cuda
+from cuda_setting import isgpu
+	
+if isgpu:
+	xp = cuda.cupy
+else:
+	xp = np
+
+def sequence_embed(embed, xs):
+	x_len = [len(x) for x in xs]
+	x_section = np.cumsum(x_len[:-1])
+	ex = embed(F.concat(xs, axis=0))
+	exs = F.split_axis(ex, x_section, 0)
+	return exs
+
+
+from model_attention import GlobalGeneralAttention
+
+
+
+class Seq2Tree(chainer.Chain):
+	def __init__(self, n_layers, n_source_vocab, trans_data, n_units,v_eos_src,n_maxsize):
+		super(Seq2Tree, self).__init__()
+
+		# for each nodetype, for each move, the result array.
+		self.trans_data = trans_data
+		self.embed_idx = []
+		ns = 0
+		def inc():
+			nonlocal ns
+			ns += 1
+			return ns-1
+		self.embed_idx = [[[inc() for v in vs] for vs in moves] for moves in self.trans_data]
+		self.embed_root_idx = ns
+		self.embed_y_size = ns+1
+		
+		#self.choice_num_sum = sum(list(map(lambda d: len(d),self.trans_data)))
+		
+		self.choicerange = []
+		self.choice_idx = []
+		s = 0
+		for d in self.trans_data:
+			b = s
+			s += len(d)
+			self.choicerange.append((b,s))
+			self.choice_idx.append(list(range(b,s)))
+		
+		self.type_size = len(self.embed_idx)
+		self.n_all_choice = sum(map(lambda x: len(x),self.trans_data))
+		
+		with self.init_scope():
+			self.embed_x = L.EmbedID(n_source_vocab, n_units)
+			self.embed_y = L.EmbedID(self.embed_y_size, n_units) # maybe mergable
+						
+			self.encoder = L.NStepBiLSTM(n_layers, n_units, n_units, 0.1)
+			self.decoder = L.NStepLSTM(n_layers, n_units, n_units*2, 0.1)
[…]

### 2019-01-27 plot_data_size.py

@@ -1,0 +1,52 @@
+
+import pickle
+
+tds = []
+tdsi = 0
+
+lens = {i: 0 for i in range(1000)}
+for i in range(13):
+	if i%10==0:
+		print(i)
+	with open('dataset_asm_ast/data_%d.pickle' % i,'rb') as fp:
+		cs = pickle.load(fp)
+		pass
+	print('loaded')
+	print(len(cs[1]))
+	#continue
+	for d in cs[1]:
+		#print(d)
+		if lens[d[1]] >= 1000:
+			continue
+		lens[d[1]] += 1
+		tds.append(d)
+		if len(tds)>=100000:
+			with open('dataset_asm_ast/data_cutoff_%d.pickle' % tdsi,'wb') as fp:
+				print(len(tds))
+				pickle.dump(tds,fp)
+			tds = []
+			tdsi += 1
+	print('calced')
+
+with open('dataset_asm_ast/data_cutoff_%d.pickle' % tdsi,'wb') as fp:
+	print(len(tds))
+	pickle.dump(tds,fp)
+
+print(tdsi)
+print(lens)
+exit()
+
+
+lens = {0: 0, 1: 0, 2: 1652760, 3: 3545865, 4: 1981035, 5: 1615788, 6: 1320921, 7: 1039905, 8: 661185, 9: 595962, 10: 649809, 11: 418311, 12: 342486, 13: 285264, 14: 388629, 15: 293904, 16: 218043, 17: 223596, 18: 110493, 19: 178794, 20: 89109, 21: 124344, 22: 102294, 23: 115794, 24: 82278, 25: 112086, 26: 62838, 27: 75258, 28: 69777, 29: 87633, 30: 56466, 31: 73809, 32: 74691, 33: 44496, 34: 84852, 35: 72459, 36: 31932, 37: 50733, 38: 62739, 39: 35154, 40: 43632, 41: 28260, 42: 24885, 43: 21951, 44: 21825, 45: 22536, 46: 19134, 47: 17352, 48: 12312, 49: 23715, 50: 13851, 51: 28827, 52: 17100, 53: 16128, 54: 16758, 55: 15084, 56: 17973, 57: 16992, 58: 12924, 59: 12285, 60: 8973, 61: 16542, 62: 9855, 63: 17478, 64: 10836, 65: 13131, 66: 12600, 67: 13212, 68: 8100, 69: 13500, 70: 9
[…]

### 2019-01-27 plot_edit_bleus.py

@@ -1,0 +1,17 @@
+from plot_edit_bleus_data import seq2seq,seq2seq_att,seq2tree
+from matplotlib import pyplot as plt
+
+
+def lap(i,v):
+	return list(map(lambda x: x[i],v))
+
+seq2seq = seq2seq[:21]
+
+ts = ['edit distance','BLEU']
+for t in range(2):
+	plt.plot(lap(t,seq2seq),marker='o',label='Seq2seq')
+	plt.plot(lap(t,seq2seq_att),marker='s',label='Seq2seqAtt')
+	plt.plot(lap(t,seq2tree),marker='^',label='Seq2tree')
+	plt.legend()
+	plt.title(ts[t])
+	plt.show()

### 2019-01-27 plot_edit_bleus_data.py

@@ -1,0 +1,114 @@
+seq2seq = [
+(0.7728057079961657, 0.04327963218358302) ,
+(0.7246681619915292, 0.062413723861251186) ,
+(0.5622441691784281, 0.161543074209792) ,
+(0.5571608709968149, 0.1705308106393741) ,
+(0.4347882265993966, 0.28413845438199764) ,
+(0.4610206859752497, 0.24585704036163694) ,
+(0.5177618755723395, 0.22331856006117884) ,
+(0.49165962997321133, 0.23942462641940268) ,
+(0.5082117594904336, 0.2759228564709456) ,
+(0.4255664281281738, 0.26495207620395755) ,
+(0.48254992982344336, 0.2605896422632786) ,
+(0.4023770008151775, 0.31263203142764895) ,
+(0.4204470683659443, 0.3557809735522121) ,
+(0.3771533494449762, 0.3346509392217184) ,
+(0.30504572769339194, 0.39270079314539363) ,
+(0.41117802105158724, 0.3168229997637956) ,
+(0.43094457089536997, 0.30918082638808747) ,
+(0.37975157428357, 0.2919482888052986) ,
+(0.3417304436207085, 0.3814106415759484) ,
+(0.3508211751171558, 0.38963207011650974) ,
+(0.3642342658631444, 0.35457698641705315) ,
+(0.39202908248362145, 0.3246332266789198) ,
+(0.4263310293350607, 0.2897421798012639) ,
+(0.31538044904740714, 0.40787065162098485) ,
+(0.3384712574886655, 0.4026523467500745) ,
+(0.3070486087857907, 0.36694571459090547) ,
+(0.36899456345601594, 0.33899782228254355) ,
+(0.3902575576964328, 0.33209793574013086) ,
+(0.3131023086790649, 0.3700978335404176) ,
+(0.319628562688506, 0.3658422257829181) ,
+(0.3075334784381214, 0.36454832407013144) ,
+(0.3676624447779134, 0.33885767486306956) ,
+(0.38268304599886, 0.35779378713339827) ,
+(0.3514617211480929, 0.3634557064465532) ,
+(0.31664434018528576, 0.38185463910105577) ,
+(0.31488753366548605, 0.3845155067510481) ,
+(0.3622080438264711, 0.38717594447431913) ,
+(0.3665682394851486, 0.3497849543961857) ,
+(0.38051241922390544, 0.3684727852612876) ,
[…]

### 2019-01-27 precision.py

@@ -65,60 +65,8 @@ import csrc2ast
 import edit_distance
 
 def prec_seq2tree(model,data,asm_vocab,fn):
-	def tree2normalizedsentense(tree,normalize=True):
-		s = csrc2ast.ast2token_seq(tree)
-		if not normalize:
-			return s
-		ts = []
-		names = []
-		for sd in s:
-			if sd[:8]=='__ALPHA_':
-				if not sd in names:
-					names.append(sd)
-				sd = '__NORMALIZED_%d' % names.index(sd)
-			ts.append(sd)
-		return ts
-	
-	def calcurate_edit_distance():
-		ratio = 0.0
-		ds = [data.get_test(-1) for _ in range(100)]
-		for i,(fr,to) in enumerate(ds):
-			result = model.translate([fr])[0]
-			result = tree2normalizedsentense(result)
-			to = tree2normalizedsentense(to)
-			ratio += 1.0 - edit_distance.SequenceMatcher(to,result).ratio()
-			print(' '.join(to))
-			print(' '.join(result))
-			print('-'*100,'rate',ratio/(i+1))
-			print
-		ratio /= len(ds)
-		return ratio
 	
 	def translate():
-		"""
-		eds = calcurate_edit_distance()
-		print('edit distance:',eds)
-		with open(fn,'w') as fp:
-			res = ""
-			for _ in range(100):
-				source,target = data.get_test(-1)
-				result = model.translate([model.xp.array(source)])[0]
-				print('got result')
-				target = tree2normalizedsentense(target,normalize=False)
-				result = tree2normalizedsentense(result,normalize=False)
-				
-				source_sentence = ' '.join([asm_vocab[x] for x in source])
-				target_sentence = ' '.join(target)
-				result_sentence = ' '.join(result)
-				nr = ""
-				nr += ('# source : ' + source_sentence) + "\n"
-				nr += ('# expect : ' + target_sentence) + "\n"
-				#print('# result_array : ' + ' '.join(["%d" % y for y in result]))
-				nr += ('# result : ' + result_sentence) + "\n"
-				print(nr)
-				res += nr
-			fp.write(res)
-		"""
 		ds = [data.get_test(-1) for _ in range(100)]
 		results = model.translate(list(map(lambda x: x[0],ds)))
 		wds = list(zip(ds,results))

### 2019-01-27 train.py

@@ -41,6 +41,7 @@ if isgpu:
 else:
 	xp = np
 
+
 class Asm_csrc_dataset(chainer.dataset.DatasetMixin):
 	def __init__(self):
 		super(Asm_csrc_dataset,self).__init__()
@@ -94,6 +95,8 @@ def init_seq2seq():
 		asm_vocab = pickle.load(fp)
 	
 	dataset = Asm_csrc_dataset()
+	print('load dataset')
+	print(len(dataset))
 	
 	v_eos_src = len(asm_vocab)
 	asm_vocab += ['__EOS_ASM_']
@@ -102,9 +105,13 @@ def init_seq2seq():
 	v_eos_dst = len(c_vocab)
 	c_vocab += ['__EOS_C_']
 	dst_vocab_len = len(c_vocab)
- 
-	model = Seq2seq(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_dst, n_maxlen)
-	#model = Seq2seq_with_GlobalAtt(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_dst, n_maxlen)
+ 	
+	if modelname == 'seq2seq':
+		model = Seq2seq(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_dst, n_maxlen)
+	elif modelname == 'seq2seq_att':
+		model = Seq2seq_with_GlobalAtt(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_dst, n_maxlen)
+	else:
+		assert False
 	#serializers.load_npz('iter1000_seq_att.npz',model)
 	#serializers.load_npz('save_models/models_prestudy_edit_dist_0.65/iter_47600__edit_dist_0.691504__time_2018_12_28_01_36_30.npz',model)
 	if not isgpu:
@@ -124,8 +131,8 @@ def init_seq2seq():
 		nonlocal logt,model,optimizer
 		if isgpu:
 			model.to_cpu()
-		serializers.save_npz('seq2seq/models/iter_%s_time_%s.npz' % (logt,getstamp()),model)
-		serializers.save_npz('seq2seq/optimizers/iter_%s_time_%s.npz' % (logt,getstamp()),optimizer)
+		serializers.save_npz(modelname + '/models/iter_%s_time_%s.npz' % (logt,getstamp()),model)
[…]

### 2019-01-27 texs/paper_base.tex
nyan

@@
 \usepackage{natbib}
+\usepackage[dvipdfmx]{graphicx}
 
@@
 In experiments, we use source codes collected from open source projects and their binary data for training and evaluating the neural networks.
-(TODO)実験結果について述べること(まだ未確定)
+From the experiment, we can observe little improvement in the decompilation result with the use of attention.
+
 \end{eabstract}
@@
 実験では、オープンソースプロジェクトから収集したソースコードとそのバイナリデータを用いてニューラルネットワークを学習し、その性能を検証した。
+実験の結果、注意機構を用いることににより、逆コンパイル結果における若干の精度向上が認められた。
 \end{jabstract}
@@
 
-The foregoing is the basic structure of the sequence-to-sequence model.
-To improve the performance of the model, there are some devices for the model.
+What is mentioned above is the basic structure of the sequence-to-sequence model.
+To improve the performance of the sequence-to-sequence model, there are some devices for the model.
 In the following, we introduce two devices, which are used in our experiment.
@@
 
-Second is the multi-layer reccurent neural networks, introduced in ここ決める.
-
-LSTMの出力を別のLSTMに入力して
+Second is the multi-layer reccurent neural networks, introduced in \cite{multi_layer}.
 
@@
 
-The attention module is first developed in \cite{attention_paper}.
+The attention module is first developed by \cite{attention_paper}.
 We inplemented the global general attention, which is intoduced in \cite{dot_attention}, for improving the quality of decompilation.
@@
 
-The model with attention
+As above mentioned, the pure sequence-to-sequence model uses the output of decoder network $ dec_{k} $ for estimating 
+the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
+In the sequence-to-sequence model with attention, 
+a context vector $ ctx_{k} $ is calculalted from $ dec_{k} $ and the internal states of encoder network $ enc_{1} \dots enc_{n} $, 
+then the distribution is estimated from the output vector $ dec_{k} $ and context vector $ ctx_{k} $.
+The context vector $ ctx_{k} $ is calculated as follows.
+For each state $ enc_{l} $, the importance of the state $ a_{l} $ is calculalted as $ a_{l} = score(dec_{k},enc_{l}) $,
+then the $ ctx_{k} $ is calculated as $ ctx_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc{l} $, as the weighted average of $ enc_{1} \dots enc_{n} $.
+% Multiple score functions are introduced by \cite{dot_attention}, and we choiced 
+In the paper by \cite{dot_attention}, various kinds of score function is suggested.
+We used general score function, which is calculated as $ score(dec_{k},enc_{l}) = dec_{k}^T W enc_{l} $ ,
+where W is the parameter matrix.
 
-TODO(satos)
+% With the information of the internal state $ ctx_{k} $ of the encoder network, the decoder network can access to the
 
-アテンション機構を用いる場合、前述したようにdecoder networkの出力 $ dec_{k} $ をそのまま用いて分布をesitmateするのではなく、
-$ dec_{k} $ と encoder network の出力 $ enc_{1} \dots enc_{n} $ (encoder が BiLSTMの場合 $ enc^{\gets}_{1} \dots enc^{\gets}_{n} $ も)
-を用いて context vector $ ctx_{k} $ を生成し、 $ dec_{k} $ と $ ctx_{k} $ によって条件付き分布をesitmateする。
+% アテンション機構を用いる場合、前述したようにdecoder networkの出力 $ dec_{k} $ をそのまま用いて分布をesitmateするのではなく、
+% $ dec_{k} $ と encoder network の出力 $ enc_{1} \dots enc_{n} $ (encoder が BiLSTMの場合 $ enc^{\gets}_{1} \dots enc^{\gets}_{n} $ も)
+% を用いて context vector $ ctx_{k} $ を生成し、 $ dec_{k} $ と $ ctx_{k} $ によって条件付き分布をesitmateする。
 
-$ ctx_{k} $ は、 $ enc_{1} \dots enc_{n} $ の加重平均によって計算される。 具体的には、
-各状態 $ enc_{l} $ について その状態のスコア $ a_{l} = score(dec_{k},enc_{l}) $ を計算し、
-$ ctx_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc{l} $ として計算される。
+% $ ctx_{k} $ は、 $ enc_{1} \dots enc_{n} $ の加重平均によって計算される。 具体的には、
+% 各状態 $ enc_{l} $ について その状態のスコア $ a_{l} = score(dec_{k},enc_{l}) $ を計算し、
+% $ ctx_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc{l} $ として計算される。
 
-この $ ctx_{k} $ を併せて用いることにより、 分布予測時に入力データの情報にアクセスすることができ、精度の向上が見込める。
+% この $ ctx_{k} $ を併せて用いることにより、 分布予測時に入力データの情報にアクセスすることができ、精度の向上が見込める。
 
@@
 The integer literal less than 256 is preserved, and the literal greater than 256 is clipped to 256.
-The string, float and character literals are converted to {\sl \_\_LITERAL\_(string|float|char)\_\_} simbol.
+The string, float and character literals are converted to {\sl \_\_LITERAL\_\_} simbol.
 
@@
 
-\begin{figure}
-	\begin{tabular}{|c|c|c|c|}
+\begin{figure}[h]
+	\begin{tabular}{|c||c|c|c|}
 		\hline
-		 model & Seq2seq & Seq2seqAtt & Seq2tree \\ \hline
-		 Predict & \multicolumn{2}{|c|}{next token} & next action \\ \hline
+		  & Seq2seq & Seq2seqAtt & Seq2tree \\ \hline \hline
+		 Generate & \multicolumn{2}{|c|}{token sequence} & AST \\ \hline
 		 With Attention & no & \multicolumn{2}{|c|}{yes} \\ \hline
@@
 Edit distance ratio is the metrics for the correctness of the decompilation result.
-Here, the edit distance ratio between two strings means the Levenshtein distance divided by the longer length of the strings.
+Here, the edit distance ratio between two strings means the Levenshtein distance divided by the average length of the two strings.
 Idealy, the correctness of the decompilation result should be measured by the distance of the meaning of the program.
@@
 
-\chapter{Results}
+\chapter{Evaluation}
+In this chapter, we show the evaluated result of the three models, Seq2seq, Seq2seqAtt, and Seq2tree.
+% We trained each models with reedbush, を用い、各モデルについて4時間学習させた。
+% We collected approximately $ 10^7 $ pairs of datasets.
 
-TODO(satos)
+% TODO(satos)
 
-まず先に、学習に用いたデータ長の分布を Figure~\ref{fig:editdist} に示す。
-ソースコードの部分木を全て列挙するデータ生成法の性質上、長さの短いコード辺が極端に多いことが確認できる。
+% At first, we show the
+
+% まず先に、学習に用いたデータ長の分布を Figure~\ref{fig:editdist} に示す。
+% ソースコードの部分木を全て列挙するデータ生成法の性質上、長さの短いコード辺が極端に多いことが確認できる。
 
@@
 
-今回、それぞれのモデルの学習には、東京大学のreedbushを用い、各モデルについて4時間学習させた。
+% 今回、それぞれのモデルの学習には、東京大学のreedbushを用い、各モデルについて4時間学習させた。
 
-精度計測では、各モデルに対して テストケースから100個のデータをランダムに取り出して翻訳させ、それらの編集距離とBLEU値の平均を計測した。
+% 精度計測では、各モデルに対して テストケースから100個のデータをランダムに取り出して翻訳させ、それらの編集距離とBLEU値の平均を計測した。
+
+For evaluating each model, we randomly sampled 100 data pairs from test cases, generated estimated decompilation results for each test cases,
+then averaged the edit distance ratios and BLEU scores between results and ground truths.
+
+\begin{figure}[]
+	\includegraphics[width=12cm]{edit_dist.png}
+	\caption{Averaged edit distance ratio for each models}
+	\label{fig:editdist}
+	\includegraphics[width=12cm]{bleu.png}
+	\caption{Averaged BLEU score for each models}
+	\label{fig:bleu}
+\end{figure}
 
@@
 % 図2は各モデルについて、学習に用いたデータ数と編集距離をプロットしたグラフである。
-Figure~\ref{fig:editdist} shows the relation of trainig data size and the edit disatnce for each models.
-Figure~\ref{fig:bleu} shows the relation of trainig data size and the BLEU score for each models.
+Figure~\ref{fig:editdist} shows the relation of trainig data size and the averaged edit distance ratio for each models.
+Figure~\ref{fig:bleu} shows the relation of trainig data size and the averaged BLEU score for each models.
+The lower edit distance ratio and the higher BLEU score means the better decompilation performance.
 
-図1からわかるように、attention付きのネットワークとそうでないネットワークの間には有意に差が存在しているが、
-Seq2seqWithAattention,Seq2Tree の間にはあまり差がみられない。
+We can see that Seq2seqAtt shows slightly better results in both edit distance ratios and BLEU scores, 
+while there are no significant difference between Seq2seq and Seq2tree in both metrics.
+Seq2seqの結果とSeq2seqAttの結果を比較することにより、attention が性能向上に寄与していることがわかります。
+逆にSeq2treeにはattentionがあるにもかかわらずSeq2seqと比較して性能向上が見られなかったわけですが、
+これはCのソースコードをASTに変換した際に、データサイズが増えたためであると考えられます。
+
+\begin{figure}[]
+	\includegraphics[width=12cm]{c_lens.png}
+	\caption{Length distribution of C token flagments}
+	\label{fig:csizes}
+	\includegraphics[width=12cm]{ast_lens.png}
+	\caption{Length distribution of datasets as AST}
+	\label{fig:astsizes}
+\end{figure}
+
+Figure~\ref{fig:csizes} shows the length distribution of the dataset as C token sequences
+, and figure~\ref{fig:astsizes} shows the size distribution of the same dataset as AST trees.
+The length 
+According to the figures, the AST size is 2~3 times larger than that of C source codes.
+
+% According to the figure 1, the 
+% 図1からわかるように、attention付きのネットワークとそうでないネットワークの間には有意に差が存在しているが、
+% Seq2seqWithAattention,Seq2Tree の間にはあまり差がみられない。
 
@@
 
-\chapter{Discussion}
-結果より、まずattention機構によって有意に精度が向上することが確認できた。
-しかしながら、 seq2seq と seq2tree の間に
+% Figure~\ref{fig:csrs_lens} and figure~\ref{fig:ast_lens} show 学習に用いたデータセットについて、C言語のトークン列としてみたときのデータ長とAST tree として見たときの action size をそれぞれグラフにしてプロットしたものである。
+% 全体的に、
+
+% \chapter{Discussion}
+% 結果より、まずattention機構によって有意に精度が向上することが確認できた。
+% しかしながら、 seq2seq と seq2tree の間に
 

### 2019-01-27 calc_precision.py

@@ -47,7 +47,7 @@ def calc_ast(fn):
 	with open(fn,'rb') as fp:
 		ds = pickle.load(fp)
 	#print(len(ds))
-	ds = ds[:1000]
+	ds = ds[:100]
 	def tree2normalizedsentense(tree,normalize=True):
 		s = csrc2ast.ast2token_seq(tree)
 		if not normalize:
@@ -99,7 +99,7 @@ for i in range(21):
 	print(r,',')
 print(']')
 """
-
+"""
 print('[')
 for i in range(19):
 	fn = 'translate_data/seq2tree_flatten_verbose_choice/iter_%d_transdata.pickle' % (i*100)
@@ -113,4 +113,4 @@ for i in range(21):
 	r = calc_ast(fn)
 	print(r,',')
 print(']')
-"""
+

### 2019-01-27 plot_data_size.py

@@ -1,13 +1,18 @@
-
 import pickle
 
 tds = []
 tdsi = 0
+'''
+def csize(d):
+	res = 1
+	_,_,cs = d
+	for c in cs:
+		res += csize(c)
+	return res
 
-lens = {i: 0 for i in range(1000)}
+lens = {i: 0 for i in range(2000)}
 for i in range(13):
-	if i%10==0:
-		print(i)
+	print(i)
 	with open('dataset_asm_ast/data_%d.pickle' % i,'rb') as fp:
 		cs = pickle.load(fp)
 		pass
@@ -16,37 +21,52 @@ for i in range(13):
 	#continue
 	for d in cs[1]:
 		#print(d)
-		if lens[d[1]] >= 1000:
-			continue
-		lens[d[1]] += 1
-		tds.append(d)
+		#if lens[d[1]] >= 1000:
+		#	continue
+		lens[csize(d[2])] += 1
+		#tds.append(d)
+		"""
 		if len(tds)>=100000:
 			with open('dataset_asm_ast/data_cutoff_%d.pickle' % tdsi,'wb') as fp:
 				print(len(tds))
 				pickle.dump(tds,fp)
 			tds = []
 			tdsi += 1
+		"""
 	print('calced')
 
-with open('dataset_asm_ast/data_cutoff_%d.pickle' % tdsi,'wb') as fp:
-	print(len(tds))
-	pickle.dump(tds,fp)
+#with open('dataset_asm_ast/data_cutoff_%d.pickle' % tdsi,'wb') as fp:
+#	print(len(tds))
+#	pickle.dump(tds,fp)
 
-print(tdsi)
+#print(tdsi)
 print(lens)
 exit()
+'''
+
[…]

### 2019-01-27 plot_data_size_data.py

@@ -1,0 +1,1 @@
+ast_lens = {0: 0, 1: 0, 2: 0, 3: 0, 4: 234, 5: 63, 6: 81414, 7: 179217, 8: 537786, 9: 813510, 10: 143001, 11: 897561, 12: 499221, 13: 334674, 14: 362682, 15: 302580, 16: 537264, 17: 541962, 18: 327078, 19: 340983, 20: 223191, 21: 218151, 22: 270549, 23: 268767, 24: 195885, 25: 138033, 26: 266229, 27: 174366, 28: 218196, 29: 191151, 30: 262161, 31: 179667, 32: 93708, 33: 116541, 34: 122121, 35: 98640, 36: 108207, 37: 130734, 38: 89001, 39: 123489, 40: 74844, 41: 93888, 42: 56403, 43: 79812, 44: 110889, 45: 56115, 46: 103599, 47: 37476, 48: 31644, 49: 50472, 50: 34524, 51: 28260, 52: 121266, 53: 43443, 54: 36090, 55: 66672, 56: 37521, 57: 28566, 58: 25245, 59: 51192, 60: 25668, 61: 59508, 62: 25218, 63: 33948, 64: 66042, 65: 40743, 66: 61119, 67: 50103, 68: 29115, 69: 28602, 70: 20655, 71: 17739, 72: 63036, 73: 44010, 74: 19944, 75: 19242, 76: 23850, 77: 24021, 78: 18387, 79: 16893, 80: 25992, 81: 21870, 82: 16092, 83: 18756, 84: 11826, 85: 19872, 86: 22932, 87: 20538, 88: 9468, 89: 10062, 90: 22203, 91: 16416, 92: 10845, 93: 18243, 94: 12150, 95: 10314, 96: 19782, 97: 9783, 98: 7830, 99: 11916, 100: 7704, 101: 7560, 102: 8874, 103: 5103, 104: 13077, 105: 8091, 106: 6399, 107: 25632, 108: 11547, 109: 26028, 110: 10863, 111: 5715, 112: 26334, 113: 8118, 114: 5976, 115: 5922, 116: 7380, 117: 6012, 118: 25038, 119: 5004, 120: 25317, 121: 6930, 122: 4626, 123: 5958, 124: 4005, 125: 32922, 126: 381
[…]

### 2019-01-27 plot_edit_bleus_data.py

@@ -89,26 +89,52 @@ seq2seq_att = [
 (0.3676185009674074, 0.3953923325297742) ,
 ]
 
-seq2tree = [
-(0.9970505050505051, 6.197235183070462e-05) ,
-(0.7187589094412051, 0.0004957930834618799) ,
-(0.6901118240686185, 0.004996848794236822) ,
-(0.5034464434653615, 0.08638450628686728) ,
-(0.5429854022876168, 0.04201859939867738) ,
-(0.46621240738000347, 0.09830306602014821) ,
-(0.46902307426259765, 0.16122306442178733) ,
-(0.48603252655884815, 0.1743227468115155) ,
-(0.41711233466222686, 0.11666703742118305) ,
-(0.43280576937199916, 0.19008071994868464) ,
-(0.3972045115164212, 0.18250706383564105) ,
-(0.4202299282158661, 0.21444062340315295) ,
-(0.3863264732234157, 0.2410830153344796) ,
-(0.3748221123572753, 0.28229094718036607) ,
-(0.42905440437492387, 0.1491205631544536) ,
-(0.4006853020471947, 0.2583429284198248) ,
-(0.3506275375668442, 0.19543068849506837) ,
-(0.3139833041422601, 0.17780945469720322) ,
-(0.3324191109831643, 0.35494961916950724) ,
+seq2tree_flatten = [
+(0.9970505050505051, 1.6215809387106907e-06) ,
+(0.7187589094412051, 0.05876180690785744) ,
+(0.6901118240686185, 0.07660470935098684) ,
+(0.5034464434653615, 0.17985647243439667) ,
+(0.5429854022876168, 0.1450251727914139) ,
+(0.46621240738000347, 0.23204679223520372) ,
+(0.46902307426259765, 0.2206184942899193) ,
+(0.48603252655884815, 0.17440119245639618) ,
+(0.41711233466222686, 0.2574045218749255) ,
+(0.43280576937199916, 0.22116086889433062) ,
+(0.3972045115164212, 0.29587676514423417) ,
+(0.4202299282158661, 0.2582484084601844) ,
+(0.3863264732234157, 0.24824370979049962) ,
+(0.3748221123572753, 0.33412177976065494) ,
+(0.42905440437492387, 0.2364804556136947) ,
+(0.4006853020471947, 0.29530915079704073) ,
+(0.3506275375668442, 0.35335379265904165) ,
[…]

### 2019-01-27 texs/compile.sh

@@ -1,3 +1,4 @@
 cp ../../tex-srcs/iscs-thesis.cls ./
 sed '/__NAMES__/r ../../names.txt' paper_base.tex | sed 's/__NAMES__//g' > paper.tex
+extractbb bleu.png && extractbb edit_dist.png && extractbb ast_lens.png && extractbb c_lens.png && 
 platex paper.tex && pbibtex paper && platex paper.tex && platex paper.tex && platex paper.tex && dvipdfm paper.dvi

### 2019-01-29 texs/paper_base.tex
save

@@
 \usepackage[dvipdfmx]{graphicx}
+\usepackage{framed}
+\usepackage{caption}
 
@@
   tabsize=2,
+ 	framesep=5pt,
 }
@@
   tabsize=2,
+  framesep=5pt,
+  %frame=none,
+}
+
+\lstdefinestyle{ForDecomp}{
+  tabsize=2,
+  frame=l,
+  framesep=5pt
 }
@@
   stringstyle={\small\ttfamily},
-  %frame={tb},
   breaklines=true,
   columns=[l]{fullflexible},%
+  % frame={tb},
   % numbers=left,%
@@
   lineskip=-0.5ex,%
-  captionpos=b
+  captionpos=b,
 }
@@
 From the experiment, we can observe little improvement in the decompilation result with the use of attention.
+However, the results were not applicable for practical use.
 
@@
 実験では、オープンソースプロジェクトから収集したソースコードとそのバイナリデータを用いてニューラルネットワークを学習し、その性能を検証した。
-実験の結果、注意機構を用いることににより、逆コンパイル結果における若干の精度向上が認められた。
+実験の結果、注意機構を用いることににより逆コンパイル結果における若干の精度向上が認められたが、実用的な精度までは至らなかった。
 \end{jabstract}
@@
 
-These days, the amount of malware has been increasing rapidly.
-
-要参考文献
-So the importance of developing malware analysis tools has been rising.
-要参考文献
+These days, the amount of malware has been increasing rapidly. In the report of AV-TEST Institute,
+over 100 million malwares are newly found in every year for the past five years \citep{malware_increase}.
+There are many case studies for malwareinfection \citep{malware_case_1,malware_case_2,malware_case_3,malware_case_4}.
+In those cases, they analyse malwares to assess the impact of the incident and to identify the vulnerability which causes the infection.
+% Therefore, the importance of developing malware analysis tools has been rising.
+% 要参考文献 -> つけた。
+In order to analyse malwares quickly and efficiently, there are some tools for analysing malwares \citep{mal_anal_tool}.
 One of these tools is a decompiler, which is a tool for analyzing the behavior of malware. 
@@
 In this thesis, we apply neural networks to the problem of decompilation to generate human-friendly pseudocodes. 
-This idea is originated from \cite{Motoneta}, in which they used recurrent neural networks.
-They used sequence-to-sequence model, which ignores the structure of the C language code. 
-Therefore, we implemented sequence-to-tree model, which is suggested in \cite{Seq2Tree}, for generating structured C language source code 
-結果が向上していれば(and improving the decompilation accuracy.)といいたい。
+This idea is originated from \cite{Motoneta}, in which they used recurrent neural networks, in particular sequence-to-sequence model, for decompilation.
+However, their model does not seem to have some features for improving the quality of decompilation.
+Therefore, we implemented the attention mechanisme, which is introduced in \cite{dot_attention}, for improving the quality.
+Additionaly, the sequence-to-sequence model, which they used for modeling, ignores the structure of the C language code.
+Therefore, we also implemented the sequence-to-tree model, which is suggested in \cite{Seq2Tree}, for generating structured C language source code.
 
-従来法の何が悪いのかを説明する．たぶんした。
-(TODO)このあとに今回やる更に具体的な内容とその成果についてが入る。
+In the experiment, we tested three models, the basic sequence-to-sequence model, the sequence-to-sequence model with attention and the sequence-to-tree model.
+As the result of the experiment, the attention mechanism showed little improvemtn in the performance, while the sequence-to-tree does not.
+Unfortunately, the results were not applicable for practical use, because the most of decompilation results were incorrect.
 
-TODO(satos)
+% In the following part of the paper, we explain the
 
-\section{Related Works}
+\chapter{Related Works}
 In this section, we review related works.
 
-\subsection{Decompilation with Machine Learning}
+\section{Decompilation with Machine Learning}
 
-Because perfect decompilation is naturally impossible, there are many machine learning applications for decompilation.
+Because perfect decompilation is naturally impossible, there are some machine learning applications for decompilation.
 
-In \cite{Motoneta}, they used the seqence-to-sequence approach, which is a popular technique in the machine translation.
+In \cite{Motoneta}, they used the seqence-to-sequence model, which is a popular technique in the machine translation.
+The seqence-to-sequence model is also evaluated in this thesis.
 
@@
 
-TODO(satos)
+% TODO(satos)
 
@@
 
-\subsection{Improvement of decompilation results}
-In this section, we do not try to recover the function name and variable name. 
+\section{Improvement of decompilation results}
+In this thesis, we do not try to recover the function name and variable name. 
 However, for hand-decompilation, sometimes the name can be estimated by the functionality of the variable.
-要参考文献
-For example, assume there is a variable X which seems to have a C struct type and has two fields P and Q.
+For example, \cite{hand_decompilation} used Boomerang decompiler and repeatedly fixed variable types and names of the decompilation results 
+to recover the source code of a software.
+
+Here, we show a example of the name estimation.
+Assume there is a variable X which seems to have a C struct type and has two fields P and Q.
 Also, there are two functions F and G which operate with X. 
@@
 \cite{JSNaughty} applied statistical machine translation for this task. 
+They calculated the future value of a variable from its functionality, then 
+sought the most suitable name from the candidates generated from the corpus.
 
-TODO(satos)
+% 変数の性質から統計情報を取り出し、それを元に
 
-変数の性質から統計情報を取り出し、それを元に
-
-They calculated estimated the name of the variable by the functionality of it
-
-\subsection{Neural Network for Program Generation}
+\section{Neural Network for Program Generation}
 
@@
 
-A compiler is a program which compiles source code written in language X to other language Y. 
-Usually, X is high-level language and Y is relatively low-level language. 
-For example, clang compiler translates C language to x64 assembly language, javac compiler translates Java to Java virtual machine code.
+A compiler is a program which compiles a source code written in language X to another language Y. 
+% 文献 Usually, X is a high-level language and Y is relatively a low-level language. 
+For example, a Clang compiler translates the C language to the x64 assembly language, a javac compiler translates Java to a Java virtual machine code.
+This process is usually
 
-A decompiler is a program which aims to reverse the process of a compiler, retrieve a source code of the high-level language X from the source code of the low-level language Y. 
-This reversing process is usually insufficient or impossible.
-This is because many informaition, such as variable name or function name, are lost when compiling.
-Additionally, the program structure described in the high level language are lost too. 
-For example, a simple {\sl for statement} can be represented by the combination of a {\sl while statement} and an {\sl if statement}, or the combination of {\sl if statement} and {\sl goto statement}.
-So a decompiler can't distinguish their representation difference, despite in the real situation {\sl for statement} are often used and {\sl goto statement} are rarely.
+A decompiler is a program which aims to reverse the process of a compiler, retrieving a source code of the high-level language X from a source code of a low-level language Y. 
+% 文献
+Especially, 
+This reverse process is usually insufficient or impossible.
+This is because a lot of informaition, such as variable names or function names, are lost when compiling.
+Additionally, the program structure described in the high level-language is lost too. 
+For example, a simple \texttt{for} statement can be represented by the combination of a \texttt{while} statement and an \texttt{if} statement, or the combination of \texttt{if} statement and \texttt{goto} statement.
+So a decompiler cannot distinguish the difference in their representations, 
+although in the real situation \texttt{for} statement are often used and \texttt{goto} statement are rarely used.
 
-Existing decompilers are made up with many steps similar to compilers. 
-They find patterns in binary data, convert them to more high-level structure, and chain them so that they finally generate high-level psudecode.
-Their output psudecodes are sometimes wrong or hard to understand.
-
-% https://github.com/torvalds/linux/blob/70c25259537c073584eb906865307687275b527f/lib/rbtree.c#L528
+% これについてちゃんと書く。
+% Their output psudecodes are sometimes wrong or hard to understand.
 
 % (DONE)表がはみ出しているのでどうにかした。
+
+% \let\oldlstinputlisting\lstinputlisting
+% \renewcommand{\lstinputlisting}[2][]{\oldlstinputlisting[frame=lines,#1]{#2}}
 
@@
 		\begin{minipage}[c]{0.5\hsize}
-			\lstinputlisting[title={sample C source code},breaklines=false]{bintree.c}
+		\begin{framed}
+			\lstinputlisting[breaklines=false]{insert_list.c}
+			\end{framed}
+			\caption*{Sample C source code}
 		\end{minipage}
 		\\
-		\begin{minipage}[c]{0.5\hsize}
-			\lstinputlisting[title={result of the Hopper Decompiler}]{hopper.c}
+		\begin{minipage}[c]{0.5\hsize} %title={Result of the Hopper Decompiler}
+			\begin{framed}
+			\lstinputlisting[]{snowman.c}
+			\end{framed}
+			\caption*{Result of the Snowman Decompiler}
 		\end{minipage}
 		\begin{minipage}[c]{0.5\hsize}
-			\lstinputlisting[title={result of the Snowman Decompiler}]{snowman.c}
+			\begin{framed}
+			\lstinputlisting[]{recstudio.c}
+			\end{framed}
+			\caption*{Result of the REC Studio Decompiler}
 		\end{minipage}
@@
 	\vspace*{-0.6cm}
-	\caption{ decompilation results of existing decompilers for C source code}
+	\caption{Decompilation results of existing decompilers for C source code}
 	\label{fig:cw}
@@
 
-Figure~\ref{fig:cw} shows the example decompilation results of the Hopper disassembler and the snowman decompiler 
-for a sample C language code.
-The Hopper decompiler fails to detect while statements, and the variable {\sl now} is incorrectly analyzed.
-The output of snowman seems rather correct, as type {\sl struct tree} is reconstructed to {\sl struct s0}, 
-and the {\sl if} statement and {\sl while} statement are correctly restored. 
-However, it fails to detect the function epilogue, and the {\sl free} function call is incorrectly analyzed.
-Ideally, the decompilers can find correct function ranges and structure of statements, but they failed.
+Figure~\ref{fig:cw} shows an example of decompilation results of the Snowman decompiler version v0.1.3 and the REC Studio decompiler version 4.1 
+for a sample C language code. The sample C code is compiled by the GNU C Compiler version 4.8.5, with the optimization level \texttt{-O0}.
+The REC decompiler missed the structure of the variable \texttt{root}.
+It also failed to estimate the number of arguments and the return value of the function.
+The Snowman Decompiler succeeded to reconstruct the structure of the variable as \texttt{struct s0}.
+It also succeeded to estimate the number of arguments and the return value as the semantically correct expressions, 
+however the statement \texttt{return 0;} is reconstructed to the complex combination of statements.
+
+These incorrect or verbose results might be due to missing patterns in the assembly codes. 
+Existing decompilers are made up with many steps similarly to compilers \citep{decompiler_path,hex_rays}.
+In each step, a decompiler finds patterns in binary data, converts them to more high-level structure.
+However, covering all patterns might be hardly impossible, since there are many compilers and compiler optimizations.
+文献欲しいが見当たらない...
+
+Therefore, applying statical machine
+
+% These patterns comprehensive
+
+% The pathes are made up of
+
+% The \texttt{for} statement in the C source code is 
+% reconstructed to the combination of the \texttt{while} statement and the {\sl if} statement in both decompiler results.
+
+% This is the example of the impossibleness of the perfect decompilation, what we mentioned.
+
+% However, there are many patterns
+
+% Existing decompilers are made up with many steps similarly to compilers. \citep{hex_rays,}
+% They find patterns in binary data, convert them to more high-level structure, and chain them so that they can finally generate a high-level psudecode.
+
+% このへん嘘書いてたので修正。
+% The Hopper decompiler fails to detect while statements, and the variable {\sl now} is incorrectly analyzed.
+% The output of snowman seems rather correct, as type {\sl struct tree} is reconstructed to {\sl struct s0}, 
+% and the {\sl if} statement and {\sl while} statement are correctly restored. 
+% However, it fails to detect the function epilogue, and the {\sl free} function call is incorrectly analyzed.
+% Ideally, the decompilers can find correct function ranges and structure of statements, but they failed.
 
@@
 % 189
-In this paper, we try to apply statistical approach, specifically SMT (statistical machine translation) technique, for decompilation.
+In this thesis, we try to apply statistical approach, specifically SMT (statistical machine translation) technique, for decompilation.
 The decompilation problem is formulated as follows.
@@
 
-\subsection{Seq-to-Seq}
+\subsection{Sequence-to-Sequence}
 % This model is called seq2seq (sequence to seqence) model.
@@
 
+% ビームサーチ書く。
+% For TODO
+
 % (TODO) このへんで 図を入れる
@@
 Second is the multi-layer reccurent neural networks, introduced in \cite{multi_layer}.
-
-TODO(satos)
+They reported that, feeding the output sequence of the LSTM network to another LSTM network, like stucking the network layers, will improve the accuracy of the prediction.
+This architecture is called as stucked reccurent neural networks or multi-layer reccurent neural networks.
 
@@
 % 184 words
-Compare to natural languages, programming languages obeys rigid grammer, wich is usually context free grammer,  
-and it is reasonable to consider the grammer of the programming language in generating programs.
+Compare to natural languages, programming languages obeys rigid grammers. % wich are usually context free grammers.
+Therefore, it is reasonable to consider the grammer of the programming language when generating programs.
 Sequence-to-Tree is a model for generating tree-structured output from sequence input. 
-This model is introduced in \cite{Seq2Tree} for generating programs from the program specification written in natural languages.
+This model is introduced in \cite{Seq2Tree} for generating a program from a program specification written in the natural language. 
 This task is similer to our task, which aims to generate programs from the sequence of the assembly code, so we implemented this model in the experiment.
@@
 
+\begin{figure}[]
+	\begin{center}
+	\includegraphics[height=12cm]{ast_zu.png}
+	\end{center}
+	\caption{AST representation of a C statement \texttt{b = a + 3;} }
+	\label{fig:ast_zu}
+\end{figure}
+
 The decoder network is a network for generating tree structured output. 
 A tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
+For example, the tree shown in figre~\ref{fig:ast_zu} is gererated from the sequence $ [act_1, \dots act_{12}] $, 
+where action $ act_k $ expands the left-most nonterminal symbol in the tree generated from the action sequence $ [act_1, \dots act_{k-1}] $. 
 Suppose the tree $ty$ is generated by the action sequence $ [act_1, \dots act_m] $, 
-where $ act_k $ is the action which expands left-most symbol of the nonterminal symbol in the tree generated by the action sequence $ [act_1, \dots act_{k-1}] $. 
-Then, the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(act_k|sx,[act_1, \dots act_{k-1}]) $, 
-so the sequence-to-sequence model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
-calculating $ LSTM_{dec}(dec_{k},av_{k}) $ for estimating $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $.
+then the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(act_k|sx,[act_1, \dots act_{k-1}]) $. 
+The sequence-to-sequence model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
+calculating $ LSTM_{dec}(dec_{k},av_{k}) $ sequentially for estimating $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $.
 
@@
 They also used devised method for generating terminal symbols, because they need to copy the name of some variables from the program specification.
-However, in our case, we don't need copy the information from the input, because the name information is lost when compiling.
+However, in our case, we do not need copy the information from the input, because the name information is lost when compiling.
 Nevertheless, it is found from the experiments that our decompilers often fail to recover the constant values in the programs.
@@
 Some example data pairs are shown in figure~\ref{fig:pairsoffragments}.
-\\*
 
@@
 		\begin{lstlisting}[style=Csample]
-		r *= a;
+		r *= a
 		\end{lstlisting}
@@
 % 155 words
-The assemblies were preprocessed in two ways.
+There are two ways for preprocessing assembly codes.
+
 First way is the raw binary integers. The assemblies are finally assembled to the sequence of the one byte integers, ranged from 0 to 255.
 So the one byte integer sequences can be directly used for input sequences.
+
 Second way is the tokenized sequence of assembly codes. 
-The disassembled opcodes and operands in {\sl S5} are split to symbols, and concatenated the sequences to one sequence, then we modified followings.
+The disassembled opcodes and operands in {\sl S5} are split to symbols, and concatenated these sequences to one sequence, then we modified followings.
 \begin{itemize}
@@
 
+We choiced second way for the experiment.
+This is because, in our case, the assembly code is generated from common C compiler, therefore the assembly code can be disassembled uniquely.
+For example, \cite{disasm_obfuscate} proposed a obfuscation technique, which deceives the disassembler to generate wrong disassembly result.
+In that case, the first way might be better than the second way.
+
 \subsection{C Code Preprocess}
@@
 For example, the {\sl CompoundStatement} node has variable number of statements. 
-We converted such list of nodes to the chains of concatnation and terminal, like a list representation in functional language.
+We converted such list of nodes to the chains of concatnation {\sl CONS} and termination {\sl NIL}, like a list representation in functional language.
 Another example is the  {\sl If} statement, whose {\sl else} clausure are sometimes missing. 
-We converted such optional node to the alternative of some node and Null node, like a optional data structure in functional language.
+We converted such optional node to the alternative of {\sl SOME} and {\sl NONE}, like a optional data structure in functional language.
 \item The variable names, function names, label names, or type names were renamed like $\alpha$-conversion.
@@
 Modifying the node to indicate the value in the assembly code corresponding to the literal is also conceibable way,
-but we couldn't implement this because of its technical difficalty, so this is left to future work.
+but we did not implement this because of its technical difficalty, so this is left to future work.
 \end{itemize}
@@
 		Number of LSTM Layers & \multicolumn{3}{|c|}{4} \\ \hline
-		% Vector Dim & \multicolumn{3}{|c|}{128} \\ \hline
+		Dimensionality of Vector Embedding & \multicolumn{3}{|c|}{128} \\ \hline
 	\end{tabular}
@@
 
+% \section{Furure work}
+
 % TODO(satos)
@@
 
+\section{Numerical Evaluation}
 For evaluating each model, we randomly sampled 100 data pairs from test cases, generated estimated decompilation results for each test cases,
@@
 We can see that Seq2seqAtt shows slightly better results in both edit distance ratios and BLEU scores,
-while there are no significant difference between Seq2seq and Seq2tree in both metrics.
-Seq2seqの結果とSeq2seqAttの結果を比較することにより、attention が性能向上に寄与していることがわかります。
-逆にSeq2treeにはattentionがあるにもかかわらずSeq2seqと比較して性能向上が見られなかったわけですが、
-これはCのソースコードをASTに変換した際に、データサイズが増えたためであると考えられます。
+ which implies that the attention improves the performance of the decompilation.
+However, there are no significant difference between Seq2seq and Seq2tree in both metrics.
+This seems to be due to the length of the sequences to be estimated.
+% Seq2seqの結果とSeq2seqAttの結果を比較することにより、attention が性能向上に寄与していることがわかります。
+% 逆にSeq2treeにはattentionがあるにもかかわらずSeq2seqと比較して性能向上が見られなかったわけですが、
+% これはCのソースコードをASTに変換した際に、データサイズが増えたためであると考えられます。
 
@@
 Figure~\ref{fig:csizes} shows the length distribution of the dataset as C token sequences
-, and figure~\ref{fig:astsizes} shows the size distribution of the same dataset as AST trees.
-The length 
-According to the figures, the AST size is 2~3 times larger than that of C source codes.
+, and figure~\ref{fig:astsizes} shows the size distribution of the same dataset as ASTs.
+The size of a AST is equals to the length of its action sequence.
+According to the two figures, the AST size is 2~3 times larger than the length of C token sequences.
+Therefore, the AST estimation may be harder than C token sequence estimation.
+
+\begin{figure}
+	\begin{tabular}{|l|l|} \hline
+	 ground truth & 
+		\begin{lstlisting}[style=Csample]
+r *= a
+		\end{lstlisting} \\ \hline
+		Seq2Seq & 
+		\begin{lstlisting}[style=Csample]
+const unsigned int V0 = V1 * floatliteral
+		\end{lstlisting} \\ \hline
+		Seq2SeqAtt & 
+		\begin{lstlisting}[style=Csample]
+V0 = ( unsigned int ) ( V1 ) * ( unsigned int ) V2
+		\end{lstlisting} \\ \hline
+		Seq2Tree & 
+		\begin{lstlisting}[style=Csample]
+V0 = V0 * V1
+		\end{lstlisting} \\ \hline
+		\hline	
+	 ground truth & 
+		\begin{lstlisting}[style=Csample]
+while(p >= 0){
+	p--;
+	r *= a;
+}
+		\end{lstlisting} \\ \hline
+		Seq2Seq & 
+		\begin{lstlisting}[style=Csample]
+for(;V0 = (1<<(((unsigned int)-1<<((32-20)-1))-1))
+*((unsigned char*)(V1.V2))[1] = (unsigned char)2;
+}
+		\end{lstlisting} \\ \hline
+		Seq2SeqAtt & 
+		\begin{lstlisting}[style=Csample]
+while(((void *) >= 0) != ((void *) 0)){ 
+	return ((void *) 0);
+} else { 
+	V0 = (( void * ) 0); 
+}
+		\end{lstlisting} \\ \hline
+		Seq2Tree & 
+		\begin{lstlisting}[style=Csample]
+while(V0 < 0){ 
+	V1 = V0 - 1;
+}
+		\end{lstlisting}
+		 \\ \hline	\hline
+	 ground truth & 
+		\begin{lstlisting}[style=Csample]
+int pow(int a,int p){
+	int r = 1;
+	while(p >= 0){
+		p--;
+		r *= a;
+	}
+	return r;
+}
+		\end{lstlisting} \\ \hline
+		Seq2Seq & 
+		\begin{lstlisting}[style=Csample]
+void V0(int V1,int V1){ 
+	int V1 = 0; 
+	int V1; 
+	for(V2=1;V1<=V2;++V2){ 
+		V1 = * V3; 
+	} 
+}
+		\end{lstlisting} \\ \hline
+		Seq2SeqAtt & 
+		\begin{lstlisting}[style=Csample]
+void V0(unsigned int V1,unsigned int V2){ 
+	unsigned int V1 = ((void *) 0); 
+	unsigned int V3 = ((void *) 0); 
+	unsigned int V1 = ((((void *) 0) != ((void *) 0))); 
+	return V4; 
+}
+	\end{lstlisting} \\ \hline
+		Seq2Tree & 
+		\begin{lstlisting}[style=Csample]
+INVALID_FUNCTION_DECL { 
+	TRANCATETRANCATE 
+}
+		\end{lstlisting}
+		 \\ \hline	
+	\end{tabular}
+	\caption{Smaple translation results for each model}
+	\label{fig:sampletranse}
+\end{figure}
+
+\section{Sampled Decompilation Results}
+
+Figure~\ref{fig:sampletranse} shows sample translate results for each model.
+
+For the first short example, each of the models recovered that the C statement is composed of multiplication and assignment,
+while only Seq2Tree recovered the name of the variables, and Seq2Seq and Seq2SeqAtt were failed to recover.
+
+For the second middle example, Seq2Seq outputs invalid parenthesesed souce code, Seq2SeqAtt outputs invalid syntax (combination of while and else statement) code,
+while Seq2Tree outputs correct syntax but many wrong subexpressions.
+
+For the third large exapmle, all of the three models output a function with wrong body statement.
+The {\sl INVALID\_FUNCTION\_DECL} in the result of Seq2Tree means it outputs wrong structured function type, and the {\sl TRANCATE} means 
+the action is truncated because the too long action sequence is estimated. 
+For long size function or statements, Seq2Tree tends to expand list type node to {\sl CONS} node, which causes infinit expansion of sequence,
+and as a result, the type of the output function becomes broken and the body of the function becoms truncated.
+
+According to these decompilation results, it can be said that these models is not acceptable for practical use.
 
@@
 
-% \chapter{Discussion}
-% 結果より、まずattention機構によって有意に精度が向上することが確認できた。
-% しかしながら、 seq2seq と seq2tree の間に
+% \section{Furure work}
+
+\chapter{Furure research}
+In this chapter, we suggest some other approaches to improve the accuracy of our decompilation models.
+
+\section{Improvement on Assembly Code Preprocessing}
+We used tokenized assembly string sequences for training. 
+However, such simple concatnation of sequences might lose the information of the unity of each instructions.
+To improve this point, we propose the following method.
+
+This method uses two LSTM networks, the instruction encoder network and the assembly code encoder network, for encoding assembly token sequences.
+First, each assembly instruction sequences are encoded by instruction encoding network into one instruction embedding vector, 
+so that the assembly codes turn into the sequennces of embedding vectors.
+Then, the sqeuence of embedding vectors is encoded into one reduced vector by assembly code encoder network.
+
+This method will be time consuming compared to the method used in the experiment, however, this might be worth trying.
+
+\section{Improvement on Sequence-to-tree Model}
+We considered that the AST representation seems to exploit the feature of C source code. 
+However, the sequence-to-tree model was not well performed.
+In this section, we seek to the improvement of the AST approach.
+\subsection{Copy Leaf Data from Assembler}
+The translation results show that the sequence-to-tree model have difficalty in recovering the leaf data of the program.
+Hence changing the method for expanding leaf node might improve the accuracy of decompilation.
+There are three kind of leaf data in the AST representation of a C source code.
+
+The first kind is the literal data. In the C source code, there are four literal data, integer, float, char and string. 
+In the assembly code, the string literal appears in the form of a memory address, and the other three literals appear in the form of an immediate value.
+Therefore, instead of estimating literal value directly, estimating the correcponding position in the assembly code might improve the correctness of decompilation.
+
+The second kind is the type of operator. These can be also estimated from the assembly code.
+For example, the operator $ + $ is compiled to the opecode {\sl add}, the operator $ | $ is compiled to the opecode {\sl or}, and so on. 
+Thus the type of operator might be estimated by indicating the correspond position in the assembly code.
+
+The third kind is the variable name. In the assembly code, a variable corresponds to a memory access. 
+Therefore, the name of a variable is identified by its corresponding memory position, similar to avobe two kinds.
+
+\subsection{Path Estimation} 
+In the sequence-to-tree model, a tree structure is flattened into an action sequence, 
+therefore the information of a tree structure might be lost in some degree.
+For example, the adjacent actions in the action sequence might be the distant actions in the AST, when they are in the different subtree of the AST.
+
+To preserve the information of the tree structure, we suddest to train the network for estimating each root-to-leaf action sequences in the AST,
+instead of the flattened action sequence. 
+For example, in the figure~\ref{fig:ast_zu}, there are four root-to-leaf action sequences, 
+$ [act_1, act_2] $, $ [act_1, act_3,act_4,act_5,act_6,act_7] $, $ [act_1, act_3,act_4,act_8] $ and $ [act_1, act_3,act_4,act_9,act_{10}] $.
+The AST can be recovered from these sequences instead of the whole sequence $ [act_1 \dots act_{10}] $, 
+and these sequences are independent of each other, when generating AST.
+Therefore, we may estimate each of the sequences from the asssembly token sequence by the sequence-to-sequence model.
+
+This approach will ease the AST size problem, because the length of a root-to-leaf path is shorter than the size of whole AST, unless the AST has no branching.
+
+% 前述の Sequence-to-Tree は プログラムの構造を考慮しているものの、アクションをそのまま列にするのは結局プログラムの木としての構造がある程度失われてしまっているのではないかと考えられる。
+% すなわち、アクションを列に展開しているため、ある部分木からその兄弟の部分木の生成に移る際に大幅なジャンプが生じている。
+
+\section{Improvement of Dataset}
+As is seen in the figure~\ref{fig:csizes} and figure~\ref{fig:astsizes}, most of the data are short length C code.
+This is due to our data generation method, which enumerates all of the subtree of a C source code.
+We intended the models to learn the structure of long data from the short data, though the result shows that 
+the poor decompilation results are generated from the longer data.
+Therefore, the length distribution of the training data might effect on the training result, 
+thus we will need to seek effective distribution for the training.
+
+% \section{For General Decompiler}
 
 \chapter{Conclusion}
+We tested three neural network models Seq2Seq, Seq2SeqAtt and Seq2Tree for decompilation.
+Numerically, Seq2SeqAtt peformanced better results compared to the other two models,
+but all of three models were not acceptable for practical use.
+Therefore, we will continue to develop practical decompiler for the good future of malware analysis.
+
+\chapter{Acknowledgement}
 

### 2019-01-29 c_cfg.py

@@ -290,7 +290,7 @@ def function_decl_func(cs):
 		#print('invalid function decl')
 		#print(cs)
 		#exit()
-		return 'INVALID_FUNCTION_DECL{' + ''.join(cs) + '}'
+		return 'INVALID_FUNCTION_DECL{' + ';'.join(cs) + ';}'
 	arg_types_len = 0
 	if len(td[1])!=0 and td[1][0] != 'void':
 		arg_types_len = 1

### 2019-01-29 gen_handsample.py

@@ -2,6 +2,12 @@ import os
 import csrc2ast
 import asm_objd_conv
 import my_c_ast
+import pickle
+
+with open('dataset_asm_ast/vocab_asm.pickle','rb') as fp:
+	vocab_asm = pickle.load(fp)
+with open('dataset_asm_csrc/vocab_csrc.pickle','rb') as fp:
+	vocab_csrc = pickle.load(fp)
 
 def getds(fn):
 	os.system('clang -Xclang -ast-dump -fsyntax-only %s.c > %s.parsed 2>/dev/null' % (fn,fn))
@@ -17,22 +23,50 @@ def getds(fn):
 	ds = asm_objd_conv.get_line_from_list(asm,objd)
 	astdata = ast.subexpr_line_list()
 	
+	
+	res = []
 	for (a,b),nsize,tree in astdata:
 		nas = ''
+		nas_d = []
 		for i,d in ds:
 			if a <= i and i < b:
 				nas += ' '.join(d) + '\n'
+				nas_d += d + ['NEW_LINE']
 				#nas.append(d)
 		if len(nas)==0:
 			continue
 		
-		print(nas)
-		print('.' * 100)
-		nast = my_c_ast.load_astdata(tree)
-		nast.before_show()
-		print(nast.show())
-		print('-' * 100)
+		#print(nas)
+		#print('.' * 100)
+		csrc = csrc2ast.ast2token_seq(tree)
+		#nast = my_c_ast.load_astdata(tree)
+		#nast.before_show()
+		#csrc = nast.show()
+		#csrc = csrc.split(' ')
+		
+		def conv_c(x):
+			if x[:7] == '__ALPHA':
+				x = x.replace('__ALPHA_name_','__ID_')
+			return x
+		def conv_asm(x):
+			if x[:6] == 'LABEL_':
+				x = x.replace('LABEL_','LA_')
+			return x
+		csrc = list(map(conv_c,csrc))
+		c_tks = list(map(lambda x: vocab_csrc.index(x),csrc))
+		nas_d = list(map(conv_asm,nas_d))
+		asm_tks = list(map(lambda x: vocab_asm.index(x),nas_d))
+		#print(csrc)
+		#print('-' * 100)
+		res.append((asm_tks,c_tks,tree))
+	
+	return res
+
+ds = getds('y')
 
 
+print(len(ds))
+with open('od.pickle','wb') as fp:
+	pickle.dump(ds,fp)
 
-getds('y')
+

### 2019-01-29 model_rnn_with_globalatt.py

@@ -91,9 +91,10 @@ class Seq2seq_with_GlobalAtt(chainer.Chain):
 			cx = F.transpose(F.reshape(F.transpose(cx,(1,0,2)),(batch,self.n_layers,self.n_units*2)),(1,0,2))
 			#print(hx.shape,cx.shape,(1,xs_states[0].shape))
 			#sprint(xs_states)
-			hx = F.transpose(hx,axes=(1,0,2))
-			cx = F.transpose(cx,axes=(1,0,2))
+			#hx = F.transpose(hx,axes=(1,0,2))
+			#cx = F.transpose(cx,axes=(1,0,2))
 			
+			"""
 			ivs = sequence_embed(self.embed_y,list(map(lambda i: xp.array([i]),range(self.n_target_vocab))))
 			v = ivs[EOS_DST]
 			
@@ -107,7 +108,12 @@ class Seq2seq_with_GlobalAtt(chainer.Chain):
 				
 				for j in range(self.n_maxlen):
 					to_beam = []
-					for r,(kd,v,nhx,ncx) in beam_data:
+					for ci,(r,(kd,v,nhx,ncx)) in enumerate(beam_data):
+						if len(kd)>0 and kd[-1]==EOS_DST:
+							to_beam.append((r,(kd,v,nhx,ncx)))
+							if ci == 0:
+								break
+							continue
 						#print(v.shape)
 						thx,tcx,ys = self.decoder(nhx,ncx,[v])
 						yh = ys[0]
@@ -124,7 +130,44 @@ class Seq2seq_with_GlobalAtt(chainer.Chain):
 					#print(list(map(lambda a: a[0],beam_data)))
 				
 				result.append(beam_data[0][1][0])			
-		
+			"""
+
+			beam_with = 3
+			vs = [xp.array([EOS_DST]) for _ in xs_outputs]
+			kds = [[] for _ in xs_outputs]
+			rs = [0.0 for _ in xs_outputs]
+			beam_data = [(rs,kds,hx,cx,vs)]
+			for j in range(self.n_maxlen):
+				#print(j)
+				to_beam = [[] for _ in range(batch)]
+				for rs,kds,nhx,ncx,vs in beam_data:
+					if type(nhx) is list:
+						#print(nhx[0].shape)
+						nhx = F.stack(nhx,axis=1)
+						ncx = F.stack(ncx,axis=1)
+						vs = list(map(lambda d: xp.array(d),vs))
+						#print(nhx.shape)
[…]

### 2019-01-29 model_seq2seq_pure.py

@@ -74,31 +74,60 @@ class Seq2seq(chainer.Chain):
 		EOS_DST = self.v_eos_dst
 		batch = len(xs)
 		
-		beam_with = 3
 		with chainer.no_backprop_mode(), chainer.using_config('train', False):
 
 			exs = sequence_embed(self.embed_x, xs)
 			hx, cx, xs_outputs = self.encoder(None, None, exs)
 			hx = F.transpose(F.reshape(F.transpose(hx,(1,0,2)),(batch,self.n_layers,self.n_units*2)),(1,0,2))
 			cx = F.transpose(F.reshape(F.transpose(cx,(1,0,2)),(batch,self.n_layers,self.n_units*2)),(1,0,2))
-			#print(hx.shape,cx.shape,(1,xs_states[0].shape))
-			#sprint(xs_states)
-			hx = F.transpose(hx,axes=(1,0,2))
-			cx = F.transpose(cx,axes=(1,0,2))
 			
-			ivs = sequence_embed(self.embed_y,list(map(lambda i: xp.array([i]),range(self.n_target_vocab))))
-			v = ivs[EOS_DST]
+			#ivs = sequence_embed(self.embed_y,list(map(lambda i: xp.array([i]),range(self.n_target_vocab))))
+			#v = ivs[EOS_DST]
 			
 			result = []
 			
-			for i,hxs in enumerate(xs_outputs):
-				print('translate',i)
+			beam_with = 3
+			vs = [xp.array([EOS_DST]) for _ in xs_outputs]
+			kds = [[] for _ in xs_outputs]
+			rs = [0.0 for _ in xs_outputs]
+			beam_data = [(rs,kds,hx,cx,vs)]
+			for j in range(self.n_maxlen):
+				#print(j)
+				to_beam = [[] for _ in range(batch)]
+				for rs,kds,nhx,ncx,vs in beam_data:
+					if type(nhx) is list:
+						#print(nhx[0].shape)
+						nhx = F.stack(nhx,axis=1)
+						ncx = F.stack(ncx,axis=1)
+						vs = list(map(lambda d: xp.array(d),vs))
+						#print(nhx.shape)
+					#print(rs,kds,nhx,ncx,vs)
+					evs = sequence_embed(self.embed_y,vs)
+					thx,tcx,ys = self.decoder(nhx,ncx,evs)
+					wy = self.W(F.concat(ys, axis=0))
+					#print(wy.shape)
[…]

### 2019-01-29 model_seq2tree_flatten.py

@@ -49,10 +49,10 @@ class Seq2Tree_Flatten(chainer.Chain):
 		for d in self.trans_data:
 			ist = len(d)<=1
 			self.is_trivial.append(ist)
-			if ist:
-				self.choicerange.append(None)
-				self.choice_idx.append([0])
-				continue
+			#if ist:
+			#	self.choicerange.append(None)
+			#	self.choice_idx.append([0])
+			#	continue
 			b = s
 			s += len(d)
 			self.choicerange.append((b,s))
@@ -182,6 +182,8 @@ class Seq2Tree_Flatten(chainer.Chain):
 	
 			return None,v
 		
+		
+		#self.n_maxsize = 10000
 		beam_with = 3
 		with chainer.no_backprop_mode(), chainer.using_config('train', False):
 			xs = [xp.array(x[::-1]) for x in xs]
@@ -196,7 +198,46 @@ class Seq2Tree_Flatten(chainer.Chain):
 			cx = F.transpose(cx,axes=(1,0,2))
 			
 			result = []
-			
+			"""
+			self.n_maxsize = 800
+			beam_with = 3
+			vs = [xp.array([EOS_DST]) for _ in xs_outputs]
+			kds = [[] for _ in xs_outputs]
+			rs = [0.0 for _ in xs_outputs]
+			beam_data = [(rs,kds,hx,cx,vs)]
+			for j in range(self.n_maxlen):
+				print(j)
+				to_beam = [[] for _ in range(batch)]
+				for rs,kds,nhx,ncx,vs in beam_data:
+					if type(nhx) is list:
+						#print(nhx[0].shape)
+						nhx = F.stack(nhx,axis=1)
+						ncx = F.stack(ncx,axis=1)
+						vs = list(map(lambda d: xp.array(d),vs))
+						#print(nhx.shape)
+					#print(rs,kds,nhx,ncx,vs)
+					evs = sequence_embed(self.embed_y,vs)
+					thx,tcx,ys = self.decoder(nhx,ncx,evs)
+					ctxs = [self.att(xh,yh) for (xh,yh) in zip(xs_outputs,ys)]
+					att_ys = [F.tanh(self.Wc(F.concat([ch,yh],axis=1))) for (ch,yh) in zip(ctxs,ys)]
+					wy = self.Ws(F.concat(att_ys, axis=0))
+					#print(wy.shape)
+					wy = F.log_softmax(wy).data
+					#print(thx.shape)
+					thx = F.separate(thx, axis=1)
[…]

### 2019-01-29 plot_edit_bleus_data.py

@@ -65,6 +65,76 @@ seq2seq = [
 (0.3413700808444274, 0.38503683652138077) ,
 (0.3764797802055383, 0.34484821579690056) ,
 ]
+
+seq2seq_1000 = [
+(0.7777643381044518, 0.03775518488674301) ,
+(0.7330739317007444, 0.06229319974979076) ,
+(0.5709742882131595, 0.17008940124090982) ,
+(0.5013915195601105, 0.23214252473103514) ,
+(0.4532906138051254, 0.2932808950249558) ,
+(0.5104084869086902, 0.23388499283233444) ,
+(0.43509847629692866, 0.29396828665812713) ,
+(0.4581326401992643, 0.290425081793663) ,
+(0.46992066060190957, 0.27980763211037335) ,
+(0.4335536769271851, 0.2954630924141994) ,
+(0.40956612583028823, 0.33614129749368227) ,
+(0.4169467269743813, 0.3230700854733605) ,
+(0.4145604134049545, 0.3123027161926283) ,
+(0.34780038605459546, 0.37803151030644316) ,
+(0.33226686626901974, 0.38694093049829037) ,
+(0.3829205531159402, 0.33003356905260345) ,
+(0.3730802935507432, 0.36837801121610597) ,
+(0.3457811674828139, 0.3789329080491431) ,
+(0.3417304436207085, 0.3814106415759484) ,
+(0.3508211751171558, 0.38963207011650974) ,
+(0.3642342658631444, 0.35457698641705315) ,
+(0.39202908248362145, 0.3246332266789198) ,
+(0.4263310293350607, 0.2897421798012639) ,
+(0.31538044904740714, 0.40787065162098485) ,
+(0.3384712574886655, 0.4026523467500745) ,
+(0.3070486087857907, 0.36694571459090547) ,
+(0.36899456345601594, 0.33899782228254355) ,
+(0.3902575576964328, 0.33209793574013086) ,
+(0.3131023086790649, 0.3700978335404176) ,
+(0.319628562688506, 0.3658422257829181) ,
+(0.3075334784381214, 0.36454832407013144) ,
+(0.3676624447779134, 0.33885767486306956) ,
+(0.38268304599886, 0.35779378713339827) ,
+(0.3514617211480929, 0.3634557064465532) ,
+(0.31664434018528576, 0.38185463910105577) ,
+(0.31488753366548605, 0.3845155067510481) ,
[…]

### 2019-01-29 texs/bintree.c

@@ -2,7 +2,7 @@ struct tree{
 	int key,value;
 	struct tree *l,*r;
 };
-void free(struct tree* p);
+void free(void* p);
 void insert(struct tree** root,struct tree* node){
 	int nk = node->key;
 	struct tree** pos = root;

### 2019-01-29 texs/compile.sh

@@ -1,4 +1,4 @@
 cp ../../tex-srcs/iscs-thesis.cls ./
 sed '/__NAMES__/r ../../names.txt' paper_base.tex | sed 's/__NAMES__//g' > paper.tex
-extractbb bleu.png && extractbb edit_dist.png && extractbb ast_lens.png && extractbb c_lens.png && 
+extractbb bleu.png && extractbb edit_dist.png && extractbb ast_lens.png && extractbb c_lens.png && extractbb ast_zu.png &&
 platex paper.tex && pbibtex paper && platex paper.tex && platex paper.tex && platex paper.tex && dvipdfm paper.dvi

### 2019-01-29 texs/hopper.c

@@ -1,27 +1,18 @@
-function insert {
-    var_30 = arg1;
-    var_14 = *(int32_t *)var_30;
-    var_10 = arg0;
-    goto loc_86;
-loc_86:
-    if (insert != 0x0) goto loc_2e;
-loc_8d:
-    rax = var_10;
-    insert = var_30;
+function get_node {
+    var_8 = arg0;
+    var_C = arg1;
+    goto loc_400557;
+loc_400557:
+    if (*(var_8 + 0x8) != 0x0) goto loc_40053a;
+loc_400564:
+    rax = 0x0;
     return rax;
-loc_2e:
-    if (*(int32_t *)insert != var_14) goto loc_55;
-loc_39:
-    *(int32_t *)(insert + 0x4) = *(int32_t *)(var_30 + 0x4);
-    rax = free(var_30);
+loc_40053a:
+    if (*(int32_t *)var_8 != var_C) goto loc_40054b;
+loc_400545:
+    rax = var_8;
     return rax;
-loc_55:
-    if (*(int32_t *)(insert + 0x4) > var_14) {
-            var_10 = insert + 0x8;
-    }
-    else {
-            var_10 = insert + 0x10;
-    }
-    goto loc_86;
+loc_40054b:
+    var_8 = *(var_8 + 0x8);
+    goto loc_400557;
 }
-

### 2019-01-29 texs/snowman.c

@@ -1,39 +1,24 @@
 struct s0 {
     int32_t f0;
-    int32_t f4;
+    signed char[4] pad8;
     struct s0* f8;
-    struct s0* f16;
 };
-struct s1 {
-    signed char[8] pad8;
-    int64_t f8;
-};
-void fun_53(struct s0* rdi) {
-    struct s1* rbp2;
-    goto rbp2->f8;
-}
-void free(struct s0** rdi, struct s0* rsi) {
+struct s0* get_node(struct s0* rdi, int32_t esi) {
     struct s0* v3;
     int32_t v4;
-    struct s0** v5;
-    struct s0* v6;
-    v3 = rsi;
-    v4 = v3->f0;
-    v5 = rdi;
-    v6 = *rdi;
-    while (!reinterpret_cast<int1_t>(v6 == free)) {
-        if (v6->f0 == v4) 
-            goto addr_39_4;
-        if (v6->f4 <= v4) {
-            v5 = &v6->f16;
-        } else {
-            v5 = &v6->f8;
-        }
-        v6 = *v5;
+    struct s0* rax5;
+    v3 = rdi;
+    v4 = esi;
+    while (v3) {
+        if (v3->f0 == v4) 
+            goto addr_400545_4;
+        v3 = v3->f8;
     }
-    *v5 = v3;
-    addr_39_4:
-    v6->f4 = v3->f4;
-    fun_53(v3);
+    *reinterpret_cast<int32_t*>(&rax5) = 0;
+    *reinterpret_cast<int32_t*>(reinterpret_cast<int64_t>(&rax5) + 4) = 0;
+    addr_400563_7:
+    return rax5;
+    addr_400545_4:
+    rax5 = v3;
+    goto addr_400563_7;
 }
-

### 2019-01-29 train.py

@@ -108,7 +108,7 @@ def init_seq2seq():
  	
 	if modelname == 'seq2seq':
 		model = Seq2seq(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_dst, n_maxlen)
-	elif modelname == 'seq2seq_att':
+	elif modelname == 'seq2seq_withatt':
 		model = Seq2seq_with_GlobalAtt(n_layer, src_vocab_len, dst_vocab_len , n_unit, v_eos_dst, n_maxlen)
 	else:
 		assert False
@@ -277,7 +277,7 @@ def init_seq2tree():
 	return (model,optimizer,data,translate,asm_vocab)
 
 
-modelname = 'seq2seq'
+modelname = 'seq2seq_withatt'
 
 import os
 def main():
@@ -290,12 +290,39 @@ def main():
 
 	global train_iter_step 
 	global modelname
-	if modelname in ['seq2seq','seq2seq_att']:
+	if modelname in ['seq2seq','seq2seq_withatt']:
 		model,optimizer,dataset,translate,asm_vocab = init_seq2seq()
 	elif modelname in ['seq2tree_flatten','seq2tree']:
 		model,optimizer,dataset,translate,asm_vocab = init_seq2tree()
 	else:
 		assert False
+	"""
+	dns = os.listdir('reedbush/' + modelname + '/models/')
+	pn = 'iter_1800_'
+	nfn = list(filter(lambda x: pn in x,dns))[0]
+	serializers.load_npz('reedbush/' + modelname + '/models/' + nfn,model)
+	ds = [dataset.get_test(-1) for _ in range(6)]
+	model.translate(list(map(lambda x: x[0],ds)))
+	exit()	
+	
+	"""
+	dns = os.listdir('reedbush/' + modelname + '/models/')
+	if modelname == 'seq2tree_flatten':
+		pn = 'iter_1800_'
+	else:
+		pn = 'iter_1800_'
+	nfn = list(filter(lambda x: pn in x,dns))[0]
+	serializers.load_npz('reedbush/' + modelname + '/models/' + nfn,model)
+	with open('od.pickle','rb') as fp:
+		ds = pickle.load(fp)[6:]
+	results = model.translate(list(map(lambda x: xp.array(x[0]),ds)))
+	ds = list(zip(ds,results))
+	sfn = 'sample_' + modelname + '.pickle'
+	print('write to',sfn)
[…]

### 2019-01-30 texs/paper_base.tex
tozita

@@
 %-------------------
-\etitle{Neural Network based Decompiler for Machine Coding}
-\jtitle{ニューラルネットを用いた機械語のための逆コンパイラ}
+\etitle{Neural Network based Decompiler for automatically recovering source codes from compiled binary data}
+\jtitle{ニューラルネットを用いた逆コンパイラ}
 
@@
 In this thesis, we do not try to recover the function name and variable name. 
-However, for hand-decompilation, sometimes the name can be estimated by the functionality of the variable.
+However, for hand-decompilation, sometimes the name can be estimated from the functionality of the variable.
 For example, \cite{hand_decompilation} used Boomerang decompiler and repeatedly fixed variable types and names of the decompilation results 
@@
 The function G receives X, subtracts 8 from P, decreases Q, and returns the value indicated by P.
-In the situation, is is estimated that X has a name related to {\sl stuck}, the function F has a name related to {\sl push},
-ands G has a name related to {\sl pop}.
+In the situation, is is estimated that X,F and G have names related to {\sl stuck}, {\sl push} and {\sl pop}, respectively.
 
@@
 
-In this chapter, we explain about the statistical formalization of the decompilation problem,
-and the neural network models used in the experiment.
+In this chapter, we explain about the decompiler, its statistical formalization and 
+the neural network models used in the experiment.
 \section{Decompiler}
@@
 % 文献 Usually, X is a high-level language and Y is relatively a low-level language. 
-For example, a Clang compiler translates the C language to the x64 assembly language, a javac compiler translates Java to a Java virtual machine code.
-This process is usually
-
+For example, a GNU C compiler translates the C language to the x64 assembly language, a javac compiler translates Java to a Java virtual machine code.
+% This process is usually 
+% 文献
+% Especially, 
+% This reverse process is usually insufficient or impossible.
 A decompiler is a program which aims to reverse the process of a compiler, retrieving a source code of the high-level language X from a source code of a low-level language Y. 
-% 文献
-Especially, 
-This reverse process is usually insufficient or impossible.
+When X is a high-level language and Y is relatively a low-level language, 
+this reverse process becomes insufficient or impossible
+\citep{hex_rays,decompile_hard_java}.
+% for instance X is the C language and Y is the x64 assembly language 
 This is because a lot of informaition, such as variable names or function names, are lost when compiling.
@@
 		\begin{minipage}[c]{0.5\hsize}
-		\begin{framed}
+		\fbox{
 			\lstinputlisting[breaklines=false]{insert_list.c}
-			\end{framed}
+			}
 			\caption*{Sample C source code}
 		\end{minipage}
-		\\
-		\begin{minipage}[c]{0.5\hsize} %title={Result of the Hopper Decompiler}
+		\\ \\
+		\begin{minipage}[b]{0.5\hsize} %title={Result of the Hopper Decompiler}
 			\begin{framed}
@@
 		\end{minipage}
-		\begin{minipage}[c]{0.5\hsize}
+		\begin{minipage}[b]{0.5\hsize}
 			\begin{framed}
-			\lstinputlisting[]{recstudio.c}
+			\lstinputlisting[breaklines=false]{recstudio.c}
 			\end{framed}
@@
 	\end{tabular}
-	\vspace*{-0.6cm}
+	% \vspace*{-0.6cm}
 	\caption{Decompilation results of existing decompilers for C source code}
@@
 \end{figure}
-
 Figure~\ref{fig:cw} shows an example of decompilation results of the Snowman decompiler version v0.1.3 and the REC Studio decompiler version 4.1 
@@
 In each step, a decompiler finds patterns in binary data, converts them to more high-level structure.
-However, covering all patterns might be hardly impossible, since there are many compilers and compiler optimizations.
-文献欲しいが見当たらない...
+However, covering all patterns might be hardly impossible, since there are many compilers and compiler optimizations \citep{hex_rays}.
 
-Therefore, applying statical machine
+By utilizing a corpus for soruce codes, a statistical method might have the potentioal for finding patterns automatically, without enumerating each patterns.
+Therefore, we tried to apply some statistical methods, which are described in the next section.
 
@@
 
-\section{Problem Settings}
+\section{Problem Settings and the Approaches}
 
@@
 In this thesis, we try to apply statistical approach, specifically SMT (statistical machine translation) technique, for decompilation.
+SMT is the task which tries to translate one sentense $sx$ written in one language into the sentense $sy$ written in another language.
+
 The decompilation problem is formulated as follows. 
+Suppose that there is a compiler $ f $ which converts a source code $ sx $ written in a programming language 
+to a source code $ sy $  written in another programming language Y with probability $p(sy|sx)$.
+In addition, suppose that the human-generated source code $ sx $ follows the probability distrubution $ p(sx) $.
+In this situation, the decompilation probability distribution $ p(sx|sy) $ in proportion to $ p(sy|sx)p(sx) $ according to the Bayesian low, 
+and the $\argmax_{sx} p(sx|sy)$ is considered as the best human-intelligible decompilation result for the code $sy$.
 
-Given $sx = [sx_1, \dots, sx_n] $ as a tokenized sequence of the source code of domain language X, compiler generates $sy$ as a code of target language Y with probability $p(sy|sx)$.
-Then, the best decompilation result for target source code $sy$ is $ \argmax_{sx} p(sx|sy)$. 
-To generate $ \argmax_{sx} p(sx|sy)$, we decomposit $ p(sx|sy) = p([sx_1, \dots, sx_n] |sy) = \prod_{k=1}^{n} p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $,
-where $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ represents the probability that the token $ sx_k $ follows to the sequence $ [sx_1,\dots,sx_{k-1}] $ 
-when the input sequence is $ sy $. 
-We try to estimate the probability $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ by LSTM, which is described in the next section.
-With estimated $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $, we can generate approximated $ \argmax_{sx} p(sx|sy)$ sequentially from $sx_1$ to $sx_n$ by selecting token $ \argmax_{sx_{k}} p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ at each timing.
+In the experiment, we collected source codes from open source projects as the random sampling from the distribution $ p(sx) $, 
+and compileded them to generate the data pairs $ {\{(sx_k,sy_k)\}}_k $.
+Then the data pairs are used for training the SMT models to estimate $p(sx|sy)$, and testing the performance of the models.
+
+% Suppose that there is a compiler  Given $ sx $ as a source code of domain language X, compiler generates $sy$ as a code of target language Y with probability $p(sy|sx)$.
+
+% Given $sx = [sx_1, \dots, sx_n] $ as a tokenized sequence of the source code of domain language X, compiler generates $sy$ as a code of target language Y with probability $p(sy|sx)$.
+% Then, the best decompilation result for target source code $sy$ is $ \argmax_{sx} p(sx|sy)$. 
+% To generate $ \argmax_{sx} p(sx|sy)$, we decomposit $ p(sx|sy) = p([sx_1, \dots, sx_n] |sy) = \prod_{k=1}^{n} p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $,
+% where $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ represents the probability that the token $ sx_k $ follows to the sequence $ [sx_1,\dots,sx_{k-1}] $ 
+% when the input sequence is $ sy $. 
+% We try to estimate the probability $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ by LSTM, which is described in this section.
+% With estimated $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $, we can generate approximated $ \argmax_{sx} p(sx|sy)$ sequentially from $sx_1$ to $sx_n$ by selecting token $ \argmax_{sx_{k}} p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ at each timing.
 
@@
 % then the objective becomes to $ \argmax_{sx,f(sx)=sy} p(sx)$.
-
 % The distribution $p(sx)$ is approximated by collecting source code from open source projects.
@@
 
-\section{Modeling}
-
 % (TODO)LSTM,Seq2seqの説明、その後Attentionについて説明、さらにその後seq2treeについて説明する。
-\subsection{LSTM}
-%72 words.
-LSTM (Long Short-Term Memory) is a unit of Recurrent Neural Network. 
-It is first introduced in \cite{first_LSTM}, for overcoming the vanishing gradient problem and exploding gradient problem.
-Roughly speaking, LSTM unit recieves two input vectors, 
-the one represents the internal state of the LSTM, and the other is the input for the LSTM unit, 
+\subsection{RNN and LSTM}
+The RNN (Recurrent Neural Network) is a neural network for dealing with sequence data.
+The structure of the RNN is the sequence of the same node units, as shown in figre~\ref{fig:encoder} and figre~\ref{fig:decoder}. 
+The LSTM (Long Short-Term Memory) is a unit of Recurrent Neural Network. 
+It was first introduced in \cite{first_LSTM}, for overcoming the vanishing gradient problem and exploding gradient problem.
+In short, LSTM unit recieves two input vectors, 
+the one is the internal state of the LSTM, and the other is the input for the LSTM unit, 
 and LSTM emits one output vectors, which represents the next internal state of the LSTM.
@@
 % 477 words.
-LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the sequence-to-sequence (sequence to sequence) model.
-SMT is the task which tries to translate one sentense $sx$ written in one language into the sentense $sy$ written in another language.
 
-Sequence-to-sequence model is composed of two modules, the encoder netwrok and the decoder network.
+The sequence-to-sequence (sequence to sequence) model is the model for SMT task, introduced in  \cite{seq2seq}.
+% The combination of RNN and LSTM is applied to SMT task in, as the essential unit of the 
+Sequence-to-sequence model is composed of two recurrent neural networks, the encoder netwrok and the decoder network.
 
+\begin{figure}[]
+	\begin{center}
+	\includegraphics[height=4cm]{encoder.png}
+	\end{center}
+	\caption{The encoder network of the sequence-to-sequence model}
+	\label{fig:encoder}
+	\begin{center}
+	\includegraphics[height=5.7cm]{decoder.png}
+	\end{center}
+	\caption{ The decoder network of the sequence-to-sequence model}
+	\label{fig:decoder}
+\end{figure}
+
+Figure figre~\ref{fig:encoder} shows the strucure of the encoder network.
 The purpose of the encoder network is to summerize the input sequence $sx$, whose length varies depending on the sequence, into one fixed length vector.
@@
 
-The purpose of the decoder network is to estimate the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $. 
+Figure figre~\ref{fig:decoder} shows the strucure of the decoder network.  The purpose of the decoder network is to estimate the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for each k. 
 The training process is carried out as follows. 
-First, $sy$ is tokenized, appended the token $ EOS $ for indicating the end of the sequence, then embedded to a vector representation $vy_{1} \dots vy_{m}$ in the same way as embedding $sx$.
-From the start vector $y_{begin}$ and encoded input $ enc_{n} $, first internal state $ dec_{1}$ is calcuated as $ LSTM_{dec}(enc_{n},y_{begin}) $.
-Then, $ dec_{1} \dots dec_{m} $ are calculated in accordance with the recursive formula $ dec_{k} = lstm_{dec}(dec_{k-1},vy_{k}) $.
+First, $sy$ is tokenized, embedded to a vector representation $vy_{1} \dots vy_{m}$ in the same way as embedding $sx$.
+% prepended the token $ EOS $ for indicating the end of the sequence, then 
+Then, the first internal state $ dec_{1}$ is calcuated from the start vector $vy_{begin}$ and encoded input $ enc_{n} = dec_{0} $ in accordance with the formula  $ LSTM_{dec}(enc_{n},y_{begin}) $.
+Then, $ dec_{2} \dots dec_{m+1} $ are calculated in accordance with the recursive formula $ dec_{k+1} = lstm_{dec}(dec_{k},vy_{k}) $.
 Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_{dec} $ and then softmaxed to generate a probability vector $ py_{k} $.
 The probability vector $ py_{k} $ is intended to represent the probability distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
-So the network is trained to reduce the difference between predicted distribution $ py_{k} $ and actual distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
+Thus the network is trained to reduce the difference between predicted distribution $ py_{k} $ and actual distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
 In the experiment, we choiced cross-entropy of $ py_{k} $ and $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for loss function.
@@
 $ \argmax_{sy} p(sy|sx) = \argmax_{sy} \prod_{k=1}^n p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
-Calculating argmax directly is time consuming, so we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_m]$ sequentially.
+Calculating argmax directly is time consuming, therefore we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_m]$ sequentially.
 First, $sy_1$ is calculated as $ \argmax_{sy_1} p(sy_1|sx,[]) $, where distribution $ p(sy_1|sx,[]) $ is approximated by 
@@
 % 219 words
-First, we collected source codes by crawling \cite[GitHub]{github}, cloning about 900 repositories with C language topic, 
+We collected source codes by crawling \cite[GitHub]{github}, cloning about 900 repositories with C language topic, 
 and recursively searched each folder to enumerate C language source code.
@@
 \chapter{Acknowledgement}
+I thank Prof. Sugiyama and Lecture Sato for providing useful advice, supplying computational resources, helping me with writing this thesis and 
+correcting my English.
+I also thank A. Sano, who is my college classmate, for checking my English.
 

### 2019-01-30 texs/compile.sh

@@ -1,4 +1,4 @@
 cp ../../tex-srcs/iscs-thesis.cls ./
 sed '/__NAMES__/r ../../names.txt' paper_base.tex | sed 's/__NAMES__//g' > paper.tex
-extractbb bleu.png && extractbb edit_dist.png && extractbb ast_lens.png && extractbb c_lens.png && extractbb ast_zu.png &&
+extractbb bleu.png && extractbb edit_dist.png && extractbb ast_lens.png && extractbb c_lens.png && extractbb ast_zu.png && extractbb encoder.png && extractbb decoder.png &&
 platex paper.tex && pbibtex paper && platex paper.tex && platex paper.tex && platex paper.tex && dvipdfm paper.dvi

### 2019-01-30 texs/paper_base.tex
mazu teisai

@@
 \etitle{Neural Network based Decompiler for automatically recovering source codes from compiled binary data}
-\jtitle{ニューラルネットを用いた逆コンパイラ}
+\jtitle{ニューラルネットを用いた逆コンパイラに}
 
@@
 \usepackage{url}
-\usepackage{natbib}
+\usepackage[numbers]{natbib}
 \usepackage[dvipdfmx]{graphicx}
@@
 In experiments, we use source codes collected from open source projects and their binary data for training and evaluating the neural networks.
-From the experiment, we can observe little improvement in the decompilation result with the use of attention.
-However, the results were not applicable for practical use.
+From the experiment, we can observe little improvement in the result of decompilation with the use of attention.
+Unfortunately, the results were not applicable for practical use.
 
@@
 In this thesis, we apply neural networks to the problem of decompilation to generate human-friendly pseudocodes. 
-This idea is originated from \cite{Motoneta}, in which they used recurrent neural networks, in particular sequence-to-sequence model, for decompilation.
-However, their model does not seem to have some features for improving the quality of decompilation.
-Therefore, we implemented the attention mechanisme, which is introduced in \cite{dot_attention}, for improving the quality.
-Additionaly, the sequence-to-sequence model, which they used for modeling, ignores the structure of the C language code.
-Therefore, we also implemented the sequence-to-tree model, which is suggested in \cite{Seq2Tree}, for generating structured C language source code.
+This idea is originated from \citet{Motoneta}, in which they used recurrent neural networks, in particular sequence-to-sequence model, for decompilation.
+However, their model does not seem to be implemented some features for improving the quality of decompilation.
+Therefore, we implemented the attention mechanism, which is introduced in \citet{dot_attention}, for improving the quality.
+Additionally, the sequence-to-sequence model, which they used for the modeling, ignores the structure of a C language code.
+Therefore, we also implemented the sequence-to-tree model, which is suggested in \citet{Seq2Tree}, for generating structured C language source code.
 
 In the experiment, we tested three models, the basic sequence-to-sequence model, the sequence-to-sequence model with attention and the sequence-to-tree model.
-As the result of the experiment, the attention mechanism showed little improvemtn in the performance, while the sequence-to-tree does not.
-Unfortunately, the results were not applicable for practical use, because the most of decompilation results were incorrect.
+As the result of the experiment, the attention mechanism showed little improvement in the performance, while the sequence-to-tree does not.
+Unfortunately, the results of the all models seemed to be not applicable for practical use.
+The results of decompilation for short C source code fragment were not so bad. 
+Nevertheless, the results for long C codes, which are considered to appear in practical use, were mostly failed.
 
@@
 \chapter{Related Works}
-In this section, we review related works.
+In this chapter, we review related works.
 
@@
 
-In \cite{Motoneta}, they used the seqence-to-sequence model, which is a popular technique in the machine translation.
+\citet{Motoneta} used the seqence-to-sequence model, which is a popular technique in the machine translation.
 The seqence-to-sequence model is also evaluated in this thesis.
 
-In \cite{genetic_decompiler}, they applied genetic programming to decompilation.
-They prepared big corpus of C source codes, and they repeatedly mutated C code to reduce the difference of the target binary and the compilation result of the source code.
+\citet{genetic_decompiler} applied genetic programming to decompilation.
+They prepared a big corpus of C source codes, then they repeatedly mutated C codes to reduce the difference of the target binary and the compilation result of a C code.
 
@@
 However, for hand-decompilation, sometimes the name can be estimated from the functionality of the variable.
-For example, \cite{hand_decompilation} used Boomerang decompiler and repeatedly fixed variable types and names of the decompilation results 
+For example, \citet{hand_decompilation} used the Boomerang decompiler and repeatedly fixed variable types and names of the decompilation results 
 to recover the source code of a software.
@@
 
-\cite{name_recover_from_decompile_result} tackled this work. 
+\citet{name_recover_from_decompile_result} tackled this work. 
 In that paper, they tried to estimate the name of a variable which appears in the decompilation result of a compiled C program.
@@
 This kind of name estimation also appears in the context of deobfuscation.
-\cite{deobfsucation_matome}
+\citep{deobfsucation_matome}
 % これ雑にreferenceしたけどあんま意味ないよなぁ...?
@@
 For example, in the web application, a JavaScript code of a program should be distributed in order to be executed on client web browsers.
-To protect the program from cracking, the JavaScript code is sometimes minified.
+Such JavaScript code is minified in order to protect the program from cracking. 
 All comments, newlines, indents are removed and variable names are substituted to automatically generated meaningless names.
 
-\cite{JSNaughty} applied statistical machine translation for this task. 
+\citet{JSNaughty} applied statistical machine translation for this task. 
 They calculated the future value of a variable from its functionality, then 
@@
 
-There are many applications of neural networks for program synthesis. They are summurized in \cite{deep_programming_matome}.
+There are many applications of neural networks for program synthesis. They are summarized by \citet{deep_programming_matome}.
 
-In this thesis, we applied sequence-to-tree model suggested in \cite{Seq2Tree}, because the input of the decompiler is the sequence of machine codes.
+In this thesis, we applied sequence-to-tree model suggested by \citet{Seq2Tree}, 
+because the input of the decompiler is a sequence of machine codes and
+the output of the decompiler is an AST.
 
-For another example, in \cite{coffeescript_to_javascript}, they tried to mutually translate from JavaScript to CoffeeScript, and its inverse.
+For another example, \citet{coffeescript_to_javascript} tried to mutually translate from JavaScript to CoffeeScript, and its inverse.
 In that case, both JavaScript codes and CoffeeScript codes are tree structured, so they suggested tree-to-tree model.
 
-\chapter{Problem Settings and Methots}
+\chapter{Problem Settings and Methods}
 
@@
 % for instance X is the C language and Y is the x64 assembly language 
-This is because a lot of informaition, such as variable names or function names, are lost when compiling.
+This is because many information, such as variable names or function names, are lost when compiling.
 Additionally, the program structure described in the high level-language is lost too. 
@@
 
-By utilizing a corpus for soruce codes, a statistical method might have the potentioal for finding patterns automatically, without enumerating each patterns.
+By utilizing a corpus for source codes, a statistical method might have the potential for finding patterns automatically, without enumerating each patterns.
 Therefore, we tried to apply some statistical methods, which are described in the next section.
@@
 In this thesis, we try to apply statistical approach, specifically SMT (statistical machine translation) technique, for decompilation.
-SMT is the task which tries to translate one sentense $sx$ written in one language into the sentense $sy$ written in another language.
+SMT is the task which tries to translate one sentence $sx$ written in one language into the sentence $sy$ written in another language.
 
@@
 to a source code $ sy $  written in another programming language Y with probability $p(sy|sx)$.
-In addition, suppose that the human-generated source code $ sx $ follows the probability distrubution $ p(sx) $.
+In addition, suppose that the human-generated source code $ sx $ follows the probability distribution $ p(sx) $.
 In this situation, the decompilation probability distribution $ p(sx|sy) $ in proportion to $ p(sy|sx)p(sx) $ according to the Bayesian low, 
@@
 In the experiment, we collected source codes from open source projects as the random sampling from the distribution $ p(sx) $, 
-and compileded them to generate the data pairs $ {\{(sx_k,sy_k)\}}_k $.
+and compiled them to generate the data pairs $ {\{(sx_k,sy_k)\}}_k $.
 Then the data pairs are used for training the SMT models to estimate $p(sx|sy)$, and testing the performance of the models.
@@
 The LSTM (Long Short-Term Memory) is a unit of Recurrent Neural Network. 
-It was first introduced in \cite{first_LSTM}, for overcoming the vanishing gradient problem and exploding gradient problem.
-In short, LSTM unit recieves two input vectors, 
+It was first introduced by \citet{first_LSTM}, for overcoming the vanishing gradient problem and exploding gradient problem.
+In short, LSTM unit receives two input vectors, 
 the one is the internal state of the LSTM, and the other is the input for the LSTM unit, 
@@
 
-The sequence-to-sequence (sequence to sequence) model is the model for SMT task, introduced in  \cite{seq2seq}.
+The sequence-to-sequence (sequence to sequence) model is the model for SMT task, introduced by \citet{seq2seq}.
 % The combination of RNN and LSTM is applied to SMT task in, as the essential unit of the 
-Sequence-to-sequence model is composed of two recurrent neural networks, the encoder netwrok and the decoder network.
+Sequence-to-sequence model is composed of two recurrent neural networks, the encoder network and the decoder network.
 
@@
 
-Figure figre~\ref{fig:encoder} shows the strucure of the encoder network.
-The purpose of the encoder network is to summerize the input sequence $sx$, whose length varies depending on the sequence, into one fixed length vector.
+Figure~\ref{fig:encoder} shows the structure of the encoder network.
+The purpose of the encoder network is to summarize the input sequence $sx$, whose length varies depending on the sequence, into one fixed length vector.
 This process is carried out as follows. 
 First, $sx$ is tokenized to sequence $sx_{1} \dots sx_{n}$, and each token $sx_{k}$ is embedded to its vector representation $vx_{k}$. 
-Then, the initial LSTM internal state $enc_0$ is intialized randomely, 
+Then, the initial LSTM internal state $enc_0$ is initialized randomly, 
 and $ enc_{1} \dots enc_{n} $ are calculated in accordance with the recursive formula $ enc_{k} = lstm_{enc}(enc_{k-1},vx_{k}) $.
@@
 
-Figure figre~\ref{fig:decoder} shows the strucure of the decoder network.  The purpose of the decoder network is to estimate the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for each k. 
+Figure~\ref{fig:decoder} shows the structure of the decoder network.  The purpose of the decoder network is to estimate the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for each k. 
 The training process is carried out as follows. 
@@
 % prepended the token $ EOS $ for indicating the end of the sequence, then 
-Then, the first internal state $ dec_{1}$ is calcuated from the start vector $vy_{begin}$ and encoded input $ enc_{n} = dec_{0} $ in accordance with the formula  $ LSTM_{dec}(enc_{n},y_{begin}) $.
+Then, the first internal state $ dec_{1}$ is calculated from the start vector $vy_{begin}$ and encoded input $ enc_{n} = dec_{0} $ in accordance with the formula  $ LSTM_{dec}(enc_{n},y_{begin}) $.
 Then, $ dec_{2} \dots dec_{m+1} $ are calculated in accordance with the recursive formula $ dec_{k+1} = lstm_{dec}(dec_{k},vy_{k}) $.
@@
 
-First is the Bidirectional Reccurent Neural Networks (BRNN) is the architecture introduced in \cite{BiRNN}.
-In the experiment, this architecture is used for the encoder network as follows.
+First is the Bidirectional Recurrent Neural Networks (BRNN) is the architecture introduced by \citet{BiRNN}.
+In our experiment, this architecture is used for the encoder network as follows.
 In addition to the internal state $ enc_{k} $, the reverse internal state $ enc_{k}^{\gets} $ is also calculated 
@@
 
-Second is the multi-layer reccurent neural networks, introduced in \cite{multi_layer}.
-They reported that, feeding the output sequence of the LSTM network to another LSTM network, like stucking the network layers, will improve the accuracy of the prediction.
-This architecture is called as stucked reccurent neural networks or multi-layer reccurent neural networks.
+Second is the multi-layer recurrent neural networks, introduced by \citet{multi_layer}.
+They reported that, feeding the output sequence of the LSTM network to another LSTM network, like stacking the network layers, will improve the accuracy of the prediction.
+This architecture is called as stacked recurrent neural networks or multi-layer recurrent neural networks.
 
@@
 
-The attention module is first developed by \cite{attention_paper}.
-We inplemented the global general attention, which is intoduced in \cite{dot_attention}, for improving the quality of decompilation.
+The attention module is first developed by \citet{attention_paper}.
+We implemented the global general attention, which is introduced by \citet{dot_attention}, for improving the quality of decompilation.
 In the following, we will describe about the global general attention.
@@
 The context vector $ ctx_{k} $ is calculated as follows.
-For each state $ enc_{l} $, the importance of the state $ a_{l} $ is calculalted as $ a_{l} = score(dec_{k},enc_{l}) $,
-then the $ ctx_{k} $ is calculated as $ ctx_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc{l} $, as the weighted average of $ enc_{1} \dots enc_{n} $.
+For each state $ enc_{l} $, the importance of the state $ a_{l} $ is calculated as $ a_{l} = score(dec_{k},enc_{l}) $,
+then the $ ctx_{k} $ is calculated as $ ctx_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc{l} $, 
+as the weighted average of $ enc_{1} \dots enc_{n} $.
 % Multiple score functions are introduced by \cite{dot_attention}, and we choiced 
-In the paper by \cite{dot_attention}, various kinds of score function is suggested.
+In the paper by \citet{dot_attention}, various kinds of score function is suggested.
 We used general score function, which is calculated as $ score(dec_{k},enc_{l}) = dec_{k}^T W enc_{l} $ ,
@@
 % 184 words
-Compare to natural languages, programming languages obeys rigid grammers. % wich are usually context free grammers.
-Therefore, it is reasonable to consider the grammer of the programming language when generating programs.
+Compare to natural languages, programming languages obeys rigid grammars. % wich are usually context free grammers.
+Therefore, it is reasonable to consider the grammar of the programming language when generating programs.
 Sequence-to-Tree is a model for generating tree-structured output from sequence input. 
-This model is introduced in \cite{Seq2Tree} for generating a program from a program specification written in the natural language. 
-This task is similer to our task, which aims to generate programs from the sequence of the assembly code, so we implemented this model in the experiment.
+This model is introduced by \citet{Seq2Tree} for generating a program from a program specification written in the natural language. 
+This task is similar to our task, which aims to generate programs from the sequence of the assembly code, so we implemented this model in the experiment.
 
 Now, we will describe about the sequence-2-tree model.
-sequence-to-tree model is composed of two modules, the encoder netwrok and the decoder network.
-The encoder network of sequence-2-tree model is the same as the encoder network of sequence-to-tree model. It summerize the input sequence into one fixed length vector.
+sequence-to-tree model is composed of two modules, the encoder network and the decoder network.
+The encoder network of sequence-2-tree model is the same as the encoder network of sequence-to-tree model. It summarize the input sequence into one fixed length vector.
 
@@
 A tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
-For example, the tree shown in figre~\ref{fig:ast_zu} is gererated from the sequence $ [act_1, \dots act_{12}] $, 
+For example, the tree shown in figure~\ref{fig:ast_zu} is generated from the sequence $ [act_1, \dots act_{12}] $, 
 where action $ act_k $ expands the left-most nonterminal symbol in the tree generated from the action sequence $ [act_1, \dots act_{k-1}] $. 
@@
 then the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(act_k|sx,[act_1, \dots act_{k-1}]) $. 
-The sequence-to-sequence model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
-calculating $ LSTM_{dec}(dec_{k},av_{k}) $ sequentially for estimating $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $.
+The sequence-to-sequence model is now applicable for generating tree structure, by embeding each action to representing vector $av_k$ and 
+calculating $ lstm_{dec}(dec_{k},av_{k}) $ sequentially for estimating $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $.
 
@@
 
-In that paper, they additionaly tries to use the information which is peculiar to the tree structure. 
+In that paper, they additionally tries to use the information which is peculiar to the tree structure. 
 For expanding the node $d$, they also use the information of node type $ nf_{d} $ and the parent action $p_{d}$ from which $d$ is generated.
-And they calculalte $ LSTM_{dec}(dec_{k},[av_{k}; nfv_{d}; pv_{d}]) $ instead of $ LSTM_{dec}(dec_{k},av_{k}) $, 
+Then they calculated $ lstm_{dec}(dec_{k},[av_{k}; nfv_{d}; pv_{d}]) $ instead of $ lstm_{dec}(dec_{k},av_{k}) $, 
 where $nfv_{d},pv_{d}$ are the vector embedding of $nf_{d},p_{d}$.
@@
 \chapter{Experiments}
-In this chapter, we explain the detail of the data preparetion and implementation.
-The implementation source codes are avaiable at \url{https://github.com/satos---jp/neural_decompiler}.
+In this chapter, we explain the detail of the data preparation and implementation.
+The implementation source codes are available at \url{https://github.com/satos---jp/neural_decompiler}.
 
@@
 % 219 words
-We collected source codes by crawling \cite[GitHub]{github}, cloning about 900 repositories with C language topic, 
+We collected source codes by crawling GitHub \citep{github}, cloning about 900 repositories with C language topic, 
 and recursively searched each folder to enumerate C language source code.
@@
 
-The pairs were generated as follows. Let {\sl S0} be an original C source code.
+The pairs were generated as follows. Let S0 be an original C source code.
 \begin{enumerate}
-\item Remove all preprocessor, such as {\sl \#include}, in {\sl S0} to generate preprosessed C code {\sl S1}. 
-\item Tokenize {\sl S1} and rearrange them in {\sl S2} so that there is exactly one token for each line. 
+\item Remove all preprocessor, such as \texttt{\#include}, in S0 to generate preprocessed C code S1. 
+\item Tokenize S1 and rearrange them in S2 so that there is exactly one token for each line. 
 \item 
-Compile {\sl S2} by gcc (GNU C compiler) with no optimization (-O0) and debug option to get assembly code {\sl S3}. 
-With debug option, {\sl S3} contains information about the source code position which each assembly operations are originated from.
-\item Assemble {\sl S3} to object file {\sl S4} and disassemble {\sl S4} to get information eliminated assembly code {\sl S5}.
+Compile S2 by the GNU C compiler with no optimization option (-O0) and debug option to get assembly code S3. 
+With debug option, S3 contains information about the source code position which each assembly operations are originated from.
+\item Assemble S3 to object file S4 and disassemble S4 to get information eliminated assembly code S5.
 \item 
-Parse {\sl S2} with clang to get AST (abstract syntax tree) of the source code. 
+Parse S2 with clang to get AST of the source code. 
 And for each subtree of AST, we can get C fragment source code which corresponds to the subtree, 
-and we can get assembly code corresponds to the C fragment by employing {\sl S5} combine with {\sl S3}.
+and we can get assembly code corresponds to the C fragment by employing S5 combine with S3.
 \end{enumerate}
@@
 Second way is the tokenized sequence of assembly codes. 
-The disassembled opcodes and operands in {\sl S5} are split to symbols, and concatenated these sequences to one sequence, then we modified followings.
+The disassembled opcodes and operands in S5 are split to symbols, and concatenated these sequences to one sequence, then we modified followings.
 \begin{itemize}
-\item For each end of the operations, the {\sl ENDLINE} symbol is added to indicate the end of operation.
+\item For each end of the operations, the \texttt{ENDLINE} symbol is added to indicate the end of operation.
 \item 
-The relative access of code address, such as {\sl call} or {\sl jump} operations, 
+The relative access of code address, such as \texttt{call} or \texttt{jump} operations, 
 are relabeled like $\alpha$-conversion for making code position independent and for reducing the vocabulary size.
 \item The big integer values are substituted. 
-In detail, the integer in the range from -255 to 256 are preserved as it is, and the other integeres are substituted with the {\sl \_\_HEX\_\_} symbol.
+In detail, the integer in the range from -255 to 256 are preserved as it is, and the other integers are substituted with the \texttt{\_\_HEX\_\_} symbol.
 This also reduces the vocabulary size.
@@
 
-We choiced second way for the experiment.
+We choosed second way for the experiment.
 This is because, in our case, the assembly code is generated from common C compiler, therefore the assembly code can be disassembled uniquely.
-For example, \cite{disasm_obfuscate} proposed a obfuscation technique, which deceives the disassembler to generate wrong disassembly result.
+For example, \citet{disasm_obfuscate} proposed a obfuscation technique, which deceives the disassembler to generate wrong disassembly result.
 In that case, the first way might be better than the second way.
@@
 % 232 words
-The C source codes were parsed to AST by the \cite{clang} and its Python bindings together with \cite{pycparser}, 
-because all of the tools are individualy not sufficient for generating dataset.
+The C source codes were parsed to AST by a Clang compiler \citep{clang} and its Python bindings together with pycparser \citep{pycparser}, 
+because all of the tools are individually not sufficient for generating dataset.
 Then, the AST is converted to input data by following modifications.
@@
 \item The variable-ary nodes and optional nodes are converted. 
-For example, the {\sl CompoundStatement} node has variable number of statements. 
-We converted such list of nodes to the chains of concatnation {\sl CONS} and termination {\sl NIL}, like a list representation in functional language.
-Another example is the  {\sl If} statement, whose {\sl else} clausure are sometimes missing. 
-We converted such optional node to the alternative of {\sl SOME} and {\sl NONE}, like a optional data structure in functional language.
+For example, the \texttt{CompoundStatement} node has variable number of statements. 
+We converted such list of nodes to the chains of concatenation \texttt{CONS} and termination \texttt{NIL}, like a list representation in functional language.
+Another example is the \texttt{if} statement, whose \texttt{else} clause are sometimes missing. 
+We converted such optional node to the alternative of \texttt{SOME} and \texttt{NONE}, like a optional data structure in functional language.
 \item The variable names, function names, label names, or type names were renamed like $\alpha$-conversion.
@@
 The integer literal less than 256 is preserved, and the literal greater than 256 is clipped to 256.
-The string, float and character literals are converted to {\sl \_\_LITERAL\_\_} simbol.
+The string, float and character literals are converted to \texttt{\_\_LITERAL\_\_} symbol.
 
-Modifying the node to indicate the value in the assembly code corresponding to the literal is also conceibable way,
-but we did not implement this because of its technical difficalty, so this is left to future work.
+Modifying the node to indicate the value in the assembly code corresponding to the literal is also conceivable way,
+but we did not implement this because of its technical difficulty, so this is left to future work.
 \end{itemize}
@@
 \section{Model Configuration}
-The training model was implemented with Chainer version 4.5.0. (\url{https://chainer.org/})
+The training model was implemented with Chainer version 4.5.0 \citep{chainer}.
 We implemented three models, Seq2seq, Seq2seqAtt, and Seq2tree.
@@
 For the optimizer of the training, we used Adam, which is introduced in \cite{Adam}.
-The paremeters of Adam are $ (\alpha,\beta_1,\beta_2) = (0.001,0.9,0.999) $, which are the default parameters of Chainer version 4.5.0.
+The parameters of Adam are $ (\alpha,\beta_1,\beta_2) = (0.001,0.9,0.999) $, which are the default parameters of Chainer version 4.5.0.
 % 学習の際のoptimizerにはAdam(文献)を用いた。
@@
 Here, the edit distance ratio between two strings means the Levenshtein distance divided by the average length of the two strings.
-Idealy, the correctness of the decompilation result should be measured by the distance of the meaning of the program.
+Ideally, the correctness of the decompilation result should be measured by the distance of the meaning of the program.
 However the decompilation result is usually uncompilable, so we used the edit distance of the source codes as the approximation of the correctness.
 
-BLEU is the metrics for the similality of the ground truth and the decompilation result. 
-It is first introduced in \cite{BLEU}, for evaluating the performance of the machine translation.
-BLEU is calculated from the sets of the n-gram for each sentense. 
-If the two sentens has similar n-gram sets, the BLEU score becomes higher.
-In our case, it means that the decompilation result is more similer to the program written by human, that is, more human intelligible.
+BLEU is the metrics for the similarity of the ground truth and the decompilation result. 
+It is first introduced by \citet{BLEU}, for evaluating the performance of the machine translation.
+BLEU is calculated from the sets of the n-gram for each sentence. 
+If the two sentences has similar n-gram sets, the BLEU score becomes higher.
+In our case, it means that the decompilation result is more similar to the program written by human, that is, more human intelligible.
 
@@
 % 図2は各モデルについて、学習に用いたデータ数と編集距離をプロットしたグラフである。
-Figure~\ref{fig:editdist} shows the relation of trainig data size and the averaged edit distance ratio for each models.
-Figure~\ref{fig:bleu} shows the relation of trainig data size and the averaged BLEU score for each models.
+Figure~\ref{fig:editdist} shows the relation of training data size and the averaged edit distance ratio for each models.
+Figure~\ref{fig:bleu} shows the relation of training data size and the averaged BLEU score for each models.
 The lower edit distance ratio and the higher BLEU score means the better decompilation performance.
@@
 
-For the second middle example, Seq2Seq outputs invalid parenthesesed souce code, Seq2SeqAtt outputs invalid syntax (combination of while and else statement) code,
+For the second middle example, Seq2Seq outputs source code with invalid parentheses, Seq2SeqAtt outputs invalid syntax (combination of while and else statement) code,
 while Seq2Tree outputs correct syntax but many wrong subexpressions.
 
-For the third large exapmle, all of the three models output a function with wrong body statement.
-The {\sl INVALID\_FUNCTION\_DECL} in the result of Seq2Tree means it outputs wrong structured function type, and the {\sl TRANCATE} means 
+For the third large example, all of the three models output a function with wrong body statement.
+The \texttt{INVALID\_FUNCTION\_DECL} in the result of Seq2Tree means it outputs wrong structured function type, and the \texttt{TRANCATE} means 
 the action is truncated because the too long action sequence is estimated. 
-For long size function or statements, Seq2Tree tends to expand list type node to {\sl CONS} node, which causes infinit expansion of sequence,
-and as a result, the type of the output function becomes broken and the body of the function becoms truncated.
+For long size function or statements, Seq2Tree tends to expand list type node to \texttt{CONS} node, which causes infinite expansion of sequence,
+and as a result, the type of the output function becomes broken and the body of the function becomes truncated.
 
@@
 
-\chapter{Furure research}
+\chapter{Future research}
 In this chapter, we suggest some other approaches to improve the accuracy of our decompilation models.
@@
 We used tokenized assembly string sequences for training. 
-However, such simple concatnation of sequences might lose the information of the unity of each instructions.
+However, such simple concatenation of sequences might lose the information of the unity of each instructions.
 To improve this point, we propose the following method.
@@
 First, each assembly instruction sequences are encoded by instruction encoding network into one instruction embedding vector, 
-so that the assembly codes turn into the sequennces of embedding vectors.
-Then, the sqeuence of embedding vectors is encoded into one reduced vector by assembly code encoder network.
+so that the assembly codes turn into the sequences of embedding vectors.
+Then, the seqeuence of embedding vectors is encoded into one reduced vector by assembly code encoder network.
 
@@
 \subsection{Copy Leaf Data from Assembler}
-The translation results show that the sequence-to-tree model have difficalty in recovering the leaf data of the program.
+The translation results show that the sequence-to-tree model have difficulty in recovering the leaf data of the program.
 Hence changing the method for expanding leaf node might improve the accuracy of decompilation.
@@
 In the assembly code, the string literal appears in the form of a memory address, and the other three literals appear in the form of an immediate value.
-Therefore, instead of estimating literal value directly, estimating the correcponding position in the assembly code might improve the correctness of decompilation.
+Therefore, instead of estimating literal value directly, estimating the corresponding position in the assembly code might improve the correctness of decompilation.
 
 The second kind is the type of operator. These can be also estimated from the assembly code.
-For example, the operator $ + $ is compiled to the opecode {\sl add}, the operator $ | $ is compiled to the opecode {\sl or}, and so on. 
+For example, the operator $ + $ is compiled to the opcode \texttt{add}, the operator $ | $ is compiled to the opcode \texttt{or}, and so on. 
 Thus the type of operator might be estimated by indicating the correspond position in the assembly code.
@@
 The third kind is the variable name. In the assembly code, a variable corresponds to a memory access. 
-Therefore, the name of a variable is identified by its corresponding memory position, similar to avobe two kinds.
+Therefore, the name of a variable is identified by its corresponding memory position, similar to above two kinds.
 
@@
 
-To preserve the information of the tree structure, we suddest to train the network for estimating each root-to-leaf action sequences in the AST,
+To preserve the information of the tree structure, we suggest to train the network for estimating each root-to-leaf action sequences in the AST,
 instead of the flattened action sequence. 
@@
 and these sequences are independent of each other, when generating AST.
-Therefore, we may estimate each of the sequences from the asssembly token sequence by the sequence-to-sequence model.
+Therefore, we may estimate each of the sequences from the assembly token sequence by the sequence-to-sequence model.
 
@@
 We tested three neural network models Seq2Seq, Seq2SeqAtt and Seq2Tree for decompilation.
-Numerically, Seq2SeqAtt peformanced better results compared to the other two models,
+Numerically, Seq2SeqAtt performed better results compared to the other two models,
 but all of three models were not acceptable for practical use.

### 2019-01-30 texs/paper_base.tex
titleigai

@@
 
-A compiler is a program which compiles a source code written in language X to another language Y. 
+A compiler is a program which compiles a source code written in language Y to another language X. 
 % 文献 Usually, X is a high-level language and Y is relatively a low-level language. 
@@
 % This reverse process is usually insufficient or impossible.
-A decompiler is a program which aims to reverse the process of a compiler, retrieving a source code of the high-level language X from a source code of a low-level language Y. 
-When X is a high-level language and Y is relatively a low-level language, 
+A decompiler is a program which aims to reverse the process of a compiler, retrieving a source code of the high-level language Y from a source code of a low-level language X. 
+When Y is a high-level language and X is relatively a low-level language, 
 this reverse process becomes insufficient or impossible
@@
 
-By utilizing a corpus for source codes, a statistical method might have the potential for finding patterns automatically, without enumerating each patterns.
+By utilizing source codes corpus, a statistical method might find patterns automatically, without enumerating each patterns.
 Therefore, we tried to apply some statistical methods, which are described in the next section.
@@
 In this thesis, we try to apply statistical approach, specifically SMT (statistical machine translation) technique, for decompilation.
-SMT is the task which tries to translate one sentence $sx$ written in one language into the sentence $sy$ written in another language.
+SMT is the task which tries to translate one sentence $sy$ written in one language into the sentence $sx$ written in another language.
 
 The decompilation problem is formulated as follows. 
-Suppose that there is a compiler $ f $ which converts a source code $ sx $ written in a programming language 
-to a source code $ sy $  written in another programming language Y with probability $p(sy|sx)$.
-In addition, suppose that the human-generated source code $ sx $ follows the probability distribution $ p(sx) $.
-In this situation, the decompilation probability distribution $ p(sx|sy) $ in proportion to $ p(sy|sx)p(sx) $ according to the Bayesian low, 
-and the $\argmax_{sx} p(sx|sy)$ is considered as the best human-intelligible decompilation result for the code $sy$.
+Suppose that there is a compiler which converts a source code $ sy $ written in a programming language 
+to a source code $ sx $  written in another programming language with probability $p(sx|sy)$.
+In addition, suppose that $ sy $ is human-generated source code and follows the probability distribution $ p(sy) $.
+In this situation, the decompilation probability distribution $ p(sy|sx) $ is in proportion to $ p(sx|sy)p(sy) $ according to the Bayesian low, 
+and the $\argmax_{sy} p(sy|sx)$ is considered as the best human-intelligible decompilation result for $sx$.
 
-In the experiment, we collected source codes from open source projects as the random sampling from the distribution $ p(sx) $, 
+In the experiment, we collected source codes from open source projects as the random sampling from the distribution $ p(sy) $, 
 and compiled them to generate the data pairs $ {\{(sx_k,sy_k)\}}_k $.
-Then the data pairs are used for training the SMT models to estimate $p(sx|sy)$, and testing the performance of the models.
+Then the data pairs are used for training the SMT models to estimate $p(sy|sx)$, and testing the performance of the models.
 
@@
 The RNN (Recurrent Neural Network) is a neural network for dealing with sequence data.
-The structure of the RNN is the sequence of the same node units, as shown in figre~\ref{fig:encoder} and figre~\ref{fig:decoder}. 
-The LSTM (Long Short-Term Memory) is a unit of Recurrent Neural Network. 
+The structure of the RNN is the sequence of the same node network units, as shown in figre~\ref{fig:encoder} and figre~\ref{fig:decoder}. 
+The LSTM (Long Short-Term Memory) is a unit of the RNN which we used in the experiment. 
 It was first introduced by \citet{first_LSTM}, for overcoming the vanishing gradient problem and exploding gradient problem.
-In short, LSTM unit receives two input vectors, 
-the one is the internal state of the LSTM, and the other is the input for the LSTM unit, 
-and LSTM emits one output vectors, which represents the next internal state of the LSTM.
+In short, a LSTM unit receives two input vectors, 
+the one is the internal state of the LSTM unit, and the other is the input for the LSTM unit, 
+and the LSTM unit emits one output vectors, which represents the next internal state of the LSTM unit.
 
@@
 
-The sequence-to-sequence (sequence to sequence) model is the model for SMT task, introduced by \citet{seq2seq}.
+The sequence-to-sequence model is the model for SMT task, introduced by \citet{seq2seq}.
 % The combination of RNN and LSTM is applied to SMT task in, as the essential unit of the 
@@
 Figure~\ref{fig:encoder} shows the structure of the encoder network.
-The purpose of the encoder network is to summarize the input sequence $sx$, whose length varies depending on the sequence, into one fixed length vector.
+The purpose of the encoder network is to summarize the input sequence $sx$, whose length varies depending on the sequence $sx$, into one fixed size vector.
 This process is carried out as follows. 
@@
 % prepended the token $ EOS $ for indicating the end of the sequence, then 
-Then, the first internal state $ dec_{1}$ is calculated from the start vector $vy_{begin}$ and encoded input $ enc_{n} = dec_{0} $ in accordance with the formula  $ LSTM_{dec}(enc_{n},y_{begin}) $.
+Then, the first internal state $ dec_{1}$ is calculated from the start vector $vy_{begin}$ and encoded input $ enc_{n} = dec_{0} $ in accordance with the formula  $ dec_1 = lstm_{dec}(dec_{0},y_{begin}) $.
 Then, $ dec_{2} \dots dec_{m+1} $ are calculated in accordance with the recursive formula $ dec_{k+1} = lstm_{dec}(dec_{k},vy_{k}) $.
-Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_{dec} $ and then softmaxed to generate a probability vector $ py_{k} $.
-The probability vector $ py_{k} $ is intended to represent the probability distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
+Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_{dec} $ and then softmaxed to generate a probability vector $ py_{k} = softmax(W_{dec}(dec_{k}))$.
+The probability vector $ py_{k} $ is intended to represent the probability distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $,
+and last probability vector $ py_{m+1} $ is intended to represent the probability of the end of the sequence $ p(EOS|sx,[sy_1,\dots,sy_{m}]) $.
 Thus the network is trained to reduce the difference between predicted distribution $ py_{k} $ and actual distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
@@
 
-The inference for sequence $sx$ is carried out by calculating 
+The inference from sequence $sx$ is carried out by estimating
 $ \argmax_{sy} p(sy|sx) = \argmax_{sy} \prod_{k=1}^n p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
-Calculating argmax directly is time consuming, therefore we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_m]$ sequentially.
+Calculating argmax directly is exponentially time consuming, therefore we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_m]$ sequentially.
 First, $sy_1$ is calculated as $ \argmax_{sy_1} p(sy_1|sx,[]) $, where distribution $ p(sy_1|sx,[]) $ is approximated by 
@@
 
-First is the Bidirectional Recurrent Neural Networks (BRNN) is the architecture introduced by \citet{BiRNN}.
+First is the Bidirectional Recurrent Neural Networks (BRNN), which is the architecture introduced by \citet{BiRNN}.
 In our experiment, this architecture is used for the encoder network as follows.
@@
 in accordance with the recursive formula $ enc_{k}^{\gets} = lstm_{enc}^{\gets}(enc_{k+1}^{\gets},vx_{k}) $.
-Then both of the internal states $ enc_{n} $ and $ enc_{1}^{\gets} $ are used for decoder network.
+Then both of the internal states $ enc_{n} $ and $ enc_{0}^{\gets} $ are used for decoder network.
 
@@
 They reported that, feeding the output sequence of the LSTM network to another LSTM network, like stacking the network layers, will improve the accuracy of the prediction.
-This architecture is called as stacked recurrent neural networks or multi-layer recurrent neural networks.
+This architecture is called as the stacked recurrent neural networks or the multi-layer recurrent neural networks.
 
@@
 Attention is a extension module for sequence-to-sequence model to improve the quality of translation. 
-Simple sequence-to-sequence model has a problem that the length of the encoded vector $enc_{n}$ is fixed 
+A simple sequence-to-sequence model has a problem that the size of the encoded vector $enc_{n}$ is fixed 
 regardless of the length of the input sequence $sx$. 
@@
 
-As above mentioned, the pure sequence-to-sequence model uses the output of decoder network $ dec_{k} $ for estimating 
+As the mentioned in the previous section, the pure sequence-to-sequence model uses the output of the decoder network $ dec_{k} $ for estimating 
 the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
@@
 The context vector $ ctx_{k} $ is calculated as follows.
-For each state $ enc_{l} $, the importance of the state $ a_{l} $ is calculated as $ a_{l} = score(dec_{k},enc_{l}) $,
-then the $ ctx_{k} $ is calculated as $ ctx_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc{l} $, 
+For each encoder state $ enc_{l} $, the importance of the state is calculated as $ a_{l} = score(dec_{k},enc_{l}) $,
+then the $ ctx_{k} $ is calculated as $ ctx_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc_{l} $, 
 as the weighted average of $ enc_{1} \dots enc_{n} $.
 % Multiple score functions are introduced by \cite{dot_attention}, and we choiced 
-In the paper by \citet{dot_attention}, various kinds of score function is suggested.
-We used general score function, which is calculated as $ score(dec_{k},enc_{l}) = dec_{k}^T W enc_{l} $ ,
+In the paper by \citet{dot_attention}, various kinds of score function was suggested.
+In our experiment, we used general score function , which is calculated as $ score(dec_{k},enc_{l}) = dec_{k}^T W enc_{l} $ ,
 where W is the parameter matrix.
@@
 Therefore, it is reasonable to consider the grammar of the programming language when generating programs.
-Sequence-to-Tree is a model for generating tree-structured output from sequence input. 
-This model is introduced by \citet{Seq2Tree} for generating a program from a program specification written in the natural language. 
-This task is similar to our task, which aims to generate programs from the sequence of the assembly code, so we implemented this model in the experiment.
+Sequence-to-Tree is a model for generating a tree-structured output from a sequence input. 
+This model is introduced by \citet{Seq2Tree} for generating a program from a program specification written in a natural language. 
+This task is similar to our task which aims to generate programs from the assembly codes, which are a sequence of instructions.
+Therefore we implemented this model in the experiment.
 
-Now, we will describe about the sequence-2-tree model.
-sequence-to-tree model is composed of two modules, the encoder network and the decoder network.
-The encoder network of sequence-2-tree model is the same as the encoder network of sequence-to-tree model. It summarize the input sequence into one fixed length vector.
+Now, we will describe about the sequence-to-tree model.
+sequence-to-tree model is composed of two networks, the encoder network and the decoder network.
+The encoder network of the sequence-to-tree model is the same as that of the sequence-to-seequence model. It summarizes the input sequence into one fixed size vector.
 
@@
 	\begin{center}
-	\includegraphics[height=12cm]{ast_zu.png}
+	\includegraphics[height=11.5cm]{ast_zu.png}
 	\end{center}
@@
 The decoder network is a network for generating tree structured output. 
-A tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
+A tree structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
 For example, the tree shown in figure~\ref{fig:ast_zu} is generated from the sequence $ [act_1, \dots act_{12}] $, 
@@
 then the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(act_k|sx,[act_1, \dots act_{k-1}]) $. 
-The sequence-to-sequence model is now applicable for generating tree structure, by embeding each action to representing vector $av_k$ and 
+Thus the sequence-to-sequence model is now applicable for generating tree structure, by embeding each action $act_k$ to representing vector $av_k$ and 
 calculating $ lstm_{dec}(dec_{k},av_{k}) $ sequentially for estimating $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $.
@@
 
-In that paper, they additionally tries to use the information which is peculiar to the tree structure. 
-For expanding the node $d$, they also use the information of node type $ nf_{d} $ and the parent action $p_{d}$ from which $d$ is generated.
-Then they calculated $ lstm_{dec}(dec_{k},[av_{k}; nfv_{d}; pv_{d}]) $ instead of $ lstm_{dec}(dec_{k},av_{k}) $, 
+In the sequence-to-tree model, the information which is peculiar to the tree structure is additionaly used.
+For expanding node $d$, the information of the node type $ nf_{d} $ and the parent action $p_{d}$ from which node $d$ is generated are used.
+Then the next internal state is calculated as $ lstm_{dec}(dec_{k},[av_{k}; nfv_{d}; pv_{d}]) $ instead of $ lstm_{dec}(dec_{k},av_{k}) $, 
 where $nfv_{d},pv_{d}$ are the vector embedding of $nf_{d},p_{d}$.
 
-They also used devised method for generating terminal symbols, because they need to copy the name of some variables from the program specification.
-However, in our case, we do not need copy the information from the input, because the name information is lost when compiling.
-Nevertheless, it is found from the experiments that our decompilers often fail to recover the constant values in the programs.
-Therefore, implementing the copying method is left for future work.
+In the sequence-to-tree paper, they also used devised method for generating terminal symbols, because they need to copy the name of some variables from the program specification.
+However, in our case, we do not need to copy the information from the input, because the name information is lost when compiling.
+Nevertheless, it is found from the experiments that our models often fail to recover the constant values in the programs.
+Therefore, implementing the copying method for values is left for future work.
 
@@
 % 219 words
-We collected source codes by crawling GitHub \citep{github}, cloning about 900 repositories with C language topic, 
-and recursively searched each folder to enumerate C language source code.
-From each source code, we generated pairs of C source code fragment and x64 assembly code corresponds to the C fragment.
+We collected source codes from GitHub \citep{github} by crawling.
+We cloned about 900 repositories with the C language topic, 
+and recursively searched each repositoriy to enumerate C language source codes.
+From each source code, we generated pairs of a C source code fragment and a x64 assembly code corresponds to the C source code fragment.
 Some example data pairs are shown in figure~\ref{fig:pairsoffragments}.
@@
 
-The pairs were generated as follows. Let S0 be an original C source code.
+These pairs were generated as following steps. Let S0 be an original C source code.
 \begin{enumerate}
-\item Remove all preprocessor, such as \texttt{\#include}, in S0 to generate preprocessed C code S1. 
+\item Remove all preprocessors, such as \texttt{\#include}, in S0 to generate preprocessed C code S1. 
 \item Tokenize S1 and rearrange them in S2 so that there is exactly one token for each line. 
 \item 
-Compile S2 by the GNU C compiler with no optimization option (-O0) and debug option to get assembly code S3. 
-With debug option, S3 contains information about the source code position which each assembly operations are originated from.
+Compile S2 by the GNU C compiler with no optimization option (-O0) and debug option (-g) to get assembly code S3. 
+With debug option, S3 contains the information about the corresponding source code positions in S2. 
+% which each assembly operations are originated from.
 \item Assemble S3 to object file S4 and disassemble S4 to get information eliminated assembly code S5.
 \item 
-Parse S2 with clang to get AST of the source code. 
-And for each subtree of AST, we can get C fragment source code which corresponds to the subtree, 
-and we can get assembly code corresponds to the C fragment by employing S5 combine with S3.
+Parse S2 with a Clang compiler to get the AST of the source code and enumerate the subtrees of the AST.
+Each subtree of the AST has the correspoinding source code positions in S2.
+Therefore, we can get the pair of an assembly code and a C fragment corresponding to the subtree 
+by using the informations in S2,S3 and S5.
 \end{enumerate}
 
-The C fragment and assembly code pairs are preprocessed for the training and testing data.
+The pairs of a C fragment and an assembly code are then preprocessed for the training and the testing data.
 
@@
 % 34 words
-In order to apply LSTM, input and output for the LSTM must be the sequence of tokens. 
-So we have to preprocess the assembly data and C fragments to the token sequences by somehow.
+In order to apply the sequence-to-sequence model, 
+we have to preprocess the assembly codes and the C fragments into the sequences of tokens.
 
@@
 
-First way is the raw binary integers. The assemblies are finally assembled to the sequence of the one byte integers, ranged from 0 to 255.
-So the one byte integer sequences can be directly used for input sequences.
+The first way is converting into the sequence of integers. 
+The assembly code can be assembled into the sequence of the one byte integers, ranged from 0 to 255.
+Therefore the one byte integer sequences can be directly used as the input sequences for the sequence-to-sequence model.
 
-Second way is the tokenized sequence of assembly codes. 
-The disassembled opcodes and operands in S5 are split to symbols, and concatenated these sequences to one sequence, then we modified followings.
+The second way is converting into the tokenized sequence of assembly codes. 
+Splitting the disassembled instructions in S5 into the sequence of symbols, and concatenating these sequences to one sequence, then modifying followings.
 \begin{itemize}
-\item For each end of the operations, the \texttt{ENDLINE} symbol is added to indicate the end of operation.
+\item For each end of the instructions, the \texttt{ENDLINE} token is added to indicate the end of the instructions.
 \item 
-The relative access of code address, such as \texttt{call} or \texttt{jump} operations, 
-are relabeled like $\alpha$-conversion for making code position independent and for reducing the vocabulary size.
-\item The big integer values are substituted. 
-In detail, the integer in the range from -255 to 256 are preserved as it is, and the other integers are substituted with the \texttt{\_\_HEX\_\_} symbol.
+The relative addressing, such as the address of \texttt{call} or \texttt{jump} instructions, 
+are relabeled like $\alpha$-conversion for making the code into position independent and for reducing the vocabulary size.
+\item The big integer values are clipped. 
+In detail, the integer in the range from -255 to 256 are preserved as it is, and the other integers are clipped and substituted with the \texttt{\_\_HEX\_\_} symbol.
 This also reduces the vocabulary size.
@@
 We choosed second way for the experiment.
-This is because, in our case, the assembly code is generated from common C compiler, therefore the assembly code can be disassembled uniquely.
+This is because, in our case, the assembly code is generated from the GNU C compiler, which is common compiler.
+Therefore the assembly code can be disassembled uniquely.
 For example, \citet{disasm_obfuscate} proposed a obfuscation technique, which deceives the disassembler to generate wrong disassembly result.
@@
 For example, the \texttt{CompoundStatement} node has variable number of statements. 
-We converted such list of nodes to the chains of concatenation \texttt{CONS} and termination \texttt{NIL}, like a list representation in functional language.
+We converted such list of nodes to the chains of the node \texttt{CONS} and the node \texttt{NIL}, like the list representation in a functional language.
 Another example is the \texttt{if} statement, whose \texttt{else} clause are sometimes missing. 
-We converted such optional node to the alternative of \texttt{SOME} and \texttt{NONE}, like a optional data structure in functional language.
+We converted such optional nodes to the alternative of the \texttt{SOME} node and the \texttt{NONE} node, like the optional data structure in a functional language.
 \item The variable names, function names, label names, or type names were renamed like $\alpha$-conversion.
-\item There are four type of literals in C language. 
-The integer literal less than 256 is preserved, and the literal greater than 256 is clipped to 256.
+\item There are four type of literals in the C language. 
+An integer literal less than 256 is preserved, and an integer literal greater than 256 is clipped to 256.
 The string, float and character literals are converted to \texttt{\_\_LITERAL\_\_} symbol.
 
-Modifying the node to indicate the value in the assembly code corresponding to the literal is also conceivable way,
-but we did not implement this because of its technical difficulty, so this is left to future work.
+% Modifying the node to indicate the value in the assembly code corresponding to the literal is also conceivable way,
+% but we did not implement this because of its technical difficulty, so this is left to future work.
 \end{itemize}
 
-The AST is used for sequence-to-Tree model dataset as it is.
-Also, the AST is converted to C token sequence for sequence-to-sequence model dataset.
+ASTs is used for the sequence-to-tree model as it is, or converted to C token sequences for the sequence-to-sequence model.
 
@@
 The training model was implemented with Chainer version 4.5.0 \citep{chainer}.
-We implemented three models, Seq2seq, Seq2seqAtt, and Seq2tree.
+We implemented three models, Seq2Seq, Seq2SeqAtt, and Seq2Tree.
 
-The encoder module was bidirectional LSTM in all of three models.
-The decoder module of Seq2seq and Seq2seqAtt predict the conditional probability of a next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $,
-while the decoder module of Seq2tree predicts the conditional probability of a next action $ p(a_{k}|sx,[a_1, \dots a_{k-1}]) $.
+The encoder network was bidirectional LSTM in all of the three models.
+The decoder network of Seq2Seq and Seq2SeqAtt predict the conditional probability of a next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $,
+while the decoder network of Seq2Tree predicts the conditional probability of a next action $ p(act_{k}|sx,[act_1, \dots act_{k-1}]) $.
 
-Seq2seqAtt and Seq2tree are the models with attention, while Seq2seq is not.
+Seq2SeqAtt and Seq2Tree are the models with attention, while Seq2Seq is not.
 
@@
 		\hline
-		  & Seq2seq & Seq2seqAtt & Seq2tree \\ \hline \hline
+		  & Seq2Seq & Seq2SeqAtt & Seq2Tree \\ \hline \hline
 		 Generate & \multicolumn{2}{|c|}{token sequence} & AST \\ \hline
@@
 % 91 words
-We trained the model to reduce the cross-entropy loss between predicted and actual conditional probability.
+We trained these models to reduce the cross-entropy loss between predicted and actual conditional probability.
 The conditional probability is the probability of next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for sequence-to-sequence model, 
-and the probability of next action $p(a_{k+1}|sx,[a_1, \dots a_{k}]) $ for sequence-to-tree model.
+and the probability of next action $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $ for sequence-to-tree model.
 
@@
 \section{Model Evaluation}
-We evaluated the quality of the decompilation by two metrics, edit distance ratio and BLEU.
+We evaluated the quality of the results by two metrics, edit distance ratio and BLEU.
 
@@
 If the two sentences has similar n-gram sets, the BLEU score becomes higher.
-In our case, it means that the decompilation result is more similar to the program written by human, that is, more human intelligible.
+In our case, it means that the decompilation result is more similar to the program written by human. %, that is, more human intelligible.
 
@@
 
-In the experiment, we normalized variable names in the source codes by renaming. 
+Before calculating these scores, we normalized variable names in the source codes by renaming.
 % 補足として、今回は edit distance と BLEU を計算する際に、変数名を先頭から順に順番に付け直すことにより、ソースコード中の変数名の付けなおしを行っている。
@@
 \chapter{Evaluation}
-In this chapter, we show the evaluated result of the three models, Seq2seq, Seq2seqAtt, and Seq2tree.
+In this chapter, we show the evaluated result of the three models, Seq2Seq, Seq2SeqAtt, and Seq2Tree.
 % We trained each models with reedbush, を用い、各モデルについて4時間学習させた。
@@
 
-We can see that Seq2seqAtt shows slightly better results in both edit distance ratios and BLEU scores,
+We can see that Seq2SeqAtt shows slightly better results in both edit distance ratios and BLEU scores,
  which implies that the attention improves the performance of the decompilation.
-However, there are no significant difference between Seq2seq and Seq2tree in both metrics.
+However, there are no significant difference between Seq2Seq and Seq2Tree in both metrics.
 This seems to be due to the length of the sequences to be estimated.
@@
 The size of a AST is equals to the length of its action sequence.
-According to the two figures, the AST size is 2~3 times larger than the length of C token sequences.
-Therefore, the AST estimation may be harder than C token sequence estimation.
+According to these two figures, the AST size is 2 or 3 times larger than the length of C token sequences.
+Therefore, the AST estimation may be harder than the C token sequence estimation.
 
@@
 For the first short example, each of the models recovered that the C statement is composed of multiplication and assignment,
-while only Seq2Tree recovered the name of the variables, and Seq2Seq and Seq2SeqAtt were failed to recover.
+while only Seq2Tree recovered the name of the variables correctly, and Seq2Seq and Seq2SeqAtt were failed to recover.
 
-For the second middle example, Seq2Seq outputs source code with invalid parentheses, Seq2SeqAtt outputs invalid syntax (combination of while and else statement) code,
-while Seq2Tree outputs correct syntax but many wrong subexpressions.
+For the second middle example, Seq2Seq outputted source code with invalid parentheses, Seq2SeqAtt outputted invalid syntax code (combination of the \texttt{while} statement and the \texttt{else} statement).
+Seq2Tree outputted a correct syntax of code and estimated the \texttt{while} loop correctly, but failed to estimate subexpressions.
 
@@
 the action is truncated because the too long action sequence is estimated. 
-For long size function or statements, Seq2Tree tends to expand list type node to \texttt{CONS} node, which causes infinite expansion of sequence,
+For long size function or statements, Seq2Tree tends to expand list type node to \texttt{CONS} node, which causes infinite expansion of a list,
 and as a result, the type of the output function becomes broken and the body of the function becomes truncated.
@@
 First, each assembly instruction sequences are encoded by instruction encoding network into one instruction embedding vector, 
-so that the assembly codes turn into the sequences of embedding vectors.
+thus the assembly codes turn into the sequences of instruction embedding vectors.
 Then, the seqeuence of embedding vectors is encoded into one reduced vector by assembly code encoder network.
 
-This method will be time consuming compared to the method used in the experiment, however, this might be worth trying.
+This method will be time consuming compared to the method used in the experiment.
+Nevertheless, this might be worth trying.
 
@@
 The translation results show that the sequence-to-tree model have difficulty in recovering the leaf data of the program.
-Hence changing the method for expanding leaf node might improve the accuracy of decompilation.
+Threfore changing the method for expanding leaf node might improve the accuracy of decompilation.
 There are three kind of leaf data in the AST representation of a C source code.
@@
 For example, the operator $ + $ is compiled to the opcode \texttt{add}, the operator $ | $ is compiled to the opcode \texttt{or}, and so on. 
-Thus the type of operator might be estimated by indicating the correspond position in the assembly code.
+Thus the type of the operator might be estimated by indicating the correspond position in the assembly code.
 
@@
 
-To preserve the information of the tree structure, we suggest to train the network for estimating each root-to-leaf action sequences in the AST,
+In order to preserve the information of the tree structure, we suggest to train the decoder network for estimating each root-to-leaf action sequences in the AST,
 instead of the flattened action sequence. 
@@
 The AST can be recovered from these sequences instead of the whole sequence $ [act_1 \dots act_{10}] $, 
-and these sequences are independent of each other, when generating AST.
+and these sequences are independent of each other, when generating the AST.
 Therefore, we may estimate each of the sequences from the assembly token sequence by the sequence-to-sequence model.
@@
 We intended the models to learn the structure of long data from the short data, though the result shows that 
-the poor decompilation results are generated from the longer data.
+the poorer decompilation results are generated from the longer data.
 Therefore, the length distribution of the training data might effect on the training result, 
-thus we will need to seek effective distribution for the training.
+thus we will need to seek an effective distribution of the length for the training.
 

### 2019-01-31 texs/paper_base.tex
syoko
fix mathrepr

@@
 %-------------------
-\etitle{Neural Network based Decompiler for automatically recovering source codes from compiled binary data}
-\jtitle{ニューラルネットを用いた逆コンパイラに}
+\etitle{Neural Network based Decompiler and its Evaluation}
+\jtitle{ニューラルネットを用いた逆コンパイラとその評価}
 
@@
 \newcommand{\argmax}{\mathop{\rm arg\,max}\limits}
-\newcommand{\argmin}{\mathop{\rm arg\,smin}\limits}
+%\newcommand{\argmin}{\mathop{\rm arg\,smin}\limits}
 
@@
 
-In this chapter, we explain about the decompiler, its statistical formalization and 
+In this chapter, we explain a decompiler, its statistical formalization and 
 the neural network models used in the experiment.
@@
 % for instance X is the C language and Y is the x64 assembly language 
-This is because many information, such as variable names or function names, are lost when compiling.
+This is because a lot of information, such as variable names or function names, is lost when compiling.
 Additionally, the program structure described in the high level-language is lost too. 
-For example, a simple \texttt{for} statement can be represented by the combination of a \texttt{while} statement and an \texttt{if} statement, or the combination of \texttt{if} statement and \texttt{goto} statement.
+For example, a simple \texttt{for} statement can be represented by the combination of a \texttt{while} statement and an \texttt{if} statement, or the combination of an \texttt{if} statement and a \texttt{goto} statement.
 So a decompiler cannot distinguish the difference in their representations, 
-although in the real situation \texttt{for} statement are often used and \texttt{goto} statement are rarely used.
+although in the real situation \texttt{for} statements are often used and \texttt{goto} statements are rarely used.
 
@@
 It also failed to estimate the number of arguments and the return value of the function.
-The Snowman Decompiler succeeded to reconstruct the structure of the variable as \texttt{struct s0}.
-It also succeeded to estimate the number of arguments and the return value as the semantically correct expressions, 
-however the statement \texttt{return 0;} is reconstructed to the complex combination of statements.
+The Snowman Decompiler succeeded in reconstructing the structure of the variable as \texttt{struct s0}.
+It also succeeded in estimating the number of arguments and the return value as semantically correct expressions. 
+However the statement \texttt{return 0;} is reconstructed to a complex combination of statements.
 
@@
 In each step, a decompiler finds patterns in binary data, converts them to more high-level structure.
-However, covering all patterns might be hardly impossible, since there are many compilers and compiler optimizations \citep{hex_rays}.
+However, covering all patterns might be hardly possible, since there are many compilers and compiler optimizations \citep{hex_rays}.
 
-By utilizing source codes corpus, a statistical method might find patterns automatically, without enumerating each patterns.
-Therefore, we tried to apply some statistical methods, which are described in the next section.
+By utilizing source code corpora, a statistical method might find patterns automatically, without enumerating each pattern.
+Therefore, we will apply some statistical methods, which are described in the next section.
 
@@
 % 189
-In this thesis, we try to apply statistical approach, specifically SMT (statistical machine translation) technique, for decompilation.
-SMT is the task which tries to translate one sentence $sy$ written in one language into the sentence $sx$ written in another language.
+In this thesis, we try to apply a statistical approach, specifically a statistical machine translation (SMT) technique, for decompilation.
+SMT is the task which tries to translate one sentence $y$ written in one language into the sentence $x$ written in another language.
 
 The decompilation problem is formulated as follows. 
-Suppose that there is a compiler which converts a source code $ sy $ written in a programming language 
-to a source code $ sx $  written in another programming language with probability $p(sx|sy)$.
-In addition, suppose that $ sy $ is human-generated source code and follows the probability distribution $ p(sy) $.
-In this situation, the decompilation probability distribution $ p(sy|sx) $ is in proportion to $ p(sx|sy)p(sy) $ according to the Bayesian low, 
-and the $\argmax_{sy} p(sy|sx)$ is considered as the best human-intelligible decompilation result for $sx$.
+Suppose that there is a compiler which converts a source code $ y $ written in one programming language 
+to a source code $ x $  written in another programming language with probability $p(x|y)$.
+In addition, suppose that $ y $ is a human-generated source code and follows the probability distribution $ p(y) $.
+In this situation, the decompilation probability distribution $ p(y|x) $ is in proportion to $ p(x|y)p(y) $ according to the Bayes law, 
+and $\argmax_{y} p(y|x)$ is considered as the best human-intelligible decompilation result for $x$.
 
-In the experiment, we collected source codes from open source projects as the random sampling from the distribution $ p(sy) $, 
-and compiled them to generate the data pairs $ {\{(sx_k,sy_k)\}}_k $.
-Then the data pairs are used for training the SMT models to estimate $p(sy|sx)$, and testing the performance of the models.
+In the experiment, we collected source codes from open source projects, which are regarded as the random sampling from the distribution $ p(y) $, 
+and compiled them to generate the data pairs $ {\{(x_k,y_k)\}}_k $.
+Then the data pairs are used for training the SMT models to estimate $p(y|x)$, and testing the performance of the models.
 
-% Suppose that there is a compiler  Given $ sx $ as a source code of domain language X, compiler generates $sy$ as a code of target language Y with probability $p(sy|sx)$.
+% Suppose that there is a compiler  Given $ x $ as a source code of domain language X, compiler generates $y$ as a code of target language Y with probability $p(sy|x)$.
 
-% Given $sx = [sx_1, \dots, sx_n] $ as a tokenized sequence of the source code of domain language X, compiler generates $sy$ as a code of target language Y with probability $p(sy|sx)$.
-% Then, the best decompilation result for target source code $sy$ is $ \argmax_{sx} p(sx|sy)$. 
-% To generate $ \argmax_{sx} p(sx|sy)$, we decomposit $ p(sx|sy) = p([sx_1, \dots, sx_n] |sy) = \prod_{k=1}^{n} p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $,
-% where $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ represents the probability that the token $ sx_k $ follows to the sequence $ [sx_1,\dots,sx_{k-1}] $ 
+% Given $x = [x_1, \dots, x_n] $ as a tokenized sequence of the source code of domain language X, compiler generates $sy$ as a code of target language Y with probability $p(sy|x)$.
+% Then, the best decompilation result for target source code $sy$ is $ \argmax_{x} p(x|sy)$. 
+% To generate $ \argmax_{x} p(x|sy)$, we decomposit $ p(x|sy) = p([x_1, \dots, x_n] |sy) = \prod_{k=1}^{n} p(x_k|sy,[x_1,\dots,x_{k-1}]) $,
+% where $ p(x_k|sy,[x_1,\dots,x_{k-1}]) $ represents the probability that the token $ x_k $ follows to the sequence $ [x_1,\dots,x_{k-1}] $ 
 % when the input sequence is $ sy $. 
-% We try to estimate the probability $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ by LSTM, which is described in this section.
-% With estimated $ p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $, we can generate approximated $ \argmax_{sx} p(sx|sy)$ sequentially from $sx_1$ to $sx_n$ by selecting token $ \argmax_{sx_{k}} p(sx_k|sy,[sx_1,\dots,sx_{k-1}]) $ at each timing.
+% We try to estimate the probability $ p(x_k|sy,[x_1,\dots,x_{k-1}]) $ by LSTM, which is described in this section.
+% With estimated $ p(x_k|sy,[x_1,\dots,x_{k-1}]) $, we can generate approximated $ \argmax_{x} p(x|sy)$ sequentially from $x_1$ to $x_n$ by selecting token $ \argmax_{x_{k}} p(x_k|sy,[x_1,\dots,x_{k-1}]) $ at each timing.
 
 % The LSTM is 
-% We assume the prior distribution $p(sx)$ as the human-generated source code. 
-% With that assumption, is in proportion to $p(sy|sx)p(sx)$ according to the Bayesian low, and 
-% the $\argmax_{sx} p(sx|sy)$ is considered as the best human-intelligible decompilation result for the low-level code $sy$.  
-% So we try to estimate $ \argmax_{sx} p(sy|sx)p(sx)$ for decompilation result.
+% We assume the prior distribution $p(x)$ as the human-generated source code. 
+% With that assumption, is in proportion to $p(sy|x)p(x)$ according to the Bayesian low, and 
+% the $\argmax_{x} p(sx|y)$ is considered as the best human-intelligible decompilation result for the low-level code $y$.  
+% So we try to estimate $ \argmax_{sx} p(y|sx)p(sx)$ for decompilation result.
 % And if the compiler is deterministic, there would be a function $f$ which represents the compiler and $p(f(sx)|sx) = 1$,
-% then the objective becomes to $ \argmax_{sx,f(sx)=sy} p(sx)$.
+% then the objective becomes to $ \argmax_{sx,f(sx)=y} p(sx)$.
 % The distribution $p(sx)$ is approximated by collecting source code from open source projects.
@@
 \subsection{RNN and LSTM}
-The RNN (Recurrent Neural Network) is a neural network for dealing with sequence data.
-The structure of the RNN is the sequence of the same node network units, as shown in figre~\ref{fig:encoder} and figre~\ref{fig:decoder}. 
-The LSTM (Long Short-Term Memory) is a unit of the RNN which we used in the experiment. 
-It was first introduced by \citet{first_LSTM}, for overcoming the vanishing gradient problem and exploding gradient problem.
-In short, a LSTM unit receives two input vectors, 
-the one is the internal state of the LSTM unit, and the other is the input for the LSTM unit, 
-and the LSTM unit emits one output vectors, which represents the next internal state of the LSTM unit.
+A recurrent neural network (RNN) is a neural network for dealing with sequence data.
+The structure of the RNN is the sequence of the same node network units, as shown in Figre~\ref{fig:encoder} and Figre~\ref{fig:decoder}. 
+The long short-term memory (LSTM) is a unit of the RNN which we used in the experiment. 
+It was first introduced by \sloppy \citet{first_LSTM} , for overcoming the vanishing gradient problem and the exploding gradient problem.
+In short, an LSTM unit receives two input vectors, 
+one is the internal state of the LSTM unit, and the other is the input for the LSTM unit, 
+and the LSTM unit emits one output vector, which represents the next internal state of the LSTM unit.
 
@@
 % The combination of RNN and LSTM is applied to SMT task in, as the essential unit of the 
-Sequence-to-sequence model is composed of two recurrent neural networks, the encoder network and the decoder network.
+The sequence-to-sequence model is composed of two recurrent neural networks, the encoder network and the decoder network.
 
@@
 Figure~\ref{fig:encoder} shows the structure of the encoder network.
-The purpose of the encoder network is to summarize the input sequence $sx$, whose length varies depending on the sequence $sx$, into one fixed size vector.
+The purpose of the encoder network is to summarize the input sequence $x$, whose length varies depending on the sequence $x$, into a vector of fixed size.
 This process is carried out as follows. 
-First, $sx$ is tokenized to sequence $sx_{1} \dots sx_{n}$, and each token $sx_{k}$ is embedded to its vector representation $vx_{k}$. 
-Then, the initial LSTM internal state $enc_0$ is initialized randomly, 
-and $ enc_{1} \dots enc_{n} $ are calculated in accordance with the recursive formula $ enc_{k} = lstm_{enc}(enc_{k-1},vx_{k}) $.
-Finally, the last internal state $ enc_{n}$ is returned as the reduced representation of the input sequence $sx$.
+First, $x$ is tokenized to sequence $x_{1} \dots x_{n}$, and each token $x_{k}$ is embedded to its vector representation $\mathrm{vx}_{k}$. 
+Then, the initial LSTM internal state $\mathrm{enc}_0$ is initialized randomly, 
+and $ \mathrm{enc}_{1} \dots \mathrm{enc}_{n} $ are calculated in accordance with the recursive formula $ \mathrm{enc}_{k} = \mathrm{lstm}_{\mathrm{enc}}(\mathrm{enc}_{k-1},\mathrm{vx}_{k}) $.
+Finally, the last internal state $ \mathrm{enc}_{n}$ is returned as the reduced representation of the input sequence $x$.
 
-Figure~\ref{fig:decoder} shows the structure of the decoder network.  The purpose of the decoder network is to estimate the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for each k. 
+Figure~\ref{fig:decoder} shows the structure of the decoder network.  The purpose of the decoder network is to estimate the distribution $ p(y_k|x,[y_1,\dots,y_{k-1}]) $ for each $ k $. 
 The training process is carried out as follows. 
-First, $sy$ is tokenized, embedded to a vector representation $vy_{1} \dots vy_{m}$ in the same way as embedding $sx$.
+First, $y$ is tokenized, embedded to a vector representation $\mathrm{vy}_{1} \dots \mathrm{vy}_{m}$ in the same way as embedding $x$.
 % prepended the token $ EOS $ for indicating the end of the sequence, then 
-Then, the first internal state $ dec_{1}$ is calculated from the start vector $vy_{begin}$ and encoded input $ enc_{n} = dec_{0} $ in accordance with the formula  $ dec_1 = lstm_{dec}(dec_{0},y_{begin}) $.
-Then, $ dec_{2} \dots dec_{m+1} $ are calculated in accordance with the recursive formula $ dec_{k+1} = lstm_{dec}(dec_{k},vy_{k}) $.
-Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_{dec} $ and then softmaxed to generate a probability vector $ py_{k} = softmax(W_{dec}(dec_{k}))$.
-The probability vector $ py_{k} $ is intended to represent the probability distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $,
-and last probability vector $ py_{m+1} $ is intended to represent the probability of the end of the sequence $ p(EOS|sx,[sy_1,\dots,sy_{m}]) $.
-Thus the network is trained to reduce the difference between predicted distribution $ py_{k} $ and actual distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
-In the experiment, we choiced cross-entropy of $ py_{k} $ and $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for loss function.
+Then, the first internal state $ \mathrm{dec}_{1}$ is calculated from the start vector $\mathrm{vy}_{\mathrm{begin}}$ and encoded input $ \mathrm{enc}_{n} = \mathrm{dec}_{0} $ in accordance with the formula  $ \mathrm{dec}_1 = \mathrm{lstm}_{\mathrm{dec}}(\mathrm{dec}_{0},\mathrm{vy}_{\mathrm{begin}}) $.
+Then, $ \mathrm{dec}_{2} \dots \mathrm{dec}_{m+1} $ are calculated in accordance with the recursive formula $ \mathrm{dec}_{k+1} = \mathrm{lstm}_{\mathrm{dec}}(\mathrm{dec}_{k},\mathrm{vy}_{k}) $.
+Each decoder internal state $ \mathrm{dec}_{k} $ is passed to the linear layer $ W_{\mathrm{dec}} $ and then softmaxed to generate a probability vector $ \mathrm{py}_{k} = \mathrm{softmax}(W_{\mathrm{dec}}(\mathrm{dec}_{k}))$.
+The probability vector $ \mathrm{py}_{k} $ is intended to represent the probability distribution $ p(y_k|x,[y_1,\dots,y_{k-1}]) $,
+and last probability vector $ \mathrm{py}_{m+1} $ is intended to represent the probability of the end of the sequence $ p(\mathrm{EOS}|x,[y_1,\dots,y_{m}]) $.
+Thus the network is trained to reduce the difference between predicted distribution $ \mathrm{py}_{k} $ and actual distribution $ p(y_k|x,[y_1,\dots,y_{k-1}]) $.
+In the experiment, we chose cross-entropy of $ \mathrm{py}_{k} $ and $ p(y_k|x,[y_1,\dots,y_{k-1}]) $ as a loss function.
 
-The inference from sequence $sx$ is carried out by estimating
-$ \argmax_{sy} p(sy|sx) = \argmax_{sy} \prod_{k=1}^n p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
-Calculating argmax directly is exponentially time consuming, therefore we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_m]$ sequentially.
-First, $sy_1$ is calculated as $ \argmax_{sy_1} p(sy_1|sx,[]) $, where distribution $ p(sy_1|sx,[]) $ is approximated by 
-$ softmax(W_{dec}(dec_{1}))$. 
-Then, the next token $sy_2 = \argmax_{sy_1} p(sy_2|sx,[sy_2]) $ is calculated from $ dec_{1} $ and the vector embedding of $sy_1$, and so on.
-When the token $sy_{m+1}$ is the $ EOS $ token, generating process is stopped and the sequence $ [sy_1, \dots sy_m]$ is returned as the inference result.
+The inference from sequence $x$ is carried out by estimating
+$ \argmax_{y} p(y|x) = \argmax_{y} \prod_{k=1}^n p(y_k|x,[y_1,\dots,y_{k-1}]) $.
+Calculating argmax directly is exponentially time consuming, therefore we have to approximate the argmax by calculating $y = [y_1, \dots, y_m]$ sequentially.
+First, $y_1$ is calculated as $ \argmax_{y_1} p(y_1|x,[]) $, where the distribution $ p(y_1|x,[]) $ is approximated by 
+$ \mathrm{softmax}(W_{\mathrm{dec}}(\mathrm{dec}_{1}))$. 
+Then, the next token $y_2 = \argmax_{y_2} p(y_2|x,[y_1]) $ is calculated from $ \mathrm{dec}_{1} $ and the vector embedding of $y_1$, and so on.
+When the token $y_{m+1}$ is the EOS token, the generating process is stopped and the sequence $ [y_1, \dots ,y_m]$ is returned as an inference result.
 
@@
 
-First is the Bidirectional Recurrent Neural Networks (BRNN), which is the architecture introduced by \citet{BiRNN}.
+The first is the bidirectional RNN (BRNN), which is the architecture introduced by \citet{BiRNN}.
 In our experiment, this architecture is used for the encoder network as follows.
-In addition to the internal state $ enc_{k} $, the reverse internal state $ enc_{k}^{\gets} $ is also calculated 
-in accordance with the recursive formula $ enc_{k}^{\gets} = lstm_{enc}^{\gets}(enc_{k+1}^{\gets},vx_{k}) $.
-Then both of the internal states $ enc_{n} $ and $ enc_{0}^{\gets} $ are used for decoder network.
+In addition to the internal state $ \mathrm{enc}_{k} $, the reverse internal state $ \mathrm{enc}_{k}^{\gets} $ is also calculated 
+in accordance with the recursive formula $ \mathrm{enc}_{k}^{\gets} = \mathrm{lstm}_{\mathrm{enc}}^{\gets}(\mathrm{enc}_{k+1}^{\gets},\mathrm{vx}_{k}) $.
+Then both of the internal states $ \mathrm{enc}_{n} $ and $ \mathrm{enc}_{0}^{\gets} $ are used for the decoder network.
 
-Second is the multi-layer recurrent neural networks, introduced by \citet{multi_layer}.
-They reported that, feeding the output sequence of the LSTM network to another LSTM network, like stacking the network layers, will improve the accuracy of the prediction.
-This architecture is called as the stacked recurrent neural networks or the multi-layer recurrent neural networks.
+The second is the multi-layer RNN, introduced by \citet{multi_layer}.
+They reported that, feeding the output sequence of one LSTM network to another LSTM network, similarly to stacking the network layers, will improve the accuracy of prediction.
+This architecture is called the stacked RNN or the multi-layer RNN.
 
@@
 \subsection{Attention}
-Attention is a extension module for sequence-to-sequence model to improve the quality of translation. 
+Attention is an extension module for the sequence-to-sequence model to improve the quality of translation. 
 A simple sequence-to-sequence model has a problem that the size of the encoded vector $enc_{n}$ is fixed 
-regardless of the length of the input sequence $sx$. 
+regardless of the length of the input sequence $x$. 
 Therefore, the longer the length of the input becomes, the more likely the information of the input will be lost.
@@
 
-The attention module is first developed by \citet{attention_paper}.
-We implemented the global general attention, which is introduced by \citet{dot_attention}, for improving the quality of decompilation.
-In the following, we will describe about the global general attention.
+The attention module was first developed by \citet{attention_paper}.
+We implemented the global general attention, which was introduced by \citet{dot_attention}, for improving the quality of decompilation.
+In the following, we will describe the global general attention.
 
-As the mentioned in the previous section, the pure sequence-to-sequence model uses the output of the decoder network $ dec_{k} $ for estimating 
-the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
+As the mentioned in the previous section, the pure sequence-to-sequence model uses the output of the decoder network $ \mathrm{dec}_{k} $ for estimating 
+the distribution $ p(y_k|x,[y_1,\dots,y_{k-1}]) $.
 In the sequence-to-sequence model with attention, 
-a context vector $ ctx_{k} $ is calculalted from $ dec_{k} $ and the internal states of encoder network $ enc_{1} \dots enc_{n} $, 
-then the distribution is estimated from the output vector $ dec_{k} $ and context vector $ ctx_{k} $.
-The context vector $ ctx_{k} $ is calculated as follows.
-For each encoder state $ enc_{l} $, the importance of the state is calculated as $ a_{l} = score(dec_{k},enc_{l}) $,
-then the $ ctx_{k} $ is calculated as $ ctx_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc_{l} $, 
-as the weighted average of $ enc_{1} \dots enc_{n} $.
-% Multiple score functions are introduced by \cite{dot_attention}, and we choiced 
-In the paper by \citet{dot_attention}, various kinds of score function was suggested.
-In our experiment, we used general score function , which is calculated as $ score(dec_{k},enc_{l}) = dec_{k}^T W enc_{l} $ ,
-where W is the parameter matrix.
+a context vector $ \mathrm{ctx}_{k} $ is calculalted from $ \mathrm{dec}_{k} $ and the internal states of encoder networks $ \mathrm{enc}_{1} \dots \mathrm{enc}_{n} $, 
+then the distribution is estimated from the output vector $ \mathrm{dec}_{k} $ and context vector $ \mathrm{ctx}_{k} $.
+The context vector $ \mathrm{ctx}_{k} $ is calculated as follows.
+For each encoder state $ \mathrm{enc}_{l} $, the importance of the state is calculated as $ a_{l} = \mathrm{score}(\mathrm{dec}_{k},\mathrm{enc}_{l}) $,
+then $ \mathrm{ctx}_{k} $ is calculated as $ \mathrm{ctx}_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} \mathrm{enc}_{l} $, 
+as the weighted average of $ \mathrm{enc}_{1} \dots \mathrm{enc}_{n} $.
+% Multiple score functions are introduced by \citet{dot_attention}, and we choiced 
+In \citet{dot_attention}, various kinds of score functions were suggested.
+In our experiment, we used a general score function, which is calculated as $ \mathrm{score}(\mathrm{dec}_{k},\mathrm{enc}_{l}) = \mathrm{dec}_{k}^T W \mathrm{enc}_{l} $ ,
+where $ W $ is a parameter matrix.
 
-% With the information of the internal state $ ctx_{k} $ of the encoder network, the decoder network can access to the
+% With the information of the internal state $ \mathrm{ctx}_{k} $ of the encoder network, the decoder network can access to the
 
@@
 % $ dec_{k} $ と encoder network の出力 $ enc_{1} \dots enc_{n} $ (encoder が BiLSTMの場合 $ enc^{\gets}_{1} \dots enc^{\gets}_{n} $ も)
-% を用いて context vector $ ctx_{k} $ を生成し、 $ dec_{k} $ と $ ctx_{k} $ によって条件付き分布をesitmateする。
+% を用いて context vector $ \mathrm{ctx}_{k} $ を生成し、 $ dec_{k} $ と $ \mathrm{ctx}_{k} $ によって条件付き分布をesitmateする。
 
-% $ ctx_{k} $ は、 $ enc_{1} \dots enc_{n} $ の加重平均によって計算される。 具体的には、
+% $ \mathrm{ctx}_{k} $ は、 $ enc_{1} \dots enc_{n} $ の加重平均によって計算される。 具体的には、
 % 各状態 $ enc_{l} $ について その状態のスコア $ a_{l} = score(dec_{k},enc_{l}) $ を計算し、
-% $ ctx_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc{l} $ として計算される。
+% $ \mathrm{ctx}_{k} = \sum_{l=1}^{n} \frac{\exp{a_{l}}}{\sum_{l=1}^{n}\exp{a_{l}}} enc{l} $ として計算される。
 
-% この $ ctx_{k} $ を併せて用いることにより、 分布予測時に入力データの情報にアクセスすることができ、精度の向上が見込める。
+% この $ \mathrm{ctx}_{k} $ を併せて用いることにより、 分布予測時に入力データの情報にアクセスすることができ、精度の向上が見込める。
 
-% In the pure sequence-to-sequence model, the conditional probability  $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ is calculated from $ dec_{k} $ ,which is the internal state of the decoder network.
+% In the pure sequence-to-sequence model, the conditional probability  $ p(y_k|x,[y_1,\dots,y_{k-1}]) $ is calculated from $ dec_{k} $ ,which is the internal state of the decoder network.
 % In the sequence-to-sequence with attention model, the probability is calcutated from $ dec_{k} $ and the context vevctor $ c_{k} $.
@@
 % The attentional hidden state $ dec'_{k} $ is calculated from the $ dec_{k} $ and $ c_{k} $.
-% Then, the probability $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ is estimated as $ softmax(W_{dec}(dec'_{k}))$, instead of $ softmax(W_{dec}(dec_{k}))$.
+% Then, the probability $ p(y_k|x,[y_1,\dots,y_{k-1}]) $ is estimated as $ \mathrm{softmax}(W_{dec}(dec'_{k}))$, instead of $ \mathrm{softmax}(W_{dec}(dec_{k}))$.
 
@@
 % 184 words
-Compare to natural languages, programming languages obeys rigid grammars. % wich are usually context free grammers.
+Compared to natural languages, programming languages obey rigid grammars. % wich are usually context free grammers.
 Therefore, it is reasonable to consider the grammar of the programming language when generating programs.
-Sequence-to-Tree is a model for generating a tree-structured output from a sequence input. 
-This model is introduced by \citet{Seq2Tree} for generating a program from a program specification written in a natural language. 
-This task is similar to our task which aims to generate programs from the assembly codes, which are a sequence of instructions.
+Sequence-to-tree is a model for generating a tree-structured output from a sequence input. 
+This model was introduced by \citet{Seq2Tree} for generating a program from a program specification written in natural language. 
+This task is similar to our task which aims to generate programs from assembly codes, which are sequences of instructions.
 Therefore we implemented this model in the experiment.
 
-Now, we will describe about the sequence-to-tree model.
-sequence-to-tree model is composed of two networks, the encoder network and the decoder network.
-The encoder network of the sequence-to-tree model is the same as that of the sequence-to-seequence model. It summarizes the input sequence into one fixed size vector.
+Now, we will describe the sequence-to-tree model.
+The sequence-to-tree model is composed of two networks, the encoder network and the decoder network.
+The encoder network of the sequence-to-tree model is the same as that of the sequence-to-seequence model. 
+It summarizes an input sequence into a vector of fixed size.
 
@@
 	\end{center}
-	\caption{AST representation of a C statement \texttt{b = a + 3;} }
+	\caption{abstract syntax tree (AST) representation of a C statement \texttt{b = a + 3;} }
 	\label{fig:ast_zu}
@@
 The decoder network is a network for generating tree structured output. 
-A tree structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
-For example, the tree shown in figure~\ref{fig:ast_zu} is generated from the sequence $ [act_1, \dots act_{12}] $, 
-where action $ act_k $ expands the left-most nonterminal symbol in the tree generated from the action sequence $ [act_1, \dots act_{k-1}] $. 
-Suppose the tree $ty$ is generated by the action sequence $ [act_1, \dots act_m] $, 
-then the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(act_k|sx,[act_1, \dots act_{k-1}]) $. 
-Thus the sequence-to-sequence model is now applicable for generating tree structure, by embeding each action $act_k$ to representing vector $av_k$ and 
-calculating $ lstm_{dec}(dec_{k},av_{k}) $ sequentially for estimating $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $.
+A tree structure is representable by a sequence of the actions which expands a nonterminal symbol of the constructing tree.
+For example, the tree shown in Figure~\ref{fig:ast_zu} is generated from the sequence $ [\mathrm{act}_1, \dots, \mathrm{act}_{10}] $, 
+where action $ \mathrm{act}_k $ expands the left-most nonterminal symbol in the tree generated from the action sequence $ [\mathrm{act}_1, \dots, \mathrm{act}_{k-1}] $. 
+Suppose the tree $t$ is generated by the action sequence $ [\mathrm{act}_1, \dots, \mathrm{act}_m] $, 
+then the tree-generating probability $ p(t|x) $ is decomposed into $ \prod_{k=1}^n p(\mathrm{act}_k|x,[\mathrm{act}_1, \dots, \mathrm{act}_{k-1}]) $. 
+Thus the sequence-to-sequence model is now applicable to generating tree structure, by embeding each action $\mathrm{act}_k$ to represent vector $\mathrm{av}_k$ and 
+calculate $ \mathrm{lstm}_{\mathrm{dec}}(\mathrm{dec}_{k},\mathrm{av}_{k}) $ sequentially for estimating $p(\mathrm{act}_{k+1}|x,[\mathrm{act}_1, \dots, \mathrm{act}_{k}]) $.
 
@@
 In the sequence-to-tree model, the information which is peculiar to the tree structure is additionaly used.
-For expanding node $d$, the information of the node type $ nf_{d} $ and the parent action $p_{d}$ from which node $d$ is generated are used.
-Then the next internal state is calculated as $ lstm_{dec}(dec_{k},[av_{k}; nfv_{d}; pv_{d}]) $ instead of $ lstm_{dec}(dec_{k},av_{k}) $, 
-where $nfv_{d},pv_{d}$ are the vector embedding of $nf_{d},p_{d}$.
+For expanding node $d$, the information of the node type $ \mathrm{nf}_{d} $ and the parent action $\mathrm{pa}_{d}$ from which node $d$ is generated is used.
+Then the next internal state is calculated as $ \mathrm{lstm}_{\mathrm{dec}}(\mathrm{dec}_{k},[\mathrm{av}_{k}; \mathrm{nfv}_{d}; \mathrm{pav}_{d}]) $ instead of $ \mathrm{lstm}_{\mathrm{dec}}(\mathrm{dec}_{k},\mathrm{av}_{k}) $,
+where $\mathrm{nfv}_{d},\mathrm{pav}_{d}$ are the vector embeddings of $\mathrm{nf}_{d},\mathrm{pa}_{d}$.
 
-In the sequence-to-tree paper, they also used devised method for generating terminal symbols, because they need to copy the name of some variables from the program specification.
+In \citet{Seq2Tree}, they also used a devised method for generating terminal symbols, because they need to copy the name of some variables from the program specification.
 However, in our case, we do not need to copy the information from the input, because the name information is lost when compiling.
-Nevertheless, it is found from the experiments that our models often fail to recover the constant values in the programs.
-Therefore, implementing the copying method for values is left for future work.
+Nevertheless, it was found from our preliminary experiments that our models often fail to recover the constant values in the programs.
+Therefore, implementing the copying method for values is left as future work.
 
@@
 \chapter{Experiments}
-In this chapter, we explain the detail of the data preparation and implementation.
+In this chapter, we explain the details of data preparation and implementation.
 The implementation source codes are available at \url{https://github.com/satos---jp/neural_decompiler}.
@@
 and recursively searched each repositoriy to enumerate C language source codes.
-From each source code, we generated pairs of a C source code fragment and a x64 assembly code corresponds to the C source code fragment.
-Some example data pairs are shown in figure~\ref{fig:pairsoffragments}.
+From each source code, we generated pairs of a C source code fragment and an x64 assembly code corresponding to the C source code fragment.
+Some example data pairs are shown in Figure~\ref{fig:pairsoffragments}.
 
@@
 
-These pairs were generated as following steps. Let S0 be an original C source code.
+These pairs were generated as follows. Let S0 be an original C source code.
 \begin{enumerate}
 \item Remove all preprocessors, such as \texttt{\#include}, in S0 to generate preprocessed C code S1. 
-\item Tokenize S1 and rearrange them in S2 so that there is exactly one token for each line. 
+\item Tokenize S1 and rearrange into S2 so that there is exactly one token for each line. 
 \item 
 Compile S2 by the GNU C compiler with no optimization option (-O0) and debug option (-g) to get assembly code S3. 
-With debug option, S3 contains the information about the corresponding source code positions in S2. 
+With the debug option, S3 contains the information about the corresponding source code positions in S2. 
 % which each assembly operations are originated from.
@@
 \item 
-Parse S2 with a Clang compiler to get the AST of the source code and enumerate the subtrees of the AST.
+Parse S2 with a Clang compiler to get the abstract syntax tree (AST) of the source code and enumerate the subtrees of the AST.
 Each subtree of the AST has the correspoinding source code positions in S2.
-Therefore, we can get the pair of an assembly code and a C fragment corresponding to the subtree 
-by using the informations in S2,S3 and S5.
+Therefore, we can get a pair of an assembly code and a C fragment corresponding to the subtree 
+by using the informations in S2, S3 and S5.
 \end{enumerate}
@@
 
-The first way is converting into the sequence of integers. 
-The assembly code can be assembled into the sequence of the one byte integers, ranged from 0 to 255.
-Therefore the one byte integer sequences can be directly used as the input sequences for the sequence-to-sequence model.
+The first way is converting each code into the sequence of integers. 
+In order to execute as a program, an assembly code is assembled into the sequence of one-byte integers, ranging from 0 to 255.
+Therefore the one-byte integer sequences can be directly used as input sequences to the sequence-to-sequence model.
 
-The second way is converting into the tokenized sequence of assembly codes. 
-Splitting the disassembled instructions in S5 into the sequence of symbols, and concatenating these sequences to one sequence, then modifying followings.
+The second way is converting each code into the tokenized sequence of assembly codes. 
+That is, we split the disassembled instructions in S5 into the sequence of symbols, 
+concatenate these sequences to one sequence, 
+and modify it as follows:
 \begin{itemize}
@@
 \item 
-The relative addressing, such as the address of \texttt{call} or \texttt{jump} instructions, 
-are relabeled like $\alpha$-conversion for making the code into position independent and for reducing the vocabulary size.
-\item The big integer values are clipped. 
-In detail, the integer in the range from -255 to 256 are preserved as it is, and the other integers are clipped and substituted with the \texttt{\_\_HEX\_\_} symbol.
+The relative addressing, such as the address of the \texttt{call} or \texttt{jump} instructions, 
+is relabeled similarly to $\alpha$-conversion for making the code position independent and for reducing the vocabulary size.
+\item Big integer values are clipped. 
+More specifically, an integer in the range from -255 to 256 are preserved as it is, and other integers are clipped and substituted with the \texttt{\_\_HEX\_\_} symbol.
 This also reduces the vocabulary size.
@@
 
-We choosed second way for the experiment.
-This is because, in our case, the assembly code is generated from the GNU C compiler, which is common compiler.
+We chose the second way for the experiment.
+This is because, in our case, the assembly code is generated from the GNU C compiler, which is a common compiler.
 Therefore the assembly code can be disassembled uniquely.
-For example, \citet{disasm_obfuscate} proposed a obfuscation technique, which deceives the disassembler to generate wrong disassembly result.
+For example, \citet{disasm_obfuscate} proposed an obfuscation technique, which deceives a disassembler to generate wrong disassembly results.
 In that case, the first way might be better than the second way.
@@
 The C source codes were parsed to AST by a Clang compiler \citep{clang} and its Python bindings together with pycparser \citep{pycparser}, 
-because all of the tools are individually not sufficient for generating dataset.
-Then, the AST is converted to input data by following modifications.
+because all of the tools are individually not sufficient for generating a dataset.
+Then, the AST is converted to input data as follows:
 
 \begin{itemize}
-\item The variable-ary nodes and optional nodes are converted. 
-For example, the \texttt{CompoundStatement} node has variable number of statements. 
-We converted such list of nodes to the chains of the node \texttt{CONS} and the node \texttt{NIL}, like the list representation in a functional language.
-Another example is the \texttt{if} statement, whose \texttt{else} clause are sometimes missing. 
-We converted such optional nodes to the alternative of the \texttt{SOME} node and the \texttt{NONE} node, like the optional data structure in a functional language.
+\item The variable-ary nodes and optional nodes were converted. 
+For example, the \texttt{CompoundStatement} node has a variable number of statements. 
+We converted such a list of nodes to the chains of the node \texttt{CONS} and the node \texttt{NIL}, as the list representation in a functional language.
+Another example is the \texttt{if} statement, whose \texttt{else} clause is sometimes missing. 
+We converted such optional nodes to the alternative of the \texttt{SOME} node and the \texttt{NONE} node, as the optional data structure in a functional language.
 \item The variable names, function names, label names, or type names were renamed like $\alpha$-conversion.
 \item There are four type of literals in the C language. 
-An integer literal less than 256 is preserved, and an integer literal greater than 256 is clipped to 256.
-The string, float and character literals are converted to \texttt{\_\_LITERAL\_\_} symbol.
+An integer literal less than 256 was preserved, and an integer literal greater than 256 was clipped to 256.
+The string, float and character literals were converted to the \texttt{\_\_LITERAL\_\_} symbol.
 
@@
 
-ASTs is used for the sequence-to-tree model as it is, or converted to C token sequences for the sequence-to-sequence model.
+ASTs were used for the sequence-to-tree model as they were, or converted to C token sequences for the sequence-to-sequence model.
 
@@
 
-The encoder network was bidirectional LSTM in all of the three models.
-The decoder network of Seq2Seq and Seq2SeqAtt predict the conditional probability of a next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $,
-while the decoder network of Seq2Tree predicts the conditional probability of a next action $ p(act_{k}|sx,[act_1, \dots act_{k-1}]) $.
+The encoder network was a bidirectional LSTM in all of the three models.
+The decoder network of Seq2Seq and Seq2SeqAtt predict the conditional probability of the next token $ p(y_k|x,[y_1,\dots,y_{k-1}]) $,
+while the decoder network of Seq2Tree predicts the conditional probability of the next action $ p(\mathrm{act}_{k}|x,[\mathrm{act}_1, \dots, \mathrm{act}_{k-1}]) $.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
+	\caption{The configuration parameters of the models}
 	\begin{tabular}{|c||c|c|c|}
@@
 	\end{tabular}
-	\caption{The configuration parameters of the models}
 	\label{fig:parameterofmodels}
@@
 % 91 words
-We trained these models to reduce the cross-entropy loss between predicted and actual conditional probability.
-The conditional probability is the probability of next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for sequence-to-sequence model, 
-and the probability of next action $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $ for sequence-to-tree model.
+We trained these models to reduce the cross-entropy loss between predicted and actual conditional probabilities.
+The conditional probability is the probability of next token $ p(y_k|x,[y_1,\dots,y_{k-1}]) $ for the sequence-to-sequence model, 
+and the probability of next action $p(\mathrm{act}_{k+1}|x,[\mathrm{act}_1, \dots, \mathrm{act}_{k}]) $ for the sequence-to-tree model.
 
-For the optimizer of the training, we used Adam, which is introduced in \cite{Adam}.
-The parameters of Adam are $ (\alpha,\beta_1,\beta_2) = (0.001,0.9,0.999) $, which are the default parameters of Chainer version 4.5.0.
+For the optimizer of the training, we used Adam, which was introduced by \citet{Adam}.
+The parameters of Adam were set to $ (\alpha,\beta_1,\beta_2) = (0.001,0.9,0.999) $, which are the default parameters of Chainer version 4.5.0.
 % 学習の際のoptimizerにはAdam(文献)を用いた。
@@
 \section{Model Evaluation}
-We evaluated the quality of the results by two metrics, edit distance ratio and BLEU.
+We evaluated the quality of the results by two metrics, 
+the edit distance ratio and the bilingual evaluation understudy (BLEU) \citep{BLEU}.
 
-Edit distance ratio is the metrics for the correctness of the decompilation result.
-Here, the edit distance ratio between two strings means the Levenshtein distance divided by the average length of the two strings.
+The edit distance ratio is a metric for for the correctness of the decompilation result.
+Here, the edit distance ratio between two strings means the Levenshtein distance \citep{levensthein_dist} divided by the average length of the two strings.
 Ideally, the correctness of the decompilation result should be measured by the distance of the meaning of the program.
-However the decompilation result is usually uncompilable, so we used the edit distance of the source codes as the approximation of the correctness.
+However the decompilation result is usually uncompilable, 
+thus we used the edit distance of the source codes as an approximation of the correctness.
 
 BLEU is the metrics for the similarity of the ground truth and the decompilation result. 
-It is first introduced by \citet{BLEU}, for evaluating the performance of the machine translation.
-BLEU is calculated from the sets of the n-gram for each sentence. 
-If the two sentences has similar n-gram sets, the BLEU score becomes higher.
+It was first introduced by \citet{BLEU}, for evaluating the performance of machine translation.
+BLEU is calculated from the sets of n-grams for each sentence. 
+If the two sentences have similar n-gram sets, the BLEU score becomes higher.
 In our case, it means that the decompilation result is more similar to the program written by human. %, that is, more human intelligible.
@@
 \section{Numerical Evaluation}
-For evaluating each model, we randomly sampled 100 data pairs from test cases, generated estimated decompilation results for each test cases,
-then averaged the edit distance ratios and BLEU scores between results and ground truths.
+In order to evaluate each model, we randomly sampled 100 data pairs from test cases.
+For each test case, we generated decompilation results from the assembly code data of the test case.
+Then, we averaged the edit distance ratios and BLEU scores between results and ground truths.
 
@@
 % 図2は各モデルについて、学習に用いたデータ数と編集距離をプロットしたグラフである。
-Figure~\ref{fig:editdist} shows the relation of training data size and the averaged edit distance ratio for each models.
-Figure~\ref{fig:bleu} shows the relation of training data size and the averaged BLEU score for each models.
-The lower edit distance ratio and the higher BLEU score means the better decompilation performance.
+Figure~\ref{fig:editdist} shows the relation between the training data size and the averaged edit distance ratio for each model.
+Figure~\ref{fig:bleu} shows the relation between the training data size and the averaged BLEU score for each model.
+The lower edit distance ratio and the higher BLEU score mean better decompilation performance.
 
-We can see that Seq2SeqAtt shows slightly better results in both edit distance ratios and BLEU scores,
+We can see that Seq2SeqAtt shows slightly better results in both the edit distance ratios and BLEU scores,
  which implies that the attention improves the performance of the decompilation.
-However, there are no significant difference between Seq2Seq and Seq2Tree in both metrics.
+However, there is no significant difference between Seq2Seq and Seq2Tree in both metrics.
 This seems to be due to the length of the sequences to be estimated.
@@
 	\includegraphics[width=12cm]{c_lens.png}
-	\caption{Length distribution of C token flagments}
+	\caption{Length distribution of C token fragments}
 	\label{fig:csizes}
@@
 
-Figure~\ref{fig:csizes} shows the length distribution of the dataset as C token sequences
-, and figure~\ref{fig:astsizes} shows the size distribution of the same dataset as ASTs.
-The size of a AST is equals to the length of its action sequence.
+Figure~\ref{fig:csizes} shows the length distribution of the dataset as C token sequences, 
+and Figure~\ref{fig:astsizes} shows the size distribution of the same dataset as ASTs.
+The size of an AST is equal to the length of its action sequence.
 According to these two figures, the AST size is 2 or 3 times larger than the length of C token sequences.
@@
 	\end{tabular}
-	\caption{Smaple translation results for each model}
+	\caption{Sample translation results for each model}
 	\label{fig:sampletranse}
@@
 
-Figure~\ref{fig:sampletranse} shows sample translate results for each model.
+Figure~\ref{fig:sampletranse} shows the sample translate results for each model.
 
@@
 For the second middle example, Seq2Seq outputted source code with invalid parentheses, Seq2SeqAtt outputted invalid syntax code (combination of the \texttt{while} statement and the \texttt{else} statement).
-Seq2Tree outputted a correct syntax of code and estimated the \texttt{while} loop correctly, but failed to estimate subexpressions.
+Seq2Tree outputted a correct syntax of codes and estimated the \texttt{while} loop correctly, but failed to estimate subexpressions.
 
-For the third large example, all of the three models output a function with wrong body statement.
-The \texttt{INVALID\_FUNCTION\_DECL} in the result of Seq2Tree means it outputs wrong structured function type, and the \texttt{TRANCATE} means 
-the action is truncated because the too long action sequence is estimated. 
-For long size function or statements, Seq2Tree tends to expand list type node to \texttt{CONS} node, which causes infinite expansion of a list,
+For the third large example, all of the three models outputted a function with wrong body statements.
+The \texttt{INVALID\_FUNCTION\_DECL} in the result of Seq2Tree means it outputted a wrong structured function type, and the \texttt{TRANCATE} means 
+the action was truncated because the estimated action sequence was too long. 
+For long size functions or statements, Seq2Tree tends to expand the list type node to the \texttt{CONS} node, which causes infinite expansion of a list,
 and as a result, the type of the output function becomes broken and the body of the function becomes truncated.
 
-According to these decompilation results, it can be said that these models is not acceptable for practical use.
+According to these decompilation results, it can be said that these models are not acceptable for practical use.
 
@@
 For example, in the figure~\ref{fig:ast_zu}, there are four root-to-leaf action sequences, 
-$ [act_1, act_2] $, $ [act_1, act_3,act_4,act_5,act_6,act_7] $, $ [act_1, act_3,act_4,act_8] $ and $ [act_1, act_3,act_4,act_9,act_{10}] $.
-The AST can be recovered from these sequences instead of the whole sequence $ [act_1 \dots act_{10}] $, 
+$ [\mathrm{act}_1, \mathrm{act}_2] $, $ [\mathrm{act}_1, \mathrm{act}_3,\mathrm{act}_4,\mathrm{act}_5,\mathrm{act}_6,\mathrm{act}_7] $, $ [\mathrm{act}_1, \mathrm{act}_3,\mathrm{act}_4,\mathrm{act}_8] $ and $ [\mathrm{act}_1, \mathrm{act}_3,\mathrm{act}_4,\mathrm{act}_9,\mathrm{act}_{10}] $.
+The AST can be recovered from these sequences instead of the whole sequence $ [\mathrm{act}_1 \dots \mathrm{act}_{10}] $, 
 and these sequences are independent of each other, when generating the AST.

### 2019-01-31 texs/paper_base.tex
fix minis

@@
 %\usepackage{mysettings}% 自分用設定
+
+\pagenumbering{arabic}
+
 %-------------------
@@
 From the experiment, we can observe little improvement in the result of decompilation with the use of attention.
-Unfortunately, the results were not applicable for practical use.
+Unfortunately, the results were not still good enough for practical use.
 
@@
 \maketitle
+
+\chapter*{Acknowledgement}
+I thank Prof. Sugiyama and Lecture Sato for providing useful advice, supplying computational resources, helping me with writing this thesis and 
+correcting my English.
+I also thank A. Sano, who is my college classmate, for checking my English.
 
@@
 As the result of the experiment, the attention mechanism showed little improvement in the performance, while the sequence-to-tree does not.
-Unfortunately, the results of the all models seemed to be not applicable for practical use.
+Unfortunately, the results of the all models were not still good enough for practical use.
 The results of decompilation for short C source code fragment were not so bad. 
@@
 
-\chapter{Experiments}
-In this chapter, we explain the details of data preparation and implementation.
-The implementation source codes are available at \url{https://github.com/satos---jp/neural_decompiler}.
+\chapter{Evaluation Experiment}
+In this chapter, we explain the details of the evaluation experiment.
+% In this chapter, we show the evaluated result of the three models, Seq2Seq, Seq2SeqAtt, and Seq2Tree.
+The source codes for the experiment are available at \url{https://github.com/satos---jp/neural_decompiler}.
 
@@
 
-\section{Model Evaluation}
+\section{Evaluation Metrics}
 We evaluated the quality of the results by two metrics, 
@@
 
-\chapter{Evaluation}
-In this chapter, we show the evaluated result of the three models, Seq2Seq, Seq2SeqAtt, and Seq2Tree.
+% \chapter{Evaluation}
+% In this chapter, we show the evaluated result of the three models, Seq2Seq, Seq2SeqAtt, and Seq2Tree.
 % We trained each models with reedbush, を用い、各モデルについて4時間学習させた。
@@
 
-% According to the figure 1, the 
+% According to Figure 1, the 
 % 図1からわかるように、attention付きのネットワークとそうでないネットワークの間には有意に差が存在しているが、
@@
 
-\chapter{Future research}
-In this chapter, we suggest some other approaches to improve the accuracy of our decompilation models.
+\chapter{Conclusion and Future Work}
+\section{Conclusion}
+We tested three neural network models Seq2Seq, Seq2SeqAtt and Seq2Tree for decompilation.
+Numerically, Seq2SeqAtt performed better compared to the other two models,
+but all of the three models were not still good enough for practical use.
+Therefore, we will continue to develop a practical decompiler for the good future of malware analysis.
 
-\section{Improvement on Assembly Code Preprocessing}
+\section{Future Work}
+In this section, we suggest some other approaches to improve the accuracy of our decompilation models.
+
+\subsection{Improvement on Assembly Code Preprocessing}
 We used tokenized assembly string sequences for training. 
-However, such simple concatenation of sequences might lose the information of the unity of each instructions.
+However, such simple concatenation of sequences might lose the information of the unity of each instruction.
 To improve this point, we propose the following method.
@@
 This method uses two LSTM networks, the instruction encoder network and the assembly code encoder network, for encoding assembly token sequences.
-First, each assembly instruction sequences are encoded by instruction encoding network into one instruction embedding vector, 
+First, each assembly instruction sequence is encoded by the instruction encoding network into one instruction embedding vector, 
 thus the assembly codes turn into the sequences of instruction embedding vectors.
-Then, the seqeuence of embedding vectors is encoded into one reduced vector by assembly code encoder network.
+Then, the seqeuence of embedding vectors is encoded into one reduced vector by the assembly code encoder network.
 
@@
 
-\section{Improvement on Sequence-to-tree Model}
-We considered that the AST representation seems to exploit the feature of C source code. 
+\subsection{Improvement on Sequence-to-tree Model}
+We considered that the AST representation could exploit the feature of C source codes. 
 However, the sequence-to-tree model was not well performed.
 In this section, we seek to the improvement of the AST approach.
-\subsection{Copy Leaf Data from Assembler}
-The translation results show that the sequence-to-tree model have difficulty in recovering the leaf data of the program.
-Threfore changing the method for expanding leaf node might improve the accuracy of decompilation.
-There are three kind of leaf data in the AST representation of a C source code.
+\subsubsection{Copy Leaf Data from Assembler}
+The translation results show that the sequence-to-tree model has difficulty in recovering the leaf data of the program.
+Therefore changing the method for expanding leaf nodes might improve the accuracy of decompilation.
+There are three kinds of leaf data in the AST representation of a C source code.
 
@@
 In the assembly code, the string literal appears in the form of a memory address, and the other three literals appear in the form of an immediate value.
-Therefore, instead of estimating literal value directly, estimating the corresponding position in the assembly code might improve the correctness of decompilation.
+Therefore, instead of estimating the literal value directly, 
+estimating the corresponding position in the assembly code might improve the correctness of decompilation.
 
-The second kind is the type of operator. These can be also estimated from the assembly code.
+The second kind is the type of operators. They can be also estimated from the assembly code.
 For example, the operator $ + $ is compiled to the opcode \texttt{add}, the operator $ | $ is compiled to the opcode \texttt{or}, and so on. 
@@
 The third kind is the variable name. In the assembly code, a variable corresponds to a memory access. 
-Therefore, the name of a variable is identified by its corresponding memory position, similar to above two kinds.
+Therefore, the name of a variable is identified by its corresponding memory position, similarly to the above two kinds.
 
-\subsection{Path Estimation} 
+\subsubsection{Path Estimation} 
 In the sequence-to-tree model, a tree structure is flattened into an action sequence, 
 therefore the information of a tree structure might be lost in some degree.
-For example, the adjacent actions in the action sequence might be the distant actions in the AST, when they are in the different subtree of the AST.
+For example, adjacent actions in the action sequence might be distant actions in an AST, when they are in the different subtree of the AST.
 
-In order to preserve the information of the tree structure, we suggest to train the decoder network for estimating each root-to-leaf action sequences in the AST,
+In order to preserve the information of the tree structure, 
+we suggest to train the decoder network for estimating each root-to-leaf action sequence in the AST,
 instead of the flattened action sequence. 
-For example, in the figure~\ref{fig:ast_zu}, there are four root-to-leaf action sequences, 
+For example, in Figure~\ref{fig:ast_zu}, there are four root-to-leaf action sequences, 
 $ [\mathrm{act}_1, \mathrm{act}_2] $, $ [\mathrm{act}_1, \mathrm{act}_3,\mathrm{act}_4,\mathrm{act}_5,\mathrm{act}_6,\mathrm{act}_7] $, $ [\mathrm{act}_1, \mathrm{act}_3,\mathrm{act}_4,\mathrm{act}_8] $ and $ [\mathrm{act}_1, \mathrm{act}_3,\mathrm{act}_4,\mathrm{act}_9,\mathrm{act}_{10}] $.
@@
 
-This approach will ease the AST size problem, because the length of a root-to-leaf path is shorter than the size of whole AST, unless the AST has no branching.
+This approach will ease the problem of the AST size, because the length of a root-to-leaf path is shorter than the size of whole AST, unless the AST has no branching.
 
@@
 
-\section{Improvement of Dataset}
-As is seen in the figure~\ref{fig:csizes} and figure~\ref{fig:astsizes}, most of the data are short length C code.
+\subsection{Improvement on Datasets}
+As is seen in Figure~\ref{fig:csizes} and figure~\ref{fig:astsizes}, most of the data are short length C codes.
 This is due to our data generation method, which enumerates all of the subtree of a C source code.
-We intended the models to learn the structure of long data from the short data, though the result shows that 
-the poorer decompilation results are generated from the longer data.
-Therefore, the length distribution of the training data might effect on the training result, 
-thus we will need to seek an effective distribution of the length for the training.
+We intended the models to learn the structure of long data from the short data, though the result showed that 
+the poorer decompilation results were generated from the longer data.
+Therefore, the length distribution of the training data might affect the training result.
+To cope with this problem, we will need to seek an effective distribution of the length for training.
 
 % \section{For General Decompiler}
-
-\chapter{Conclusion}
-We tested three neural network models Seq2Seq, Seq2SeqAtt and Seq2Tree for decompilation.
-Numerically, Seq2SeqAtt performed better results compared to the other two models,
-but all of three models were not acceptable for practical use.
-Therefore, we will continue to develop practical decompiler for the good future of malware analysis.
-
-\chapter{Acknowledgement}
-I thank Prof. Sugiyama and Lecture Sato for providing useful advice, supplying computational resources, helping me with writing this thesis and 
-correcting my English.
-I also thank A. Sano, who is my college classmate, for checking my English.
 

### 2019-01-31 texs/paper_base.tex
toriaezu dasita

@@
 
-\date{December 11, 2018}
+\date{February 1, 2018}
 %-------------------
@@
 I also thank A. Sano, who is my college classmate, for checking my English.
+
+\tableofcontents
 
@@
 A recurrent neural network (RNN) is a neural network for dealing with sequence data.
-The structure of the RNN is the sequence of the same node network units, as shown in Figre~\ref{fig:encoder} and Figre~\ref{fig:decoder}. 
+The structure of the RNN is the sequence of the same node network units, as shown in Figure~\ref{fig:encoder} and Figure~\ref{fig:decoder}. 
 The long short-term memory (LSTM) is a unit of the RNN which we used in the experiment. 
@@
 	\begin{center}
-	\includegraphics[height=4cm]{encoder.png}
+	\includegraphics[height=3cm]{encoder.png}
 	\end{center}
@@
 	\begin{center}
-	\includegraphics[height=5.7cm]{decoder.png}
+	\includegraphics[height=4.2cm]{decoder.png}
 	\end{center}
@@
 In the sequence-to-sequence model with attention, 
-a context vector $ \mathrm{ctx}_{k} $ is calculalted from $ \mathrm{dec}_{k} $ and the internal states of encoder networks $ \mathrm{enc}_{1} \dots \mathrm{enc}_{n} $, 
+a context vector $ \mathrm{ctx}_{k} $ is calculated from $ \mathrm{dec}_{k} $ and the internal states of encoder networks $ \mathrm{enc}_{1} \dots \mathrm{enc}_{n} $, 
 then the distribution is estimated from the output vector $ \mathrm{dec}_{k} $ and context vector $ \mathrm{ctx}_{k} $.
@@
 % In the pure sequence-to-sequence model, the conditional probability  $ p(y_k|x,[y_1,\dots,y_{k-1}]) $ is calculated from $ dec_{k} $ ,which is the internal state of the decoder network.
-% In the sequence-to-sequence with attention model, the probability is calcutated from $ dec_{k} $ and the context vevctor $ c_{k} $.
+% In the sequence-to-sequence with attention model, the probability is calculated from $ dec_{k} $ and the context vevctor $ c_{k} $.
 % $ c_{k} $
@@
 then the tree-generating probability $ p(t|x) $ is decomposed into $ \prod_{k=1}^n p(\mathrm{act}_k|x,[\mathrm{act}_1, \dots, \mathrm{act}_{k-1}]) $. 
-Thus the sequence-to-sequence model is now applicable to generating tree structure, by embeding each action $\mathrm{act}_k$ to represent vector $\mathrm{av}_k$ and 
+Thus the sequence-to-sequence model is now applicable to generating tree structure, by embedding each action $\mathrm{act}_k$ to represent vector $\mathrm{av}_k$ and 
 calculate $ \mathrm{lstm}_{\mathrm{dec}}(\mathrm{dec}_{k},\mathrm{av}_{k}) $ sequentially for estimating $p(\mathrm{act}_{k+1}|x,[\mathrm{act}_1, \dots, \mathrm{act}_{k}]) $.
@@
 Parse S2 with a Clang compiler to get the abstract syntax tree (AST) of the source code and enumerate the subtrees of the AST.
-Each subtree of the AST has the correspoinding source code positions in S2.
+Each subtree of the AST has the corresponding source code positions in S2.
 Therefore, we can get a pair of an assembly code and a C fragment corresponding to the subtree 
@@
 
-\subsection{Assembly Code Preprocess}
+\subsection{Assembly Code Preprocessing}
 % 155 words
@@
 The relative addressing, such as the address of the \texttt{call} or \texttt{jump} instructions, 
-is relabeled similarly to $\alpha$-conversion for making the code position independent and for reducing the vocabulary size.
+is normalized by renaming so as to make the code position independent and to reduce the vocabulary size.
 \item Big integer values are clipped. 
@@
 
-\subsection{C Code Preprocess}
+\subsection{C Code Preprocessing}
 % 232 words
@@
 We converted such optional nodes to the alternative of the \texttt{SOME} node and the \texttt{NONE} node, as the optional data structure in a functional language.
-\item The variable names, function names, label names, or type names were renamed like $\alpha$-conversion.
+\item The variable names, function names, label names, or type names were renamed similarly to the addresses in the assembly code data.
 \item There are four type of literals in the C language. 
@@
 We evaluated the quality of the results by two metrics, 
-the edit distance ratio and the bilingual evaluation understudy (BLEU) \citep{BLEU}.
+the edit distance ratio \citep{Motoneta} and the bilingual evaluation understudy (BLEU) \citep{BLEU}.
 
 The edit distance ratio is a metric for for the correctness of the decompilation result.
-Here, the edit distance ratio between two strings means the Levenshtein distance \citep{levensthein_dist} divided by the average length of the two strings.
+Here, the edit distance ratio between two strings means the Levenshtein distance \citep{levensthein_dist} divided by the length of the longer string.
 Ideally, the correctness of the decompilation result should be measured by the distance of the meaning of the program.

### 2019-01-31 calc_precision.py

@@ -1,4 +1,4 @@
-import edit_distance
+#import edit_distance
 import pickle
 
 from nltk.translate import bleu_score
@@ -12,11 +12,36 @@ sys.setrecursionlimit(10000)
 with open('dataset_asm_csrc/vocab_csrc.pickle','rb') as fp:
 	c_vocab = pickle.load(fp)
 
+# verified by http://judge.u-aizu.ac.jp/onlinejudge/review.jsp?rid=3362979#1
+def my_edit_dist(s,t):
+	#print('call',s,t)
+	mem = {}
+	def dp(i,j):
+		nonlocal mem,s,t
+		if (i,j) in mem.keys():
+			return mem[(i,j)]
+		if i<0:
+			res = j+1
+		elif j<0:
+			res = i+1
+		else:
+			res = min(dp(i-1,j)+1,dp(i,j-1)+1,dp(i-1,j-1) + (0 if s[i]==t[j] else 1))
+		mem[(i,j)] = res
+		#print(i,j,s[:i+1],t[:j+1],res)
+		return res
+	 
+	return dp(len(s)-1,len(t)-1)
+
+
+def calc_edit_ratio(s,t):
+	#edit_distance.SequenceMatcher(s,t).ratio()
+	return my_edit_dist(s,t)/max(len(s),len(t))
 
 def calc_csrc(fn):
 	#print(fn)
 	with open(fn,'rb') as fp:
 		ds = pickle.load(fp)
+	ds = ds[:100]
 	def normalize_sentense(s):
 		s = list(map(lambda i: c_vocab[i],s))
 		ts = []
@@ -43,7 +68,7 @@ def calc_csrc(fn):
 		#print(' '.join(b))
 		#print(' '.join(c))
 		#print('-' * 100)
-		edit_ratio += 1.0 - edit_distance.SequenceMatcher(b,c).ratio()
+		edit_ratio += calc_edit_ratio(b,c)
 		bleu_ratio += bleu_score.sentence_bleu([b],c,smoothing_function=bleu_score.SmoothingFunction().method1)
 	edit_ratio /= len(ds)
 	bleu_ratio /= len(ds)
@@ -51,7 +76,7 @@ def calc_csrc(fn):
 	
 
 def calc_ast(fn):
-	print(fn)
+	#print(fn)
 	with open(fn,'rb') as fp:
 		ds = pickle.load(fp)
 	#print(len(ds))
@@ -80,10 +105,10 @@ def calc_ast(fn):
 	for a,b,c in ds:	
[…]

### 2019-01-31 plot_edit_bleus.py

@@ -1,4 +1,4 @@
-from plot_edit_bleus_data import seq2seq,seq2seq_att,seq2tree_flatten,seq2tree,seq2seq_1000
+from plot_edit_bleus_data import seq2seq,seq2seq_att,seq2tree_flatten,seq2tree
 from matplotlib import pyplot as plt
 
 
@@ -6,7 +6,6 @@ def lap(i,v):
 	return list(map(lambda x: x[i],v))
 
 seq2seq = seq2seq[:19]
-seq2seq_1000 = seq2seq_1000[:19]
 seq2seq_att = seq2seq_att[:19]
 
 def xlas(x):
@@ -26,7 +25,7 @@ for t in range(2):
 	plt.xlabel('training data size',fontsize=15)
 	plt.xticks([(i*1000.0/1024) for i in range(21)][::5],[xlas('%0.1e' % (100 * 1000 * i)) for i in range(21)][::5])
 	plt.ylabel(ys[t],fontsize=15)
-	plt.show()
-	continue
+	#plt.show()
+	#continue
 	plt.savefig('texs/' + sn[t])
 	plt.clf()

### 2019-01-31 plot_edit_bleus_data.py

@@ -1,185 +1,117 @@
 seq2seq = [
-(0.7728057079961657, 0.04327963218358302) ,
-(0.7246681619915292, 0.062413723861251186) ,
-(0.5622441691784281, 0.161543074209792) ,
-(0.5571608709968149, 0.1705308106393741) ,
-(0.4347882265993966, 0.28413845438199764) ,
-(0.4610206859752497, 0.24585704036163694) ,
-(0.5177618755723395, 0.22331856006117884) ,
-(0.49165962997321133, 0.23942462641940268) ,
-(0.5082117594904336, 0.2759228564709456) ,
-(0.4255664281281738, 0.26495207620395755) ,
-(0.48254992982344336, 0.2605896422632786) ,
-(0.4023770008151775, 0.31263203142764895) ,
-(0.4204470683659443, 0.3557809735522121) ,
-(0.3771533494449762, 0.3346509392217184) ,
-(0.30504572769339194, 0.39270079314539363) ,
-(0.41117802105158724, 0.3168229997637956) ,
-(0.43094457089536997, 0.30918082638808747) ,
-(0.37975157428357, 0.2919482888052986) ,
-(0.3417304436207085, 0.3814106415759484) ,
-(0.3508211751171558, 0.38963207011650974) ,
-(0.3642342658631444, 0.35457698641705315) ,
-(0.39202908248362145, 0.3246332266789198) ,
-(0.4263310293350607, 0.2897421798012639) ,
-(0.31538044904740714, 0.40787065162098485) ,
-(0.3384712574886655, 0.4026523467500745) ,
-(0.3070486087857907, 0.36694571459090547) ,
-(0.36899456345601594, 0.33899782228254355) ,
-(0.3902575576964328, 0.33209793574013086) ,
-(0.3131023086790649, 0.3700978335404176) ,
-(0.319628562688506, 0.3658422257829181) ,
-(0.3075334784381214, 0.36454832407013144) ,
-(0.3676624447779134, 0.33885767486306956) ,
-(0.38268304599886, 0.35779378713339827) ,
-(0.3514617211480929, 0.3634557064465532) ,
-(0.31664434018528576, 0.38185463910105577) ,
-(0.31488753366548605, 0.3845155067510481) ,
-(0.3622080438264711, 0.38717594447431913) ,
-(0.3665682394851486, 0.3497849543961857) ,
-(0.38051241922390544, 0.3684727852612876) ,
[…]

### 2020-05-26 texs/paper_base.tex
add broken pdf

@@
-\documentclass[senior,final,11pt]{iscs-thesis}
+% documentclass[senior,final,11pt]{iscs-thesis}
+\documentclass[11pt]{jarticle}
 %論文の種類とフォントサイズをオプションに
@@
 %-------------------
-\etitle{Neural Network based Decompiler and its Evaluation}
-\jtitle{ニューラルネットを用いた逆コンパイラとその評価}
+% \title{Neural Network based Decompiler and its Evaluation}
+\title{ニューラルネットを用いた逆コンパイラとその評価}
 
-__NAMES__
+% __NAMES__
 
@@
 \usepackage{caption}
+\usepackage{comment}
 
@@
 \begin{document}
+\begin{comment}
 \begin{eabstract}
@@
 \end{eabstract}
-\begin{jabstract}
+\end{comment}
+\begin{abstract}
 逆コンパイラはコンパイル後のバイナリデータからソースコードを復元するためのツールである。
@@
 実験の結果、注意機構を用いることににより逆コンパイル結果における若干の精度向上が認められたが、実用的な精度までは至らなかった。
-\end{jabstract}
+\end{abstract}
 
@@
 		\fbox{
-			\lstinputlisting[breaklines=false]{insert_list.c}
+			% \lstinputlisting[breaklines=false]{insert_list.c}
 			}
@@
 			\begin{framed}
-			\lstinputlisting[breaklines=false]{recstudio.c}
+			% \lstinputlisting[breaklines=false]{recstudio.c}
 			\end{framed}
